
\chapter{11}

Manon Blackbeak landed in Morath more than ready to start slitting throats. Everything had gone to shit.

Everything.

She'd ended that Yellowlegs bitch and her wyvern, saved the sapphire-eyed king, and watched the Fae Prince slaughter those four other Yellowlegs sentinels.

Five. Five Yellowlegs witches now lay dead, either by her hand or through her inaction. Five members of Iskra's coven.

In the end, she'd barely participated in Rifthold's destruction, leaving it to the others. But she'd again donned her crowned helm, then ordered Abraxos to sail to the highest spire of the stone castle and roar his victory---and command.

Even at the distant white walls of the city, ripping apart the guards and fleeing folk, the wyverns had paused at his order to stand down. Not one coven disobeyed.

The Thirteen had found her moments later. She didn't tell them what had happened, but both Sorrel and Asterin stared closely at her: the former to inspect for any cuts or wounds received during the "attack" Manon had claimed occurred, the latter because she had been with Manon that day they'd flown to Rifthold and painted a message to the Queen of Terrasen in Valg blood.

With the Thirteen perched on the castle towers, some draped along them like cats or serpents, Manon had waited for Iskra Yellowlegs.

As Manon now stalked down the dim, reeking halls of Morath, that crowned helm tucked into the crook of her arm, Asterin and Sorrel on her heels, she went over that conversation again.

Iskra had landed on the only space left: a lower bit of roofing below Manon. The positioning had been intentional.

Iskra's brown hair had come untangled from her tight braid, and her haughty face was splattered with human blood as she'd snarled at Manon, "\emph{This was my victory}."

Her face veiled in shadow beneath the helm, Manon had said, "The city is mine."

"Rifthold was \emph{mine} to take---you were only to oversee." A flash of iron teeth. On the spire to Manon's right, Asterin growled in warning. Iskra cast her dark eyes on the blond sentinel and snarled again. "Get your pack of bitches out of my city."

Manon sized up Fendir, Iskra's bull. "You've left your mark enough. Your work is noted."

Iskra trembled with rage. Not from the words.

The wind had shifted, blowing toward Iskra.

Blowing Manon's scent at her.

"Who?" Iskra seethed. \emph{"Who of mine did you butcher?"}

Manon had not yielded, had not allowed one flicker of regret or worry to shine through. "Why should I know any of your names? She attacked me as I closed in on my prey, wanting to get the king for herself and willing to strike an heir for it. She deserved her punishment. Especially because my prey slipped away while I dealt with her." \emph{Liar liar liar.}

Manon bared her iron teeth, the only bit of her face visible beneath that crowned helm. "Four others lie dead inside the castle---at the hand of the Fae Prince who came to rescue the king while \emph{I} dealt with your unruly bitch. Consider yourself lucky, Iskra Yellowlegs, that I do not take that loss out of your hide as well."

Iskra's tan face had gone pale. She surveyed Manon, all of the Thirteen assembled. Then she said, "Do what you want with the city. It's yours." A flash of a smile as she lifted her hand and pointed at Manon. The Thirteen tensed around her, arrows silently drawn and aimed at the Yellowlegs heir. "But \emph{you}, Wing Leader\ldots" That smile grew and she reined her wyvern, preparing to take to the skies. "You are a liar, \emph{Witch Killer}." Then she was gone.

Soaring not for the city, but the skies.

Within minutes, she'd vanished from sight---sailing toward Morath.

Toward Manon's grandmother.

Manon now glanced at Asterin, then at Sorrel, as they slowed to a stop before turning the corner that would lead to Erawan's council chamber. Where she knew Iskra, and her grandmother, and the other Matrons would be waiting. Indeed, a glance around the corner revealed the Thirds and Fourths of several covens on guard, eyeing one another as suspiciously as the blank-faced men posted beside the double doors.

Manon said to her Second and Third, "This will be messy."

Sorrel said quietly, "We'll deal with it."

Manon clenched the helmet a bit harder. "If it goes poorly, you are to take the

Thirteen and leave."

Asterin breathed, "You cannot go in there, Manon, accepting defeat. Deny it until your last breath." Whether Sorrel had realized Manon had killed that witch to save their enemy, she didn't let on. Asterin demanded, "Where would we even go?"

Manon said, "I don't know or care. But when I am dead, the Thirteen will be targeted by anyone with a score to settle." A very, very long list. She held her

Second's stare. "You get them out. At any cost."

They glanced at each other. Sorrel said, "We will do as you ask, Wing Leader."

Manon waited---waited for any objection from her Second, but Asterin's dark eyes were bright as she bowed her head and murmured her agreement.

A knot in Manon's chest loosened, and she rolled her shoulders once before turning away. But Asterin gripped her hand. "Be careful."

Manon debated snapping to not be a spineless fool, but  she'd seen what her grandmother was capable of. It was carved into Asterin's flesh.

She would not go into this looking guilty, looking like a liar. No---she'd make Iskra crawl by the end.

So Manon took a solid breath before she resumed her usual storming pace, red cape flapping behind her on a phantom wind.

Everyone stared as they approached. But that was to be expected.

Manon didn't deign to acknowledge the Thirds and Fourths assembled, though she took them in through her peripheral vision. Two young ones from

Iskra's coven. Six old ones, iron teeth flecked with rust, from the covens of the Matrons. And---

There were two other young sentinels in the hall, braided bands of dyed blue leather upon their brows.

Petrah Blueblood had come.

If the heirs and their Matrons were all assembled\ldots{} She did not have room for fear in her husk of a heart.

Manon flung open the doors, Asterin on her heels, Sorrel falling back to join the others in the hall.

Ten witches turned toward Manon as she entered. Erawan was nowhere in sight.

And though her grandmother was in the center of where they all stood in the room, her own Second against the stone wall behind Manon, lined up with the four other Seconds gathered, Manon's attention went to the golden-haired heir.

To Petrah.

She had not seen the Blueblood heir since the day of the War Games, when Manon had saved her life from a sure-kill fall. Saved her life, but was unable to save the life of Petrah's wyvern---whose throat had been ripped to shreds by Iskra's bull.

The Blueblood heir stood beside her mother, Cresseida, both of them tall and thin. A crown of iron stars sat upon the Matron's pale brow, the face below unreadable.

Unlike Petrah's. Caution---warning shone in her deep blue eyes. She wore her riding leathers, a cloak of midnight blue hanging from bronze clasps at her shoulders, her golden braid snaking over her chest. Petrah had always been odd, head in the clouds, but that was the way of the Bluebloods. \emph{Mystics}, \emph{fanatics}, \emph{zealots} were among the pleasanter terms used to describe them and their worship of the Three-Faced Goddess.

But there was a hollowness in Petrah's face that had not been there months ago. Rumor had claimed that losing her wyvern had broken the heir---that she had not gotten out of bed for weeks.

Witches did not mourn, because witches did not love enough to allow it to break them. Even if Asterin, now taking up her place by the Blackbeak Matron's Second, had proved otherwise.

Petrah nodded, a slight dip of the chin---more than a mere acknowledgment of an heir to an heir. Manon turned toward her grandmother before anyone could notice.

Her grandmother stood in her voluminous black robes, her dark hair plaited over the crown of her head. Like the crown her grandmother sought for them--- for her and Manon. \emph{High Queens of the Wastes}, she'd once promised Manon.

Even if it meant selling out every witch in this room.

Manon bowed to her grandmother, to the other two Matrons assembled.

Iskra snarled from beside the Yellowlegs Matron, an ancient, bent-backed crone with bits of flesh still in her teeth from lunch. Manon fixed the heir with a cool stare as she straightened.

"Three stand gathered," her grandmother began, and every bone in Manon's body went stiff. "Three Matrons, to honor the three faces of our Mother." Maiden, Mother, Crone. It was why the Yellowlegs Matron was always ancient, why the Blackbeak was always a witch in her prime, and why Cresseida, as the Blueblood Matron, still looked young and fresh.

But Manon did not care about that. Not when the words were being spoken.

"The Crone's Sickle hangs above us," Cresseida intoned. "Let it be the

Mother's blade of justice." This was not a meeting.

This was a trial.

Iskra began smiling.

As if a thread wove between them, Manon could feel Asterin straightening behind her, feel her Second readying for the worst.

"Blood calls for blood," the Yellowlegs crone rasped. "We shall decide how much is owed."

Manon kept still, not daring to show one inch of fear, of trepidation.

Witch trials were brutal, exact. Usually, problems were settled with the three blows to face, ribs, and stomach. Rarely, only in the gravest circumstances, did the three Matrons gather to mete out judgment.

Manon's grandmother said, "You stand accused, Manon Blackbeak, of cutting down a Yellowlegs sentinel with no provocation beyond your own pride."

Iskra's eyes positively burned.

"And, as the sentinel was a part of the Yellowlegs' heir's own coven, it is also a crime against Iskra." Her grandmother's face was tight with rage---not for what Manon had done, but for getting caught. "Through either your own neglect or ill-planning, the lives of four other coven members were ended. Their blood, too, stains your hands." Her grandmother's iron teeth shone in the candlelight. "Do you deny these charges?"

Manon kept her back straight, looked each of them in the eye. "I do not deny that I killed Iskra's sentinel when she tried to claim my rightful prize. I do not deny that the other four were slaughtered by the Fae Prince. But I do deny any wrongdoing on my part."

Iskra hissed. "You can smell Zelta's blood on her---smell the fear and
\emph{pain}."

Manon sneered, "You smell that, Yellowlegs, because your sentinel had a coward's heart and attacked another sister-in-arms. When she realized she would not win our fight, it was already too late for her."

Iskra's face contorted with fury. \emph{"Liar---"}

"Tell us, Blackbeak Heir," Cresseida said, "what happened in Rifthold three days past."

So Manon did.

And for the first time in her century of miserable existence, she lied to her elders. She wove a fine tapestry of falsehoods, \emph{believing}
the stories she told them. As she finished, she gestured to Iskra Yellowlegs. "It's common knowledge the Yellowlegs heir has long coveted my position. Perhaps she rushed back here to fling accusations at me so she might steal my place as Wing Leader, just as her sentinel tried to steal my prey."

Iskra bristled but kept her mouth shut. Petrah took a step forward, however, and spoke. "I have questions for the Blackbeak heir, if it would not be an impertinence."

Manon's grandmother looked like she'd rather have her own nails ripped out, but the other two nodded.

Manon straightened, bracing herself for whatever Petrah thought she was doing.

Petrah's blue eyes were calm as she met Manon's stare. "Would you consider me your enemy or rival?"

"I consider you an ally when the occasion demands it, but always a rival, yes." The first true thing Manon had said.

"And yet you saved me from sure death at the War Games. Why?" The other Matrons glanced at one another, faces unreadable.

Manon lifted her chin. "Because Keelie fought for you as she died. I would not allow her death to be wasted. I could offer a fellow warrior nothing less."

At the sound of her dead wyvern's name, pain flickered across Petrah's face.

"You remember her name?"

Manon knew it wasn't an intended question. But she nodded all the same.

Petrah faced the Matrons. "That day, Iskra Yellowlegs nearly killed me, and her bull slaughtered my mare."

"We have dealt with that," Iskra cut in, teeth flashing, "and dismissed it as accidental---"

Petrah held up a hand. "I am not finished, Iskra Yellowlegs."

Nothing but brutal steel in those words as she addressed the other heir. A small part of Manon was glad not to be on the receiving end of it.

Iskra saw the unfinished business that waited in that tone and backed down.

Petrah lowered her hand. "Manon Blackbeak had the chance to let me die that day. The easier choice would have been to let me die, and she would not be standing accused as she is now. But she risked her life, and the life of her mount, to spare me from death."

A life debt---that was what lay between them. Did Petrah think to fill it by speaking in her favor now? Manon reined in her sneer.

Petrah went on, "I do not comprehend why Manon Blackbeak would save me only to later turn on her Yellowlegs sisters. You crowned her Wing Leader for her obedience, discipline, and brutality---do not let the anger of Iskra Yellowlegs sully the qualities you saw in her then, and which still shine forth today. Do not lose your Wing Leader over a misunderstanding."

The Matrons again glanced among them as Petrah bowed, backing into her place at her mother's right. But the three witches continued that unspoken discussion waging between them. Until Manon's grandmother stepped forward, the other two falling back---yielding the decision to her. Manon almost sagged in relief.

She'd corner Petrah the next time the heir was foolish enough to be out alone, get her to admit why she'd spoken in Manon's favor.

Her grandmother's black-and-gold gaze was hard. Unforgiving.

"Petrah Blueblood has spoken true."

That tense, tight string between Manon and Asterin loosened, too.

"It would be a waste to lose our obedient, \emph{faithful} Wing Leader."

Manon had been beaten before. She could endure her grandmother's fists again.

"Why should the heir of the Blackbeak Witch-Clan yield her life for that of a mere sentinel? Wing Leader or not, it is still the word of heir against heir in this

matter. But the blood has still been shed. And blood must be paid."

Manon again gripped her helm. Her grandmother smiled a little.

"The blood shed must be equal," her grandmother intoned. Her attention flicked over Manon's shoulder. "So you, Granddaughter, will not die for this. But one of your Thirteen will."

For the first time in a long, long while, Manon knew what fear, what human helplessness, tasted like as her grandmother said, triumph lighting her ancient eyes, "Your Second, Asterin Blackbeak, shall pay the blood debt between our clans. She dies at sunrise tomorrow."
