
\chapter{12}

Without Evangeline slowing them down, Aelin, Aedion, and Lysandra traveled with little rest as they hauled ass for the coast.

Aelin remained in her Fae form to keep up with Aedion, who she begrudgingly admitted was by far the better rider, while Lysandra shifted in and out of various bird shapes to scout the land ahead for any danger.
Rowan had been instructing her on how to do it, what things to note and what to avoid or get a closer look at, while they'd been on the road these weeks.
But Lysandra found little to report from the skies, and Aelin and Aedion encountered few dangers on the ground as they crossed the valleys and plains of Terrasen's lowlands.

So little remained of the once-rich territory.

Aelin tried not to dwell on it too much---on the threadbare estates, the abandoned farms, the gaunt-faced people whenever they ventured into town, cloaked and disguised, for desperately needed supplies.
Though she had faced darkness and emerged full of light, a voice whispered in her head, \emph{You did this, you did this, you did this}.

That voice often sounded like Weylan Darrow's icy tones.

Aelin left gold pieces in her wake---tucked under a mug of watery tea offered to her and Aedion on a stormy morning; dropped in the bread box of a farmer who'd given them slices and a bit of meat for Lysandra in falcon form; slipped into the coin drawer of an innkeeper who had offered them a free extra bowl of stew upon seeing how swiftly they devoured their lunches.

But that gold didn't ease the cracking in her heart---that hideous voice that haunted her waking and dreaming thoughts.

By the time they reached the ancient port town of Ilium a week later, she'd stopped leaving gold behind.

It'd started to feel more like a bribe.
Not to her people, who had no inkling she'd been among them, but to her own conscience.

The green flatlands eventually yielded to rocky, arid coastline miles before the white-walled town rose between the thrashing turquoise sea and the broad mouth of the Florine River snaking inland, all the way to Orynth.
The town of Ilium was as ancient as Terrasen itself, and would likely have already been forgotten by traders and history were it not for the crumbling temple at the northeastern edge of the city, drawing enough pilgrims to keep it thriving.

The Temple of the Stone, it was called, had been built around the very rock where Brannon had first placed his foot upon the continent before sailing up the Florine to its source at the base of the Staghorns.
How the Little Folk had known how to render the temple for her, she had no idea.

Ilium's stout, sprawling temple had been erected on a pale cliff with commanding views of the storm-worn, pretty town behind it and the endless ocean beyond---so blue that it reminded Aelin of the tranquil waters of the South.

Waters where Rowan and Dorian should now be headed, if they were lucky.
Aelin tried not to dwell on that, either.
Without the Fae Prince at her side, there was a horrible, endless silence.

Almost as quiet as the white walls of the town---and the people inside.
Hooded and armed to the teeth beneath their heavy cloaks, Aelin and Aedion rode through the open gates, no more than two cautious pilgrims on their way to the temple.
Disguised for secrecy---and for the little fact that Ilium was now under Adarlanian occupation.

Lysandra had brought the news that morning after flying ahead, lingering in human form only long enough to inform them.

"We should have gone north to Eldrys," Aedion murmured as they rode past a cluster of hard-faced sentries in Adarlanian armor, the soldiers only glancing their way to note the sharp-eyed, sharper-beaked falcon perched on Aelin's shoulder.
None marked the shield hidden amongst Aedion's saddlebags, carefully veiled by the folds of his cloak.
Or the swords they'd both concealed as well.
Damaris remained where she'd stored it these weeks on the road: strapped beneath the heavy bags containing the ancient spellbooks she'd \emph{borrowed} from Dorian's royal library in Rifthold.
"We can still turn around."

Aelin shot him a glare beneath the shadows of her hood.
"If you think for one moment I'm leaving this city in Adarlan's hands, you can go to hell."
Lysandra clicked her beak in agreement.

The Little Folk had not been wrong to send the message to come here, their rendering of the temple near-perfect.
Through whatever magic they possessed, they had foreseen the news long before it ever reached Aelin on the road: Rifthold had indeed fallen, its king vanished and the city sacked by witches.
Emboldened by this, and by the rumor that \emph{she}
was not taking back her throne but rather running as well, the Lord of Meah, Roland Havilliard's father and one of the most powerful lords in Adarlan, had marched his garrison of troops just over the border into Terrasen.
And claimed this port for himself.

"Fifty soldiers are camped here," Aedion warned her and Lysandra.

The shifter only puffed out her feathers as if to say, \emph{So?}

His jaw clenched.
"Believe me, I want a piece of them, too.
But---"

"I am not hiding in my own kingdom," Aelin cut in.
"And I am not going to leave without sending a reminder of who this land belongs to."

Aedion kept quiet as they rounded a corner, aiming for the small seaside inn Lysandra had also scouted that morning.
On the other side of the city from the temple.

The temple the soldiers had the \emph{nerve} to use as their barracks.

"Is this about sending a message to Adarlan, or to Darrow?"
Aedion asked at last.

"It is about freeing my people, who have dealt with these Adarlanian pieces of shit for too long," Aelin snapped, reining her mare in to a halt before the inn courtyard.
Lysandra's talons dug into her shoulder in silent agreement.
Mere feet beyond the weatherworn courtyard wall, the sea gleamed sapphire-bright.
"We move at nightfall."

Aedion remained quiet, his face partially hidden as the inn's owner scuttled out and they secured a room for the night.
Aelin let her cousin brood a bit, wrangling her magic under control.
She hadn't released any of it this morning, wanting it to be at full force for what they were to do tonight, but the strain now tugged at her, an itch with no relief, an edge she could not dull.

Only when they were ensconced in their tiny, two-bed chamber, Lysandra perched on the windowsill, did Aedion say, "Aelin, you know I'll help---you know I want these bastards out of here.
But the people of Ilium have lived here for centuries, aware that in war, they are the first to be attacked."

And these soldiers could easily return as soon as they left, he didn't need to add.

Lysandra pecked the window---a quiet request.
Aelin strode over, shoved open the window to let the sea breeze flit in.
"Symbols have power, Aedion," she said, watching the shifter fan her speckled wings.
She'd read books and books on it during that ridiculous competition in Rifthold.

He snorted.
"I know.
Believe me---I've wielded them to my advantage as often as I can."
He patted the bone pommel of the Sword of Orynth for emphasis.
"Come to think of it, I said the same exact thing once to Dorian and Chaol."
He shook his head at the memory.

Aelin just leaned against the windowsill.
"Ilium used to be the stronghold of the Mycenians."

"The Mycenians are nothing more than a myth---they were banished three hundred years ago.
If you're looking for a symbol, they're fairly outdated---and divisive."

She knew that.
The Mycenians had once ruled Ilium not as nobility, but crime lords.
And during some long-ago war, their lethal fleet had been so crucial in winning that they'd been turned legitimate by whatever king ruled at the time.
Until they had been exiled centuries later for their refusal to come to Terrasen's aid in another war.

She met Lysandra's green-eyed stare as the shifter lowered her wings, sufficiently cooled.
She'd been distant on the road this week, preferring feathers or fur to skin.
Perhaps because some piece of her heart now rode for Orynth with Ren and Murtaugh.
Aelin stroked her friend's silken head.
"The Mycenians abandoned Terrasen so they would not die in a war they did not believe in."

"And they disbanded and vanished soon after that, never to be seen again," Aedion countered.
"What's your point?
You think liberating Ilium will summon them again?
They're long gone, Aelin, their sea dragons with them."

Indeed, there was no sign anywhere in this city of the legendary fleet and warriors who had sailed to wars across distant, violent seas, who had defended these borders with their own blood spilled upon the waves beyond the windows.
And the blood of their sea dragons, both allies and weapons.
Only when the last of the dragons had died, heartsick to be banished from Terrasen's waters, had the Mycenians truly been lost.
And only when the sea dragons returned would the Mycenians, too, come home.
Or so their ancient prophecies claimed.

Aedion began removing the extra blades hidden in their saddlebags, save for Damaris, and strapped them on, one by one.
He double-checked that Rowan's knife was securely buckled at his side before he said to Aelin and Lysandra, still by the window, "I know you two are of the opinion that we males are here to provide you with a pretty view and meals, but I \emph{am} a general of Terrasen.
We need to find a real army---not spend our time chasing ghosts.
If we don't get a host to the North by mid-fall, the winter storms will keep it away by land and sea."

"If you're so versed in symbols wielding such power, Aedion," she said, "then you know why Ilium is vital.
We can't allow Adarlan to hold it.
For a dozen reasons."
She was certain her cousin had already calculated all of them.
"So take back the town," Aedion challenged.
"But we need to sail by dawn."
Her cousin's eyes narrowed.
"The temple.
It's also that they took the temple, isn't it?"

"That temple is my birthright," Aelin said.
"I cannot allow that insult to go unchecked."
She rolled her shoulders.
Revealing her plans, explaining herself\ldots It would take some getting used to.
But she'd promised she'd try to be more\ldots open about her plotting.
And for this matter, at least, she could be.
"Both for Adarlan and for Darrow.
Not if I am to one day reclaim my throne."

Aedion considered.
Then snorted, a hint of a smile on his face.
"An undisputed queen of not just blood, but also of legends."
His face remained contemplative.
"You would be the undisputed queen if you got the kingsflame to bloom again."

"Too bad Lysandra can only shift herself and not things," Aelin muttered.
Lysandra clicked her beak in agreement, puffing her feathers.

"They say the kingsflame bloomed once during Orlon's reign," Aedion mused.
"Just one blossom, found in Oakwald."

"I know," Aelin said quietly.
"He kept it pressed within glass on his desk."
She still remembered that small red-and-orange flower, so simple in its make, but so vibrant it had always snatched her breath away.
It had bloomed in fields and across mountains throughout the kingdom the day Brannon set foot on this continent.
And for centuries afterward, if a solitary blossom was ever found, the current sovereign was deemed blessed, the kingdom truly at peace.

Before the flower was found in Orlon's second decade of kingship, the last one had been spotted ninety-five years earlier.
Aelin swallowed hard.
"Did Adarlan---"

"Darrow has it," Aedion said.
"It was the only thing of Orlon's he managed to grab before the soldiers took the palace."

Aelin nodded, her magic flickering in answer.
Even the Sword of Orynth had fallen into Adarlan's hands---until Aedion had won it back.
Yes, her cousin understood perhaps more than anyone else the power a single symbol could wield.
How the loss or reclaiming of one could shatter or rally an army, a people.
Enough---it was \emph{enough} destruction and pain inflicted on her kingdom.

"Come on," she said to Lysandra and Aedion, heading for the door.
"We'd better eat before we raise hell."
