
\chapter{13}

It had been a long while since Dorian had seen so many stars.

Far behind them, smoke still stained the sky, the plumes illuminated by the crescent moon overhead. At least the screams had faded miles ago. Along with the thump of mighty wings.

Seated behind him in the one-masted skiff, Prince Rowan Whitethorn gazed over the calm black expanse of the sea. They'd sail south, pushed by the prince's own magic, to the Dead Islands. The Fae warrior had gotten them quickly to the coast, where he'd had no qualms about stealing this boat while its owner was focused on the panicking city to the west. And all the while, Dorian had been silent, useless. As he had been while his city was destroyed, his people murdered.

"You should eat," Rowan said from the other end of the small boat.

Dorian glanced toward the sack of supplies Rowan had also stolen. Bread, cheese, apples, dried fish  Dorian's stomach turned.

"You were impaled by a poisoned barb," Rowan said, his voice no louder than the waves lapping against their boat as the swift wind pushed them from behind. "Your magic was drained keeping you alive and walking. You need to eat, or else it won't replenish." A pause. "Didn't Aelin warn you about that?"

Dorian swallowed. "No. She didn't really have the time to teach me about magic." He looked toward the back of the boat, where Rowan sat with a hand braced on the rudder. The sight of those pointed ears was still a shock, even months after meeting the male. And that silver hair---

Not like Manon's hair, which was the pure white of moonlight on snow.

He wondered what had become of the Wing Leader---who had killed for him, spared him.

Not spared him. Rescued him.

He wasn't a fool. He knew she'd done it for whatever reasons were useful to her. She was as alien to him as the warrior sitting at the other end of the boat--- more so.

And yet, that darkness, that violence and stark, honest way of looking at the world  There would be no secrets with her. No lies.

"You need to eat to keep up your strength," Rowan went on. "Your magic feeds on your energy---feeds on \emph{you}. The more rested you are, the greater the strength. More important, the greater the control. Your power is both part of you and its own entity. If left to its own devices, it will consume you, wield \emph{you} like a tool." A flash of teeth as Rowan smiled. "A certain person we know likes to siphon off her power, use it on frivolous things to keep its edge dull." Dorian could feel Rowan's stare pin him like a physical blow. "The choice is yours how much you allow it into your life, how to use it---but go any longer without mastering it, Majesty, and it will destroy you." A chill went down Dorian's spine.

And maybe it was the open ocean, or the endless stars above them, but Dorian said, "It wasn't enough. That day  that day Sorscha died, it wasn't enough to save her." He spread his hands on his lap. "It only wishes to destroy."

Silence fell, long enough that Dorian wondered if Rowan had fallen asleep. He hadn't dared ask when the prince himself had last slept; he'd certainly eaten enough for a starved man.

"I was not there to save my mate when she was murdered, either," Rowan said at last.

Dorian straightened. Aelin had told him plenty of the prince's history, but not this. He supposed it wasn't her secret, her sorrow to share. "I'm sorry," Dorian said.

His magic had felt the bond between Aelin and Rowan---the bond that went deeper than blood, than their magic, and he'd assumed it was just that they were mates, and hadn't announced it to anyone. But if Rowan already had a mate, and had lost her\ldots{}

Rowan said, "You're going to hate the world, Dorian. You are going to hate yourself. You will hate your magic, and you will hate any moment of peace or happiness. But I had the luxury of a kingdom at peace and no one depending upon me. You do not."

Rowan shifted the rudder, adjusting their course farther out to sea as the coastline jutted to meet them, a rising wall of steep cliffs. He'd known they were traveling swiftly, but they had to be almost halfway to the southern border---and traveling far faster than he'd realized under the cover of darkness.

Dorian said at last, "I am the sovereign of a broken kingdom. My people do not know who rules them. And now that I am fleeing\ldots" He shook his head, exhaustion gnawing on his bones. "Have I yielded my kingdom to Erawan?

What---what do I even \emph{do} from here?"

The ship's creaking and the rush of water were the only sounds. "Your people will have learned by now that you were not among the dead. It is upon you to tell them how to interpret it---if they are to see you as abandoning them, or if they are to see you as a man who is leaving to find help---to save them. You must make that clear."

"By going to the Dead Islands."

A nod. "Aelin, unsurprisingly, has a fraught history with the Pirate Lord. You don't. It's in your best interest to make him see you as an advantageous ally. Aedion told me the Dead Islands were once overrun by General Narrok and several of Erawan's forces. Rolfe and his fleet fled---and though Rolfe is now once more ruler of Skull's Bay, that disgrace might be your way in with him. Convince him you are not your father's son---and that you'll grant Rolfe and his pirates privileges."

"You mean turn them into privateers."

"You have gold, we have gold. If promising Rolfe money and free rein to loot Erawan's ships will secure us an armada in the South, we'd be fools to shy from it."

Dorian considered the prince's words. "I've never met a pirate."

"You met Aelin when she was still pretending to be Celaena," Rowan said drily. "I can promise you Rolfe won't be much worse."

"That's not reassuring."

A huffed laugh. Silence fell between them again. At last, Rowan said, "I'm sorry---about Sorscha."

Dorian shrugged, and hated himself for the gesture, as if it diminished what Sorscha had meant, how brave she'd been---how special. "You know," he said, "sometimes I wish Chaol were here---to help me. And then sometimes I'm glad he's not, so he wouldn't be at risk again. I'm glad he's in Antica with Nesryn." He studied the prince, the lethal lines of his body, the predatory stillness with which he sat, even as he manned their boat. "Could you---could you teach me about magic? Not everything, I mean, but  what you can, whenever we can."

Rowan considered for a moment, and then said, "I have known many kings in my life, Dorian Havilliard. And it was a rare man indeed who asked for help when he needed it, who would put aside pride."

Dorian was fairly certain his pride had been shredded under the claws of the Valg prince.

"I'll teach you as much as I can before we arrive in Skull's Bay," Rowan said. "We may find someone there who escaped the butchers---someone to instruct you more than I can."

"You taught Aelin."

Again, silence. Then, "Aelin is my heart. I taught her what I knew, and it worked because our magics understood each other deep down---just as our souls did. You are  different. Your magic is something I have rarely encountered. You need someone who grasps it, or at least how to train you in it. But I can teach you control; I can teach you about spiraling down into your power, and taking care of yourself."

Dorian nodded his thanks. "The first time you met Aelin, did you know
 ?"

A snort. "No. Gods, no. We wanted to kill each other." The amusement flickered. "She was  in a very dark place. We both were. But we led each other out of it. Found a way---together."

For a heartbeat, Dorian could only stare. As if reading his mind, Rowan said, "You will find your way, too, Dorian. You'll find your way out."

He didn't have the right words to convey what was in his heart, so he sighed up at the starry, endless sky. "To Skull's Bay, then."

Rowan's smile was a slash of white in the darkness. "To Skull's Bay."
