
\chapter{16}

The overseer spoke, but the voice was not his. And the voice was not Perrington's.

It was a new voice, an old voice, a voice from a different world and lifetime, a voice that fed on screams and blood and pain. Her magic thrashed against the sound, and even Aedion swore softly, still trying to herd her behind him.

But Aelin stood fast against the darkness peering at them from the man's cracked chest. And she knew that even if his body hadn't been irreparably broken, there was nothing left inside him to save anyway. Nothing worth saving to begin with.

She flexed her fingers at her sides, rallying her magic against the darkness that coiled and swirled inside the man's shattered chest.

Erawan said, "I would think gratitude is in order, Heir of Brannon."

She flicked her brows up, tasting smoke in her mouth. \emph{Easy}, she murmured to her magic. Careful---she'd have to be so careful he did not see the amulet around her neck, sense the presence of the final Wyrdkey inside. With the first two already in his possession, if Erawan suspected that the third key was in this temple, and that his utter dominance over this land and all others was close enough to grab
 She had to keep him distracted.

So Aelin snorted. "Why should I thank you, exactly?"

The embers of eyes slid upward, as if surveying the hollow body of the overseer. "For this small warning present. For ridding the world of one more bit of vermin."

\emph{And for making you realize how fruitless standing against me will be}, that voice whispered right into her skull.

She slammed fire outward in a blind maneuver, stumbling back into Aedion at the caress in that hideous, beautiful voice. From her cousin's pale face, she knew he'd heard it, too, felt its violating touch.

Erawan chuckled. "I'm surprised you tried to save him first. Given what he did to you at Endovier. My prince could scarcely stand to be inside his mind, it was already so vile. Do you find pleasure in deciding who shall be saved and who is beyond it? So easy, to become a little, burning god." Nausea, true and cold, struck her.

But it was Aedion who smirked, "I'd think you'd have better things to do, Erawan, than taunt us in the dead hours of the morning. Or is this all just a way to make yourself feel better about Dorian Havilliard slipping through your nets?"

The darkness hissed. Aedion squeezed her shoulder in silent warning. End it now. Before Erawan might strike. Before he could sense that the Wyrdkey he sought was mere feet away.

So Aelin inclined her head to the force staring at them through flesh and bone. "I suggest you rest and gather your strength, Erawan," she purred, winking at him with every shred of bravado left in her. "You're going to need it."

A low laugh as flames started to flicker in her eyes, heating her blood with welcome, delicious warmth. "Indeed. Especially considering the plans I have for the would-be King of Adarlan." Aelin's heart stopped.

"Perhaps you should have told your lover to disguise himself before he snatched Dorian Havilliard out of Rifthold." Those eyes narrowed to slits. "What was his name  Oh, yes," Erawan breathed, as if someone had whispered it to him. "Prince Rowan Whitethorn of Doranelle. What a prize he shall be."

Aelin plummeted down into fire and darkness, refusing to yield one inch to the terror creeping over her.

Erawan crooned, "My hunters are already tracking them. And I am going to hurt them, Aelin Galathynius. I am going to hone them into my most loyal generals. Starting with your Fae Prince---"

A battering ram of hottest blue slammed into that pit in the man's chest cavity, into those burning eyes.

Aelin kept her magic focused on that chest, on the bones and flesh melting away, leaving only that heart of iron and Wyrdstone untouched. Her magic flowed around it like a stream surging past a rock, burning his body, that \emph{thing} inside him---

"Don't bother saving any part of him," Aedion snarled softly.

Her magic roaring out of her, Aelin glanced over a shoulder. Lysandra was now in human form beside Aedion, teeth gritted at the overseer--- The look cost her.

She heard Aedion's shout before she felt Erawan's punch of darkness crash into her chest.

Felt the air snap against her as she was hurled back, felt her body bark against the stone wall before the agony of that darkness really sank in. Her breath stalled, her blood halted--- \emph{Get up get up get up.}

Erawan laughed softly as Aedion was instantly at her side, dragging her to her feet as her mind, her body tried to reorder itself---

Aelin threw out her power again, letting Aedion believe she allowed him to hold her upright simply because she forgot to step away, not because her knees were shaking so violently she wasn't sure she \emph{could}
stand.

But her hand remained steady, at least, as she extended it.

The temple around them shuddered at the force of the power she hurled out of herself. Dust and kernels of debris trickled from the ceiling high above; columns swayed like drunken friends.

Aedion's and Lysandra's faces glowed in the blue light of her flame, their features wide-eyed but set with solid determination---and wrath. She leaned farther into Aedion as her magic roared from her, his grip tightening at her waist.

Each heartbeat was a lifetime; each breath ached.

But the overseer's body at last ripped apart under her power---the dark shields around it yielding to her.

And some small part of her realized that it only did so when Erawan deigned to leave, those amused, ember-like eyes guttering into nothing.

When the man's body was only ashes, Aelin reeled back her magic, cocooned her heart in it. She gripped Aedion's arm, trying not to breathe too loudly, lest he hear the rasp of her battered lungs, realize how hard that single plume of darkness had hit.

A heavy \emph{thud} echoed through the silent temple as the lump of iron and Wyrdstone fell.

That was the cost---Erawan's plan. To realize that the only mercy she might offer her court would be death.

If they were ever captured  he'd make her watch as they were all carved apart and filled with his power. Make her look into their faces when he'd finished, and find no trace of their souls within. Then he'd get to work on her.

And Rowan and Dorian  If Erawan was hunting them at this very moment, if he learned that they were in Skull's Bay, and how hard he'd actually struck her

---

Aelin's flames banked to a quiet ember, and she finally found enough strength in her legs to push away from Aedion's grip.

"We need to be on that ship before dawn, Aelin," he said. "If Erawan wasn't bluffing\ldots"

Aelin only nodded. They had to get to Skull's Bay as fast as the winds and currents could carry them.

But as she turned toward the archway out of the temple, heading for the archives, she glanced at her chest---utterly untouched, though Erawan's power had hit her like a hurled spear.

He'd missed. By three inches, Erawan had narrowly missed hitting the amulet. And possibly sensing the Wyrdkey inside it.

Yet the blow still reverberated against her bones in brutal ripples.

A reminder that she might be the heir of fire  but Erawan was King of the Darkness.
