
\chapter{21}

The Pirate Lord of Skull's Bay did not turn from where he was sprawled on the chaise, piles of papers littering the worn cobalt rug beneath it. From the neat columns that Dorian could barely make out from where he and Rowan stood a few feet into the man's office, the papers seemed crammed with tallies of goods or expenses---ill-gained or otherwise.

But Rolfe continued monitoring the ships tilting and bobbing in the harbor, the shadow of Ship-Breaker's sagging chain cleaving the storm-tossed world beyond them.

Rolfe had likely learned of their arrival not due to any magic map, but from sitting here. Indeed, dark leather gloves adorned his hands---the material scarred and cracked with age. Not a hint of the legendary tattoos lurking beneath.

Rowan didn't move; barely blinked as he took in the captain, the office. Dorian himself had been part of enough political maneuverings to know the uses of silence---the power in who spoke first. The power in making someone wait.

The rain drumming on the windows and the muffled dripping of their own soaked clothes on the threadbare carpet filled the quiet.

Captain Rolfe tapped a gloved finger on the arm of the chaise, watching the harbor for a heartbeat longer---as if to make sure the \emph{Sea Dragon} still floated--- and finally turned to them.

"Take off your hoods. I want to know who I'm talking to."

Dorian stiffened at the command, but Rowan said, "Your barmaid implied that you know damn well who we are."

A wry half smile tugged on Rolfe's lips, the upper-left corner flecked with a small scar. Hopefully not from Aelin. "My barmaid talks too much."

"Then why keep her?"

"Easy on the eyes---hard to come by around here," Rolfe said, uncoiling to his feet. He was about Dorian's height and clothed in simple but well-made black. An elegant rapier hung at his side, along with a matching parrying knife.

Rowan snorted, but to Dorian's surprise, removed his hood.

Rolfe's sea-green eyes flared---no doubt at the silver hair, pointed ears, and slightly elongated canines. Or the tattoo. "A man who likes ink as much as I do," Rolfe said with an appreciative nod. "I think you and I will get along just fine, Prince."

"Male," Rowan corrected. "Fae males are not human men."

"Semantics," Rolfe said, flicking his attention to Dorian. "So you're the king everyone's in such a tizzy over."

Dorian finally tugged back his hood. "What of it?"

With that gloved hand, Rolfe pointed toward a paper-covered desk and two upholstered chairs before it. Like the man himself, it was elegant, but worn--- either from age, use, or battles past. And those gloves 
To cover the maps inked there?

Rowan gave Dorian a nod to sit. The flames on the candles burning throughout guttered as they passed, and claimed their seats.

Rolfe edged around the stacks of papers on the floor and took up his spot at the desk. His carved, high-backed chair might very well have been a throne from some distant kingdom. "You seem remarkably calm for a king who's just been

declared a traitor to his crown and robbed of his throne."

Dorian was glad he was in the process of sitting down.

Rowan lifted a brow. "According to whom?"

"According to the messengers who arrived yesterday," Rolfe said, leaning back in his seat and crossing his arms. "Duke Perrington---or should I call him King Perrington now?---issued a decree, signed by the majority of Adarlan's lords and ladies, naming \emph{you}, Majesty, an enemy to your kingdom, and claiming that he liberated Rifthold from
\emph{your} claws after you and the Queen of Terrasen slaughtered so many innocents this spring. It also claims that any ally"---a nod toward Rowan---"is an enemy. And that you will be crushed under his armies if you do not yield."

Silence filled his head. Rolfe went on, perhaps a bit more gently, "Your brother has been named Perrington's heir and Crown Prince."

Oh gods. Hollin was a child, but still  something had rotted in him, festered---

He had left them there. Rather than deal with his mother and brother, he'd told them to stay in those mountains. Where they were now as good as lambs surrounded by a pack of wolves.

He wished Chaol were with him. Wished for time to just 
\emph{stop} so he might sort out all these fractured pieces of himself, put them into some kind of order, if not back together entirely.

Rolfe said, "From the look on your face, I'm guessing your arrival indeed has something to do with the fact that Rifthold now lies in ruin, its people fleeing wherever they can."

Dorian shoved out the insidious thoughts and drawled, "I came to learn what side of the line you stand on, Captain, in regard to this conflict."

Rolfe sat forward, resting his forearms on the desk. "You must be desperate indeed, then." A glance at Rowan. "And is your queen equally desperate for my aid?"

"My queen," Rowan said, "is not a part of this discussion."

Rolfe only grinned at Dorian. "You wish to know what side of the line I stand on? I stand on the side that keeps the hell out of my territory."

"Rumor has it," Rowan countered smoothly, "that the easternmost part of this archipelago is no longer your territory at all."

Rolfe held Rowan's gaze. A heartbeat passed. Then another. A muscle flickered in Rolfe's jaw.

Then he pulled off those gloves to reveal hands tattooed from fingertip to wrist. He turned them palm up, revealing a map of the archipelago, and what---

Dorian and Rowan leaned forward as the blue waters did indeed flow, little dots among it sailing by. And in the easternmost tip of the archipelago, curving out to sea\ldots{}

Those waters were gray, the islands a ruddy brown. But nothing moved---no dots indicated ships. As if the map had frozen.

"They have magic that shields them---even from this," Rolfe said. "I can't get a count of their ships, or men, or beasts. Scouts never return. This winter, we'd hear roaring from the islands---some almost-human, some definitely not. Often, we'd spy  things standing out on those rocks. Men, but not. We let it go unchecked for too long---and paid the price."

"Beasts," Dorian said. "What sort of beasts?"

A grim smile, scar stretching. "Ones to make you consider fleeing this continent, Majesty."

The condescension snapped something loose in Dorian's temper. "I have walked through more nightmares than you realize, Captain."

Rolfe snorted, but his eyes went to that pale line across Dorian's throat.

Rowan leaned back in his chair with lazy grace---the War

Commander incarnate. "It must be a solid truce you hold, then, if you're still camped here with minimal ships in your harbor."

Rolfe simply tugged on his worn gloves. "My fleet does have to do a little pirating every now and then, you know. Bills to pay and all that."

"I'm sure. Especially when you employ four guards to watch your hallway."

Dorian caught Rowan's train of thought and said to the Fae Prince, "I didn't scent the Valg in town." No, whatever that power had been
 it had flickered into nothing now.

"That's because," Rolfe drawled, cutting them off, "we killed most of them." Wind rattled the windows, smearing the rain across them.

"And as for the four men in the hall---they are all that's left of my crew. Thanks to the battle we had early this spring to reclaim this island after

Perrington's general stole it from us."

Dorian swore low and viciously. The captain nodded.

"But I am again Pirate Lord of Skull's Bay, and if the eastern islands are as far as Morath plans to go, then Perrington and his beasts can have them. The

Dead End is barely more than caves and rock anyway." "What manner of beasts," Dorian said again.

Rolfe's pale green eyes darkened. "Sea-wyverns. Witches rule the skies with their wyverns---but these waters are now ruled by beasts bred for naval battle, foul corruptions of an ancient template. Imagine a creature half the size of a first-rate ship---faster than a racing dolphin---and the damage it can cause with tooth and claw and a poisoned tail big as a mast. Worse, if you kill one of their vicious offspring, the adults will hunt you to the ends of the earth." Rolfe shrugged. "So you will find, Majesty, that I have no interest in disturbing the eastern islands if they do not disturb me any further. I have no interest in doing anything but continuing to profit from my endeavors." He waved a vague hand to the papers scattered throughout.

Dorian held his tongue. The offer he'd been planning to make 
His coffers belonged to Morath now. He doubted privateers would volunteer based on credit.

Rowan gave him a look that said the same. Another route to win Rolfe to their cause, then. Dorian surveyed the office, the taste leaning toward finery and yet so little that was not worn. The half-wrecked town around them. The four surviving crew. The way Rolfe had looked at that band of white along his throat.

Rowan opened his mouth, but Dorian said, "They weren't just killed, your crew. Some were taken, weren't they?" Rolfe's sea-green eyes went cold.

Dorian pushed, "Captured, along with others, and taken into the Dead Islands. Used for information about how and where to strike you. The only way to free them when they were sent back to you, demons wearing their bodies, was to behead them. Burn them."

Rowan asked roughly, "Was it rings or collars they wore, Captain?"

Rolfe's throat bobbed once. After a long moment, he said, "Rings. They said they'd been set free. But they weren't the men who\ldots" A shake of the head. "Demons," he breathed, as if it explained something. "That's what he put in them."

So Rowan told him. Of the Valg, their princes, and of Erawan, the last Valg king.

Even Rolfe had the wits to look unnerved as Rowan concluded, "He has cast off the disguise as Perrington. He is only Erawan now---King Erawan, apparently."

Rolfe's eyes again drifted to Dorian's neck, and it was an effort not to touch the scar there. "How did you survive it? We even cut the rings off---but my men  they were gone."

Dorian shook his head. "I don't know." No answer didn't make Rolfe's men sound  lesser for not having survived. Maybe he'd been infested by a Valg prince who'd savored taking his time.

Rolfe shifted a piece of paper on his desk, reading it again for a heartbeat--- as if it were a mere distraction while he thought. He said at last, "Wiping what's left of them from the Dead Islands won't do shit against the might of Morath."

"No," Rowan countered, "but if we hold the archipelago, we can use these islands to wage a battle from the seas while we strike from the land. We can use these islands to house fleets from other kingdoms, other continents."

Dorian added, "My Hand is currently in the southern continent---in Antica itself. He will persuade them to send a fleet." Chaol would do nothing less for him, for Adarlan.

"None will come," Rolfe said. "They didn't come ten years ago; they certainly won't come now." He surveyed Rowan and added with a small smirk,

"Especially not with the latest news."

This couldn't end well, Dorian decided as Rowan asked flatly, "What news?"

Rolfe didn't answer, instead watching the stormy bay, or whatever out there held his interest. A rough few months for the man, Dorian realized. Someone holding on to this place through sheer arrogance and will. And all those tables below, assembled from the wreckage of conquered ships  How many enemies were circling, waiting for a shot at revenge?

Rowan opened his mouth, no doubt to demand an answer, when Rolfe thumped his booted foot thrice on the worn floorboards. An answering thump on the wall sounded.

Silence fell. Given Rolfe's hatred for the Valg, Dorian doubted Morath was about to spring shut a trap, but  he slid deep into his magic as footsteps thudded down the hall. From the tight cast of Rowan's tattooed face, he knew the prince was doing the same. Especially as Dorian felt his magic reach toward the Fae Prince's, as it had done that day with Aelin atop the glass castle.

Those footsteps paused outside the office door, and again, that pulse of foreign, mighty magic rose up. Rowan's hand slid into casual distance of the hunting knife at his thigh.

Dorian focused on his breathing, on hauling up lines and pieces of his magic.

Ice bit into his palms as the office door opened.

Two golden-haired males appeared in the doorway.

Rowan's snarl reverberated through the floorboards and along Dorian's feet as he took in the muscle, the pointed ears, the gaping mouths that revealed elongated canines\ldots{}

The two strangers, the source of that power  They were Fae.

The one with night-dark eyes and an edged grin looked Rowan over and drawled, "I liked your hair longer."

A dagger embedding itself in the wall not an inch from the male's ear was Rowan's only answer.
