
\chapter{23}

Holy gods.

Rowan froze. "That explains the two of you, then."

Fenrys tossed his hair out of his dark eyes. "Three, actually. Vaughan left yesterday afternoon to fly north---while we take the South." Vaughan, with his osprey form, could cover the far harsher terrain more easily. "We landed in this shithole town to see if Rolfe had dealings with Lorcan---to bribe him to tip us off if Lorcan should come through here again, looking to hire a boat." Skull's Bay would be one of the few ports where Lorcan could do such a thing without questions. "Warning Rolfe about Maeve's armada was part of convincing the bastard to help us. We're to make our way onto the continent from here---start our hunt in the South. And since these lands are rather large\ldots" A flash of white teeth in a feral smile. "Any inkling about his general whereabouts would be much appreciated, \emph{Prince}."

Rowan debated it. But if they caught Lorcan, and the commander had possession of even one of the Wyrdkeys  If they brought both commander and keys back to Maeve, especially if she was already sailing for Eyllwe for whatever reasons of her own\ldots{}

Rowan shrugged. "I washed my hands of you all this spring. Lorcan's business is his own."

"You \emph{prick}---" Fenrys snarled.

Gavriel cut in, "If we could bargain?"

There was something like pain---and regret---in Gavriel's eyes. Of all of them, Gavriel had probably been his only friend.

Rowan debated if he should tell him about the son who now was making his way here. Debated if Aedion would like the chance to meet his father
 perhaps before war made corpses of them all.

But Rowan said, "Has Maeve given you leave to bargain on her behalf?"

"We only received our orders," Fenrys drawled, "and the permission to use any means necessary to kill Lorcan. She did not mention your queen at all. So that amounts to a \emph{yes}."

Rowan crossed his arms. "You send me an army of Doranelle warriors, and

I'll tell you where Lorcan is, and where he plans to go."

Fenrys let out a harsh laugh. "Mother's tits, Rowan. Even if we could, the armada's already in use."

"I suppose I'll have to make do with you two, then."

Dorian had the good sense not to look as surprised as Rowan's former brothers-in-arms.

Fenrys burst out laughing. "What---work for your queen? Fight in your battles?"

"Isn't that what you want, Fenrys?" Rowan fixed him with a stare. "To serve my queen? You've been pulling on the leash for months. Well, here's your shot."

All amusement faded from Fenrys's beautiful face. "You're a bastard, Rowan."

Rowan turned to Gavriel. "I'm assuming Maeve didn't specify \emph{when}
you had to do this." A shallow nod was his only confirmation. "And you will technically be fulfilling her command to you." The blood oath operated on specific, clear demands. And relied on close physical contact to enable that \emph{tug} to get the body to yield. This far away  they had to obey Maeve's orders---but could use any loopholes in the language to their own advantage.

"Lorcan might very well be gone by the time you've considered our bargain fulfilled," Fenrys countered.

Rowan smiled a bit. "Ah, but the thing is  Lorcan's path will eventually lead him right back to me. To my queen. Who knows how long it will take, but he will find us again. At which time, he'll be yours." He tapped a finger against his bicep. "People are going to be talking about this war for a thousand years. Longer." Rowan jerked his chin at Fenrys. "You've never shied from a fight."

"That's if we survive," Fenrys said. "And what of Brannon's gifts? How long will a single flame last against the darkness that gathers? Maeve hid her motives about the armada and Eyllwe, but she at least told us who really reigns in Morath."

When Rowan had walked through the door of the Sea Dragon, he'd wondered what god had sent the storm that had pushed them to arrive in Skull's Bay on this day, at this time.

Together, he and the cadre had taken on a legion of Adarlan's forces this spring and won---easily.

And even if Lorcan, Vaughan, and Connall weren't with them  One Fae warrior was as good as a hundred mortal soldiers. Maybe more.

Terrasen needed more troops. Well, here was a three-male army.

And against the aerial Ironteeth legions, they would need Fae speed and strength and centuries of experience.

Together, they had sacked cities and kingdoms for Maeve; together, they had waged war and ended it.

Rowan said, "Ten years ago, we did nothing to stop this. If Maeve had sent a force, we might have kept it from growing so out of control. Our brethren were hunted and killed and tortured. Maeve let it happen for spite, because Aelin's mother would not yield to her wishes. So yes---my Fireheart is one flame in the sea of darkness. But she is willing to fight, Fenrys. She is willing to take on Erawan, take on Maeve and the gods themselves, if it means peace can be had."

Across the room, Dorian's eyes had shuttered. Rowan knew the king would fight---and go down swinging---and that his gift could make a difference between victory and defeat. Yet  he was untrained. Still untried, despite all he'd endured.

"But Aelin is one person," Rowan went on. "And even her gifts might not be enough to win. Alone," he breathed, meeting Fenrys's stare, then Gavriel's, "she will die. And once that flame goes out, it is done. There is no second chance. Once that fire extinguishes, we are all doomed, in every land and every world."

The words were poison on his tongue, his very bones aching at the thought of that death---what he'd do if it should happen.

Gavriel and Fenrys looked at each other, speaking in that silent way he used to do with them. There was one card Rowan had to play to convince them---to convince Gavriel.

Even if the specificity of Maeve's command might allow it, she could very well punish them for acting \emph{around} her orders. She'd done it before; they all bore scars from it. They knew the risk of it as well as Rowan did. Gavriel shook his head slightly at Fenrys.

Before they could turn to say no, Rowan said to Gavriel, "If you do not fight in this war, Gavriel, then you doom your son to die." Gavriel froze.

Fenrys spat, "Bullshit." Even Dorian was gaping a bit.

Rowan wondered just how pissed Aedion would be as he said, "Think on my proposal. But know that your son makes for Skull's Bay. You may want to wait to decide until you meet him."

"Who\ldots" Rowan wasn't sure Gavriel was breathing properly. The warrior's hands were clenched so tightly the scars over his knuckles were moon white. "I have a son?"

Some part of Rowan felt like the prick Fenrys claimed he was and not the male that Aelin believed him to be as he nodded.

The information would have gotten out sooner or later.

If Maeve had learned first, she might have schemed to ensnare Aedion--- might have sent the cadre to kill or steal him. But now, Rowan supposed, he'd ensnared the cadre himself. It was only a matter of how desperately Gavriel wanted to meet his son  and how afraid they were of failing Maeve should they not find Lorcan.

So Rowan said coldly, "Stay out of our way until they arrive and we'll stay out of yours."

Putting his back to them went against every instinct, but Rowan kept his shields tight, his magic spread to alert him if either so much as breathed wrong while he twisted to open the bedroom door in silent dismissal. He had much to do. Starting with writing a warning to the Eyllwe royals and Terrasen's forces.

Ending with trying to figure out how the hell they could fight two wars at once.

Gavriel rose, slack-faced, pale---something like devastation written there.

Rowan caught the spark of realization that flashed across Dorian's eyes a heartbeat before the king buried it. Yes---at first glance, Aedion and Aelin looked like siblings, but it was Aedion's smile that gave away his heritage. Gavriel would know in a heartbeat  if Aedion's scent didn't give it away first.

Fenrys stepped closer to the male, a hand on his shoulder as they entered the hallway. For both Rowan and Fenrys, Gavriel had always been their sounding board. Never each other---no, he and Fenrys  it was easier to be at each other's throats instead.

Rowan said to both of his former companions, "If you so much as hint about Gavriel's son to Maeve, our bargain is over. You'll never find Lorcan. And if Lorcan does show up  I'll gladly help him kill you." Rowan prayed it wouldn't come to it---to a fight that brutal and devastating.

This was war, though. And he had no intention of losing it.
