
\chapter{24}

The \emph{Wind-Singer} left Ilium at dawn, its crew and captain unaware that the two hooded individuals---and their pet falcon---who had paid in gold had no intention of going the entire journey to Leriba. Whether they pieced together that those two individuals were also the general and queen who had liberated their town the night before, they didn't let on.

It was considered an easy trip down the coast of the continent, though Aelin wondered if voicing that statement would guarantee it
\emph{wasn't} an easy trip. First, there was the matter of sailing through Adarlan's waters---near Rifthold,

specifically. If the witches patrolled far out to sea\ldots{}

But they had no other choice, not with the net Erawan had stretched across the continent. Not with his threat to find and capture Rowan and Dorian still ringing fresh in her mind, along with the throbbing of the deep purple bruise on her chest, right over her heart.

Standing on the deck of the ship, the rising sun staining the turquoise bay of Ilium with gold and pink, Aelin wondered if the next time she'd see these waters, they'd be red. Wondered how long the Adarlanian soldiers would remain on their side of the border.

Aedion stepped to her side, finished with his \emph{third} inspection. "Everything looks fine."

"Lysandra said all was clear." Indeed, from high up on the mainmast of the ship, Lysandra's falcon eyes missed nothing.

Aedion frowned. "You know, you ladies \emph{can} let us males do things every now and then."

Aelin lifted a brow. "Where would the fun be in that?" But she knew this would be an ongoing argument---stepping back so that others, so that Aedion, might fight for her. It'd been bad enough in Rifthold, bad enough knowing that those rings and collars might enslave them---but what Erawan had done to that overseer  as an \emph{experiment}.

Aelin glanced toward the scurrying crew, biting back her demand to
\emph{hurry.} Every minute delayed could be one that Erawan closed in on Rowan and Dorian.

It was only a matter of time before a report reached him regarding where they'd been spotted. Aelin tapped her foot on the deck.

The rocking of the ship on the calm waves echoed the beat of her foot. She'd always loved the smell and feel of the sea. But now  even the lapping of those waves seemed to say, \emph{Hurry, hurry}.

"The King of Adarlan---and Perrington, I suppose---had me in their grasp for years," Aedion said. His voice was tight enough that Aelin turned from the sea to face him. He'd gripped the wooden railing, the scars on his hands stark against his summer-tanned skin. "They met with me in Terrasen, in Adarlan. He had me in his rutting \emph{dungeon}, gods above. And yet he didn't do \emph{that} to me. He offered me the ring but didn't notice I wore a fake instead. Why not cleave me open and corrupt me? He had to know---he \emph{had} to know that you'd come for me."

"The king left Dorian alone for as long as he could---perhaps that goodness extended to you, too. Perhaps he knew that if you were gone, I might very well

have decided to let this world go to hell and never free him for spite."

"Would you have done that?"

\emph{The people you love are just weapons that will be used against you}, Rowan had once told her. "Don't waste your energy worrying about what could have been." She knew she hadn't answered his question.

Aedion didn't look at her as he said, "I knew what happened in Endovier, Aelin, but seeing that overseer, hearing what he said\ldots" His throat bobbed. "I was so close to the salt mines. That year---I was camped with the Bane right over the border for three months."

She whipped her head to him. "We're not starting down this road. Erawan sent that man for a reason---for \emph{this} reason. He knows my past---\emph{wants} me to know he's aware of it---and will use it against me. Against us. He'll use everyone we know, if he needs to."

Aedion sighed. "Would you have told me what happened last night if I hadn't been there?"

"I don't know. I bet you would have awoken as soon as I unleashed my power on him."

He snorted. "It's hard to miss."

The crying of gulls swooping overhead filled the quiet that followed. Despite her declaration not to linger in the past, Aelin said carefully, "Darrow claimed you fought at Theralis." She'd been meaning to ask for weeks, but hadn't worked up the nerve.

Aedion fixed his stare on the churning water. "It was a long time ago."

She swallowed against the burning in her throat. "You were barely fourteen."

"I was." His jaw tightened. She could only imagine the carnage. And the horror---not just of a boy killing and fighting, but seeing the people they cared for fall. One by one.

"I'm sorry," she breathed. "That you had to endure it."

Aedion turned toward her. No hint of the haughty arrogance and insolence. "Theralis is the battlefield I see the most---in my dreams." He scratched at a fleck on the rail. "Darrow made sure I stayed out of the thick of it, but we were overwhelmed. It was unavoidable."

He'd never told her---that Darrow had tried to shield him. She put a hand atop Aedion's and squeezed. "I'm sorry," she said again. She couldn't bring herself to ask more.

He shrugged with a shoulder. "My life as a warrior was chosen long before that battlefield."

Indeed, she couldn't imagine him without that sword and shield---both currently strapped across his back. She couldn't decide if it was a good thing.

Silence settled between them, heavy and old and weary.

"I don't blame him," Aelin said at last. "I don't blame Darrow for blocking me from Terrasen. I would do the same, judge the same, if I were him."

Aedion frowned. "I thought you were going to fight his decree."

"I am," she swore. "But\ldots{} I understand why Darrow did it."

Aedion observed her before nodding. A grave nod, from one soldier to another.

She put a hand against the amulet beneath her clothes. Its ancient, otherworldly power rubbed up against her, and a shiver went down her spine.

\emph{Find the Lock.}

Good thing Skull's Bay was on their way to the Stone Marshes of Eyllwe.

And good thing that its ruler possessed a magical map inked on his hands. A map that revealed enemies, storms  and hidden treasure. A map to find things that did not wish to be found.

Aelin lowered her hand, propping both on the rail and examining the scar across each palm. So many promises and oaths made. So many debts and favors to still call in.

Aelin wondered what answers and oaths she might find waiting in Skull's Bay.

If they got there before Erawan did.
