
\chapter{27}

Dorian didn't dare move as Rolfe let out a snarl.
"I have a distinct memory, Celaena Sardothien, of saying that if you set foot in my territory again, your life was forfeit."

"Ah," Aelin said, lowering her hands but leaving her feet still propped on Rolfe's desk, "but where would the fun be in that?"

Rowan was still as death beside him.
Aelin's grin became feline as she finally lowered her feet and ran her hands along either side of the desk, assessing the smooth wood as if it was a prize horse.
She inclined her head to Dorian.
"Hello, Majesty."

"Hello, Celaena," he said as calmly as he could, well aware that two Fae males behind him could hear his thundering heart.
Rolfe whipped his head toward him.

Because it was Celaena who sat here---for whatever purpose, it was Celaena Sardothien in this room.

She jerked her chin at Rolfe.
"You've seen better days, but considering half your fleet has abandoned you, I'd say you look decent enough."
"Get out of my chair," Rolfe said too quietly.

Aelin did no such thing.
She just gave Rowan a sultry sweep from foot to face.
Rowan's expression remained unreadable, eyes intent---near-glowing.
And then Aelin said to Rowan with a secret smile, "You, I don't know.
But I'd like to."

Rowan's lips tugged upward.
"I'm not on the market, unfortunately."

"Pity," Aelin said, cocking her head as she noticed a bowl of small emeralds on Rolfe's desk.
\emph{Don't do it, don't}---

Aelin swiped up the emeralds in a hand, picking them over as she glanced at Rowan beneath her lashes.
"She must be a rare, staggering beauty to make you so faithful."

Gods save them all.
He could have sworn Fenrys coughed behind him.

Aelin chucked the emeralds into the metal dish as if they were bits of copper, their plunking the only sound.
"She must be clever"---\emph{plunk}---"and fascinating"---\emph{plunk}---"and very, \emph{very} talented."
\emph{Plunk, plunk, plunk} went the emeralds.
She examined the four gems remaining in her hand.
"She must be the most wonderful person who ever existed."

Another cough from behind him---from Gavriel this time.
But Aelin only had eyes for Rowan as the warrior said to her, "She is indeed that.
And more."

"Hmmm," Aelin said, rolling the emeralds in her scarred palm with expert ease.

Rolfe growled, "What.
Are.
You.
Doing.
Here."

Aelin dumped the emeralds into their dish.
"Is that any way to speak to an old friend?"

Rolfe stalked toward the desk, and Rowan trembled with restraint as the Pirate Lord braced his hands on the wooden surface.
"Last I heard, your master was dead and you sold the Guild to his underlings.
You're a free woman.
What are you doing in \emph{my} city?"

Aelin met his sea-green eyes with an irreverence that Dorian wondered if she had been born with or had honed through skill and blood and adventure.
"War is coming, Rolfe.
Am I not allowed to weigh my options?
I thought to see what \emph{you} planned to do."

Rolfe looked over his broad shoulder at Dorian.
"Rumor has it she was your Champion this fall.
Do you wish to deal with \emph{this}?"

Dorian said smoothly, "You will find, Rolfe, that one does not \emph{deal} with Celaena Sardothien.
One survives her."

A flash of a grin from Aelin.
Rolfe rolled his eyes and said to the assassinqueen, "So, what is the plan, then?
You made a bargain to get out of Endovier, became the King's Champion, and now that he is dead, you wish to see how you might profit?"

Dorian tried not to flinch.
Dead---his father was dead, at his own hands.

"You know how my tastes run," Aelin said.
"Even with Arobynn's fortune and the sale of the Guild\ldots War can be a profitable time for people who are smart with their business."

"And where is the sixteen-year-old self-righteous brat who wrecked six of my ships, stole two of them, and destroyed my town, all for the sake of two hundred slaves?"

A shadow flickered in Aelin's eyes that sent a chill down Dorian's spine.
"Spend a year in Endovier, Rolfe, and you quickly learn how to play a different sort of game."

"I told you"---Rolfe seethed with quiet venom---"that you'd one day pay for that arrogance."

Aelin's smile became lethal.
"Indeed I did.
And so did Arobynn Hamel."

Rolfe blinked---just once, then straightened.
"Get out of my seat.
And put back that emerald you slipped up your sleeve."

Aelin snorted, and with a flash of her fingers, an emerald---the fourth one Dorian had forgotten---appeared between her fingers.
"Good.
At least your eyesight isn't failing in your old age."

"And the other one," Rolfe said through clenched teeth.

Aelin grinned again.
And then leaned back in Rolfe's chair, tipped up her head, and spat out an emerald she'd somehow kept hidden under her tongue.

Dorian watched the gem arc neatly through the air.

Its plunk in the dish was the only sound.

Dorian glanced at Rowan.
But delight shone in the prince's eyes---delight and pride and simmering lust.
Dorian quickly looked away.

Aelin said to the Pirate Lord, "I have two questions for you."

Rolfe's hand twitched toward his rapier.
"You're in no rutting position to ask questions."

"Aren't I?
After all, I made you a promise two and a half years ago.
One that you signed."

Rolfe snarled.

Aelin propped her chin on a fist.
"Have you or have any of your ships bought, traded, or transported slaves since that\ldots unfortunate day?"

"No."

A satisfied little nod.
"And have you provided sanctuary for them here?"

"We haven't gone out of our way, but if any arrived, yes."
Each word was tighter than the last, a spring about to burst forward and throttle the queen.
Dorian prayed the man wouldn't be dumb enough to draw on her.
Not with Rowan watching his every breath.

"Good and good," Aelin said.
"Smart of you, not to lie to me.
As I took it upon myself when I arrived this morning to look into your warehouses, to ask around in the markets.
And then I came here\ldots" She ran her hands over the papers and books on the desk.
"To see your ledgers for myself."
She dragged a finger down a page containing various columns and numbers.
"Textiles, spices, porcelain dining ware, rice from the southern continent, and various contraband, but 
no slaves.
I have to say, I'm impressed.
Both at you honoring your word and at your thorough record keeping."

A low snarl.
"Do you know what your stunt cost me?"

Aelin flicked her eyes toward a piece of parchment on the wall, various daggers, swords, and even scissors embedded in it---target practice, apparently, for Rolfe.
"Well, there's the bar tab I left unpaid  ," she said of the document, which was indeed a list of items, and---holy gods, that was a large sum of money.

Rolfe turned to Rowan, Fenrys, and Gavriel.
"You want my assistance in this war?
Here's the cost.
Kill her.
Now.
Then my ships and men are yours."

Fenrys's dark eyes glittered, but not at Rolfe, as Aelin rose to her feet.
Her black clothes were travel-worn, her golden hair gleaming in the gray light.
And even in a room of professional killers, she took the lion's share of air.
"Oh, I don't think they will," she said.
"Or even can."

Rolfe whirled to her.
"You'll find that you are not so skilled in the face of Fae warriors."

She pointed to one of the chairs before the desk.
"You might want to sit."
"Get the \emph{hell} out of---"

Aelin let out a low whistle.
"Allow me to introduce to you, Captain Rolfe, the \emph{incomparable}, the beautiful, and the absolutely and all-around flawless Queen of Terrasen."

Dorian's brows creased.
But footsteps sounded, and then---

The males shifted as Aelin Galathynius indeed strode into the room, clad in a dark green tunic of equal wear and dirt, her golden hair unbound, her turquoiseand-gold eyes laughing as she strode past a slack-jawed Rolfe and perched on the arm of Aelin's chair.

Dorian couldn't tell---without a Fae's sense of smell, he couldn't tell.

"What---what devilry is this," Rolfe hissed, yielding a single step.

Aelin and Aelin looked at each other.
The one in black grinned up at the newcomer.
"Oh, you \emph{are} gorgeous, aren't you?"

The one in green smiled, but for all its delight, all its wicked mischief\ldots It was a softer smile, made with a mouth that was perhaps less used to snarling and teeth-baring and getting away with saying hideous, swaggering things.
Lysandra, then.

The two queens faced Rolfe.

"Aelin Galathynius had no twin," he growled, a hand on his sword.

Aelin in black---the true Aelin, who had been among them all along---rolled her eyes.
"Ugh, Rolfe.
You ruin my fun.
\emph{Of course}
I don't have a twin."

She jerked her chin at Lysandra, and the shifter's flesh glowed and melted, hair becoming a heavy, straight fall of dark tresses, her skin sun-kissed, her uptilted eyes a striking green.

Rolfe barked in alarm and staggered back---only for Fenrys to steady him with a hand on his shoulder as the Fae warrior stepped forward, eyes wide.
"A shifter," Fenrys breathed.

Aelin and Lysandra fixed the warrior with an unimpressed look that would have sent lesser men running.

Even Gavriel's placid face was slack at the sight of the shape-shifter---his tattoos bobbing as he swallowed.
Aedion's father.
And if Aedion was here with Aelin\ldots{}

"As intrigued as I am to see that the cadre is present," Aelin said, "will you verify to His Pirateness that I am who I say I am, and we can move on to more pressing matters?"

Rolfe's face was white with fury as he realized they'd all known who truly sat before them.

Dorian said, "She is Aelin Galathynius.
And Celaena Sardothien."

But it was to Fenrys and Gavriel, the outside party, that Rolfe turned.
Gavriel nodded, Fenrys's eyes now fixed on the queen.
"She is who she says she is."

Rolfe turned to Aelin, but the queen frowned up at Lysandra as the shifter handed her a wax-sealed tube.
"You made your hair shorter."

"You try hair that long and see if you last more than a day," Lysandra said, fingering the hair brushing her collarbone.

Rolfe gaped at them.
Aelin grinned at her companion and faced the Pirate Lord.

"So, Rolfe," the queen drawled, tossing the tube from hand to hand, "let's discuss this little business of you refusing to aid my cause."
