
\chapter{29}

Too many animals loitering about the streets at this hour would attract the wrong sort of attention.

But Aedion still wished that the shifter was wearing fur or feathers compared to\ldots this.

Not that she was sore on the eyes as an auburn-haired and green-eyed young woman.
She could have passed for one of the lovely mountain maidens of northern Terrasen with that coloring.
It was \emph{who}
Lysandra was supposed to be as they waited just inside an alley.
Who \emph{he} was supposed to be, too.

Lysandra leaned against the brick wall, a foot propped against it to reveal a length of creamy-white thigh.
And Aedion, with his hand braced against the wall beside her head, was no more than an hourly customer.

No sound in the alley but scuttling rats digging through rotten, discarded fruit.
Skull's Bay was precisely the shithole he expected it to be, right down to its Pirate Lord.

Who now unwittingly held the only map to the Lock that Aelin had been commanded to find.
When Aedion had complained that \emph{of course} it was a map they could not steal, Rowan had been the one to suggest this  plan.
Trap.
Whatever it was.

He glanced at the delicate gold chain dangling around Lysandra's pale throat, tracing its length down the front of her bodice, to where the Amulet of Orynth was now hidden beneath.

"Admiring the view?"

Aedion snapped his eyes up from the generous swells of her breasts.
"Sorry."

But the shifter somehow saw the thoughts churning in his head.
"You think this won't work?"

"I think there are plenty of valuable things on this island---why would Rolfe bother to go after this?"
Storms, enemies, and treasure---that was what the map showed.
And since he and Lysandra were not the first two\ldots only one, it seemed, would be able to appear on that map inked on Rolfe's hands.

"Rowan claimed Rolfe would find the amulet interesting enough to go after it."

"Rowan and Aelin have a tendency to say one thing and mean something else entirely."
Aedion heaved a breath through his nose.
"We've already been here an hour."

She arched an auburn brow.
"Do you have somewhere else to be?"

"You're tired."

"We're all tired," she said sharply.

He shut his mouth, not wanting his head ripped off just yet.

Each shift took something out of Lysandra.
The bigger the change, the bigger the animal, the steeper the cost.
Aedion had witnessed her morph from butterfly to bumblebee to hummingbird to bat within the span of a few minutes.
But going from human to ghost leopard to bear or elk or horse, she'd once demonstrated, took longer between shifts, the magic having to draw up the strength to \emph{become} that size, to fill the body with all its inherent power.

Casual footsteps sounded, accented by a two-note whistle.
Lysandra's breath brushed against his jaw at the sound.
Aedion, however, stiffened slightly as those steps grew closer, and he found himself staring at the son of his great enemy.
King, now.

But still a face he'd hated, sneered at, debated cutting into tiny pieces for many, many years.
A face he'd seen drunk out of his mind at parties mere seasons ago; a face he'd seen buried against the necks of women whose names he'd never bothered to learn; a face that had taunted him in that dungeon cell.

That face was now hooded, and for all the world, he looked like he was here to inquire about Lysandra's services---once Aedion had finished with her.
The general clenched his teeth.
"What?"

Dorian looked over Lysandra, as if surveying the goods, and Aedion fought the urge to bristle.
"Rowan sent me to see if you had any developments."
The prince and Aelin were back at the inn, drinking in the dining room---where all of Rolfe's spying eyes might see and report them.
Dorian blinked at the shifter, starting.
"And gods above---you really \emph{can} take on any human form."

Lysandra shrugged, the irreverent street whore debating her rate.
"It's not as interesting as you'd think.
I'd like to see if I could become a plant.
Or a bit of wind."

"Can you\ldots \emph{do} that?"

"Of course she can," Aedion said, pushing off the wall and crossing his arms.

"No," Lysandra said, cutting a glare in Aedion's direction.
"And there's nothing to report.
Not even a whiff of Rolfe or his men."

Dorian nodded, sliding his hands into his pockets.
Silence.

Aedion's ankle barked in pain as Lysandra subtly kicked him.

He reined in his scowl as he said to the king, "So, you and Whitethorn didn't kill each other."

Dorian's brows scrunched.
"He saved my life, nearly got himself burned out to do it.
Why should I be anything but grateful?"
Lysandra gave Aedion a smug smile.

But the king asked him, "Are you going to see your father?"

Aedion cringed.
He'd been glad for their venture tonight to avoid deciding.
Aelin hadn't brought it up, and he had been content to come out here, even if it put him at risk of running into the male.

"Of course I'll see him," Aedion said tightly.
Lysandra's moon-white face was calm, steady as she watched him, the face of a woman trained to listen to men, to never show surprise---

He did not resent what she had been, what she portrayed now, only the monsters who had seen the beauty the child would grow into and taken her into that brothel.
Aelin had told him what Arobynn had done to the man she'd loved.
It was a miracle the shifter could smile at all.

Aedion jerked his chin at Dorian.
"Go tell Aelin and Rowan we don't need their hovering.
We can manage on our own."

Dorian stiffened, but backed down the alley, no more than a disgruntled would-be customer.

Lysandra shoved a hand against Aedion's chest and hissed, "That man has endured \emph{enough}, Aedion.
A little kindness wouldn't kill you."

"He \emph{stabbed} Aelin.
If you knew him as I have, you wouldn't be so willing to fawn over---"

"No one expects you to fawn over him.
But a kind word, some \emph{respect}---"

He rolled his eyes.
"Keep your voice down."

She did---but went on, "He was enslaved; he was \emph{tortured} for months.
Not just by his father, but by that \emph{thing} inside of him.
He was \emph{violated}, and even if you cannot draw up forgiveness for stabbing Aelin against his own will, then try to have some compassion for \emph{that}."
Aedion's heart stuttered at the anger and pain on her face.
And that word she'd used---

He swallowed hard, checking the street behind them.
No sign of anyone hunting for the treasure they bore.
"I knew Dorian as a reckless, arrogant---"

"I knew your queen as the same.
We were children then.
We are allowed to make mistakes, to figure out who we wish to be.
If you will allow Aelin the gift of your acceptance---"

"I don't care if he was as arrogant and vain as Aelin, I don't \emph{care} if he was enslaved to a demon that took his mind.
I look at him and see my family \emph{butchered}, see those tracks to the river, and hear Quinn tell me that Aelin was drowned and \emph{dead}."
His breathing was uneven, and his throat burned, but he ignored it.

Lysandra said, "Aelin forgave him.
Aelin never once held it against him."

Aedion snarled at her.
Lysandra snarled right back and held his stare with the face not trained or built for bedrooms, but the true one beneath---wild and unbroken and indomitable.
No matter what body she wore, she was the Staghorns given form, the heart of Oakwald.

Aedion said hoarsely, "I'll try."

"Try harder.
Try better."

Aedion braced his palm against the wall again and leaned in to glower in her face.
She did not yield an inch.
"There is an order and rank in our court, \emph{lady}, and last I checked, you were \emph{not} number three.
You don't give me commands."

"This isn't a battlefield," Lysandra hissed.
"Any ranks are formalities.
And the last \emph{I} checked\ldots" She poked his chest, right between his pectorals, and he could have sworn the tip of a claw pierced the skin beneath his clothes.
"\emph{You} weren't pathetic enough to enforce rank to hide from being in the wrong."

His blood sparked and thrummed.
Aedion found himself taking in the sensuous curves of her mouth, now pressed thin with anger.

The hot temper in her eyes faded, and as she retracted her finger as if she'd been burned, he froze at the panic that filled her features instead.
Shit.
\emph{Shit}---

Lysandra backed away a step, too casual to be anything but a calculated move.
But Aedion tried---for her sake, he tried to stop thinking about her mouth ---

"You truly want to meet your father?"
she asked calmly.
Too calmly.

He nodded, swallowing hard.
Too soon---she wouldn't want a man's touch for a long time.
Maybe forever.
And he'd be damned if he pushed her into it before she wanted to.
And gods above, if Lysandra ever looked at \emph{any} man with interest like that\ldots he'd be glad for her.
Glad she was choosing for herself, even if it wasn't him she picked---

"I\ldots" Aedion swallowed, forcing himself to remember what she'd asked.
His father.
Right.
"Did he want to see me?"
was all he could think to ask.

She cocked her head to the side, the movement so feline he wondered if she was spending too much time in that ghost leopard's fur.
"He nearly bit Aelin's head off when she refused to tell him where and who you are."
Ice filled his veins.
If his father had been rude to her---"But I got the sense," Lysandra quickly clarified as he tensed, "that he is the sort of male who would respect your wishes if you chose not to see him.
Yet in this small town, with the company we're keeping 
that might prove impossible."

"Did you also get the sense that it could persuade him to help us?
Knowing me?"

"I don't think Aelin would ever ask that of you," Lysandra said, laying a hand on the arm still braced beside her head.

"What do I even say to him?"
Aedion murmured.
"I've heard so many stories about him---the Lion of Doranelle.
He's a gods-damned white knight.
I don't think he'll approve of a son most people call Adarlan's Whore."
She clicked her tongue, but Aedion pinned her with a look.
"What would you do?"

"I can't answer that question.
My own father\ldots" She shook her head.
He knew about that---the shifter-father who had either abandoned her mother or not even known she was pregnant.
And then the mother who had thrown Lysandra into the street when she discovered her heritage.
"Aedion, what do \emph{you} want to do?
Not for us, not for Terrasen, but for \emph{you}."

He bowed his head a bit, glancing sidelong at the quiet street again.
"My whole life has been\ldots not about what I want.
I don't know how to choose those things."

No, from the moment he'd arrived in Terrasen at age five, he'd been trained ---his path chosen.
And when Terrasen had burned beneath Adarlan's torches, another hand had gripped the leash of his fate.
Even now, with war upon them\ldots Had he truly never wanted something for himself?
All he'd wanted had been the blood oath.
And Aelin had given that away to Rowan.
He didn't resent her for it, not anymore, but  He had not realized he had asked for so little.

Lysandra said quietly, "I know.
I know what that feels like."

He lifted his head, finding her green eyes again in the darkness.
He sometimes wished Arobynn Hamel were still alive---just so he could kill the assassin-king himself.

"Tomorrow morning," he murmured.
"Will you come with me?
To see him."

She was quiet for a moment before she said, "You really want me to go with you?"

He did.
He couldn't explain why, but he wanted her there.
She got under his skin so damn easily, but\ldots Lysandra steadied him.
Perhaps because she was something new.
Something he had not encountered, had not filled with hope and pain and wishes.
Not too many of them, at least.

"If you wouldn't mind\ldots yes.
I want you there."

She didn't respond.
He opened his mouth, but steps sounded.

Light.
Too casual.

They ducked deeper into the shadows of the alley, its dead-end wall looming behind them.
If this went poorly\ldots{}

If it went poorly, he had a shape-shifter capable of shredding apart droves of men at his side.
Aedion flashed Lysandra a grin as he leaned over her once more, his nose within grazing distance of her neck.

Those steps neared, and Lysandra loosed a breath, her body going pliant.

From the shadows of his hood, he monitored the alley ahead, the shadows and shafts of moonlight, bracing himself.
They'd picked the dead-end alley for a reason.

The girl realized her mistake a step too late.
"Oh."

Aedion looked up, his own features hidden within his hood, as Lysandra purred to the young woman who perfectly matched Rowan's description of Rolfe's barmaid, "I'll be done in two minutes, if you want to wait your turn."

Color stained the girl's cheeks, but she gave them a flinty look, scanning them from head to toe.
"Wrong turn," she said.

"You sure?"
Lysandra crooned.
"A bit late in the evening for a stroll."

Rolfe's barmaid fixed them with that sharp stare and sauntered back down the street.

They waited.
A minute.
Five.
Ten.
No others came.

Aedion at last pulled away, Lysandra now watching the alley entrance.
The shifter wound an auburn curl around her finger.
"She seems an unlikely thief."

"Some would say similar things about you and Aelin."
Lysandra hummed in agreement.
Aedion mused, "Perhaps she was just a scout---Rolfe's eyes."

"Why bother?
Why not just come take the thing?"

Aedion glanced again at the amulet that disappeared beneath Lysandra's bodice.
"Maybe she thought she was looking for something else."

Lysandra, wisely, didn't fish the Amulet of Orynth out from her dress.
But his words hung between them as they carefully picked their way back to the Ocean Rose.
