
\chapter{31}

Well, on the one hand, at least Rolfe's map worked.

It had been Rowan's idea, actually.
And she might have felt slightly guilty for letting Aedion and Lysandra believe the Pirate Lord had only gone after the Amulet of Orynth, but\ldots at least they now knew his unholy map functioned.
And that the Pirate Lord was indeed living in terror of the Valg returning to this harbor.

She wondered what Rolfe made of it---what his map had shown him of the Wyrdkey.
If it revealed the difference between it and the Wyrdstone rings his men had been enslaved with.
Whatever the reason, the Pirate Lord had sent his barmaid to scout for any hint of the Valg, not realizing Rowan had selected that dead-end alley to ensure \emph{only}
someone sent by Rolfe would venture so far down it.
And since Aelin had no doubt whatsoever that Aedion and Lysandra had snuck through the streets unnoticed\ldots Well, at least that part of her evening had gone right.

As for the rest of it\ldots It was just past midnight when Aelin wondered how the hell she and Rowan would ever go back to normalcy if they survived this war.
If there'd be a day when it wasn't easy to leap over rooftops as if they were stones on a stream, to break into someone's room and hold a blade to the occupant's throat.

They did the first two within the span of fifteen minutes.

And as they found Gavriel and Fenrys waiting for them in their shared room in the Sea Dragon inn, Aelin supposed she needn't bother with the third.
Even if both she and Rowan kept their hands within casual reach of their daggers while they leaned against the wall beside the now-shut window.
They'd unlocked it with Rowan's wind---only to have a candle ignite the moment the window swung away.
Revealing two stone-faced Fae warriors, both dressed and armed.

"You could have used the door," Fenrys said, arms crossed---a bit too casually.

"Why bother when a dramatic entrance is so much more fun?"
Aelin countered.

Fenrys's beautiful face twitched with amusement that didn't quite meet his onyx eyes.
"What a shame it'd be for you to miss out on any of that."
She grinned at him.
He grinned at her.

She supposed both of their smiles were less of a grin and more 
teethexposing.

She snorted.
"You two look like you enjoyed your summer in Doranelle.
How's sweet Aunt Maeve?"

Gavriel's tattooed hands closed into loose fists.
"You deny me the right to see my son and yet you barge into our room in the dead of the night to demand we divulge information about our blood-sworn queen."

"One, \emph{I} did not deny you anything, kitty-cat."

Fenrys let out what might have been a choking sound.

"It's your son's decision, not mine.
I don't have enough time to oversee or really care."
Lies.

"It must be hard to find the time to care at all," Fenrys cut in, "when you are facing a mortal life span."
A sly, cutting glance at Rowan.
"Or is she due to Settle soon?"

Oh, he was a bastard.
A bitter, hard-edged bastard, the laughing side of the coin to Lorcan's sullen brooding.
Maeve certainly had a type.

Rowan's face yielded nothing.
"The matter of Aelin's Settling is none of your concern."

"Isn't it?
Knowing if she's immortal changes things.
Many things."
"Fenrys," Gavriel warned.

She knew enough about it---the transition pureblooded Fae, and some demiFae, went through once their bodies locked into immortal youth.
It was a rough process, their bodies and magic needing months to adjust to the sudden freezing and reordering of their aging process.
Some Fae had no control over their power ---some lost it entirely during the time it took to Settle.

And demi-Fae\ldots some might be longer-lived, some might have the true immortal gift given to them.
Like Lorcan.
And possibly Aedion.
They'd find out in the next few years if he'd take after his mother  or the male sitting across the room from her.
If they survived the war.

And as for her\ldots She did not let herself think about it.
Precisely for the reasons Fenrys claimed.
"I don't see what it would change," she said to him.
"There's already one immortal queen.
Surely a second would be nothing new."

"And will you hand out blood oaths to males who catch your eye, or will it just be Whitethorn at your side?"

She could feel the aggression beginning to pour off Rowan, and she was half tempted to grumble, \emph{They're your friends.
Deal with them.}
But he kept quiet, containing himself, as she said, "You didn't seem nearly so interested in me that day at Mistward."

"Trust me, he was," Gavriel muttered.

Aelin lifted a brow.
But Fenrys was giving Gavriel a look that promised a slow death.

Rowan explained, "Fenrys was the one who\ldots volunteered to train you when Maeve told us you'd come to Wendlyn."

Was he, now.
Interesting.
"Why?"

Rowan opened his mouth, but Fenrys cut him off.
"It would have gotten me out of Doranelle.
And we likely would have had far more fun, anyway.
I know what a bastard Whitethorn can be when it comes to training."

"You two would have stayed on that rooftop in Varese and drunk yourselves to death," Rowan said.
"And as for training\ldots You're alive today because of that training, boyo."

Fenrys rolled his eyes.
Younger, she realized.
Still old by human standards, but Fenrys was and felt younger.
Wilder.

"Speaking of Varese," Aelin said with cool amusement.
"And Doranelle\ldots"

"I will warn you," Gavriel said quietly, "that there is little we know regarding Maeve's plans, and less still we can reveal with the blood oath's constraints."

"How does she do it?"
Aelin asked baldly.
"With Rowan, it's not  Every order I give him, even casual ones, are his to decide what to do with.
Only when I actively pull on the bond can I get him to  yield.
And even then it's more of a suggestion."

"It is different with her," Gavriel said softly.
"Dependent on the ruler it is sworn to.
You two took the oath to each other with love in your hearts.
You had no desire to own or rule him."

Aelin tried not to flinch at the truth of that word---\emph{love}.
That day\ldots when Rowan had looked into her eyes as he drank her blood  she'd started to realize what it was.
That the feeling that passed between them, so powerful there was no language to describe it  It was not mere friendship, but something born of and strengthened by it.

"Maeve," Fenrys added, "offers it with those things in mind.
And so the bond itself is born of obedience to her---no matter what.
She orders, we submit.
For whatever she wishes."
Shadows danced in those eyes, and Aelin's fingers curled into fists.
That Maeve felt the need to force any of them into her bed\ldots Rowan had told her their familial bloodline, while distant, was still close enough that it had kept Maeve from seeking him out, but the others\ldots{}

"So you couldn't break it on your own."

"Never---if we did so, the magic that binds us to her would kill us in the process," Fenrys said.
She wondered if he'd tried.
How many times.
He angled his head to the side, the movement purely lupine.
"Why are you asking this?"

\emph{Because if Maeve somehow can claim ownership over Aedion's life thanks to his bloodline, I can't do a damn thing to help him}.

Aelin shrugged.
"Because you sidetracked me."
She gave him a little smile that she knew drove Rowan and Aedion insane, and---yes.
It seemed it was a surefire way to piss off \emph{any} Fae male, because ire flashed across Fenrys's stupidly perfect face.

She picked at her nails.
"I know you two are old and up past your bedtime, so I'll keep this quick: Maeve's armada sails for Eyllwe.
We are now allies.
But my path might take me into direct conflict with that fleet, maybe with her, whether I desire it or not."
Rowan had tensed slightly, and she wished it wouldn't look weak to glance at him, try to read whatever had sparked the reaction.

Fenrys looked to Rowan---as if it were habit.
"I think the bigger concern is whether Maeve sails to join Erawan.
She could go either way."

"Our---her network of information is too vast," Rowan countered.
"There's not a chance she doesn't already know the empire's fleet is camped out in the Gulf of Oro."

Aelin wondered how often her Fae Prince had to silently correct himself about what terms to use.
\emph{Our}, \emph{her}  Wondered if he ever missed the two males frowning at them.

"Maeve could be going to intercept it," Gavriel mused.
"Vanquish Morath's fleet as proof of her intentions to assist you, then 
play it into whatever agenda she has beyond that."

Aelin clicked her tongue.
"Even with Fae soldiers on those ships, she couldn't be stupid enough to risk such catastrophic losses just to get into my good graces again."
No matter that Aelin knew she'd accept any offer of aid from Maeve, risk or no.

Fenrys's edged smile flashed.
"Oh, the losses of Fae lives would be of little concern to her.
It likely just increases her excitement about it."

"Careful," Gavriel said.
Gods, he nearly sounded identical to Aedion with that tone.

Aelin went on, "Regardless.
You two know what we face with Erawan; you know what Maeve wanted from me in Doranelle.
What Lorcan left to do."
Their faces had resumed their warrior-calm and didn't so much as flicker as she asked, "Did Maeve give you an order to take those keys from Lorcan as well?
And the ring?
Or is it just his life you'll be claiming?"

"If we say she gave us the order to take everything," Fenrys drawled, bracing his hands behind him on the bed, "will you kill us, Heir of Fire?"

"It'll depend on how useful you prove to be as an ally," Aelin simply said.

The weight hanging between her breasts beneath her shirt rumbled as if in answer.

"Rolfe has weapons," Gavriel said quietly.
"Or will be receiving them."

Aelin lifted a brow.
"And will hearing about it cost me?"

Gavriel wasn't stupid enough to ask for Aedion.
The warrior just said, "They're called firelances.
Alchemists in the southern continent developed them for their own territory wars.
More than that, we don't know, but the device can be wielded by one man---to devastating effect."

And with magic-users still so new to their returned gifts, or mostly dead thanks to Adarlan\ldots{}

She would not be alone.
Not the only fire-wielder on that battlefield.

But only if Rolfe's armada became hers.
If he did what she was carefully, so carefully, guiding him to do.
Reaching out to the southern continent could take months she didn't have.
But if Rolfe had already ordered a supply\ldots Aelin nodded at Rowan once more, and they pushed off the wall.

"That's it?"
Fenrys demanded.
"Do we get to know what you plan to do with this information, or are we just your lackeys, too?"

"You don't trust me; I don't trust you," Aelin said.
"It's easier that way."
She nudged open the window with her elbow.
"But thank you for the information."

Fenrys's brows rose high enough that she wondered if Maeve had uttered those words in his hearing.
And she honestly wished she'd melted her aunt that day in Doranelle.

She and Rowan leaped and climbed the rooftops of Skull's Bay, the ancient shingles still slick from the day's rain.

When the Ocean Rose glittered like a pale jewel a block ahead, Aelin paused in the shadows beside a chimney and murmured, "There is no room for error."

Rowan laid a hand on her shoulder.
"I know.
We'll make it count."

Her eyes burned.
"We're playing a game against two monarchs who have ruled and schemed longer than most kingdoms have existed."
And even for her, the odds of outsmarting and outmaneuvering them\ldots "Seeing the cadre, how Maeve contains them\ldots She came so close to separating us this spring.
So close."

Rowan traced his thumb over her mouth.
"Even if Maeve had kept me enslaved, I would have fought her.
Every day, every hour, every breath."
He kissed her softly and said onto her lips, "I would have fought for the rest of my life to find a way to return to you again.
I knew it the moment you emerged from the Valg's darkness and smiled at me through your flames."

She swallowed the tightness in her throat and raised a brow.
"You were willing to do that before all this?
So few benefits back then."

Amusement and something deeper danced in his eyes.
"What I felt for you in Doranelle and what I feel for you now are the same.
I just didn't think I'd ever get the chance to act on it."

She knew why she needed to hear it---he knew, too.
Darrow's and Rolfe's words danced around in her head, an endless chorus of bitter threats.
But Aelin only smirked at him.
"Then act away, Prince."

Rowan let out a low laugh, and said nothing else as he claimed her mouth, nudging her back against the crumbling chimney.
She opened for him, and his tongue swept in, thorough, lazy.

Oh, gods---this.
This was what drove her out of her mind---this fire between them.

They could burn the entire world to ashes with it.
He was hers and she was his, and they had found each other across centuries of bloodshed and loss, across oceans and kingdoms and war.

Rowan pulled back, breathing heavily, and whispered against her lips, "Even when you're in another kingdom, Aelin, your fire is still in my blood, my mouth."
She let out a soft moan, arching into him as his hand grazed her backside, not caring if anyone spotted them in the streets below.

"You said you wouldn't take me against a tree the first time," she breathed, sliding her hands up his arms, across the breadth of his sculpted chest.
"What about a chimney?"

Rowan huffed another laugh and nipped at her bottom lip.
"Remind me again why I missed you."

Aelin chuckled, but the sound was quickly silenced as Rowan claimed her mouth again and kissed her deeply in the moonlight.
