
\chapter{38}

The meeting with Rolfe once the harbor was again safe was quick. Frank.

And Aelin knew if she didn't get the hell out of this city for an hour or two, she might very well explode again.

\emph{Every key has a lock}, Deanna had said, a little reminder of Brannon's order. Using \emph{her} voice. And had called her that title
 that title that struck some chord of horror and understanding in her, so deep she was still working out what it meant. \emph{The Queen Who Was Promised}.

Aelin stormed onto a spit of beach on the far side of the island, having run here, needing to get her blood roaring, needing it to silence the thoughts in her head. Behind her, Rowan's steps were quiet as death.

Only the two of them had been in that meeting with Rolfe. Bloodied, soaked, the Pirate Lord had met them in the main room of his inn, the name of it now a permanent reminder of the ship she'd wrecked. He demanded, "What the \emph{hell} happened?"

And she had been so tired, so pissed off and full of disgust and despair, that it had been nearly impossible to muster the swagger. "When you are blessed by

Mala, you find that sometimes your control can slip."

"\emph{Slip?} I don't know what you fools were talking about down there, but from where I was standing, it looked like you lost your gods-damned mind and were about to fire on \emph{my} town."

Rowan, leaning against the edge of a nearby table, explained, "Magic is a living thing. When you are that deep in it, remembering yourself, your purpose, is an effort. That my queen did so before it was too late is a feat in itself."

Rolfe wasn't impressed. "It looks to me like you were a little girl playing with power too big for you to handle, and only your prince jumping in your path made you decide \emph{not} to slaughter my innocent people."

Aelin closed her eyes for a heartbeat, the image of Rowan leaping in front of that fist of moonfire flashing before her. When she opened her eyes, she let the crackling assuredness fade into something frozen and hard. "It looks to \emph{me}," she said, "like the Pirate Lord of Skull's Bay and long-lost Mycenian heir has just allied with a young queen so powerful she can decimate \emph{cities} if she wishes. It looks to me like you have made yourself untouchable with that alliance, and any fool who seeks to harm you, usurp you, will have \emph{me} to contend with. So I suggest you salvage what you can of your precious ship, mourn the dozen men I take full responsibility for losing and whose families I will compensate accordingly, and shut your rutting mouth."

She turned toward the door, exhaustion and rage nipping at her bones.

Rolfe said to her back, "Do you want to know what the cost of this map was?"

She halted, Rowan glancing between them, face unreadable.

She smirked over her shoulder. "Your soul?"

Rolfe let out a hoarse laugh. "Yes---in a way. When I was sixteen, I was barely more than a slave on one of these festering ships, my Mycenian heritage just a one-way ticket to a beating." He laid a tattooed hand on the \emph{Thresher}'s lettering. "Every coin I earned came back here---to my mother and sister. And one day the ship I was on got caught in a storm. The captain was a haughty bastard, refused to find safe harbor, and the ship was destroyed. Most of the crew drowned. I drifted for a day, washed up on an island at the edge of the archipelago, and awoke to find a man staring down at me. I asked if I was dead, and he laughed and inquired what I wanted for myself. I was so delirious I told him that I wanted to be captain---I wanted to be Pirate Lord of Skull's Bay and make the arrogant fools like the captain who had killed my friends \emph{bow} before me. I thought I was dreaming when he explained that if he were to grant me the skills to do it, there would be a price. What I valued most in the world, he would have. I said I'd pay it---whatever it was. I had no belongings, no wealth, no people anyway. A few coppers would be nothing. He smiled before he vanished into sea mist. I awoke with the ink on my hands." Aelin waited.

Rolfe shrugged. "I made it back here, finding friendly ships using the map the stranger had inked there. A gift from a god---or so I thought. But it wasn't until I saw the black sheets over my cottage's windows that I began to worry. And it wasn't until I learned that my mother and sister had used their little money to hire a skiff to go looking for me---and that the skiff had returned to harbor but they had not---that I realized the price I'd handed over. That's what the sea claimed. What
\emph{he} claimed. And it made me soulless enough that I loosed myself upon this city, this archipelago." Rolfe's green eyes were as merciless as the Sea God who had gifted and damned him. "That was the price of my power.

What shall yours be, Aelin Galathynius?"

She didn't reply to him before storming out. Though Deanna's voice had echoed in her mind.

\emph{The Queen Who Was Promised}.

Now, standing on that empty beach and monitoring the glimmering expanse of the sea as the last of the sun vanished, Rowan said beside her, "Did you willingly use the key?"

No hint of judgment, of condemnation. Just curiosity---and concern.

Aelin rasped, "No. I don't know what happened. One minute it was us
 then \emph{she} came." She rubbed at her chest, avoiding the touch of the golden chain against it. Her throat tightened as she took in that spot on his own chest, right between his pectorals. Where her fist had been aimed.

"How could you?" she breathed, a tremor running through her. "How could you put yourself in front of me like that?"

Rowan took a step closer but no farther. The crashing of waves and cries of gulls heading home for the night filled the space between them. "If you had destroyed that city, it would have destroyed \emph{you}, and any sort of hope at an alliance."

Shaking began in her hands, spreading to her arms, her chest, her knees. Flame and ash curled on her tongue. "If I had killed you," she hissed, but choked on the words, unable to finish the thought, the idea of it. Her throat burned, and she squeezed her eyes shut, warm flames rippling around her. "I thought I'd found the bottom of my power," she admitted, magic already overflowing, so soon, too soon after she'd emptied herself. "I thought what I found in Wendlyn was the bottom. I had no idea it was all just an  antechamber."

Aelin lifted her hands, opening her eyes to find her fingers wreathed in flame. Darkness spread over the world. Through the veil of gold and blue and red, she looked at her prince. She raised her burning hands helplessly between them. "\emph{She stole me}---she \emph{took} me. And I could feel her---feel her consciousness. It was like she was a spider, waiting in a web for \emph{decades}, knowing I'd one day be strong and stupid enough to use my magic and the key together. I might as well have rung the dinner bell." Her fire burned hotter, brighter, and she let it build and rise and flicker.

A wry, bitter smile. "It seems she wants us to make finding this Lock a priority, if you were given the message \emph{twice.}"

Indeed. "Isn't it enough to contend with Erawan and Maeve, to do the bidding of Brannon and Elena? Now I have to face the gods breathing down my neck about it as well?"

"Perhaps it was a warning---perhaps Deanna wished to show you how a notso-friendly god might use you if you're not careful."

"She enjoyed every rutting second of it. She \emph{wanted} to see what my power might do, what she could do with my body, with the key." Her flames burned hotter, shredding through her clothes until they were ash, until she was naked and clothed in only her own fire. "And what she called me---the Queen Who Was Promised. Promised when? To whom? To do what? I've never heard that phrase in my life, not even before Terrasen fell." "We'll figure it out." And that was that.

"How can you be so  \emph{fine} with this?" Embers sprayed from her like a swarm of fireflies.

Rowan's mouth tightened. "Trust me, Aelin, I am anything but
\emph{fine} with the idea that you are fair game to those immortal bastards. I am anything but \emph{fine} with the idea that you could be taken from me like that. If I could, I would hunt Deanna down and pay her back for it."

"She's the Goddess of the Hunt. You might be at a disadvantage." Her flames eased a bit.

A half smile. "She's a haughty immortal. She's bound to slip up. And besides  " A shrug. "I have her sister on my side." He angled his head, studying her fire, her face. "Perhaps that's why Mala appeared to me that morning, why she gave me her blessing."

"Because you're the only one arrogant and insane enough to hunt a goddess?"

Rowan shucked off his boots, tossing them onto the dry sand behind him. "Because I'm the only one arrogant and insane enough to ask Mala Fire-Bringer to let me stay with the woman I love."

Her flames turned to pure gold at the words---at that word. But she said, "Perhaps you're just the only one arrogant and insane enough to love \emph{me}."

That unreadable mask cracked. "This new depth to your power, Aelin, changes nothing. What Deanna did changes nothing. You are still young;
your power is still growing. And if this new well of power gives us even the slightest advantage against Erawan, then thank the rutting darkness for it. But you and I will learn to manage your power together. You do not face this alone; you do not decide that you are unlovable because you have powers that can save \emph{and} destroy. If you start to resent that power\ldots" He shook his head. "I do not think we will win this war if you start down that road."

Aelin strode into the lapping waves and sank to her knees in the surf, steam rising around her in great plumes. "Sometimes," she admitted over the hissing water, "I wish someone else could fight this war."

Rowan stepped into the bubbling surf, his magic shielding against the heat of her. "Ah," he said, kneeling beside her as she still gazed out over the dark sea, "but who else would be able to get under Erawan's skin? Never underestimate the power of that insufferable swagger."

She chuckled, starting to feel the cool kiss of the water on her naked body. "As far as memory serves, Prince, it was that insufferable swagger that won your cranky, immortal heart."

Rowan leaned into the thin veil of flame now melting into night-sweet air and nipped her lower lip. A sharp, wicked bite. "There's my Fireheart."

Aelin let him pivot her in the surf and sand to face him fully, let him slide his mouth along her jaw, the curve of her cheekbone, the point of her Fae ear."These," he said, nibbling at her earlobe, "have been tempting me for months." His tongue traced the delicate tip, and her back arched. The strong hands at her hips tightened. "Sometimes, you'd be sleeping beside me at Mistward, and it'd take all my concentration
\emph{not} to lean over and bite them. Bite you all over."

"Hmmm," she said, tipping back her head to grant him access to her neck.

Rowan obliged her silent demand, pressing kisses and soft, growling nips to her throat. "I've never taken a woman on a beach," he purred against her skin, sucking gently on the space between her neck and shoulder. "And look at that--- we're far from any sort of 
collateral." One hand drifted from her hip to caress the scars on her back, the other sliding to cup her backside, drawing her fully against him.

Aelin spread her hands over his chest, tugging his white shirt over his head. Warm waves crashed against them, but Rowan held her fast---unmovable, unshakable.

Aelin remembered herself enough to say, "Someone might come looking for us."

Rowan huffed a laugh against her neck. "Something tells me," he said, his breath skittering along her skin, "you might not mind if we were discovered. If someone saw how thoroughly I plan to worship you."

She felt the words dangling there, felt herself dangling there, off the edge of the cliff. She swallowed. But Rowan had caught her each time she had fallen--- first, when she had plummeted into that abyss of despair and grief; second, when that castle had shattered and she had plunged to the earth. And now this time, this third time  She was not afraid.

Aelin met Rowan's stare and said clearly and baldly and without a speckle of doubt, "I love you. I am in love with you, Rowan. I have been for a while. And I know there are limits to what you can give me, and I know you might need time

---"

His lips crushed into hers, and he said onto her mouth, dropping words more precious than rubies and emeralds and sapphires into her heart, her soul, "I love you. There is no limit to what I can give to you, no time I need. Even when this world is a forgotten whisper of dust between the stars, I will love you."

Aelin didn't know when she started crying, when her body began shaking with the force of it. She had never said such words---to anyone. Never let herself be that vulnerable, never felt this burning and unending
\emph{thing}, so consuming she might die from the force of it.

Rowan pulled back, wiping away her tears with his thumbs, one after another. He said softly, barely audible over the crashing waves around them,

"Fireheart."

She sniffed back tears. "Buzzard."

He roared a laugh and she let him lay her down on the sand with a gentleness near reverence. His sculpted chest heaved slightly as he ran an eye over her bare body. "You  are so beautiful."

She knew he didn't just mean the skin and curves and bones.

But Aelin still smiled, humming. "I know," she said, lifting her arms above her head, setting the Amulet of Orynth onto a safe, high part of the beach. Her fingers dug into the soft sand as she arched her back in a slow stretch.

Rowan tracked every movement, every flicker of muscle and skin. When his gaze lingered on her breasts, gleaming with seawater, his expression turned ravenous.

Then his gaze slid lower. Lower. And when it lingered on the apex of her thighs and his eyes glazed, Aelin said to him, "Are you going to stand there gawking all night?"

Rowan's mouth parted slightly, his breathing shallow, his body already showing her precisely where this was going to end.

A phantom wind hissed through the palms, whispered over the sand. Her magic tingled as she felt, more than saw, Rowan's shield fall into place around them. She sent her own power tracing over it, knocking and tapping at the shield in sparks of flame.

Rowan's canines gleamed. "Nothing is getting past that shield. And nothing is going to hurt me, either."

Something tight in her chest eased. "Is it that different? With someone like me."

"I don't know," Rowan admitted. Again, his eyes slid along her body, as if he could see through skin to her burning heart beneath. "I've never been with  an equal. I've never allowed myself to be that unleashed."

For every bit of power she threw at him, he'd throw back at her. She braced herself on her elbows, lifting her mouth to the new scar on his shoulder, the wound small and jagged---as broad as an arrowhead. She kissed it once, twice.

Rowan's body was so tense above hers she thought his muscles would snap. But his hands were gentle as they drifted to her back, stroking her scars and the tattoos he'd inked over them.

The waves tickled and caressed her, and he made to settle over her, but she lifted a hand to his chest---halting him dead. She smiled against his mouth. "If we're equals, then I don't understand why you're still half clothed."

She didn't give him the chance to explain as she traced her tongue over the seam of his lips, as her fingers unlatched the buckle of his worn sword belt. She wasn't sure he was breathing.

And just to see what he'd do, she palmed him through his pants.

Rowan barked a curse.

She laughed quietly, kissed his newest scar again, and dragged a finger down lazily, indolently, holding his gaze for every single inch she touched.

And when Aelin laid her palm flat on him again, she said, "You are mine."

Rowan's breathing started again, jagged and savage as the waves breaking around them. She flicked open the top button of his pants. "I'm yours," he ground out.

Another button popped free. "And you love me," she said. Not a question.

"To whatever end," he breathed.

She popped the third and final button free, and he let go of her to toss his pants into the sand nearby, taking his undershorts with them. Her mouth went dry as she took in the sight of him.

Rowan had been bred and honed for battle, and every inch of him was pureblooded warrior.

He was the most beautiful thing she'd ever seen. Hers---he was
\emph{hers}, and---

"You are mine," Rowan breathed, and she felt the claiming in her bones, her soul.

"I am yours," she answered.

"And you love me." Such hope and quiet joy in his eyes, beneath all that fierceness.

"To whatever end." For too long---for too long had he been alone and wandering. No longer.

Rowan kissed her again. Slow. Soft. A hand slid up the plane of her torso while he lowered himself over her, his hips nestling against hers. She gasped a bit at the touch, gasped a bit more as his knuckle grazed the heavy, aching underside of her breast. As he leaned down to kiss the other.

His teeth grazed over her nipple, and her eyes drifted closed, a moan slipping out of her.

Oh, gods. Oh, burning, rutting gods. Rowan knew what he was doing; he really gods-damned did.

His tongue flicked against her nipple, and her head tipped back, her fingers digging into his shoulders, urging him to take more, take
\emph{harder}.

Rowan growled his approval, her breast still in his mouth, on his tongue, his hand making lazy strokes from her ribs down her waist, down her thighs, then back up. She arched in silent demand---

A phantom touch, like the northern wind given form, flicked over her bare breast.

Aelin burst into flames.

Rowan laughed darkly at the reds and golds and blues that erupted around them, illumining the palms that towered over the edge of the beach, the waves breaking behind him. She might have panicked, might have been mortified, had he not lifted his mouth to hers, had those phantom hands of ice-kissed wind not kept working her breasts, had his own hand not continued stroking, closer and closer to where she needed him. "You're magnificent," he murmured onto her lips, his tongue sliding into her mouth.

The hardness of him pushed against her, and she bucked her hips, needing to grind herself against him, to do anything to ease the building ache between her legs. Rowan groaned, and she wondered if there was any other male in the world who would be so naked and prone with a woman on fire, who would not look at those flames with any ounce of fear.

She slid her hand between them, and when she closed her fingers around him, marveling at the velvet-wrapped steel, Rowan groaned again, pushing into her hand. She pulled her mouth from his, staring into those pine-green eyes as she slid her hand along him. He lowered his head---not to kiss her, but to watch where she stroked him.

A roaring wind full of ice and snow blasted around them. And it was her turn to huff a laugh. But Rowan gripped her wrist, drawing her hand away. She opened her mouth in protest, wanting to touch more,
\emph{taste} more. "Let me," Rowan growled onto the sea-slick skin between her breasts. "Let me touch you." His voice trembled enough that Aelin lifted his chin with her thumb and forefinger.

A flicker of fear and relief shone beneath the glazed lust. As if doing this, touching her, was as much to remind him that she had made it today, that she was safe, as it was to pleasure her. She leaned up, brushing her mouth against his. "Do your worst, Prince."

Rowan's smile was nothing short of wicked as he pulled away to run a broad hand from her throat down to the juncture of her thighs. She shuddered at the sheer possession in the touch, her breath coming in tight pants as he gripped either thigh and spread her legs, baring her fully for him.

Another wave crashed, parting around them, the cool water like a thousand kisses along her skin. Rowan kissed her navel, then her hip.

Aelin couldn't take her eyes from his silver hair shining with salt water and moonlight, from the hands holding her wide for him as his head dipped between her legs.

And as Rowan tasted her on that beach, as he laughed against her slick skin while her hoarse cries of his name shattered across palm trees and sand and water, Aelin let go of all pretense at reason.

She moved, hips undulating, begging him to \emph{go, go,} go. So Rowan did, sliding a finger into her as his tongue flicked that one spot, and oh, gods, she was going to explode into starfire---

"Aelin," he growled, her name a plea.

"Please," she moaned. \emph{"Please."}

The word was his undoing. Rowan rose over her again, and she let out a sound that might have been a whimper, might have been his name.

Then Rowan had a hand braced in the sand beside her head, fingers twining in her hair, while the other guided himself into her. At the first nudge of him, she forgot her own name. And as he slid in with gentle, rolling thrusts, filling her inch by inch, she forgot that she was queen and that she had a separate body and a kingdom and a world to look after.

When Rowan was seated deep in her, trembling with restraint as he let her adjust, she lifted her burning hands to his face, wind and ice tumbling and roaring around them, dancing across the waves with ribbons of flame. There were no words in his eyes; none in hers, either.

Words did not do it justice. Not in any language, in any world.

He leaned in, claiming her mouth as he began to move, and they let go entirely.

She might have been crying, or it might have been his tears on her face, turning to steam amid her flames.

She dragged her hands down his powerful, muscled back, over scars from battles and terrors long since past. And as his thrusts turned deeper, she dug in her fingers, dragging her nails across his back, claiming him, marking him. His hips slammed home at the blood she drew, and she arched, baring her throat to him. For him---only him.

Rowan's magic went wild, though his mouth on her neck was so careful, even as his canines dragged along her skin. And at the touch of those lethal teeth against her, the death that hovered nearby and the hands that would always be gentle with her, always love her---

Release blasted through her like wildfire. And though she could not remember her name, she remembered Rowan's as she cried it while he kept moving, wringing every last ounce of pleasure from her, fire searing the sand around them to glass.

Rowan's own release barreled through him at the sight of it, and he groaned her name so that she remembered it at last, lightning joining wind and ice over the water.

Aelin held him through it, sending the fire-opal of her magic to twine with his power. On and on, as he spilled himself in her, lightning and flame danced on the sea.

The lightning continued to strike, silent and lovely, even after he stilled. The sounds of the world came pouring back in, his breathing as ragged as the hiss of the crashing waves while he brushed lazy kisses to her temple, her nose, her mouth. Aelin drew her eyes away from the beauty of their magic, the beauty of \emph{them}, and found his face to be the most beautiful of all.

She was trembling---and so was Rowan as he remained in her. He buried his face in the crook of her neck and shoulder, his uneven breath warming her skin. "I never  ," he tried, voice hoarse. "I didn't know it could be\ldots"

She ran her fingers down his scarred back, over and over. "I know," she breathed. "I know."

Already, she wanted more, already she was calculating how long she'd have

to wait. "You once told me that you don't bite the females of other males." Rowan stiffened a bit. But she went on coyly, "Does that mean
 you'll bite your own female, then?"

Understanding flashed in those green eyes as he raised his head from her neck to study the spot where those canines had once pierced her skin. "That was the first time I really lost control around you, you know. I wanted to chuck you off a cliff, yet I bit you before I knew what I was doing. I think my body knew, my magic knew. And you tasted\ldots" Rowan loosed a jagged breath. "So good. I hated you for it. I couldn't stop thinking about it. I'd wake up at night with that taste on my tongue---wake up thinking about your foul, beautiful mouth." He traced his thumb over her lips. "You don't want to know the depraved things I've thought about this mouth."

"Hmmm, likewise, but you didn't answer my question," Aelin said, even as her toes curled in the wet sand and warm water.

"Yes," Rowan said thickly. "Some males enjoy doing it. To mark territory, for pleasure\ldots"

"Do females bite males?"

He began to harden again inside her as the question lingered. Oh, gods---Fae lovers. Everyone should be so damn lucky to have one. Rowan rasped, "Do you \emph{want} to bite me?"

Aelin eyed his throat, his glorious body, and the face she had once so fiercely hated. And she wondered if it were possible to love someone enough to die from it. If it were possible to love someone enough that time and distance and death

were of no concern. "Am I limited to your neck?"

Rowan's eyes flared, and his answering thrust was answer enough.

They moved together, undulating like the sea before them, and when Rowan roared her name again into the star-flecked black, Aelin hoped the gods themselves heard it and knew their days were now numbered.
