
\chapter{4}

Aedion and Rowan did not let Darrow's messenger go ahead to warn the lords of their arrival.
If this was some maneuver to get them on uneven footing, despite all that Murtaugh and Ren had done for them this spring, then they'd gain the advantage whatever way they could.

Aelin supposed that she should have taken the stormy weather as an omen.
Or perhaps Murtaugh's age provided a convenient excuse for Darrow to test her.
She leashed her temper at the thought.

The tavern was erected at a crossroads just inside the tangle of Oakwald.
With the rain and night settling in, it was packed, and they had to pay double to stable their horses. 
Aelin was fairly certain that one word from her, one flicker of that telltale fire, would have cleared out not only the stables, but also the tavern itself.

Lysandra had padded off half a mile away, and when they arrived, she slunk from the bushes and nodded her fuzzy, drenched head at Aelin.
All clear.

Inside the inn, there were no rooms to be found for rent, and the taproom itself was crammed full of travelers, hunters, and whoever else was escaping the downpour. 
Some even sat against the walls---and Aelin supposed that it was how she and her friends might very well spend their evening once this meeting concluded.

A few heads twisted their way as they entered, but dripping hoods and cloaks concealed their faces and weapons, and those heads quickly returned to their drinks or cards or drunken songs.

Lysandra had finally shifted back into her human form---and true to her oath months ago, her once-full breasts were now smaller. 
Despite what awaited them in the private dining room at the back of the inn, Aelin caught the shape-shifter's eye and smirked.

"Better?"
she murmured over Evangeline's head as Darrow's messenger, Aedion at his side, strolled through the crowd.

Lysandra's grin was half feral. 
"Oh, you have no idea."

Behind them, Aelin could have sworn Rowan chuckled.

The messenger and Aedion turned down a hallway, the dim candlelight flickering amongst the raindrops still sliding off the round, scarred shield strapped across her cousin's back. 
The Wolf of the North, who, even though he had won battles with his Fae speed and strength, had earned the respect and loyalty of his legion as a man---as a human. 
Aelin, still in her Fae form, wondered if she should have shifted herself.

Ren Allsbrook waited in there. 
Ren, another childhood friend, whom she had almost killed, \emph{tried} to kill this past winter, and who had no idea who she really was. 
Who had stayed at her apartment without realizing it belonged to his lost queen. 
And Murtaugh\ldots She had vague memories of the man, mostly involving him sitting at her uncle's table, slipping her extra blackberry tarts.

Any good that remained, any shred of safety, it was thanks to Aedion, the dents and scratches marring his shield utter proof of it, and to the three men who awaited her.

Aelin's shoulders began to curve inward, but Aedion and the messenger paused before a wooden door, knocking once. 
Fleetfoot brushed against her calf, tail wagging, and Aelin smiled down at the hound, who shook herself again, flinging droplets of water. 
Lysandra snorted. 
Bringing a wet dog into a covert meeting---very queenly.

But Aelin had promised herself, months and months ago, that she would not pretend to be anything but what she was.
She had crawled through darkness and blood and despair---she had survived.
And even if Lord Darrow could offer men and funding for a war\ldots she had both, too. 
More would be better, but---she was not empty-handed. 
She had done that for herself. 
For them all.

Aelin squared her shoulders as Aedion stepped into the room, already speaking to those inside: "Just like you bastards to make us trudge through the rain because you don't want to get wet. 
Ren, looking put-out, as usual.
Murtaugh, always a pleasure.
Darrow---your hair looks as bad as mine."

Someone said from within in a dry, cold voice, "Given the secrecy with which you arranged this meeting, one would think you were sneaking through your own kingdom, Aedion."

Aelin reached the ajar door, debating whether it was worth it to open the conversation by telling the fools inside to keep their voices down, but---

They were. 
With her Fae ears, she picked up more sounds than the average human. 
She stepped ahead of Lysandra and Evangeline, letting them enter behind her as she paused in the doorway to survey the private dining room.

One window, cracked to soothe the stifling heat of the inn. 
A large rectangular table before a roaring hearth, littered with empty plates, crumbs, and worn serving platters. 
Two old men sat at it, one with the messenger whispering something in his ear too softly for her Fae hearing before he bowed to all of them and saw himself out. 
Both old men straightened as they looked past where Aedion stood before the table---to her.

But Aelin focused upon the dark-haired young man by the hearth, an arm braced against the mantel, his scarred, tan face slack.

She remembered those twin swords at his back. 
Those dark, burning eyes.

Her mouth had gone slightly dry by the time she tugged back her hood. 
Ren Allsbrook started.

But the old men had risen to their feet.
She knew one of them.

Aelin didn't know how she hadn't recognized Murtaugh that night she'd gone to the warehouse to end so many of them. 
Especially when he'd been the one who halted her slaughtering.

The other old man, though\ldots while wrinkled, his face was strong---hard. 
Without amusement or joy or warmth. 
A man used to getting his way, to being obeyed without question. 
His body was thin and wiry, but his spine was still straight. 
Not a warrior of the sword, but of the mind.

Her great-uncle, Orlon, had been both. 
And kind---she'd never heard a stern or raging word from Orlon. 
This man, though\ldots Aelin held Darrow's gray-eyed gaze, predator recognizing predator.

"Lord Darrow," she said, inclining her head. 
She couldn't help the crooked grin. 
"You look toasty."

Darrow's plain face remained unmoved.
Unimpressed.

Well, then.

Aelin watched Darrow, waiting---refusing to break his stare until he bowed.

A dip of his head was all he offered.

"A bit lower," she purred.

Aedion's gaze snapped to her, full of warning.

Darrow did no such thing.

It was Murtaugh who bowed deeply at the waist and said, "Majesty. 
We apologize for sending the messenger to fetch you---but my grandson worries after my health." 
An attempt at a smile. 
"To my chagrin."

Ren ignored his grandfather and pushed off the mantel, his boot-steps the only sound as he rounded the table.
"You knew," he breathed to Aedion.

Lysandra, wisely, shut the door and bid Evangeline and Fleetfoot to stand by the window---to watch for any peering eyes. 
Aedion gave Ren a little smile. 
"Surprise."

Before the young lord could retort, Rowan stepped to Aelin's side and pulled back his hood.

The men stiffened as the Fae warrior was revealed in his undimmed glory--- glazed violence already in his eyes. 
Already focused on Lord Darrow.

"Now, that is a sight I have not seen for an age," Darrow murmured.

Murtaugh mastered his shock---and perhaps a bit of fear---enough to extend a hand toward the empty chairs across from them. 
"Please, sit. 
Apologies for the mess. 
We hadn't realized the messenger might retrieve you so swiftly." 
Aelin made no move to sit. 
Neither did her companions. 
Murtaugh added, "We can order fresh food if you wish. 
You must be famished." 
Ren shot his grandfather an incredulous look that told her everything she needed to know about the rebel's opinion of her.

Lord Darrow was watching her again.
Assessing.

Humility---gratitude. 
She should try; she \emph{could} try, damn it. 
Darrow had sacrificed for her kingdom; he had men and money to offer in the upcoming battle with Erawan. 
\emph{She} had called this meeting; \emph{she} had asked these lords to meet them. 
Who cared if it was in another location? 
They were all here. 
It was enough.

Aelin forced herself to walk to the table. 
To claim the chair across from Darrow and Murtaugh.

Ren remained standing, monitoring her with dark fire in his eyes.

She said quietly to Ren, "Thank you---for helping Captain Westfall this spring."

A muscle flickered in Ren's jaw, but he said, "How does he fare?
Aedion mentioned his injuries in his letter."

"Last I heard, he was on his way to the healers in Antica. 
To the Torre Cesme."

"Good."

Lord Darrow said, "Would you care to enlighten me on how you know each other, or shall I be required to guess?"

Aelin began counting to ten at the tone. 
But it was Aedion who said as he claimed a seat, "Careful, Darrow."

Darrow interlaced his gnarled but manicured fingers and set them on the table. 
"Or what?
Shall you burn me to ash, Princess? 
Melt my bones?"

Lysandra slipped into a chair beside Aedion and asked with the sweet, unthreatening politeness that had been trained into her, "Is there any water left in that pitcher? 
Traveling through the storm was rather taxing."

Aelin could have kissed her friend for the attempt at dulling the razor-sharp tension.

"Who, pray tell, are you?" 
Darrow frowned at the exquisite beauty, the uptilted eyes that did not shy from his despite her gentle words. 
Right---he had not known who traveled with her and Aedion. 
Or what gifts they bore.

"Lysandra," Aedion answered, unbuckling his shield and setting it on the floor behind them with a heavy thunk. 
"Lady of Caraverre."
"There is no Caraverre," Darrow said.

Aelin shrugged. 
"There is now." 
Lysandra had settled on the name a week ago, whatever it meant, bolting upright in the middle of the night and practically shouting it at Aelin once she'd mastered herself long enough to shift back into her human form. 
Aelin doubted she'd soon forget the image of a wide-eyed ghost leopard trying to speak. 
She smiled a bit at Ren, still watching her like a hawk.
"I took the liberty of buying the land your family yielded.
Looks like you'll be neighbors."

"And what bloodline," Darrow asked, his mouth tightening at the brand across Lysandra's tattoo, the mark visible no matter what form she took, "does Lady Lysandra hail from?"

"We didn't arrange this meeting to discuss bloodlines and heritage," Aelin countered evenly. 
She looked to Rowan, who gave a confirming nod that the inn staff was far from the room and no one was within hearing range.

Her Fae Prince stalked to the serving table against the wall to fetch the water Lysandra had asked for. 
He sniffed it, and she knew his magic swept through it, probing the water for any poison or drug, while he floated four glasses over to them on a phantom wind.

The three lords watched in wide-eyed silence. 
Rowan sat and casually poured the water, then summoned a fifth cup, filled it, and floated it to Evangeline. 
The girl beamed at the magic and went back to staring out the rainsplattered window. 
Listening while pretending to be pretty, to be useless and small, as Lysandra had taught her.

Lord Darrow said, "At least your Fae warrior is good for something other than brute violence."

"If this meeting is interrupted by unfriendly forces," Aelin said smoothly,

"you'll be glad for that brute violence, Lord Darrow."

"And what of your particular skill set?
Should I be glad of that, too?"

She didn't care how he'd learned. 
Aelin cocked her head, choosing each word, forcing herself to think it through for once. 
"Is there a skill set that you would prefer I possess?"

Darrow smiled. 
It didn't reach his eyes. 
"Some control would do Your Highness well."

On either side of her, Rowan and Aedion were taut as bowstrings. 
But if \emph{she} could keep her temper leashed, then they could--- \emph{Your Highness}. 
Not \emph{Majesty}.

"I'll take that into consideration," she said with a little smile of her own. 
"As for why my court and I wished to meet with you today---"

"Court?" 
Lord Darrow raised his silver brows. 
Then he slowly raked his stare over Lysandra, then Aedion, and finally Rowan. 
Ren was gaping at them all, something like longing---and dismay---on his face. 
"This is what you consider a court?"

"Obviously, the court will be expanded once we're in Orynth---"

"And for that matter, I do not see how there can even \emph{be} a court, as you are not yet queen."

She kept her chin high. 
"I'm not sure I catch your meaning."

Darrow sipped from his tankard of ale. 
The plunk as he set it down echoed through the room. 
Beside him, Murtaugh had gone still as death. 
"Any ruler of Terrasen must be approved by the ruling families of each territory."

Ice, cold and ancient, cracked through her veins. 
Aelin wished she could blame it on the thing hanging from her neck.

"Are you telling me," she said too quietly, fire flickering in her gut, dancing along her tongue, "that even though I am the last living Galathynius, my throne does not yet belong to me?"

She felt Rowan's attention fix upon her face, but she didn't look away from Lord Darrow.

"I am telling you, Princess, that while you might be the last living direct descendant of Brannon, there are other possibilities, other directions to go in, should you be deemed unfit."

"Weylan, please," Murtaugh cut in. 
"We did not accept the offer to meet for this. 
It was to discuss rebuilding, to \emph{help} her and work with her." 
They all ignored him.

"Other possibilities such as yourself?" 
Aelin asked Darrow. 
Smoke curled in her mouth. 
She swallowed it down, nearly choking on it.

Darrow didn't so much as flinch. 
"You can hardly expect us to allow a nineteen-year-old assassin to parade into our kingdom and start yapping orders, regardless of her bloodline."

\emph{Think it through, take a deep breath. 
Men, money, support from your already-broken people. 
That's what Darrow offers, what you can stand to gain, if you just control your rutting temper.}

She stifled the fire in her veins into murmuring embers. 
"I understand that my personal history might be considered problematic---"

"I find everything about you, Princess, to be problematic. 
The least of which is your choice in friends and \emph{court} members. 
Can you explain to me why a common whore is in your company and being passed as a lady? 
Or why one of Maeve's minions is now sitting at your side?" 
He tossed a sneer in Rowan's direction. 
"Prince Rowan, is it?"
He must have pieced it together from what the messenger had whispered in his ear upon arriving. 
"Oh, yes, we've heard of you. 
What an interesting turn of events, that when our kingdom is weakest and its heir so young, one of Maeve's most trusted warriors manages to gain a foothold, after so many years of gazing at our kingdom with such longing. 
Or perhaps the better question is, why serve at Maeve's feet when you could rule beside Princess Aelin?"

It took considerable effort to keep her fingers from curling into fists. 
"Prince Rowan is my \emph{carranam}.
He is above any doubt."

"\emph{Carranam}.
A long-forgotten term. 
What other things did Maeve teach you in Doranelle this spring?"

She bit back her retort as Rowan's hand grazed hers beneath the table---his face bored, uninterested. 
The calm of a feral, frozen storm.
\emph{Permission to speak,} Majesty\emph{?}

She had a feeling Rowan would very, very much enjoy the task of shredding Darrow into little pieces. 
She also had the feeling that she'd very, very much enjoy joining him.

Aelin gave a slight nod, at a loss for words herself as she struggled to keep her flames at bay.

Honestly, she felt slightly bad for Darrow as the Fae Prince gave him a look laced with three hundred years of cold violence. 
"Are you accusing me of taking the blood oath to my queen with dishonor?"

Nothing human, nothing merciful in those words.

To his credit, Darrow didn't shrink. 
Rather, he raised his brows at Aedion, then turned and shook his head at Aelin. 
"You gave away the sacred oath to this\ldots male?"

Ren gaped a bit as he surveyed Aedion, that scar stark against his tan skin.

She had not been there to protect him from it. 
Or to protect Ren's sisters when their magic academy became a slaughterhouse during Adarlan's invasion. 
Aedion caught Ren's surprise and subtly shook his head, as if to say, \emph{I'll explain later}.

But Rowan leaned back in his chair with a faint smile---and it was a horrifying, terrible thing. 
"I have known many princesses with kingdoms to inherit, Lord Darrow, and I can tell you that absolutely none of them were ever stupid enough to allow a male to manipulate them that way, least of all my queen. 
But if I were going to scheme my way onto a throne, I'd pick a far more peaceful and prosperous kingdom." 
He shrugged.
"But I do not think my brother and sister in this room would allow me to live for very long if they suspected I meant their queen ill---or their kingdom."

Aedion gave a grim nod, but beside him, Lysandra straightened---not in anger or surprise, but pride. 
It broke Aelin's heart as much as it lightened it.

Aelin smiled slowly at Darrow, flames banking. 
"How long did it take you to come up with a list of every possible thing to insult me with and accuse me of during this meeting?"

Darrow ignored her and jerked his chin at Aedion. 
"You're rather quiet tonight."

"I don't think you particularly want to hear my thoughts right now, Darrow," Aedion replied.

"Your blood oath is stolen by a foreign prince, your queen is an assassin who appoints common whores to serve her, and yet you have nothing to say?"

Aedion's chair groaned, and Aelin dared a look---to find him gripping the sides of it so hard his knuckles were white.

Lysandra, though stiff-backed, did not give Darrow the pleasure of blushing with shame.

And she was done.
Sparks danced at her fingertips beneath the table.

But Darrow went on before Aelin could speak or incinerate the room.
"Perhaps, Aedion, if you hope to still gain an official position in Terrasen, you could see if your kin in Wendlyn have reconsidered the betrothal proposition of so many years ago. 
See if they'll recognize you as family. 
What a difference it might have made, if you and our beloved Princess Aelin had been betrothed---if Wendlyn had not rejected the offer to formally unite our kingdoms, likely at Maeve's behest." 
A smile in Rowan's direction.

Her world tilted a bit. 
Even Aedion had paled. 
No one had ever hinted that there had been an official attempt at betrothing them. 
Or that the Ashryvers had truly left Terrasen to war and ruin.

"Whatever will the adoring masses say of their savior princess," Darrow mused, putting his hands flat on the table, "when they hear of how she has spent her time while they suffered?" 
A slap in the face, one after another. 
"But," Darrow added, "you've always been good at whoring yourself out, Aedion.

Though I wonder if Princess Aelin knows what---" Aelin lunged.

Not with flame, but steel.

The dagger shuddering between Darrow's fingers flickered with the light of the crackling hearth.

She snarled in the old man's face, Rowan and Aedion half out of their chairs, Ren reaching for a weapon, but looking sick---sick at the sight of the ghost leopard now sitting where Lysandra had been a moment ago.

Murtaugh gaped at the shape-shifter.
But Darrow glared at Aelin, his face white with rage.

"You want to sling insults at me, Darrow, then go ahead," Aelin hissed, her nose almost touching his. 
"But you insult my own again, and I won't miss next time." 
She flicked her eyes to the dagger between the old man's splayed fingers, a hairsbreadth separating the blade from his speckled flesh.

"I see you inherited your father's temper," Darrow sneered. 
"Is this how you plan to rule? 
When you don't like someone, you'll threaten them?" 
He slid his hand from the blade and pulled back far enough to cross his arms. 
"What would Orlon think of this behavior, this bullying?"

"Choose your words wisely, Darrow," Aedion warned.

Darrow lifted his brows. 
"All the work I have done, all that I have sacrificed these past ten years, has been in Orlon's name, to honor him and to save his kingdom---\emph{my} kingdom. 
I do not plan to let a spoiled, arrogant child destroy that with her temper tantrums. 
Did you enjoy the riches of Rifthold these years, Princess? 
Was it very easy to forget us in the North when you were buying clothes and serving the monster who butchered your family and friends?" 
\emph{Men, and money, and a unified Terrasen.}

"Even your cousin, despite his whoring, helped us in the North. 
And Ren Allsbrook"---a wave of the hand in Ren's direction---"while you were living in luxury, did you know that Ren and his grandfather were scraping together every copper they could, all to find a way to keep the rebel effort alive? 
That they squatted in shanties and slept under horses?"
"That's enough," Aedion said.

"Let him go on," Aelin said, sitting back in her seat and crossing her arms.

"What else is there to say, Princess? 
Do you think the people of Terrasen will be glad to have a queen who served their enemy? 
Who shared a bed with the son of their enemy?"

Lysandra snarled softly, rattling the glasses.

Darrow was unfazed. 
"And a queen who now undoubtedly shares a bed with a Fae Prince who served the other enemy at our backs---what do you suppose our people will make of \emph{that}?"

She didn't want to know how Darrow had guessed, what he'd read between them.

"Who shares my bed," she said, "is none of your concern."

"And that is why you are not fit to rule. 
Who shares the queen's bed is \emph{everyone's} concern. 
Will you lie to our people about your past, deny that you served the deposed king---and served his son, too, in a different manner?"

Beneath the table, Rowan's hand shot out to grip her own, his fingers coated in ice that soothed the fire starting to flicker at her nails. 
Not in warning or reprimand---just to tell her that he, too, was struggling with the effort to keep from using the pewter food platter to smash in Darrow's face.

So she didn't break Darrow's stare, even as she laced her fingers with Rowan's.

"I will tell \emph{my} people," Aelin said quietly but not weakly, "the entire truth. 
I will show them the scars on my back from Endovier, the scars on my body from my years as Celaena Sardothien, and I will tell them that the new King of Adarlan is not a monster. 
I will tell them that we have one enemy: the bastard down in Morath. 
And Dorian Havilliard is the only chance for survival---and future peace between our two kingdoms."

"And if he is not?
Will you shatter his stone castle as you shattered the glass one?"

Chaol had mentioned this---months ago. 
She should have considered it more, that ordinary humans might demand checks against her power. 
Against the power of the court gathering around her. 
But let Darrow believe she'd shattered the glass castle; let him believe she'd killed the king. 
Better than the potentially disastrous truth.

"Should you still wish to be a part of Terrasen," Darrow continued when none of them replied, "I'm sure Aedion can find some use for you in the Bane. 
But I will have no use for you in Orynth."

She flicked her brows up. 
"Is there anything else that you have to say to me?"

His gray eyes turned flinty. 
"I do not recognize your right to rule; I do not recognize you as the rightful Queen of Terrasen. 
Neither do the Lords Sloane, Ironwood, and Gunnar, who make up the remaining surviving majority of what was once your uncle's court. 
Even if the Allsbrook family sides with you, that is still one vote against four. 
General Ashryver has no lands or title here---and no say as a result. 
As for \emph{Lady} Lysandra, Caraverre is not a recognized territory, nor do we recognize her lineage or your \emph{purchase} of those lands." 
Formal words, for a formal declaration. 
"Should you return to Orynth and seize your throne without our invitation, it will be considered an act of war and treason." 
Darrow pulled a piece of paper from his jacket---lots of fancy writing and four different signatures on the bottom. 
"As of this moment, until it is otherwise decided, you shall remain a princess by blood---but not queen."
