
\chapter{62}

Manon was awake when Dorian stormed into her room an hour before dawn. He ignored her unlaced shirt, the swell of those lush breasts he'd tasted only

yesterday, as he said, "Put your clothes on and follow me."

Mercifully, the witch obeyed. Though he had a feeling it was mostly from curiosity.

When he reached Aelin's chamber, he bothered to knock---just in case the queen and Rowan were utilizing their potentially last few hours together. But the queen was already awake and dressed, the prince nowhere to be found. Aelin took one look at Dorian's face. "What is it?"

He didn't tell either woman anything as he led them down into the cargo hold, the upper levels of the ship already astir with battle preparations.

While they'd debated and readied for the past day, he'd contemplated Manon's warning, after she'd made his very blood sing with pleasure.
\emph{Unless you would like to learn precisely what parts of me are made of iron the next time you touch me, I decide those things.}

Over and over, he'd considered the way the words had snagged on a sharp corner of memory. He'd lain awake all night while he descended into his stilldepleted well of magic. And as the light had begun to shift


Dorian tugged the sheet off the witch mirror carefully held in place against the wall. The Lock---or whatever it was. In the muted reflection, the two queens were frowning at his back.

Manon's iron nails slid out. "I would be careful handling that if I were you."

"The warning is noted and appreciated," he said, meeting those gold eyes in the mirror. She didn't return his smile. Neither did Aelin. He sighed. "I don't think this witch mirror has any power. Or, rather, not a tangible, brute power. I think its power is knowledge."

Aelin's steps were near-silent as she approached. "I was told the Lock would allow me to bind the three keys into the gate. You think this mirror knows how to do that?"

He simply nodded, trying not to be too offended by the skepticism scrunching her face.

Aelin picked at a loose thread on her jacket. "But what does the Lock-mirrorwhatever-it-is have to do with the armada breathing down our necks?"

He tried not to roll his eyes. "It has to do with what Deanna said. What if the Lock wasn't just for binding them back into the gate, but a tool for safely controlling the keys?"

Aelin frowned at the mirror. "So I'm going to lug that thing onto the deck and use it to blow apart Maeve's armada with the two keys we have?"

He took a steadying breath, beseeching the gods for patience. "I said I think this mirror's power is knowledge. I think it will \emph{show} you how to wield the keys safely. So you can come back here and wield them without consequence."

A slow blink. "What do you mean, \emph{come back here}?"

Manon answered, now stepping close as she studied the mirror. "It's a traveling mirror."

Dorian nodded. "Think about Deanna's words: `\emph{Flame and iron, together bound, merge into silver to learn what must be found}. \emph{A mere step is all it shall take.}'\," He pointed to the mirror. "Step into the silver---and \emph{learn}."

Manon clicked her tongue. "And I suppose she and I are flame and iron." Aelin crossed her arms.

Dorian cut the Queen of Terrasen a wry glance. "People other than you
\emph{can} solve things, you know."

Aelin glared at him. "We don't have time for what-ifs. Too many things could go wrong."

"You have little magic left," Dorian countered, waving a hand toward the mirror. "You could be in and out of this mirror before dawn. And use what you learn to send Maeve a message in no uncertain terms."

"I can still fight with steel---without the risks and waste of time."

"You can stop this battle before the losses are too great on either side." He added carefully, "We're out of time already, Aelin."

Those turquoise eyes were steady---if not still furious he'd beat her to the riddle---but something flickered in them. "I know," she said. "I was hoping \ldots" She shook her head, more at herself. "I ran out of time," she murmured as if it were an answer, and considered the mirror, then Manon. Then blew out a breath.

"This wasn't my plan."

"I know," Dorian said with a half smile. "That's why you don't like it."

Manon asked before Aelin could bite off his head, "But where will the mirror lead?"

Aelin clenched her jaw. "Hopefully not Morath." Dorian tensed. Perhaps this plan---

"That symbol belongs to both of us," Manon said, studying the Eye of Elena etched onto it. "And if it takes you to Morath, you're going to need someone who knows the way out."

Steps thudded down the stairs at the back of the hold. Dorian twisted toward them, but Aelin smirked at Manon and approached the mirror. "Then I'll see you on the other side, witch."

Aedion's golden head appeared between the crates. "What the hell are you

---"

Aelin's shallow nod seemed all that Manon needed. She placed her hand atop Aelin's.

Golden eyes met Dorian's for a moment, and he opened his mouth to say something to her, the words surging from some barren field in his chest.

But Aelin and Manon pressed their joined hands to the speckled glass.

Aedion's shout of warning rang through the hold as they vanished.
