
\chapter{64}

Aelin had a body that was not a body.

She knew only because in this void, this foggy twilight, Manon had a body. A nearly transparent, wraithlike body, but  a form nonetheless.

Manon's teeth and nails glinted in the dim light as she surveyed the swirling gray mists. "What is this place?" The mirror had transported them to  wherever this was.

"Your guess is as good as mine, witch."

Had time stopped beyond the mists? Had Maeve held her fire upon learning she was not present---or attacked anyway? Aelin had no doubt Rowan would hold the lines for as long as possible. Had no doubt he and Aedion would lead them. But 

Whether the witch mirror was the Lock she'd sought, she'd expected it to have \emph{some} immediate reaction to the two Wyrdkeys she'd snuck into her jacket.

Not  this. Not absolutely \emph{nothing}.

Aelin drew Goldryn. In the mist, the sword's ruby flickered---the only color, only light.

Manon said, "We stick close; we only speak when necessary."

Aelin was inclined to agree. There was solid ground beneath them, but the mist hid her feet---hid any inkling that they stood on dirt beyond a faint, crumbling scraping.

"Any guess which way?" Aelin murmured. But they didn't have to decide.

The eddying fog darkened, and Manon and Aelin stepped close together, back to back. Pure night swept around them---blinding them.

Then---a murky, dim light ahead. No, not ahead. Approaching them. Manon's bony shoulder dug into her own as they pressed tighter together, an impenetrable wall.

But the light rippled and expanded, figures within it appearing. Solidifying.

Aelin knew three things as the light and color enveloped them and became tangible:

They were not seen, or heard, or scented by those before them.

And this was the past. A thousand years ago, to be exact.

And that was Elena Galathynius on her knees in a black barren mountain pass, blood dripping from her nose, tears sliding through the dirt crusting her face to splatter on her armor, an obsidian sarcophagus somehow stationed before her.

All across the sarcophagus, Wyrdmarks simmered with pale blue fire. And in the center of it  the Eye of Elena, the amulet held within the stone itself, its pale gold unvarnished and gleaming.

Then, as if a phantom breath blew over it, the Eye dimmed, along with the Wyrdmarks.

Elena reached with a trembling hand to twist the Eye, rotating it thrice in the black stone. The Eye clicked and tumbled into Elena's awaiting hand. Sealing the sarcophagus.

Locking it.

"You've had the Lock all along," Manon murmured. "But then the mirror

\ldots"

"I think," Aelin breathed, "we have been deliberately misled about what we must retrieve."

"Why?" Manon said with equal quiet.

"I suppose we're about to find out."

A memory---that's what this was. But what was so vital that they had been sent to retrieve it when the whole damn world was falling apart around them?

Aelin and Manon stood in silence as the scene unfolded. As the truth, at last the truth, now wove together.
