
\chapter{68}

It was an agony.

An agony, to see Nehemia, young and strong and wise.
Speaking to Elena in the marshes, among those same ruins.

And then there was the other agony.

That Elena and Nehemia had known each other.
Worked together.

That Elena had laid these plans a thousand years ago.

That Nehemia had gone to Rifthold knowing she'd die.

Knowing she'd need to break Aelin---use her death to \emph{break her}, so she could walk away from the assassin and ascend her throne.

Aelin and Manon were shown another scene.
Of a whispered conversation at midnight, deep beneath the glass castle.

A queen and a princess, meeting in secret.
As they had for months.

The queen asking the princess to pay that price she'd offered back in the marshes.
To arrange for her own death---to set this all in motion.
Nehemia had warned Elena that she---that Aelin---would be broken.
Worse, that she would go so far into an abyss of rage and despair that she wouldn't be able to get out.
Not as Celaena.

Nehemia had been right.

Aelin was shaking---shaking in her half-invisible body, shaking so badly she thought her skin would ripple off her bones.
Manon stepped closer, perhaps the only comfort the witch knew how to offer: solidarity.

They stared into the swirling mist again, where the scenes---the \emph{memories}--- had unfolded.

Aelin wasn't sure she could stomach another truth.
Another revelation of just how thoroughly Elena had sold her and Dorian to the gods, for the fool's mistake she'd made, not understanding the Lock's true purpose, to seal Erawan in his tomb rather than let Brannon finally end it---and send the gods to wherever they called home, dragging Erawan with them.

Send them home\ldots using the keys to open the Wyrdgate.
And a new Lock to seal it forever.

\emph{Nameless is my price}.

Using \emph{her} power, drained to the last drop, \emph{her} life to forge that new Lock.
To wield the power of the keys only once---just once, to banish them all, and then seal the gate forever.

Memories flickered by.

Elena and Brannon, screaming at each other in a room Aelin had not seen for ten years---the king's suite in the palace at Orynth.
Her suite---or it would have been.
A necklace glittered at Elena's throat: the Eye.
The first and now-broken Lock, that Elena, now the Queen of Adarlan, seemed to wear as some sort of reminder of her foolishness, her promise to those furious gods.

Her argument with her father raged and raged---until the princess walked out.
And Aelin knew Elena had never returned to that shining palace in the North.

Then the reveal of that witch mirror in some nondescript stone chamber, a black-haired beauty with a crown of stars standing before Elena and Gavin, explaining how the witch mirror worked---how it would contain these memories.
Rhiannon Crochan.
Manon started at the sight of her, and Aelin glanced between them.

The face\ldots it was the same.
Manon's face, and Rhiannon Crochan's.
The last Crochan Queens---of two separate eras.

Then an image of Brannon alone---head in his hands, weeping before a shrouded body atop a stone altar.
A crone's bent shape lay beneath.

Elena, her immortal grace yielded in order to live out a human life span with Gavin.
Brannon still looked no older than thirty.

Brannon, the heat of a thousand forges shining on his red-gold hair, his teeth bared in a snarl as he pounded a metal disk on an anvil, the muscles of his back rippling beneath golden skin as he struck and struck and struck.

As he forged the Amulet of Orynth.

As he placed a sliver of black stone within either side, then sealed it, defiance written in every line of his body.

Then wrote the message in Wyrdmarks on the back.

One message.

For her.

For his true heir, should Elena's punishment and promise to the gods hold true.
The punishment and promise that had cleaved them.
That Brannon could not and would not accept.
Not while he had strength left.

\emph{Nameless is my price}.
Written right there---in Wyrdmarks.
The one who bore Brannon's mark, the mark of the bastard-born nameless 
\emph{She} would be the cost to end this.

The message on the back of the Amulet of Orynth was the only warning he could offer, the only apology for what his daughter had done, even as it contained a secret inside so deadly no one must know, no one could ever be told.

But there would be clues.
For her.
To finish what they'd started.

Brannon built Elena's tomb with his own hands.
Carved the messages in there for Aelin, too.

The riddles and the clues.
The best he could offer to explain the truth while keeping those keys hidden from the world, from powers who would use them to rule, to destroy.

Then he made Mort, the metal for the door knocker gifted by Rhiannon Crochan, who brushed a hand over the king's cheek before she left the tomb.

Rhiannon was not present when Brannon hid the sliver of black stone beneath the jewel in Elena's crown---the second Wyrdkey.

Or when he set Damaris in its stand, near the second sarcophagus.
For the mortal king he hated and had barely tolerated, but he had leashed that loathing for his daughter's sake.
Even if Gavin had taken his daughter, the daughter of his soul, away from him.

The final key\ldots he went to Mala's temple.

It was where he had wanted to end this all along anyway.

The molten fire around the temple was a song in his blood, a beckoning.
A welcoming.

Only those with his gifts---\emph{her} gifts---could get there.
Even the priestesses could not reach the island in the heart of the molten river.
Only his heir would be able to do that.
Or whoever held another key.

So he set the remaining key under a flagstone.

And then he walked into that molten river, into the burning heart of his beloved.

And Brannon, King of Terrasen, Lord of Fire, did not emerge again.

Aelin didn't know why it surprised her to be able to cry in this body.
That this body had tears to spill.

But Aelin shed them for Brannon.
Who knew what Elena had promised the gods---and had raged against it, the passing of this burden onto one of his descendants.

Brannon had done what he could for her.
To soften the blow of that promise, if he could not change its course wholly.
To give Aelin a fighting chance.

\emph{Nameless is my price}.

"I don't understand what this means," Manon said quietly.

Aelin did not have the words to tell her.
She had not been able to tell Rowan.

But then Elena appeared, real as they were real, and stared into the fading golden light of Mala's temple as the memory vanished.
"I'm sorry," she said to Aelin.

Manon stiffened at Elena's approach, taking a step from Aelin's side.

"It was the only way," Elena offered.
That was genuine pain in her eyes.
Regret.

"Was it a choice, or just to spare Gavin's precious bloodline, that I was the one who was selected?"
The voice that came from Aelin's throat was raw, vicious.
"Why spill Havilliard blood, after all, when you could fall back on old habits and choose another to bear the burden?"

Elena flinched.
"Dorian was not ready.
You were.
The choice Nehemia and I made was to ensure that things went according to plan."

"According to plan," Aelin breathed.
"According to all your schemes to make me clean up the mess of what \emph{you started with your gods-damned thieving and cowardice}?"

"They wanted me to suffer," Elena said.
"And I have.
Knowing you must do this, bear this burden\ldots It has been a steady, endless shredding of my soul for a thousand years.
It was so easy to say yes, to imagine you would be a stranger, someone who would not need to know the truth, only to be in the right place with the right gift, and yet  and yet I was wrong.
I was so wrong."
Elena lifted her hands before her, palms up.
"I thought Erawan would rise, and the world would face him.
I did not know\ldots I did not know darkness would fall.
I did not know that your land would suffer.
Suffer as I tried to keep mine from suffering.
And there were so many voices\ldots so many voices even before Adarlan conquered.
It was those voices that woke me.
The voices of those wishing for an answer, for help."
Elena's eyes slid to Manon, then back to hers.
"They were from all kingdoms, all races.
Human, witch-kind, Fae\ldots But they wove a tapestry of dreams, all begging for that one thing\ldots A better world.

"Then you were born.
And you were an answer to the gathering darkness, with that flame.
My father's flame, my mother's might---reborn at last.
And you were strong, Aelin.
So strong, and so vulnerable.
Not to outside threats, but the threat of your own heart, the isolation of your power.
But there were those who knew you for what you were, what you could offer.
Your parents, their court, your great-uncle\ldots and Aedion.
Aedion knew you were the Queen Who Was Promised without knowing what it meant, without knowing anything about you, or me, or what I did to spare my own people."

The words hit her like stones.
"The Queen Who Was Promised," Aelin said.
"But not to the world.
To the gods---to the keys."

To pay the price.
To be their sacrifice in order to seal the keys in the gate at last.

Deanna's appearance hadn't been only to tell her how to use the mirror, but to remind her that she \emph{belonged} to them.
Had a debt owed to them.

Aelin said too quietly, "I didn't survive that night in the Florine River because of pure luck, did I?"

Elena shook her head.
"We did not---"

"No," Aelin snapped.
"\emph{Show me.}"

Elena's throat bobbed.
But then the mists turned dark and colored, and the very air around them became laced with frost.

Breaking branches, ragged breath punctuated with gasping sobs, light footsteps crashing through bramble and brush.
A horse's thunderous gait, closing in---

Aelin made herself stand still when that familiar, frozen wood appeared, exactly as she remembered it.
As \emph{she} appeared, so small and young, white nightgown torn and muddy, hair wild, eyes bright with terror and grief so profound it had broken her entirely.
Frantic to reach the roaring river beyond, the bridge---

There were the posts, and the forest on the other side.
Her sanctuary---

Manon swore softly as Aelin Galathynius flung herself through the bridge posts, realized the bridge had been cut\ldots and plummeted into the raging, halffrozen river below.

She had forgotten how far that fall was.
How violent the black river was, the white rapids illuminated by the icy moon overhead.

The image shifted, and then it was dark, and silent, and they were being tumbled, over and over as the river tossed her in its wrath.

"There was so much death," Elena whispered as they watched Aelin being thrown and twisted and dragged down by the river.
The cold was crushing.

"So much death, and so many lights extinguished," Elena said, voice breaking.
"You were so small.
And you fought\ldots you fought so hard."

And there she was, clawing at the water, kicking and thrashing, trying to get to the surface, to the air, and she could feel her lungs begin to seize, feel the pressure building---

Then light flickered from the Amulet of Orynth hanging around her neck, greenish symbols fizzing like bubbles around her.

Elena slid to her knees, watching that amulet glow beneath the water.
"They wanted me to take you, right then.
You had the Amulet of Orynth, everyone thought you were dead, and the enemy was distracted with the slaughter.
I could take you, help you track down the other two keys.
I was allowed to help you---to do that much.
And once we got the other two, I was to force you to forge the Lock anew.
To use every last drop of \emph{you} to make that Lock, summon the gate, put the keys back into it, send them home, and end it all.
You had enough power, even then.
It'd kill you to do it, but you were likely dead anyway.
So they let me form a body, to get you."

Elena took a shuddering breath as a figure plunged into the water.
A silverhaired, beautiful woman in an ancient dress.
She grabbed Aelin around the waist, hauling her up, up, up.

They hit the surface of the river, and it was dark and loud and wild, and it was all she could do to grab the log Elena shoved her onto, to dig her nails into the soaked wood and cling to it while she was carried downriver, deep into the night.

"I hesitated," Elena breathed.
"You clung to that log with all your strength.
Everything had been taken from you---\emph{everything}---and yet you still fought.
You did not yield.
And they told me to hurry, because even then their power to hold me in that solid body was fading.
They said to just take you and go, but\ldots I hesitated.
I waited until you got to that riverbank."

Mud and reeds and trees looming overhead, snow still patching the steep hill of the bank.

Aelin watched herself crawl up that riverbank, inch by painful inch, and she felt the phantom, icy mud beneath her nails, felt her broken, frozen body as it slumped onto the earth and shuddered, over and over.

As lethal cold gripped her while Elena hauled herself onto the bank beside her.

As Elena lunged for her, screaming her name, cold and shock setting in 
"I thought the danger would be drowning," Elena whispered.
"I didn't realize being out in the cold for so long \ldots"

Her lips had gone blue.
Aelin watched her own small chest rise, fall, rise\ldots Then stop moving all together.

"You died," Elena whispered.
"Right there, you died.
You had fought so hard, and I failed you.
And in that moment, I didn't care that I'd again failed the gods, or my promise to make it right, or any of it.
All I could think \ldots" Tears ran down Elena's face.
"All I could think was how unfair it was.
You had not even lived, you had not even been given a chance\ldots And all those people, who had wished and waited for a better world\ldots You would not be there to give it to them."

Oh gods.

"Elena," Aelin breathed.

The Queen of Adarlan sobbed into her hands, even as her former self shook Aelin, over and over.
Trying to wake her, trying to revive the small body that had given out.

Elena's voice broke.
"I could not allow it.
I could not endure it.
Not for the gods' sake, but---but for your own."

Light flared at Elena's hand, then down her arm, then along her whole body.
Fire.
She wrapped herself around Aelin, the heat melting the snow around them, drying her ice-crusted hair.

Lips that were blue turned pink.
And a chest that had stopped breathing now lifted.

Darkness faded to the gray light of dawn.
"And then I defied them."

Elena set her down between the reeds and rose, scanning the river, the world.

"I knew who had an estate near this river, so far away from your home that your parents had tolerated its presence, as long as he was not stupid enough to stir up trouble."

Elena, a mere flicker of light, tugged Arobynn from a deep sleep inside his former residence in Terrasen.
As if in a trance, he shoved on his boots, his red hair gleaming in the light of dawn, mounted his horse, and set off into the woods.

So young, her former master.
Only a few years older than she was now.

Arobynn's horse paused as if an invisible hand had yanked its bridle, and the assassin scanned the raging river, the trees, as if looking for something he didn't even know was there.

But there was Elena, invisible as sunlight, crouching in the reeds when Arobynn's eyes fell upon the small, dirty figure unconscious on the riverbank.
He leaped from his horse with feline grace, slinging off his cloak as he threw himself to his knees in the mud and felt for her breathing.

"I knew what he was, what he'd likely do with you.
What training you would receive.
But it was better than dead.
And if you could survive, if you could grow up strong, if you had the chance to reach adulthood, I thought perhaps you could give those people who had wished and dreamed of a better world\ldots at least give them a chance.
Help them---before the debt was called in again."

Arobynn's hands hesitated as he noticed the Amulet of Orynth.

He eased the amulet from around her neck and placed it in his pocket.
Gently, he scooped her into his arms and carried her up the bank to his waiting horse.

"You were so young," Elena said again.
"And more than the dreamers, more than the debt\ldots I wanted to give you time.
To at least know what it was to live."

Aelin rasped, "What was the price, Elena?
What did they do to you for this?"

Elena wrapped her arms around herself as the image faded, Arobynn mounting his horse, Aelin in his arms.
Mist swirled again.
"When it is done," Elena managed to say, "I go, too.
For the time I bought you, when this game is finished, my soul will be melted back into the darkness.
I will not see Gavin, or my children, or my friends\ldots I will be gone.
Forever."

"Did you know that before you---"

"Yes.
They told me, over and over.
But\ldots I couldn't.
I couldn't do it."

Aelin slid to her knees before the queen.
Took Elena's tearstained face between her hands.

"Nameless is my price," Aelin said, her voice breaking.

Elena nodded.
"The mirror was just that---a mirror.
A ploy to get you here.
So that you could understand everything we did."
\emph{Just a bit of metal and glass}, Elena had said when Aelin had summoned her in Skull's Bay.
"But now you are here, and have seen.
Now you comprehend the cost.
To forge the Lock anew, to put the three keys back in the gate \ldots"

A mark glowed on Aelin's brow, heating her skin.
The bastard mark of Brannon.

The mark of the nameless.

"Mala's blood must be spent---your power must be spent.
Every drop, of magic, of blood.
You are the cost---to make a new Lock, and seal the keys into the gate.
To make the Wyrdgate whole."

Aelin said softly, "I know."
She had known for some time now.

Had been preparing for it as best she could.
Preparing things for the others.

Aelin said to the queen, "I have two keys.
If I can find the third, steal it from Erawan\ldots will you come with me?
Help me end it once and for all?"
\emph{Will you come with me, so I will not be alone?}

Elena nodded, but whispered, "I'm sorry."

Aelin lowered her hands from the queen's face.
Took a deep, shuddering breath.
"Why didn't you tell me---from the start?"

Behind them, she had the vague sense that Manon was quietly assessing.

"You were barely climbing out of slavery," Elena said.
"Hardly holding yourself together, trying so hard to pretend that you were still strong and whole.
There was only so much I could do to guide you, nudge you along.
The mirror was forged and hidden to one day show you all of this.
In a way I couldn't tell you---not when I could only manage a few minutes at a time."

"Why did you tell me to go to Wendlyn?
Maeve poses as great a threat as Erawan."

Glacier-blue eyes met hers at last.
"I know.
Maeve has long wished to regain possession of the keys.
My father believed it was for something other than conquest.
Something darker, worse.
I don't know why she only began hunting for them once you arrived.
But I sent you to Wendlyn for the healing.
And so you would\ldots find him.
The one who had been waiting so long for you."

Aelin's heart cracked.
"Rowan."

Elena nodded.
"He was a voice in the void, a secret, silent dreamer.
And so were his companions.
But the Fae Prince, he was \ldots"

Aelin reined in her sob.
"I know.
I've known for a long time."

"I wanted you to know that joy, too," Elena whispered.
"However briefly."

"I did," Aelin managed to say.
"Thank you."

Elena covered her face at those words, shuddering.
But after a moment, she surveyed Aelin, then Manon, still silent and watching.
"The witch mirror's power is fading; it will not hold you here for much longer.
Please---let me show you what must be done.
How to end it.
You won't be able to see me after, but\ldots I will be with you.
Until the very end, every step of the way, I will be with you."

Manon only put a hand on her sword as Aelin swallowed and said, "Show me, then."

So Elena did.
And when she was done, Aelin was silent.
Manon was pacing, snarling softly.

But Aelin did not fight it as Elena leaned in to kiss her brow, where that damning mark had been her whole life.
A bit of chattel, branded for the slaughterhouse.

Brannon's mark.
The mark of the bastard-born\ldots the Nameless.

\emph{Nameless is my price}.
To buy them a future, she'd pay it.

She'd done as much as she could to set things in motion to ensure that once she was gone, help would still come.
It was the only thing she could give them, her last gift to Terrasen.
To those she loved with her heart of wildfire.

Elena stroked her cheek.
Then the ancient queen and the mists were gone.

Sunlight flooded them, blinding Aelin and Manon so violently that they hissed and slammed into each other.
The brine of the sea, crash of nearby waves, and rustle of seagrasses greeted them.
And beyond that, distantly: the clamor and bellowing of all-out war.

They were on the outskirts of the marshes, upon the lip of the sea itself, the battle miles and miles out to sea.
They must have traveled within the mists, somehow---

A soft female laugh slithered through the grass.
Aelin knew that laugh.

And knew that somehow, perhaps they had not traveled through the mists 
But they had been placed here.
By whatever forces were at work, whatever gods watching.

To stand in the sandy field before the turquoise sea, dead guards in Briarcliff armor slaughtered upon the nearby dunes, still bleeding out.
To stand before Queen Maeve of the Fae.

Elide Lochan on her knees before her---with a Fae warrior's blade at her throat.
