
\chapter{72}

Aelin's body hurt.

Everything hurt. Her blood, her breath, her bones.

There was no magic left. Nothing left to save her.

"No," Lorcan said softly.

Just turning her head sparked agony down her spine. But Aelin looked at Elide, at Lorcan forced to hold her, his face white with pure terror as he glanced between Cairn and Maeve and Elide. Manon was doing the same---sizing up the odds, how fast she'd have to be to clear the area.

Good. Good---Manon would get Elide out. The witch had been waiting for Aelin to make a move, not realizing that  she had nothing left. There was no power left for a final strike.

And that dark power was still coiled around her bones, so tightly that one move of aggression  one move, and her bones would snap.

Maeve said to Lorcan, "No to what, Lorcan? Elide Lochan being taken with us if Aelin decides to put up a fight, or my generous offer to leave Elide be if Her Majesty comes willingly?"

One look at the brown-haired Fae warrior---Cairn---standing at Maeve's side, and Aelin had known what he was. She'd killed enough of them over the years. She'd spent time with Rourke Farran. What he'd do to Elide
 Lorcan also knew what a male like Cairn would do to a young woman. And if he was sanctioned by Maeve herself 

Lorcan said, "She is innocent. Take the queen, and let us go."

Manon even snapped at Maeve, "She belongs to the Ironteeth. If you have no quarrel with me, then you have no quarrel with her. Leave Elide Lochan out of it."

Maeve ignored Manon and drawled to Lorcan, "I command you to stand down. I command you to watch and do nothing. I command you to not move or

speak until I say so. The order applies to you as well, Fenrys."

And Lorcan obeyed. So did Fenrys. Their bodies simply stiffened---and then nothing.

Elide twisted to beg Lorcan, "You can stop this, you can fight it---" Lorcan didn't even look at her.

Aelin knew Elide would fight. Would not understand that Maeve had been playing this game for centuries, and had waited until this moment, until the trap was perfect, to seize her.

Aelin found Maeve smiling at her. She had played, and gambled, and lost.

Maeve nodded as if to say yes.

The unspoken question danced in Aelin's eyes as Elide screamed at Lorcan, at Manon, to help. But the witch knew her orders. Her task.

Maeve read the question in Aelin's face and said, "I will bear the keys in one hand, and Aelin Fire-Bringer in the other."

She'd have to break her first. Kill her or break  Cairn grinned.

The escorts were now hauling something up the beach, from the longboat they'd rowed over from their awaiting ship. Already, the dark sails were unfurling.

Elide faced Maeve, who did not deign to glance her way. "Please, please---" Aelin simply nodded at the Fae Queen. Her acceptance and surrender.

Maeve bowed her head, triumph dancing on her red lips. "Lorcan, release her."

The warrior's hands slackened at his sides.

And because she had won, Maeve even loosened her power's grip on Aelin's bones. Allowed Aelin to turn to Elide and say, "Go with Manon. She will take care of you."

Elide began crying, shoving away from Lorcan. "I'll go with you, I'll come with you---"

The girl would. The girl would face Cairn, and Maeve  But Terrasen would need that sort of courage. If it was to survive, if it was to heal, Terrasen would need Elide Lochan.

"Tell the others," Aelin breathed, trying to find the right words. "Tell the others that I am sorry. Tell Lysandra to remember her promise, and that I will never stop being grateful. Tell Aedion 
Tell him it is not his fault, and that \ldots" Her voice cracked. "I wish he'd been able to take the oath, but Terrasen will look to him now, and the lines must not break."

Elide nodded, tears sliding down her blood-splattered face.

"And tell Rowan \ldots"

Aelin's soul splintered as she saw the iron box the escorts now carried between them. An ancient, iron coffin. Big enough for one person. Crafted for her.

"And tell Rowan," Aelin said, fighting her own sob, "that I'm sorry I lied. But tell him it was all borrowed time anyway. Even before today, I knew it was all just borrowed time, but I still wish we'd had more of it." She fought past her trembling mouth. "Tell him he has to fight. He \emph{must} save Terrasen, and remember the vows he made to me. And tell him  tell him thank you---for walking that dark path with me back to the light."

They opened the lid of the box, pulling out long, heavy chains within.

One of the escorts handed Maeve an ornate iron mask. She examined it in her hands.

The mask, the chains, the box  they had been crafted long before now.

Centuries ago. Forged to contain and break Mala's scion.

Aelin glanced at Lorcan, whose dark eyes were fixed on her own.

And gratitude shone there. For sparing the young woman he'd given his heart to, whether he knew it or not.

Elide begged Maeve one last time, "Don't do this."

Aelin knew it would do her no good. So she said to Elide, "I'm glad we met. I'm proud to know you. And I think your mother would have been proud of you, too, Elide."

Maeve lowered the mask and drawled to Aelin, "Rumor claims you will bow to no one, Heir of Fire." That serpentine smile. "Well, now you will bow to me." She pointed to the sand.

Aelin obeyed.

Her knees barked as she dropped to the ground.

"Lower."

Aelin slid her body until her brow was in the sand. She did not let herself feel it, let her soul feel it.

"Good."

Elide was sobbing, wordlessly begging.

"Take off your shirt."

Aelin hesitated---realizing where this was going.

Why Cairn's belt carried a whip.

"Take off your shirt."

Aelin tugged her shirt out of her pants and slung it over her head, tossing it in the sand beside her. Then she removed the flexible cloth around her breasts.

"Varik, Heiron." Two Fae males came forward.

Aelin didn't fight as they each gripped her by an arm and hauled her up. Spread her arms wide. The sea air kissed her breasts, her navel.

"Ten lashes, Cairn. Let Her Majesty have a taste of what to expect when we reach our destination, if she does not cooperate."

"It would be my pleasure, Lady."

Aelin held Cairn's vicious gaze, willing ice into her veins as he thumbed free his whip. As he raked his eyes over her body and smiled. A canvas for him to paint with blood and pain.

Maeve said, the mask dangling from her fingers, "Why don't you count for us, Aelin?"

Aelin kept her mouth shut.

"Count, or we'll begin again with each stroke you miss. You decide how long this goes on for. Unless you'd rather Elide Lochan receive these strokes." No. Never.

Never anyone else but her. \emph{Never.}

But as Cairn walked slowly, savoring each step, as he let that whip drag along the ground, her body betrayed her. Began shaking.

She knew the pain. Knew what it'd feel like, what it'd sound like.

Her dreams were still full of it.

No doubt why Maeve had picked a whipping, why she'd done it to Rowan in Doranelle.

Cairn halted. She felt him studying the tattoo on her back. Rowan's loving words, written there in the Old Language.

Cairn snorted. Then she felt him revel in how he'd destroy that tattoo.

"Begin," Maeve said.

Cairn's breath sucked in.

And even bracing herself, even clamping down hard, there was nothing to prepare for the crack, the sting, the pain. She did not let herself cry out, only hissed through her teeth.

A whip wielded by an overseer at Endovier was one thing.

One wielded by a full-blooded Fae male 

Blood slid down the back of her pants, her split skin screaming.

But she knew how to pace herself. How to yield to the pain. How to take it.

"What number was that, Aelin?"

She would not. She would \emph{never} count for that rutting
\emph{bitch}--- "Start over, Cairn," Maeve said.

A breathy laugh. Then the crack and the pain and Aelin arched, the tendons

in her neck near snapping as she panted through clenched teeth. The males holding her gripped her firm enough to bruise.

Maeve and Cairn waited.

Aelin refused to say the word. To start the count. She'd die before she did it.

"Oh gods, oh gods," Elide sobbed.

"Start over," Maeve merely ordered over the girl.

So Cairn did.

Again.

Again. Again.

They started over nine times before Aelin finally screamed. The blow had been right atop another one, tearing skin down to the bone.

Again.

Again.

Again.

Again.

Cairn was panting. Aelin refused to speak.

"Start over," Maeve repeated.

"Majesty," murmured one of the males holding her. "It might be prudent to postpone until later."

"There's still plenty of skin," Cairn snapped.

But the male said, "Others are approaching---still far off, but approaching." Rowan.

Aelin whimpered then. Time---she had needed \emph{time}---

Maeve made a small noise of distaste. "We'll continue later. Get her ready."

Aelin could barely lift her head as the males heaved her up. The movement set her body roaring in such pain that darkness swarmed in. But she fought it, gritted her teeth and silently roared back at that agony, that darkness.

A few feet away, Elide slid to her knees as if she'd beg until her body gave out, but Manon caught her. "We're going now," Manon said, tugging her away--- inland.

"No," Elide spat, thrashing.

Lorcan's eyes widened, but with Maeve's command, he couldn't move, couldn't do anything as Manon slammed the hilt of Wind-Cleaver into the side of Elide's head.

The girl dropped like a stone. That was all Manon needed to haul her over a shoulder and say to Maeve, "Good luck." Her eyes slid to Aelin's once---only once. Then she looked away.

Maeve ignored the witch as Manon prowled toward the heart of the marshes.

Lorcan's body strained.

Strained---like he was fighting that blood oath with everything in him.

Aelin didn't care.

The males half dragged her toward Maeve.

Toward the iron box. And the chains. And the iron mask.

Whorls of fire, little suns, and embers had been shaped into its dark surface. A mockery of the power it was to contain---the power Maeve had needed to ensure was fully drained before she locked her up. The only way she could ever lock her up.

Every inch her feet dragged through the sand was a lifetime; every inch was a heartbeat. Blood soaked her pants. She likely wouldn't be able to heal her wounds within all that iron. Not until Maeve decided to heal them herself.

But Maeve wouldn't let her die. Not with the Wyrdkeys in the balance. Not yet.

Time---she was grateful Elena had given her that stolen time.

Grateful she had met them all, that she had seen some small part of the world, had heard such lovely music, had danced and laughed and known true friendship. Grateful that she had found Rowan.

She was grateful.

So Aelin Galathynius dried her tears.

And did not fight when Maeve strapped that beautiful iron mask over her face.
