
\chapter{73}

Manon kept walking.

She didn't dare look back. Didn't dare give that ancient, cold-eyed queen one hint that Aelin did not possess the Wyrdkeys. That Aelin had slipped them both into Manon's pocket when she'd nudged her. Elide would hate her for it--- already did hate her for it.

Let that be the cost.

One look from Aelin and she'd known what she had to do.

Get the keys away from Maeve. Get Elide away.

They had forged an iron box to contain the Queen of Terrasen.

Elide stirred, at last coming to, just as they were nearly out of hearing range. She began thrashing, and Manon dumped her behind a dune, gripping the back of her neck so tightly Elide stilled at the iron nails piercing her skin.

"Silence," Manon hissed, and Elide obeyed.

Keeping low, they peered through the grasses. Only a moment---she could spare only a moment to watch, to glean where Maeve was taking the Queen of Terrasen.

Lorcan remained frozen as Maeve had commanded. Gavriel was barely conscious, panting in the grass, as if ripping that blood oath from him had been as grave as any physical wound.

Fenrys---Fenrys's eyes were alive with hatred as he watched Maeve and Cairn. Blood coated Cairn's whip, still dangling at his side as Maeve's soldiers finished strapping that mask over Aelin's face.

Then they clamped irons around her wrists.

Ankles.

Neck.

No one healed her ravaged back, barely more than a bloody slab of meat, as they guided her into the iron box. Made her lie upon her wounds.

And then slid the lid into place. Locked it.

Elide vomited in the grass.

Manon put a hand on the girl's back as the males began carrying the box down the dunes, to the boat, and the ship beyond.

"Fenrys, go," Maeve ordered, pointing to the ship.

Breathing raggedly but unable to refuse the order, Fenrys followed. He glanced once at the white shirt discarded in the sand. It was splattered with blood ---spray from the whipping.

Then he was gone, stepping through air and wind and into nothing.

Alone with Lorcan, Maeve said to the warrior, "You have done all this---for me?"

He did not move. Maeve said, "Speak."

Lorcan loosed a shuddering breath and said, "Yes. Yes---it was all for you. All of it."

Elide gripped the seagrass in fistfuls, and Manon half wondered if she'd grow iron nails and shred it apart at the fury in her face. The hate.

Maeve stepped over Aelin's blood-splattered shirt, and brushed her hand over Lorcan's cheek. "I have no use," she crooned, "for self-righteous males who think they know best."

He stiffened. "Majesty---"

"I strip you of the blood oath. I strip you of your assets and your titles and your properties. You, like Gavriel, are released with dishonor and shame. You are exiled from Doranelle for your disobedience, your treachery. Should you step foot inside my borders, you will die."

"Majesty, I beg you---"

"Go beg someone else. I have no use for a warrior I cannot trust. I rescind my kill order. Letting you live with the shame will be far worse for you, I think." Blood welled at his wrist, then hers. Spilling on the ground.

Lorcan fell to his knees.

"I do not suffer fools gladly," Maeve said, leaving him in the sand, and walked away.

As if she'd dealt him a blow, the twin to Gavriel's, Lorcan couldn't seem to move, to think or breathe. He tried crawling, though. Toward Maeve. The bastard tried crawling.

"We need to go," Manon murmured. The moment Maeve checked to see where those keys were  They had to go.

A roar grumbled on the horizon.

Abraxos.

Her heart thundered in her chest, joy sparking, but---

Elide remained in the grass. Watching Lorcan crawl toward the queen now striding across the beach, black gown flowing behind her.

Watching the boat row to the awaiting ship, that iron coffin in its center, Maeve sitting beside it, one hand on the lid. For her sanity, Manon prayed that Aelin wouldn't be awake the entire time she was inside.

And for the sake of their world, Manon prayed the Queen of Terrasen could survive it.

If only so Aelin could then die for them all.
