
\chapter{75}

Rowan had married Aelin before dawn barely two days ago.

Aedion and Lysandra had been the only witnesses as they'd awoken the bleary-eyed captain, who married them quickly and quietly and signed a vow of secrecy.

They'd had fifteen minutes in their cabin to consummate that marriage.

Aedion still carried the formal documents; the captain bearing the duplicates.

Rowan had been kneeling on that spit of beach for half an hour now. Silent, wandering the paths of his churning thoughts. Aedion had kept him company, staring blankly at the sea.

Rowan had known.

Part of him had known that Aelin was his mate. And had turned away from that knowledge, again and again, out of respect for Lyria, out of terror for what it'd mean. He'd leapt in front of her at Skull's Bay knowing it, deep down. Knowing mates aware of the bond could not bear to harm each other, and that it might be the only force to compel her to regain control from Deanna. And even when she had proved him right  He had turned from that proof, still unready, pushing it from his mind even as he claimed her in every other way.

Aelin had known, though. That he was her mate. And she had not pushed it, or demanded he face it, because she loved him, and he knew she'd rather carve out her own heart than cause him pain or distress.

His Fireheart.

His equal, his friend, his lover. His wife.

His mate.

That gods-damned bitch had put her in an iron box.

She'd whipped his mate so brutally that he'd rarely seen such blood spilled as a result. Then chained her. Then put Aelin in a veritable iron coffin, still bleeding, still hurting.

To contain her. To break her. To torture her.

His Fireheart, locked in the dark.

She'd tried to tell him. Right before the ilken converged.

Tried to tell him she'd vomited her guts up on the ship that day not because she was pregnant but because she'd realized she was going to die. That the cost of sealing the gate, forging a new Lock to do so, was her life. Her immortal life.

Goldryn lying beside him, its ruby dull in the bright sun, Rowan gathered up two fistfuls of sand and let the grains slide out, let the wind carry them toward the sea.

\emph{It was all borrowed time anyway.}

Aelin did not expect them to come for her.

She, who had come for them, who had found them all. She had arranged for everything to fall into place when she yielded her life. When she gave up a thousand years to save them.

And Rowan knew she believed they'd make the right choice, the wise choice, and remain here. Lead their armies to victory---the armies she'd secured for them, guessing that she wouldn't be there to see it through.

She did not think she'd ever see him again.

He did not accept that.

He would not accept that.

And he would not accept that he had found her, and she had found him, and they had survived such sorrow and pain and despair together, only to be cleaved apart. He would not accept the fate that had been dealt to her, would not accept that her life was the asking price for saving this world. Her life, or Dorian's.

He would not accept it for one heartbeat.

Footsteps thudded on the sand, and he scented Lorcan before he bothered to look. For half a breath, he debated killing the male where he stood.

Rowan knew that today---today he'd win. Something had fractured in Lorcan, and if Rowan attacked now, the other male would die. Lorcan might not even put up much of a fight.

Lorcan's granite-hewn face was hard, but his eyes  That was agony in them. And regret.

The others flowed down the dunes, the witch's coven remaining behind, and Aedion rose to his feet.

They all stared at Rowan as he remained kneeling.

The sea rolled away, undulating under the clearing blue sky.

He speared that bond into the world, casting it wide as a net. Flinging it out with his magic, his soul, his cracked heart. Searching for her.

\emph{Fight it}, he willed her, sending the words down the bond---the mating bond, which perhaps had settled into place that first moment they'd become \emph{carranam}, hidden beneath flame and ice and hope for a better future. \emph{Fight her. I am coming for you. Even if it takes me a thousand years. I will find you, I will find you, I will find you.}

Only salt and wind and water answered him.

Rowan rose to his feet. And slowly turned to face them.

But their attention snagged on the ships now sailing out of the west---from the battle site. His cousins' ships, with what remained of the fleet Ansel of Briarcliff had won for them, and Rolfe's three ships.

But it was not those boats that made him pause.

It was the one that rounded the eastern tip of the land---a longboat. It swept closer on a phantom wind, too fast to be natural.

Rowan braced himself. The boat's shape didn't belong to any of the fleets assembled. But its style nagged at his memory.

From their own fleet, Ansel of Briarcliff and Enda were soaring over the waves in a longboat, aiming for this beach.

But Rowan and the others watched in silence as the foreign boat crested through the surf and slid onto the sand.

Watched the olive-skinned sailors haul it up the beach. A broad-shouldered young man nimbly leaped out, his slightly curling dark hair tossed in the sea breeze.

He did not emit a whiff of fear as he stalked for them---didn't even go for the comforting touch of the fine sword at his side.

"Where is Aelin Galathynius?" the stranger asked a bit breathlessly as he scanned them.

And his accent 

"Who are you," Rowan ground out.

But the young man was now close enough that Rowan could see the color of his eyes. Turquoise---with a core of gold.

Aedion breathed as if in a trance, "Galan." Galan Ashryver, Crown Prince of Wendlyn.

The young man's eyes widened as he took in the warrior-prince. "\emph{Aedion}," he said hoarsely, something like awe and grief in his face. But he blinked it away, self-assured and steady, and again asked, "Where is she?"

None of them answered. Aedion demanded, "What are you doing here?"

Galan's dark brows flicked toward each other. "I thought she would have informed you."

"Informed us of \emph{what}?" Rowan said too quietly.

Galan reached into the pocket of his worn blue tunic, pulling out a crinkled letter that looked like it had been read a hundred times. He silently handed it to Rowan.

Her scent still clung to it as he unfolded the paper, Aedion reading over his shoulder.

Aelin's letter to the Prince of Wendlyn had been short. Brutal. The large letters were sprawled across the page as if her temper had gotten the better of her:

\emph{TERRASEN REMEMBERS EVALIN ASHRYVER.}

\emph{DO YOU?}

\emph{I FOUGHT AT MISTWARD FOR YOUR PEOPLE. RETURN THE GODS-DAMNED FAVOR.}

And then coordinates---for this spot.

"It only went to me," Galan said softly. "Not to my father. Only to me." To the armada that Galan controlled---as a blockade runner against Adarlan.

"Rowan," Lysandra murmured in warning. He followed her stare.

Not to where Ansel and Enda now arrived at the edge of their group, giving the Thirteen a wide berth as they lifted their brows at Galan.

But to the small company of white-clad people that appeared on the cresting dunes behind them, splattered in mud and looking like they had trekked across the marshes themselves.

And Rowan knew.

He knew who they were before they even reached the beach.

Ansel of Briarcliff had gone pale at the sight of their layered, flowing clothes. And as the tall male in their center peeled off his hood to reveal a brown-skinned, green-eyed face still handsome with youth, the Queen of the Wastes whispered, "Ilias."

Ilias, son of the Mute Master of the Silent Assassins, gaped at Ansel, his back stiffening. But Rowan stepped toward the man, drawing his attention. Ilias's eyes narrowed in assessment. And he, like Galan, scanned them all, searching for a golden-haired woman who was not there. His eyes returned to Rowan as if he'd marked him as the axis of this group.

In a voice hoarse from disuse, Ilias asked him, "We have come to fulfill our life debt to Celaena Sardothien---to Aelin Galathynius. Where is she?"

"You are the \emph{sessiz suikast}," Dorian said, shaking his head. "The Silent Assassins of the Red Desert."

Ilias nodded. And glanced at Ansel, who still seemed near vomiting, before saying to Rowan, "It seems my friend has called in many debts in addition to ours."

As if the words themselves were a signal, more white-clad figures filled the dunes behind them.

Dozens. Hundreds.

Rowan wondered if every single assassin from that desert Keep had come to honor their debt to the young woman. A lethal legion in themselves.

And Galan 

Rowan turned to the Crown Prince of Wendlyn. "How many," he asked.

"How many did you bring?"

Galan only smiled a bit and pointed to the eastern horizon.

Where white sails now broke over its rim. Ship after ship after ship, each bearing the cobalt flag of Wendlyn.

"Tell Aelin Galathynius that Wendlyn has never forgotten Evalin Ashryver,"

Galan said to him, to Aedion. "Or Terrasen."

Aedion fell to his knees in the sand as Wendlyn's armada spread before them.

\emph{I promise you that no matter how far I go, no matter the cost, when you call for my aid, I will come}, Aelin had told him she'd sworn to Darrow. \emph{I'm going to call in old debts and promises. To raise an army of assassins and thieves and exiles and commoners.}

And she had. She had meant and accomplished every word of it.

Rowan counted the ships that slid over the horizon. Counted the ships in their own armada. Added Rolfe's---and the Mycenians he was rallying in the North.

"Holy gods," Dorian breathed as Wendlyn's armada kept spreading wider and wider.

Tears slid down Aedion's face as he silently sobbed. \emph{Where are our allies, Aelin? Where are our armies?} She had taken the criticism---taken it, because he knew she hadn't wanted to disappoint them if she failed. Rowan put a hand on Aedion's shoulder.

\emph{All of it for Terrasen}, she had said that day she'd revealed she'd schemed her way into getting Arobynn's fortune. And Rowan knew that every step she had taken, every plan and calculation, every secret and desperate gamble  For Terrasen. For them. For a better world.

Aelin Galathynius had raised an army not just to challenge Morath
 but to rattle the stars.

She'd known that she would not get to lead it. But she would still hold true to her promise to Darrow: \emph{I promise you on my blood, on my family's name, that I will not turn my back on Terrasen as you have turned your back on me.}

And the last piece of it  if Chaol Westfall and Nesryn Faliq could rally forces from the southern continent 

Aedion at last looked up at him, eyes wide as he came to the same realization.

A chance. His wife, his mate, had bought them a fool's shot at this war. And she did not believe that they would come for her.

"Galan?"

Rowan went still as death at the voice that floated over the dunes. At the golden-haired woman who wore the skin of his beloved.

Aedion shot to his feet, about to snarl, when Rowan gripped his arm.

When Lysandra, as Aelin, as she had promised, swept for them, grinning wide.

That smile  It punched a hole through his heart. Lysandra had taught herself Aelin's smile, that bit of wickedness and delight, honed with that razor edge of cruelty.

Lysandra's acting, honed in the same hellhole Aelin had learned hers, was flawless as she spoke to Galan. As she spoke to Ilias, embracing him like a longlost friend, and a relieved ally.

Aedion was trembling beside him. But the world could not know.

Their allies, their enemies, could not know that the immortal fire of Mala had been stolen. Leashed.

Galan said to the one whom he believed to be his cousin, "Where now?"

Lysandra looked to him, then to Aedion, not a sign of regret or guilt or doubt on her face. "We go north. To Terrasen."

Rowan's stomach turned leaden. But Lysandra caught his eye, and said steadily and casually, "Prince---I need you to retrieve something for me before you join us in the North."

\emph{Find her, find her, find her}, the shifter seemed to beg.

Rowan nodded, at a loss for words. Lysandra took his hand, squeezed it once in thanks, a polite, public farewell between a queen and her consort, and stepped away.

"Come," Lysandra said to Galan and Ilias, motioning them toward where a white-faced Ansel and frowning Enda waited. "We have matters to discuss before we head out."

Then their little company was alone once more.

Aedion's hands clenched and unclenched at his sides as he gazed after the shape-shifter wearing Aelin's skin, leading their allies down the beach. To give them privacy.

An army to take on Morath. To give them a fighting chance 

Sand whispered behind him as Lorcan stepped up to his side. "I will go with you. I will help you get her back."

Gavriel rasped, "We'll find her." Aedion at last looked away from Lysandra at that. But he said nothing to his father---had said nothing to him at all since they'd landed on the beach.

Elide took a limping step closer, her voice as raw as Gavriel's. "Together. We'll go together."

Lorcan gave the Lady of Perranth an assessing look that she made a point to ignore. His eyes flickered as he said to Rowan, "Fenrys is with her. He'll know we're coming for her---try to leave tracks if he can."

If Maeve didn't have him on lockdown. But Fenrys had battled the blood oath every day since swearing it. And if he was all that now stood between Cairn and Aelin  Rowan didn't let himself think about Cairn. About what Maeve had already had him do, or would do to her before the end. No---Fenrys would fight it. And Aelin would fight it.

Aelin would never stop fighting.

Rowan faced Aedion, and the warrior-prince again peeled his attention away from Lysandra long enough to meet his eyes. Aedion understood the look, and put a hand on the Sword of Orynth's hilt. "I'll go north. With---her. To oversee the armies, make sure it's all in place."

Rowan clasped Aedion's forearm. "The lines have to hold. Buy us whatever time you can, brother."

Aedion gripped his forearm in return, eyes burning bright. Rowan knew how much it killed him. But if the world believed Aelin was returning north, then one of her generals had to be at her side to lead her armies. And since Aedion commanded the loyalty of the Bane 
"Bring her back, Prince," Aedion said, voice cracking. "Bring her home."

Rowan held his brother's stare and nodded. "We will see you again. All of you."

He did not waste words persuading the warrior-prince to forgive the shifter.

He wasn't entirely sure what to even make of Aelin and Lysandra's plan. What \emph{his} role would have been in it.

Dorian stepped forward, but glanced to Manon, who was staring toward the sea as if she could see wherever Maeve had spirited away her ship. Using that cloaking power she'd wielded to hide Fenrys and Gavriel in Skull's Bay---hide her armada from the eyes of Eyllwe. "The witches fly north," Dorian said. "And

I will go with them. To see if I can do what needs to be done."

"Stay with us," Rowan offered. "We'll find a way to deal with the keys and the Lock and the gods---all of it."

Dorian shook his head. "If you go after Maeve, the keys should be kept far away. If I can help by doing this, by finding the third  I will serve you better that way."

"You'll likely die," Aedion cut in sharply. "We go north to bloodshed and killing fields---you head into dangers far worse than that. Morath will be waiting." Rowan cut him a glare. But his brother was beyond caring. No, Aedion was riding a vicious, vulnerable edge right now---and it wouldn't take much for that edge to turn lethal. Especially when Dorian had played his part in separating Aelin from their group.

Dorian again looked to Manon, who now smiled faintly at him. It was a smile that softened her face, made it come alive. "He won't die if I can help it," the witch said, then surveyed them all. "We journey to find the Crochans---to rally what forces they might have."

A witch army to counter the Ironteeth legions.

Hope---precious, fragile hope---stirred Rowan's blood.

Manon merely jerked her chin in farewell and prowled up the bluff to her coven.

So Rowan nodded to Dorian. But the man bowed his head---not the gesture of a friend to a friend. But of one king to another.

Consort, he wanted to say. He was just her consort.

Even if she'd married him so he could have the legal right to save Terrasen and rebuild it. To command the armies she'd given everything to gather for them.

"When we are done, I will join you in Terrasen, Aedion," the King of Adarlan promised. "So that when you get back, Rowan---when \emph{both}
of you get back---there will be something left to fight for."

Aedion seemed to consider. To weigh the man's words and expression. And then the general-prince stepped forward and embraced the king. It was quick, and hard, and Dorian flinched, but that edge in Aedion's grief-dull eyes had been eased a bit. Silently, Aedion glanced at Damaris, sheathed at Dorian's side. The blade of Adarlan's first and greatest king. Aedion seemed to weigh its presence, who bore it. At last, the general-prince nodded, more to himself than anyone. But Dorian still bowed his head in thanks.

When Aedion had stalked toward the longboats, deliberately stepping around Lysandra-Aelin when she tried to speak to him, Rowan said to the king, "You trust the witches?"

A nod. "They're leaving two wyverns to guard your ship to the edge of the continent. From there, they'll join us again---and you'll set off wherever  wherever you need to go."

Maeve could have taken her anywhere, vanished that ship halfway across the world.

Rowan said to Dorian, "Thank you."

"Don't thank me." A half smile. "Thank Manon."

If they all lived through this, if he got Aelin back, he would.

He embraced Dorian, wished the king well, and watched the man climb up the sandbank to the white-haired witch who waited for him.

Lysandra was already giving orders to Galan and Ilias regarding transporting the two hundred Silent Assassins onto Wendlyn's ships, Aedion monitoring with crossed arms. Ansel was deep in conversation with Endymion, who didn't seem to quite know what to do with the red-haired queen with a wolf's smile. Ansel, however, seemed already inclined to raise hell and have a damn good time doing it. Rowan wished he had more than a moment to spare to thank them both---to thank Enda and each one of his cousins.

All was set, all was ready for that desperate push north. As Aelin had planned.

There would be no rest, no waiting. They did not have the time to spare.

The wyverns stirred, flapping their wings. Dorian climbed into the saddle behind Manon and wrapped his arms around her waist. The witch said something that made him smile. Truly smile.

Dorian lifted his hand in farewell, wincing as Abraxos soared into the skies.

Ten other wyverns took to the air behind them.

The grinning, golden-haired witch---Asterin---and a slender, black-haired, green-eyed one named Briar waited atop their mounts for Gavriel, Lorcan, and Elide. To carry them to the ship that would take them hunting across the sea.

Lorcan made to step toward Elide as she approached Asterin's wyvern, but

she ignored him. Didn't even look at the male as she took Asterin's hand and was hauled up into the saddle. And though Lorcan hid it well, Rowan caught the glimmer of devastation on those centuries-hardened features.

Gavriel's barked curse as he gripped the golden-haired witch's waist was the only sound of his unease as they flapped into the sky. Only when they were all airborne did Rowan slowly walk up the sandy hill, tying Goldryn's ancient scabbard to his knife belt as he went.

Her blood-splattered shirt was still lying there, just to the side of the pool of her blood soaking the sand. He had no doubt Cairn had purposely left it.

Rowan bent, picking up the shirt, running his thumbs over the soft fabric.

The coven faded into the horizon; his companions reached their ship, and the others were readying to move the army his mate had summoned for them, pushing the longboats into the surf.

Rowan brought the shirt to his face and breathed in her scent. Felt something stir in him---felt the bond flicker.

He let the shirt drop, let the wind carry it far out to sea, far away from this blood-drenched place that reeked of pain.

\emph{I will find you.}

Rowan shifted and soared high on a fast, wicked wind of his own making, the glimmering sea sprawling to his right, the marshes a green-and-gray tangle to his left. Chaining the wind to him, swiftly catching up with his companions now flying down the coast, he committed her scent to memory, committed that flicker in the bond to memory.

That flicker he could have sworn he felt in answer, like the fluttering heart of an ember.

Unleashing a cry that set the world trembling, Prince Rowan Whitethorn Galathynius, Consort of the Queen of Terrasen, began the hunt to find his wife.
