
\chapter{8}

Rowan Whitethorn had flown without food or water or rest for two days.

He'd still reached Rifthold too late.

The capital was in chaos under the claws of the witches and their wyverns.
He'd seen enough cities fall over the centuries to know that this one was done for.

Even if the people rallied, it would only be to meet their deaths head-first.
The witches had already brought down Aelin's glass wall.
Another calculated move by Erawan.

It had been an effort to leave the innocent to fight on their own, to race hard and fast for the stone castle and the king's tower.
He had one order, given to him by his queen.

He'd still come too late---but not without a glimmer of hope.

Dorian Havilliard stumbled as they hurried down the castle hallway, Rowan's keen ears and sense of smell keeping them from areas where the fighting raged.
If the secret tunnels were watched, if they could not reach the sewers\ldots Rowan calculated plan after plan.
None ended well.

"This way," the king panted.
It was the first thing Dorian had said since rushing down the stairs.
They were in a residential part of the palace Rowan had only seen from his own scouting outside---in hawk form.
The queen's quarters.

"There's a secret exit from my mother's bedroom."
The pale white doors to the queen's suite were locked.

Rowan blasted through them with half a thought, wood splintering and impaling the lavish furniture, the art on the walls.
Baubles and valuables shattered.
"Sorry," Rowan said to the king---not sounding like it at all.

His magic flickered, a distant flutter to let him know it was draining.
Two days of riding the winds at breakneck speed, then fighting off those wyverns outside, had taken its toll.

Dorian surveyed the casual damage.
"Someone would have done it anyway."
No feeling, no sorrow behind it.
He hurried through the room, limping a bit.
If the king had possessed a fraction less magic, he might have succumbed to the wyvern's venomous tail.

Dorian reached a large, gilded portrait of a beautiful auburn-haired young woman with a sapphire-eyed babe in her arms.

The king looked at it for a heartbeat longer than necessary, enough to tell Rowan everything.
But Dorian hauled the painting toward him.
It pulled away to reveal a small trapdoor.

Rowan saw to it that the king went inside first, candle in hand, before using his magic to float the painting back into its resting place, then shutting the door behind them.

The hall was cramped, the stones dusty.
But the wind ahead whispered of open spaces, of dampness and mold.
Rowan sent a tendril of magic to probe the stairs they now strode down and the many halls ahead.
No sign of the cave-in from when they'd destroyed the clock tower.
No signs of enemies lying in wait, or the corrupt reek of the Valg and their beasts.
A small mercy.

His Fae ears picked up the muffled screams and shouts of the dying above them.

"I should stay," Dorian said softly.

A gift of the king's magic, then---the enhanced hearing.
Raw magic that could grant him any gifts: ice, flame, healing, heightened senses and strength.
Perhaps shape-shifting, if he tried.

"You are more useful to your people alive," Rowan said, his voice rough against the stones.
Exhaustion nagged at him, but he shoved it aside.
He'd rest when they were safe.

The king didn't respond.

Rowan said, "I have seen many cities fall.
I have seen entire kingdoms fall.
And the destruction I saw as I flew in was thorough enough that even with your considerable gifts, there is nothing you could have done."
He wasn't entirely sure what they'd do if that destruction were brought to Orynth's doorstep.
Or why Erawan was waiting to do it.
He'd think about that later.

"I should die with them," was the king's answer.

They reached the bottom of the stairs, the passage now widening into breathable chambers.
Rowan again snaked his magic through the many tunnels and stairs.
The one to the right suggested a sewer entrance lay at its bottom.

Good.

"I was sent here to keep you from doing just that," Rowan said at last.

The king glanced over his shoulder at him, wincing a bit as the motion stretched his still-healing skin.
Where Rowan suspected a gaping wound had been minutes before, now only an angry red scar peeked through the side of his torn jacket.
Dorian said, "You were going to kill her."

He knew whom the king meant.
"Why did you tell me not to?"

So the king told him of the encounter as they descended deeper into the castle's bowels.
"I wouldn't trust her," Rowan said after Dorian had finished, "but perhaps the gods will throw us a bone.
Perhaps the Blackbeak heir will join our cause."

If her crimes weren't discovered first.
But even if they only had thirteen witches and their wyverns, if that coven was the most skilled of all the Ironteeth\ldots it could mean the difference between Orynth falling or standing against Erawan.

They reached the castle sewers.
Even the rats were fleeing through the small stream entrance, as if the bellowing of the wyverns were a death knell.

They passed an archway sealed off by collapsed stones---no doubt from the hellfire eruption this summer.

Aelin's passageway, Rowan realized with a tug deep in his chest.
And a few steps ahead, an old pool of dried blood stained the stones along the water's edge.

A human reek lingered around it, tainted and foul.

"She gutted Archer Finn right there," Dorian said, following his stare.

Rowan didn't let himself think about it, or that these fools had unwittingly given an assassin a room that connected to their queen's chambers.

There was a boat moored to a stone post, its hull almost rotted through, but solid enough.
And the grate to the little river snaking past the castle remained open.

Rowan again speared his magic into the world, tasting the air beyond the sewers.
No wings cleaved it, no blood scented its path.
A quiet, eastern part of the castle.
If the witches had been smart, they'd have sentries monitoring every inch of it.

But from the screaming and pleading going on above, Rowan knew the witches were too lost in their bloodlust to think straight.
At least for a few minutes.

Rowan jerked his chin to the boat.
"Get in."

Dorian frowned at the mold and rot.
"We'll be lucky if it doesn't collapse around us."

"You," Rowan corrected.
"Around you.
Not me.
Get in."

Dorian heard his tone and wisely got in.
"What are you---"

Rowan yanked off his cloak and threw it over the king.
"Lie down, and put that over you."

Face a bit pale, Dorian obeyed.
Rowan snapped the ropes with a flash of his knives.

He shifted, wings flapping loudly enough to inform Dorian what had happened.
Rowan's magic groaned and strained while it pushed what looked like an empty, meandering vessel out of the sewers, as if someone had accidentally loosed it.

Flying through the sewer mouth, he shielded the boat with a wall of hard air ---containing the king's scent and keeping any stray arrows from piercing it.

Rowan looked back only once as he flew down the little river, high above the boat.

Only once, at the city that had forged and broken and sheltered his queen.

Her glass wall was no more than chunks and shards gleaming in the streets and the grass.

These past weeks of travel had been torture---the need to claim her, taste her, driving him out of his wits.
And given what Darrow had said  perhaps, despite his promise when he'd left, it had been a good thing that they had not taken that final step.

It had been in the back of his mind long before Darrow and his horse-shit decrees: he was a prince, but in name only.

He had no army, no money.
The substantial funds he possessed were in Doranelle---and Maeve would never allow him to claim them.
They'd likely already been distributed amongst his meddlesome cousins, along with his lands and residences.
It wouldn't matter if some of them---the cousins he'd been raised with---might refuse to accept out of typical Whitethorn loyalty and stubbornness.
All Rowan now had to offer his queen were the strength of his sword, the depth of his magic, and the loyalty of his heart.

Such things did not win wars.

He'd scented the despair on her, though her face had hidden it, when Darrow had spoken.
And he knew her fiery soul: she would do it.
Consider marriage to a foreign prince or lord.
Even if this thing between them  even if he knew it was not mere lust, or even just love.

This thing between them, the force of it, could devour the world.

And if they picked it, picked \emph{them}, it might very well cause the end of it.

It was why he had not uttered the words he'd meant to tell her for some time, even when every instinct was roaring for him to do it as they parted.
And maybe having Aelin only to lose her was his punishment for letting his mate die; his punishment for finally letting go of that grief and loathing.

The lap of waves was barely audible over the roar of wyverns and the innocents screaming for help that would never come.
He shut out the ache in his chest, the urge to turn around.

This was war.
These lands would endure far worse in the coming days and months.
His queen, no matter how he tried to shield her, would endure far worse.

By the time the boat drifted down the little river snaking toward the Avery delta, a white-tailed hawk soaring high above it, the walls of the stone castle were bathed in blood.
