
\chapter*{Nightfall}
\addcontentsline{toc}{chapter}{Nightfall}

The bone drums had been pounding across the jagged slopes of the Black Mountains since sundown.

From the rocky outcropping on which her war tent groaned against the dry wind, Princess Elena Galathynius had monitored the dread-lord's army all afternoon as it washed across those mountains in ebony waves. And now that the sun had long since vanished, the enemy campfires flickered across the mountains and valley below like a blanket of stars.

So many fires---so many, compared to those burning on her side of the valley.

She did not need the gift of her Fae ears to hear the prayers of her human army, both spoken and silent. She'd offered up several herself in the past few hours, though she knew they would go unanswered.

Elena had never considered where she might die---never considered that it might be so far from the rocky green of Terrasen. That her body might not be burned, but devoured by the dread-lord's beasts.

There would be no marker to tell the world where a Princess of Terrasen had fallen. There would be no marker for any of them.

"You need rest," a rough male voice said from the tent entrance behind her.

Elena looked over her shoulder, her unbound silver hair snagging on the intricate leather scales of her armor. But Gavin's dark gaze was already on the two armies stretching below them. On that narrow black band of demarcation, too soon to be breached.

For all his talk of rest, Gavin hadn't removed his own armor upon entering their tent hours before. Only minutes ago had his war leaders finally shoved out of the tent, bearing maps in their hands and not a shred of hope in their hearts. She could scent it on them---the fear. The despair.

Gavin's steps hardly crunched on the dry, rocky earth as he approached her lonely vigil, near-silent thanks to his years roaming the wilds of the South. Elena again faced those countless enemy fires.

He said hoarsely, "Your father's forces could still make it."

A fool's hope. Her immortal hearing had picked up every word of the hours of debate raging inside the tent behind them. "This valley is now a death trap," Elena said.

And she had led them all here.

Gavin did not answer.

"Come dawn," Elena went on, "it will be bathed in blood."

The war leader at her side remained silent. So rare for Gavin, that silence. Not a flicker of that untamed fierceness shone in his uptilted eyes, and his shaggy brown hair hung limp. She couldn't remember the last time either of them had bathed.

Gavin turned to her with that frank assessment that had stripped her bare from the moment she'd first met him in her father's hall nearly a year ago. Lifetimes ago.

Such a different time, a different world---when the lands had still been full of singing and light, when magic hadn't begun to flicker in the growing shadow of Erawan and his demon soldiers. She wondered how long Orynth would hold out once the slaughter here in the South had ended. Wondered if Erawan would first destroy her father's shining palace atop the mountain, or if he would burn the royal library---burn the heart and knowledge of an age. And then burn its people.

"Dawn is yet hours away," said Gavin, his throat bobbing. "Time enough for you to make a run for it."

"They'd tear us to shreds before we could clear the passes---"

"Not us. You." The firelight cast his tan face in flickering relief. "You alone." "I will not abandon these people." Her fingers grazed his. "Or you."

Gavin's face didn't stir. "There is no avoiding tomorrow. Or the bloodshed. You overheard what the messenger said---I know you did. Anielle is a slaughterhouse. Our allies from the North are gone. Your father's army is too far behind. We will all die before the sun is fully risen."

"We'll all die one day anyway."

"No." Gavin squeezed her hand. "I will die. Those people down there---they will die. Either by sword or time. But you\ldots" His gaze flicked to her delicately pointed ears, the heritage of her father. "You could live for centuries. Millennia. Do not throw it away for a doomed battle."

"I would sooner die tomorrow than live for a thousand years with a coward's shame."

But Gavin stared across the valley again. At his people, the last line of defense against Erawan's horde.

"Get behind your father's lines," he said roughly, "and continue the fight from there."

She swallowed hard. "It would be no use."

Slowly, Gavin looked at her. And after all these months, all this time, she confessed, "My father's power is failing. He is close---decades now---from the fading. Mala's light dims inside him with every passing day. He cannot stand against Erawan and win." Her father's last words before she'd set out on this doomed quest months ago: \emph{My sun is setting, Elena}. \emph{You must find a way to ensure yours still rises}.

Gavin's face leeched of color. "You choose now to tell me this?"

"I choose now, Gavin, because there is no hope for me, either---whether I flee tonight or fight tomorrow. The continent will fall."

Gavin shifted toward the dozen tents on the outcropping. His friends.

Her friends.

"None of us are walking away tomorrow," he said.

And it was the way his words broke, the way his eyes shone, that had her reaching for his hand once more. Never---not once in all their adventures, in all the horrors that they had endured together---had she seen him cry.

"Erawan will win and rule this land, and all others, for eternity," Gavin whispered.

Soldiers stirred in their camp below. Men and women, murmuring, swearing, weeping. Elena tracked the source of their terror---all the way across the valley.

One by one, as if a great hand of darkness wiped them away, the fires of the dread-lord's camp went out. The bone drums beat louder.

He had arrived at last.

Erawan himself had come to oversee the final stand of Gavin's army.

"They are not going to wait until dawn," Gavin said, a hand lurching to where Damaris was sheathed at his side.

But Elena gripped his arm, the hard muscle like granite beneath his leather armor.

\emph{Erawan had come.}

Perhaps the gods were still listening. Perhaps her mother's fiery soul had convinced them.

She took in Gavin's harsh, wild face---the face that she had come to cherish above all others. And she said, "We are not going to win this battle. And we are not going to win this war."

His body quivered with the restraint to keep from going to his war leaders,

but he gave her the respect of listening. They'd both given each other that, had learned it the hard way.

With her free hand, Elena lifted her fingers in the air between them. The raw magic in her veins now danced, from flame to water to curling vine to cracking ice. Not an endless abyss like her father's, but a versatile, nimble gift of magic. Granted by her mother. "We are not going to win this war," Elena repeated, Gavin's face aglow in the light of her uncut power. "But we can delay it a little while. I can get across that valley in an hour or two." She curled her fingers into a fist, and snuffed out her magic.

Gavin's brows furrowed. "What you speak of is madness, Elena. Suicide. His lieutenants will catch you before you can even slip through the lines."

"Exactly. They'll bring me right to him, now that he has come. They'll consider me his prized prisoner---not his assassin." "No." An order and a plea.

"Kill Erawan, and his beasts will panic. Long enough for my father's forces to arrive, unite with whatever remains of ours, and crush the enemy legions."

"You say `kill Erawan' as if that is some easy task. He is a Valg
\emph{king}, Elena. Even if they bring you to him, he will leash you to his will before you can make a move."

Her heart strained, but she forced the words out. "That is why\ldots" She couldn't stop her wobbling lips. "That is why I need you to come with me instead of fight with your men." Gavin only stared at her.

"Because I need\ldots" Tears slid down her cheeks. "I need you as a distraction. I need you to buy me time to get past his inner defenses." Just as the battle tomorrow would buy them time.

Because Erawan would go for Gavin first. The human warrior who had been a bastion against the Dark Lord's forces for so long, who had fought him when no other would  Erawan's hatred for the human prince was rivaled only by his hatred for her father.

Gavin studied her for a long moment, then reached to brush her tears away.

"He cannot be killed, Elena. You heard what your father's oracle whispered."

She nodded. "I know."

"And even if we manage to contain him---trap him\ldots" Gavin considered her words. "You know that we are only pushing the war onto someone else---to whoever one day rules these lands."

"This war," she said quietly, "is but the second movement in a game that has been played since those ancient days across the sea."

"We put it off for someone else to inherit if he's freed. And it will not save those soldiers down there from slaughter tomorrow."

"If we do not act, there won't be anyone to inherit this war," Elena said. Doubt danced in Gavin's eyes. "Even now," she pushed, "our magic is failing, our gods abandoning us. Running from us. We have no Fae allies beyond those in my father's army. And their power, like his, is fading. But perhaps, when that third movement comes  perhaps the players in our unfinished game will be different. Perhaps it will be a future in which Fae and humans fight side by side, ripe with power. Maybe they will find a way to end this. So we will lose this battle, Gavin," she said. "Our friends will die on that killing field come dawn, and we will use it as our distraction to contain Erawan so that Erilea might have a future."

His lips tightened, his sapphire eyes wide.

"No one must know," she said, her voice breaking. "Even if we succeed, no one must know what we do."

Doubt etched deep lines into his face. She gripped his hand harder. "\emph{No one},

Gavin."

Agony rippled across his features. But he nodded.

Hand in hand, they stared toward the darkness coating the mountains, the dread-lord's bone drums pounding like hammers on iron. Too soon, those drums would be drowned out by the screams of dying soldiers. Too soon, the valley fields would be carved with streams of blood.

Gavin said, "If we are to do this, we need to leave now." His attention again snagged on the nearby tents. No good-byes. No last words. "I'll give Holdren the order to lead tomorrow. He'll know what to tell the others."

She nodded, and it was confirmation enough. Gavin released her hand, striding for the tent closest to their own, to where his dearest friend and most loyal war leader was likely making the best of his final hours with his new wife.

Elena drew her eyes away before Gavin's broad shoulders pushed through the heavy flaps.

She gazed over the fires, across the valley, to the darkness perched on the other side. She could have sworn it stared back, sworn she heard the thousand whetstones as the dread-lord's beasts sharpened their poison-slick claws.

She lifted her eyes toward the smoke-stained sky, the plumes parting for a heartbeat to reveal a star-flecked night.

The Lord of the North flickered down at her. Perhaps the final gift of Mala to these lands---in this age, at least. Perhaps a thank-you to Elena herself, and a farewell.

Because for Terrasen, for Erilea, Elena would walk into the eternal darkness lurking across the valley to buy them all a chance.

Elena sent up a final prayer on a pillar of smoke rising from the valley floor that the unborn, faraway scions of this night, heirs to a burden that would doom or save Erilea, would forgive her for what she was about to do.
