
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

It's always so difficult to sum up my overwhelming gratitude for the people who not only work so tirelessly to make this book a reality, but who also provide me with such unwavering support and friendship. I don't know what I would do without them in my life, and I thank the universe every single day that they're in it.

To my husband, Josh: Even when this world is a forgotten whisper of dust between the stars, I will love you. Thank you for the laughter on the days when I didn't think I could smile, for holding my hand when I needed a reminder that I was loved, and for being my best friend and safe harbor. You are the greatest joy in my life, and even a thousand pages would not be enough to express how much I love you.

To Annie: By now, it would not surprise me at all if you've learned to read. You are the other great joy in my life, and your unconditional love and unfailing sass make a solitary job into something that never feels lonely---not for one moment. I love you, baby pup.

To Tamar Rydzinski: I have been so grateful for your wisdom, bad-assery, and brilliance from the very first moment you called me all those years ago. But this year especially, I've been even more thankful for your friendship. Thank you for having my back no matter what. I'm so lucky to have you in my corner.

To Cat Onder: Working with you has been such a huge highlight of my career. Thank you from the bottom of my heart for your clever and insightful feedback, for championing my books, and for making this entire process just so \emph{fun}. I'm incredibly proud to have you as an editor and a friend.

To Margaret Miller: Thank you for all of your help and guidance over the years---I've grown so much as a writer because of you, and I'm so grateful for it. To Cassie Homer: Where do I even begin to thank you for all that you do? I truly don't know how I'd manage without your help. You're amazing.

To my unparalleled and marvelous teams at Bloomsbury worldwide and CAA---Cindy Loh, Cristina Gilbert, Jon Cassir, Kathleen Farrar, Nigel Newton, Rebecca McNally, Natalie Hamilton, Sonia Palmisano, Emma Hopkin, Ian

Lamb, Emma Bradshaw, Lizzy Mason, Courtney Griffin, Erica Barmash, Emily Ritter, Grace Whooley, Eshani Agrawal, Emily Klopfer, Alice Grigg, Elise Burns, Jenny Collins, Linette Kim, Beth Eller, Kerry Johnson, Kelly de Groot, Ashley Poston, Lucy Mackay-Sim, Melissa Kavonic, Diane Aronson, Donna Mark, John Candell, Nicholas Church, and the entire foreign rights team: I am so blessed to work with such a spectacular group of people, and I can't imagine my books being in better hands. Thank you, thank you, thank you for \emph{everything}.

To my parents: Thank you for the unwavering love, and for owning a truly embarrassing number of copies of all my books. To my in-laws: Thank you for looking after Annie when we're away---and for always being there for us no matter what. To my wonderful family: I love you all.

To Louisse Ang, Sasha Alsberg, Vilma Gonzalez, Alice Fanchiang, Charlie Bowater, Nicola Wilksinson, Damaris Cardinali, Alexa Santiago, Rachel Domingo, Kelly Grabowski, Jessica Reigle, Jamie Miller, Laura Ashforth, Steph Brown, and the Maas Thirteen: Thank you so, so, so much for your kindness, your generosity, and your friendship. I'm honored to know you guys.

And to my readers: Thank you for the letters, the art, the tattoos(!!), the music---thank you for \emph{all} of it. I can't begin to express how much it means to me, or how thankful I am. You make all the hard work worth it.
