
\chapter{1}

Chaol Westfall, former Captain of the Royal Guard and now Hand to the newly crowned King of Adarlan, had discovered that he hated one sound above all others.

Wheels.

Specifically, their clattering along the planks of the ship on which he'd spent the past three weeks sailing through storm-tossed waters.
And now their rattle and thunk over the shining green marble floors and intricate mosaics throughout the Khagan of the Southern Continent's shining palace in Antica.

With nothing to do beyond sit in the wheeled chair that he'd deemed had become both his prison and his only path to seeing the world, Chaol took in the details of the sprawling palace perched atop one of the capital city's countless hills.
Every bit of material had been taken from and built in honor of some portion of the khagan's mighty empire:

Those polished green floors his chair now clattered over were hewn from quarries in the southwest of the continent.
The red pillars fashioned like mighty trees, their uppermost branches stretching across the domed ceilings high above---all part of one endless receiving hall---had been hauled in from the northeastern, sand-blasted deserts.

The mosaics that interrupted the green marble had been assembled by craftsmen from Tigana, another of the khagan's prized cities at the mountainous southern end of the continent.
Each portrayed a scene from the khaganate's rich, brutal, glorious past: the centuries spent as a nomadic horse-people in the grassy steppes of the continent's eastern lands; the emergence of the first khagan, a warlord who unified the scattered tribes into a conquering force that took the continent piece by piece, wielding cunning and strategic brilliance to forge a sweeping empire; and then depictions of the three centuries since---the various khagans who had expanded the empire, distributing the wealth from a hundred territories across the lands, building countless bridges and roads to connect them all, ruling over the vast continent with precision and clarity.

Perhaps the mosaics provided a vision of what Adarlan might have been, Chaol mused as the murmurings of the gathered court flitted between the carved pillars and gilded domes ahead.
That is, if Adarlan hadn't been ruled by a man controlled by a demon king hell-bent on turning this world into a feast for his hordes.

Chaol twisted his head to peer up at Nesryn, stone-faced behind him as she pushed his chair.
Only her dark eyes, darting over every passing face and window and column, revealed any sort of interest in the khagan's sprawling home.

They'd saved their finest set of clothes for today, and the newly appointed Captain of the Guard was indeed resplendent in her crimson-and-gold uniform.
Where Dorian had dug up one of the uniforms Chaol had once worn with such pride, he had no idea.

He'd initially wanted to wear black, simply because color\ldots He'd never felt comfortable with colors, save the red and gold of his kingdom.
But black had become the color of Erawan's Valg-infested guards.
They had worn those blackon-black uniforms as they'd terrorized Rifthold.
As they'd rounded up, tortured, and then butchered his men.

Then strung them along the palace gates to swing in the wind.

He'd barely been able to look at the Antican guards they'd passed on their way here, both in the streets and in this very palace---standing proud and alert, swords at their backs and knives at their sides.
Even now, he resisted the urge to glance to where he knew they'd be stationed in the hall, exactly where he would have positioned his own men.
Where he himself would undoubtedly have been standing, monitoring all, while emissaries from a foreign kingdom arrived.

Nesryn met his stare, those ebony eyes cool and unblinking, her shoulderlength black hair swaying with each step.
Not a trace of nerves flickered across her lovely, solemn face.
No inkling that they were about to meet one of the most powerful men in the world---a man who could alter the fate of their own continent in the war surely now breaking out across Adarlan and Terrasen.

Chaol faced forward without saying a word.
The walls and pillars and arched doorways had ears and eyes and mouths, she'd warned him.

It was that thought alone that kept Chaol from fiddling with the clothes he'd finally decided upon: light brown pants, knee-high chestnut-colored boots, a white shirt of finest silk, mostly concealed by a dark teal jacket.
The jacket was simple enough, the cost of it only revealed by the fine brass buckles down the front and the glimmer of delicate golden thread skimming the high collar and edges.
No sword hung from his leather belt---the absence of that comforting weight like some phantom limb.

Or legs.

Two tasks.
He had two tasks while here, and he still was not certain which one would prove the more impossible:

Convincing the khagan and his six would-be heirs to lend their considerable armies to the war against Erawan\ldots Or finding a healer in the Torre Cesme who could discover some way to get him walking again.

To---he thought with no small ripple of disgust---fix him.

He hated that word.
Almost as much as the clattering of the wheels.
\emph{Fix}.
Even if that's what he was beseeching the legendary healers to do for him, the word still grated, made his gut churn.

He shoved the word and the thought from his mind as Nesryn followed the near-silent flock of servants who had led them from the docks, through the winding and dusty cobblestoned streets of Antica, all the way up the sloped avenue to the domes and thirty-six minarets of the palace itself.

Strips of white cloth---from silk to felt to linen---had been hanging from countless windows and lanterns and doorways.
Likely because of some official or distant royal relation dying recently, Nesryn had murmured.
Death rituals were varied and often a blend from the countless kingdoms and territories now governed by the khaganate, but the white cloth was an ancient holdover from the centuries when the khagan's people had roamed the steppes and laid their dead to rest under the watchful, open sky.

The city had been hardly gloomy, though, as they traveled through it.
People still hurried about in clothes of various makes, vendors still called out their wares, acolytes in temples of wood or stone---every god had a home in Antica, Nesryn supplied---still beckoned to those on the street.
All of it, even the palace, watched over by the shining, pale-stoned tower atop one of its southern hills.

The Torre.
The tower that housed the finest mortal healers in the world.
Chaol had tried not to look too long at it through the carriage windows, even if the massive tower could be seen from nearly every street and angle of Antica.
None of the servants had mentioned it, or pointed out the dominant presence that seemed to rival even the khagan's palace.

No, the servants hadn't said much at all on the trek here, even regarding the mourning-banners flapping in the dry wind.
Each of them remained silent, men and women alike, their dark hair shining and straight, and each wore loose pants and flowing jackets of cobalt and bloodred edged with pale gold.
Paid servants ---but descendants of the slaves who had once been owned by the khagan's bloodline.
Until the previous khagan, a visionary and firebrand, had outlawed slavery a generation ago as one of her countless improvements to the empire.
The khagan had freed her slaves but kept them on as paid servants---along with their children.
And now their children's children.

Not a single one of them appeared underfed or undercompensated, and none had shown even a flicker of fear as they'd escorted Chaol and Nesryn from the ship to the palace.
The current khagan, it seemed, treated his servants well.
Hopefully his yet-undecided Heir would as well.

Unlike Adarlan or Terrasen, inheritance of the empire was decided by the khagan---not by birth order or gender.
Having as many children as possible to provide him or her with a wide pool to choose from made that choice only somewhat easier.
And rivalry amongst the royal children\ldots It was practically a blood sport.
All designed to prove to their parent who was the strongest, the wisest, the most suited to rule.

The khagan was required by law to have a sealed document locked away in an unmarked, hidden trove---a document that listed his or her Heir, should death sweep upon them before it could be formally announced.
It could be altered at any time, but it was designed to avoid the one thing the khaganate had lived in fear of since that first khagan had patched together the kingdoms and territories of this continent: collapse.
Not from outside forces, but from war within.

That long-ago first khagan had been wise.
Not once during the three hundred years of the khaganate had a civil war occurred.

And as Nesryn pushed him past the graceful bowing of the servants now paused between two enormous pillars, as the lush, ornate throne room spread before them with its dozens of people gathered around the golden dais glittering in the midday sun, Chaol wondered which of the five figures standing before the enthroned man would one day be chosen to rule this empire.

The only sounds came from the rustling clothing of the four dozen people--- he counted in the span of a few casual blinks---gathered along either side of that glinting dais, forming a wall of silk and flesh and jewels, a veritable avenue through which Nesryn wheeled him.

Rustling clothing---and the clatter and squeak of the wheels.
She'd oiled them this morning, but weeks at sea had worn on the metal.
Every scrape and shriek was like nails on stone.

But he kept his head high.
Shoulders back.

Nesryn paused a healthy distance from the dais---from the wall of five royal children, all in their prime, male and female, standing between them and their father.

Defense of their emperor: a prince or princess's first duty.
The easiest way to prove their loyalty, to angle for being tapped Heir.
And the five before them\ldots Chaol schooled his face into neutrality as he counted again.
Only five.
Not the six Nesryn had described.

But he didn't scan the hall for the missing royal sibling as he bowed at the waist.
He'd practiced the movement over and over this final week at sea, as the weather had turned hotter, the air becoming dry and sunbaked.
Doing it in the chair still felt unnatural, but Chaol bowed low---until he was staring at his unresponsive legs, at his spotless brown boots and the feet he could not feel, could not move.

From the whisper of clothing to his left, he knew Nesryn had come to his side and was bowing deeply as well.

They held it for the three breaths Nesryn claimed were required.

Chaol used those three breaths to settle himself, to shut out the weight of what was upon them both.

He had once been skilled at maintaining an unfaltering composure.
He'd served Dorian's father for years, had taken orders without so much as blinking.
And before that, he'd endured his own father, whose words had been as cutting as his fists.
The true and current Lord of Anielle.

The \emph{Lord} now in front of Chaol's name was a mockery.
A mockery and a lie that Dorian had refused to abandon despite Chaol's protests.

Lord Chaol Westfall, Hand of the King.

He hated it.
More than the sound of wheels.
More than the body he now could not feel beneath his hips, the body whose stillness still surprised him, even all these weeks later.

He was Lord of Nothing.
Lord of Oath-Breakers.
Lord of Liars.

And as Chaol lifted his torso and met the upswept eyes of the white-haired man on that throne, as the khagan's weathered brown skin crinkled in a small, cunning smile\ldots Chaol wondered if the khagan knew it as well.

