
\chapter{10}

A summer storm galloped in off the Narrow Sea just before midnight.

Even tucked into the sprawling library at the base of the Torre, Yrene felt every shudder of thunder.
Occasional flashes of lightning sliced down the narrow corridors of the stacks and halls, chased by wind that crept through the cracks in the pale stone, guttering the candles in its wake.
Most were shielded within glass lanterns, the books and scrolls too precious to risk open flame.
But the wind found them in there, too---and set the glass lanterns hanging from the arched ceilings swinging and groaning.

Seated at an oak desk built into an alcove far from the brighter lights and busier areas of the library, Yrene watched the metal lantern dangling from the arch above her sway in that storm wind.
Stars and crescent moons had been cut from its sides and filled with colored glass that cast splotches of blue and red and green on the stone wall before her.
The splotches bobbed and dipped, a living sea of color.

Thunder cracked, so loud she flinched, the ancient chair beneath her creaking in objection.

A few feminine yelps answered it, then giggles.

Acolytes---studying late for their examinations next week.

Yrene huffed a laugh, mostly at herself, and shook her head as she focused again upon the texts Nousha had dug up for her hours ago.

Yrene and the Head Librarian had never been close, and Yrene was certainly not inclined to seek out the woman if she spotted her in the mess hall, but\ldots Nousha was fluent in fifteen languages, some of them dead, and had trained at the famed Parvani Library on the western coast, nestled amid the lush and spicerich lands outside Balruhn.

The City of Libraries, they called Balruhn.
If the Torre Cesme was the domain of healers, the Parvani was the domain of knowledge.
Even the great road that linked Balruhn to the mighty Sister-Road, the main artery through the continent that flowed from Antica all the way to Tigana, had been named for it: the Scholars' Road.

Yrene didn't know what had brought Nousha here all those decades ago, or what the Torre had offered her to stay, but she was an invaluable resource.
And for all of her unsmiling nature, Nousha had always found Yrene the information she needed, no matter how outlandish the request.

Tonight, the woman had not looked pleased when Yrene had approached her in the mess hall, apologies falling from her lips for interrupting the librarian's meal.
Yrene might have waited until the morning, but she had lessons tomorrow, and Lord Westfall after that.

Nousha had met Yrene here after finishing her meal, and had listened, long fingers folded in front of her flowing gray robes, to Yrene's story---and needs:

Information.
Any she could find.

Wounds from demons.
Wounds from dark magic.
Wounds from unnatural sources.
Wounds that left echoes but did not appear to continue to wreak havoc upon the victim.
Wounds that left marks but no scar tissue.

Nousha had found them.
Stack after stack of books and bundles of scrolls.
She'd piled them on the desk in silence.
Some were in Halha.
Some in Yrene's own tongue.
Some in Eyllwe.
Some were 

Yrene scratched her head at the scroll she'd weighted with the smooth onyx stones from the jar set on each library desk.

Even Nousha had admitted she did not recognize the strange markings--- runes of some sort.
From where, she had no inkling, either, only that the scrolls had been wedged beside the Eyllwe tomes in a level of the library so deep beneath the ground that Yrene had never ventured there.

Yrene ran a finger over the marking before her, tracing its straight lines and curving arcs.

The parchment was old enough that Nousha had threatened to flay Yrene alive if she got any food, water, or drink on it.
When Yrene had asked just how old, Nousha had shook her head.

\emph{A hundred years?} Yrene had asked.

Nousha had shrugged and said that judging by the location, the type of parchment, and ink pigment, it was over ten times that.

Yrene cringed at the paper she was so flagrantly touching, and eased the weighting stones off the corners.
None of the books in her own language had yielded anything valuable---more old wives' warnings about ill-wishers and spirits of air and rot.

Nothing like what Lord Westfall had described.

A faint, distant \emph{click} echoed from the gloom to her right, and Yrene lifted her head, scanning the darkness, ready to leap onto her chair at the first sign of a scurrying mouse.

It seemed even the library's beloved Baast Cats---thirty-six females, no more, no less---could not keep out all vermin, despite their warrior-goddess namesake.

Yrene again scanned the gloom to her right, cringing, wishing she could summon one of the beryl-eyed cats to go hunting.

But no one summoned a Baast Cat.
No one.
They appeared when and where they willed, and not a moment before.

The Baast Cats had dwelled in the Torre library for as long as it had existed, yet none knew where they had come from, or how they were replaced when age claimed them.
Each was as individual as any human, save for those berylcolored eyes they each bore, and the fact that all were just as prone to curl up in a lap as they were to shun company altogether.
Some of the healers, old and young alike, swore the cats could step through pools of shadow to appear on another level of the library; some swore the cats had been caught pawing through the pages of open books---\emph{reading}.

Well, it'd certainly be helpful if they bothered to read less and hunt \emph{more}.
But the cats answered to no one and nothing, except, perhaps, their namesake, or whatever god had found a quiet home in the library, within Silba's shadow.
To offend one Baast Cat was to insult them all, and even though Yrene loved most animals---with the exception of some insects---she had been sure to treat the cats kindly, occasionally leaving morsels of food, or providing a belly rub or ear scratch whenever they deigned to command them.

But there was no sign of those green eyes glinting in the dark, or of a scurrying mouse fleeing their path, so Yrene loosed a breath and set aside the ancient scroll, carefully placing it at the edge of the desk before pulling an Eyllwe tome toward her.

The book was bound in black leather, heavy as a doorstop.
She knew a little of the Eyllwe language thanks to living so close to its border with a mother who spoke it fluently---certainly not from the father who had hailed from there.

None of the Towers women had ever married, preferring either lovers who left them with a present that arrived nine months later or who perhaps stayed a year or two before moving on.
Yrene had never known her father, never learned anything about who he was other than a traveler who had stopped at her mother's cottage for the night, seeking shelter from a wild storm that swept over the grassy plain.

Yrene traced her fingers over the gilt title, sounding out the words in the language she had not spoken or heard in years.

"The\ldots The \ldots" She tapped her finger on the title.
She should have asked Nousha.
The librarian had already promised to translate some other texts that had caught her eye, but\ldots Yrene sighed again.
"The \ldots" Poem.
Ode.
Lyric ---"\emph{Song}," she breathed.
"\emph{The Song of} \ldots" Start.
Onset---"\emph{Beginning}."
\emph{The Song of Beginning}.

The demons---the Valg---were ancient, Lord Westfall had said.
They had waited an eternity to strike.
Part of near-forgotten myths; little more than bedside stories.

Yrene flipped open the cover, and cringed at the unfamiliar tangle of writing within the table of contents.
The type itself was old, the book not even printed on a press.
Handwritten.
With some word variations that had long since died out.

Lightning flashed again, and Yrene rubbed at her temple as she leafed through the musty, yellow-lined pages.

A history book.
That's all it was.

Her eye snagged on a page, and she paused, backtracking until the illustration reappeared.

It had been done in sparing colors: blacks, whites, reds, and the occasional yellow.

All painted by a master's hand, no doubt an illustration of whatever was written beneath it.

The illustration revealed a barren crag, an army of soldiers in dark armor kneeling before it.

Kneeling before what was \emph{atop} the crag.

A towering gate.
No wall flanking it, no keep behind it.
As if someone had built the gateway of black stone out of thin air.

There were no doors within the archway.
Only swirling black \emph{nothing}.
Beams of it shot from the void, some foul corruption of the sun, falling upon the soldiers kneeling before it.

She squinted at the figures in the foreground.
Their bodies were human, but the hands clutching their swords\ldots Clawed.
Twisted.

"Valg," Yrene whispered.

Thunder cracked in answer.

Yrene scowled at the swaying lantern as the reverberations from the thunderhead rumbled beneath her feet, up her legs.

She flipped through the pages until the next illustration appeared.
Three figures stood before the same gate, the drawing too distant to make out any features beyond their male bodies, tall and powerful.

She ran a finger over the caption below and translated:

\emph{Orcus.
Mantyx.
Erawan.}

\emph{Three Valg Kings.}

\emph{Wielders of the Keys.}

Yrene chewed on her bottom lip.
Lord Westfall had not mentioned such things.

But if there was a gate\ldots then it would need a key to open.
Or several.

If the book was correct.

Midnight chimed in the great clock of the library's main atrium.

Yrene riffled through the pages, to another illustration.
It was divided into three panels.

Everything the lord had said---she had believed him, of course, but  it was true.
If the wound wasn't proof enough, these texts offered no other alternative.

For there in the first panel, tied down upon an altar of dark stone  a desperate young man strained to free himself from the approach of a crowned dark figure.
Something swirled around the figure's hand---some asp of black mist and wicked thought.
No real creature.

The second panel\ldots Yrene cringed from it.

For there was that young man, eyes wide in supplication and terror, mouth forced open as that creature of black mist slithered down his throat.

But it was the last panel that made her blood chill.

Lightning flashed again, illumining the final illustration.

The young man's face had gone still.
Unfeeling.
His eyes\ldots Yrene glanced between the previous drawing and the final one.
His eyes had been silver in the first two.

In the final one\ldots they had gone black.
Passable as human eyes, but the silver had been wiped away by unholy obsidian.

Not dead.
For they had shown him rising, chains removed.
Not a threat.

No---whatever they had put inside him 

Thunder groaned again, and more shrieks and giggles followed.
Along with the slam and clatter of the acolytes leaving for the night.

Yrene surveyed the book before her, the other stacks Nousha had laid out.

Lord Westfall had described collars and rings to hold the Valg demons within a human host.
But even after they were removed, he'd said, they could linger.
They were merely implantation devices, and if they remained on too long, feeding off their host 

Yrene shook her head.
The man in the drawing had not been enslaved---he'd been infested.
The magic had come from someone \emph{with} that sort of power.
Power from the demon host within.

A clash of lightning, then thunder immediately on its heels.

And then another \emph{click} sounded---faint and hollow---from the dim stacks to her right.
Closer now than that earlier one had been.

Yrene glanced again toward the gloom, the hair on her arms rising.

Not a movement of a mouse.
Or even the scrape of feline claws on stone or bookshelf.

She had never once feared for her safety, not from the moment she had set foot within these walls, but Yrene found herself going still as she stared into that gloom to her right.
Then slowly looked over her shoulder.

The shelf-lined corridor was a straight shot toward a larger hallway, which would, in three minutes' walk, take her back to the bright, constantly monitored main atrium.
Five minutes at most.

Only shadows and leather and dust surrounded her, the light bobbing and tilting with the swaying lanterns.

Healing magic offered no defenses.
She'd discovered such things the hard way.

But during that year at the White Pig Inn, she'd learned to listen.
Learned to read a room, to \emph{sense} when the air had shifted.
Men could unleash storms, too.

The grumbling echo of the thunder faded, and only silence remained in its wake.

Silence, and the creaking of the ancient lanterns in the wind.
No other click issued.

Foolish---foolish to read such things so late.
And during a storm.

Yrene swallowed.
Librarians preferred the books remain within the library proper, but 

She slammed shut \emph{The Song of Beginning}, shoving it into her bag.
Most of the books she'd already deemed useless, but there were perhaps six more, a mixture of Eyllwe and other tongues.
Yrene shoved those into her bag, too.
And gently placed the scrolls into the pockets of her cloak, tucked out of view.

All while keeping one eye over her shoulder---on the hall behind her, the stacks to her right.

\emph{You wouldn't owe me anything if you'd used some common sense}.
The young stranger had snapped that at her that fateful night---after she'd saved Yrene's life.
The words had lingered, biting deep.
As had the other lessons she'd been taught by that girl.

And though Yrene knew she'd laugh at herself in the morning, though maybe it \emph{was} one of the Baast Cats stalking something in the shadows, Yrene decided to listen to that tug of fear, that trickle down her spine.

Though she could have cut down dark stacks to reach the main hallway faster, she kept to the lights, her shoulders back and head high.
Just as the girl had told her.
\emph{Look like you'd put up a fight---be more trouble than you're worth}.

Her heart pounded so wildly she could feel it in her arms, her throat.
But Yrene made her mouth a hard line, her eyes bright and cold.
Looking as furious as she'd ever been, her pace clipped and swift.
As if she had forgotten something or someone had failed to retrieve a book for her.

Closer and closer, she neared the intersection of that broad, main hallway.
To where the acolytes would be trudging up to bed in their cozy dormitory.

She cleared her throat, readying to scream.

\emph{Not rape, not theft---not something that cowards would rather hide from.
Yell fire}, the stranger had instructed her.
\emph{A threat to all.
If you are attacked, yell about a fire.}

Yrene had repeated the instructions so many times these past two and a half years.
To so many women.
Just as the stranger had ordered her to.
Yrene had not thought she'd ever again need to recite them for herself.

Yrene hurried her steps, jaw angled.
She had no weapons save for a small knife she used for cleaning out wounds or cutting bandages---currently in the bottom of her bag.

But that satchel, laden with books\ldots She wrapped the leather straps around her wrist, getting a good grip on it.

A well-placed swing would knock someone to the ground.

Closer and closer to the safety of that hallway--- From the corner of her eye, she saw it.
Sensed it.

Someone in the next stack over.
Walking parallel to her.

She didn't dare look.
Acknowledge it.

Yrene's eyes burned, even as she fought the terror that clawed its way up her body.

Glimpses of shadows and darkness.
Stalking her.
Hunting her.

Quickening its pace to grab her---cut her off at that hallway and snatch her into the dark.

\emph{Common sense.
Common sense.}

Running---it would know.
It would know she was aware.
It might strike.

Whoever it was.

\emph{Common sense}.

A hundred feet left until the hallway, shadows pooling between the dim lanterns, the lights now precious islands in a sea of darkness.

She could have sworn fingers lightly thudded as they trailed over the books on the other side of the shelf.

So Yrene lifted her chin further and smiled, laughing brightly as she looked ahead to the hallway.
"Maddya!
What are you doing here so late?"

She hurried her pace, especially as whoever it was slowed in surprise.
Hesitation.

Yrene's foot slammed into something soft---soft and yet hard---and she bit down her yelp---

She hadn't seen the healer curled on her side in the shadows along the shelf.

Yrene bent, hands grappling for the woman's thin arms, her build slender enough that when she turned her over---

The footsteps began once more just as she turned the healer over.
As she swallowed the scream that tried to shatter out of her.

Light brown cheeks turned to hollowed husks, eyes stained purple beneath, lips pale and cracked.
A simple healer's gown that had likely fit her that morning now hung loose, her slim form now emaciated, as if something had sucked the life from her---

She knew that face, gaunt as it was.
Knew the golden-brown hair, nearly the twin to her own.
The healer from the Womb, the very one she'd comforted only hours earlier---

Yrene's fingers shook as she fumbled for a pulse, the skin leathery and dry.

Nothing.
And her magic\ldots There was no life for it to swirl toward.
No life at all.

The footsteps on the other side of the stack neared.
Yrene stood on trembling knees, taking a steadying breath as she forced herself to walk again.
Forced herself to leave that dead healer in the dark.
Forced herself to lift her bag as if nothing had happened, as if showing the satchel to someone ahead.

But with the angle of the stacks---the person didn't know that.

"Just finishing up my reading for the night," she called to her invisible salvation ahead.
She sent up a silent prayer of thanks to Silba that her voice held steady and merry.
"Cook is expecting me for a last cup of tea.
Want to join?"

Making it seem like someone was expecting her: another trick she'd picked up.

Yrene cleared five more steps before she realized whoever it was had again halted.

Buying her ruse.

Yrene dashed the last few feet to the hallway, spotted a cluster of acolytes just emerging from another haze of stacks, and hurtled flat out toward them.

Their eyes widened at Yrene's approach, and all she whispered was, "\emph{Go}."

The three girls, barely more than fourteen, caught the tears of terror in her eyes, the sure whiteness of her face, and did not look behind Yrene.
They did not disobey.

They were in her class.
She'd trained them for months now.

They saw the straps of her satchel wrapped around her fist and closed ranks around her.
Smiled broadly, nothing at all wrong.
"Come to Cook's to get tea," Yrene told them, fighting to keep her scream from shattering out of her.
Dead.
A healer was \emph{dead}---"She is expecting me."

\emph{And will raise the alarm if I do not arrive}.

To their credit, those girls did not tremble, did not show one lick of dread as they walked down the main hall.
As they neared the atrium, with its roaring fire and thirty-six chandeliers and thirty-six couches and chairs.

A sleek black Baast Cat was lounging in one of those embroidered chairs by the fire.
And as they neared, she leaped up, hissing as fiercely as her felineheaded namesake.
Not at Yrene or the girls\ldots No, those beryl-colored eyes were narrowed at the library \emph{behind} them.

One of the girls tightened her grip on Yrene's arm.
But not one of them left Yrene's side as she approached the massive desk of the Head Librarian and her Heir.
Behind them, the Baast Cat held her ground---held the line---as the Heir Librarian, on duty for the night, looked up from her book at the commotion.

Yrene murmured to the middle-aged woman in gray robes, "A healer has been gravely attacked in the stacks off the main hall.
Get everyone out and call for the royal guard.
\emph{Now}."

The woman did not ask questions.
Did not falter or shake.
She only nodded before she reached for the bell bolted onto the desk's edge.

The librarian rang it thrice.
To an outsider, it was no more than a final call.
But to those who lived here, who knew the library was open day and night\ldots First ring: Listen.

Second: Listen \emph{now}.

The Heir Librarian rang it a third time, loud and clear, the pealing echoing down into the library, into every dark corner and hallway.

Third ring: \emph{Get out.}

Yrene had once asked, when Eretia had explained the warning bell her first day here, after she had taken a vow never to repeat its meaning to an outsider.
They all had.
And Yrene had asked why it was needed, who had installed it.

Long ago, before the khaganate had conquered Antica, this city had passed from hand to hand, victim to a dozen conquests and rulers.
Some invading armies had been kind.
A few had not.

Tunnels still existed beneath the library that they had used to evade them--- long since boarded up.

But the warning bell to those within remained.
And for a thousand years, the Torre had kept it.
Occasionally had drills with it.
Just in case.
If it should ever happen.

The third ring echoed off stone and leather and wood.
And Yrene could have sworn she heard the sound of countless heads popping up from where they bent over desks.
Heard the sound of chairs shoved back and books dropped.

\emph{Run}, she begged.
\emph{Keep to the lights.}

But Yrene and the others lingered in silence, counting the seconds.
The minutes.
The Baast Cat quieted her hissing and monitored the hall beyond the atrium, black tail slashing over the chair cushion.
One of the girls beside Yrene sprinted off to the guards by the Torre gates.
Who had likely heard that bell pealing and were already running toward them.

Yrene was shaking by the time quick steps and rustling clothing drew near.
She and the Heir Librarian marked each face that emerged---each wide-eyed face that hurried out of the library.

Acolytes, healers, librarians.
No one out of place.
The Baast Cat seemed to be checking them all, too---those beryl eyes seeing things perhaps beyond Yrene's comprehension.

Armor and stomping steps, and Yrene clamped down on the weeping relief at the approach of half a dozen Torre guards now stalking through the open library doors, the acolyte at their heels.

The acolyte and her two companions remained with Yrene while she explained.
While the guards called for reinforcements, while the Heir Librarian summoned Nousha, Eretia, and Hafiza.
The three girls remained, two holding Yrene's trembling hands.

They did not let go.

