
\chapter{11}

Yrene was late.

Chaol had come to expect her at ten, though she had given no indication of when she might arrive. Nesryn had left well before he'd awoken to seek out Sartaq and his ruk, leaving him here to bathe and 
wait.

And wait.

An hour in, Chaol began going through what exercises he could manage on his own, unable to stand the silence, the heavy heat, the endless trickle of water from the fountain outside. The thoughts that kept sliding back to Dorian, wondering where his king was now headed.

She'd mentioned exercises---some involving his legs, however she'd manage to accomplish that---but if Yrene didn't bother to arrive on time, then he certainly wouldn't bother to wait for her.

His arms were trembling by the time the clock on the sideboard chimed noon, little silver bells atop the carved wood piece filling the space with clear, bright ringing. Sweat slid down his chest, his spine, his face as he managed to haul himself into his chair, arms trembling with the effort. He was about to call for Kadja to bring him a jug of water and a cool cloth when Yrene appeared.

In the sitting room, he listened as she entered the main door, then halted.

She said to Kadja, waiting in the foyer, "I have a matter of discretion that I need you to personally oversee." Obedient silence.

"Lord Westfall requires a tonic for a rash developing on his legs. Likely from some oil you dumped into his bath." The words were calm, yet edged. He frowned down at his legs. He'd seen no such thing this morning, but he certainly couldn't sense an itch or burning. "I need willow bark, honey, and mint. The kitchens will have them. Tell no one why. I don't want word getting around." Silence again---then a door closing.

He watched the open doors to the sitting room, listening to \emph{her}
listen to Kadja leaving. Then her heavy sigh. Yrene emerged a moment later.

She looked like hell.

"What's wrong?"

The words were out before he could consider the fact that he had no right to ask such things.

But Yrene's golden-brown face was ashen, her eyes smudged with purple, her hair limp.

She only said, "You exercised."

Chaol glanced down at his sweat-soaked shirt. "It seemed as good a way to pass the time as anything else." Each of her steps toward the desk was slow--- heavy. He repeated, "What's wrong?"

But she reached the desk and kept her back to him. He ground his teeth, debating wheeling the chair over just so he could see her face, as he might have once stormed over to see---to push into her space until she told him what the hell had happened.

Yrene just set her satchel on the desk with a thud. "If you wish to exercise, perhaps a better place for it would be the barracks." A wry look at the carpet.

"Rather than sweating all over the khagan's priceless rugs."

His hands clenched at his sides. "No," was all he said. All he
\emph{could} say.

She lifted a brow. "You were Captain of the Guard, weren't you? Perhaps training with the palace guard will be beneficial to---"

\emph{"No."}

She peered over her shoulder, those golden eyes sizing him up. He didn't balk, even as the still-shredded thing in his chest seemed to twist and rend itself further.

He had no doubt she marked it, no doubt she'd tucked away that bit of information. Some small part of him hated her for it, hated himself for revealing that wound through his obstinance, but Yrene only turned from the desk and strode toward him, face unreadable.

"I apologize if rumor now gets out that you have an unfortunate rash on your legs." That usual, sure-footed grace had been replaced by trudging feet. "If Kadja is as smart as I think she is, she'll worry that the rash being a result of \emph{her} ministrations would get her in trouble and not tell anyone. Or at least realize that if word gets out, we'll know \emph{she} was the only one told of it."

Fine. She still didn't want to answer his question. So he instead asked, "Why did you want Kadja gone?"

Yrene slumped onto the golden sofa and rubbed her temples. "Because someone killed a healer in the library last night---and then hunted me, too."

Chaol went still. "What?"

He glanced to the windows, the open garden doors, the exits. Nothing but heat and gurgling water and birdsong.

"I was reading---about what you told me," Yrene said, the freckles on her face so stark against her wan skin. "And I felt someone approaching."

"Who?"

"I don't know. I didn't see them. The healer  I found her as I fled." Her throat bobbed. "We cleared the library from top to bottom once she was  retrieved, but found no one." She shook her head, jaw tight.

"I'm sorry," he said, and meant it. Not just for the loss of life, but also for what seemed like the loss of a long-held peace and serenity. But he asked, because he could no more stop himself from getting answers, from assessing the risks, than he could halt his own breathing, "What manner of injuries?" Half of him didn't want to know.

Yrene leaned back against the sofa cushions, the down stuffing sighing as she stared at the gilded ceiling. "I'd seen her before in passing. She was young, a little older than me. And when I found her on the floor, she looked like a longdesiccated corpse. No blood, no sign of injury. Just  drained."

His heart stumbled at the too-familiar description. Valg. He'd bet all he had left, he'd bet everything on it. "And whoever did this just left her body there?"

A nod. Her hands shook as she dragged them through her hair, closing her eyes. "I think they realized they'd attacked the wrong person---and moved away quickly."

"Why?"

She turned her head, opening her eyes. Exhaustion lay there. And utter fear. "She looks---\emph{looked} like me," Yrene rasped. "Our builds, our coloring. Whoever it was  I think they were looking for
\emph{me}."

"Why?" he asked again, scrambling to sort through all she'd said.

"Because what I was reading last night, about the potential source of the power that injured you  I left some books about it on the table. And when the guards searched the area, the books were gone." She swallowed again. "Who knew you were coming here?"

Chaol's blood chilled despite the heat.

"We did not make it a secret." It was instinct to rest his hand on a sword that was not there---a sword he had chucked in the Avery months ago. "It wasn't announced, but anyone could have learned. Long before we set foot here."

It was happening again. Here. A Valg demon had come to Antica---an underling at best, a prince at worst. It could be either.

The attack Yrene had described fit Aelin's account of the remains she and Rowan had found from the Valg prince's victims in Wendlyn. People teeming with life turned to husks as if the Valg drank their very souls.

He found himself saying quietly, "Prince Kashin suspects Tumelun was killed."

Yrene sat up, any lingering color draining from her face. "Tumelun's body was not drained. Hafiza---the Healer on High herself declared it was a suicide."

There was, of course, a chance the two deaths weren't connected, a chance that Kashin was wrong about Tumelun. Part of Chaol prayed it was so. But even if they were unrelated, what had happened last night---

"You need to warn the khagan," Yrene said, seeming to read his mind.

He nodded. "Of course. Of course I will." Damned as the entire situation was  Perhaps it was the in he'd been waiting for with the khagan. But he studied her haggard face, the fear there. "I'm sorry---to have brought you into this. Has security been increased around the Torre?"

"Yes." A breathy push of sound. She scrubbed at her face.

"And you? Did you come here under guard?"

She threw him a frown. "In plain daylight? In the middle of the city?"

Chaol crossed his arms. "I would put nothing past the Valg."

She waved a hand. "I won't be heading alone into any dark corridors anytime soon. None of us in the Torre will. Guards have been called in---stationed down every hall, in every few feet of the library. I don't even know where Hafiza summoned them from."

Valg underlings could take bodies of anyone they wished, but their princes were vain enough that Chaol doubted they'd bother to take the form of a lowly guard. Not when they preferred beautiful young men.

A collar and a dead, cold smile flashed before his eyes.

Chaol blew out a breath. "I am truly sorry---about that healer." Especially if his being here had somehow triggered this attack, if they pursued Yrene only because of her helping him. He added, "You should be on your guard. Constantly."

She ignored the warning and scanned the room, the carpets, and the lush palms. "The girls---the young acolytes  They're frightened."

\emph{And you?}

Before, he would have volunteered to stand watch, to guard her door, to organize the soldiers because he \emph{knew} how these things operated. But he was no captain, and he doubted the khagan or his men would be inclined to listen to a foreign lord, anyway.

But he couldn't stop himself, that part of him, as he asked, "What can I do to help?"

Yrene's eyes shifted toward him, assessing. Weighing. Not him, but he had the feeling it was something inside herself. So he kept still, kept his gaze steady, while she looked inward. While she at last took a breath and said, "I teach a class. Once a week. After last night, they were all too tired, so I let them sleep instead. Tonight, we have a vigil for the healer who---who died. But tomorrow \ldots" She chewed on her lip, again debating for a heartbeat before she added, "I should like you to come."

"What sort of class?"

Yrene toyed with a heavy curl. "There is no tuition for students here---but we pay our way in other forms. Some help with the cooking, the laundry, the cleaning. But when I came, Hafiza  I told her I was good at all those things. I'd done them for---a while. She asked me what else I knew beyond healing, and I told her \ldots" She bit her lip. "Someone once taught me self-defense. What to do against attackers. Usually the male kind."

It was an effort not to look at the scar across her throat. Not to wonder if she had learned it after---or if even that had not been enough.

Yrene sighed through her nose. "I told Hafiza that I knew a little about it, and that  I had made a promise to someone, to the person who taught \emph{me}, to show and teach it to as many women as possible. So I have. Once a week, I teach the acolytes, along with any older students, healers, servants, or librarians who would like to know."

This delicate, gentle-handed woman  He supposed he'd learned that strength could be hidden beneath the most unlikely faces.

"The girls are deeply shaken. There hasn't been an intruder in the Torre for a great while. I think it would go a long way if you were to join me tomorrow---to teach what you know."

For a long moment, he stared at her. Blinked.

"You realize I'm in this chair."

"And? Your mouth still works." Tart, crisp words.

He blinked again. "They might not find me the most reassuring instructor---"

"No, they'll likely be swooning and sighing over you so much they'll
\emph{forget} to be afraid."

His third and final blink made her smile slightly. Grimly. He wondered what that smile would look like if she ever was truly amused---happy.

"The scar adds a touch of mystery," she said, cutting him off before he could remember the slice down his cheek.

He studied her as she rose from the sofa to stride back to the desk and unpack her bag. "You would truly like me to be there tomorrow?"

"We'll have to figure out how to \emph{get} you there, but it should not be so difficult."

"Stuffing me into a carriage will be fine."

She stiffened, glancing over her shoulder. "Save that anger for
\emph{our} training, Lord Westfall." She fished out a vial of oil and set it on the table. "And you will not be taking a carriage."

"A litter carried by servants, then?" He'd sooner crawl.

"A horse. Ever heard of one?"

He clenched the arms of his chair. "You need legs to ride."

"So it's a good thing you still have both of them." She went back to studying whatever vials were in that bag. "I spoke to my superior this morning. She has seen similarly injured people ride until they could meet with us---with special straps and braces. They are fashioning them for you in the workshops as we speak."

He let those words sink in. "So you assumed I would come with you tomorrow."

Yrene turned at last, satchel in her hand now. "I assumed you would wish to ride regardless."

He could only stare while she approached, vial in hand. Only a prim sort of irritation on her face. Better than the stark fear. He asked, voice a bit raw, "You think such a thing is possible?"

"I do. I'll arrive at dawn, so we have enough time to figure it out. The lesson begins at nine."

To ride---even if he could not walk, \emph{riding}  "Please do not give me this hope and let it crumble," he said hoarsely.

Yrene set the satchel and vial down on the low-lying table before the sofa and motioned him to move closer. "Good healers don't do such things, Lord Westfall."

He hadn't bothered with a jacket today, and had left his belt in the bedroom. Sliding his sweat-soaked shirt over his head, he made quick work of unbuttoning the tops of his pants. "It's Chaol," he said after a moment. "My name---it's Chaol. Not Lord Westfall." He grunted as he hoisted himself from the chair onto the sofa. "Lord Westfall is my father."

"Well, you're a lord, too."

"Just Chaol."

"Lord Chaol."

He shot her a look as he positioned his legs. She did not reach to help, to adjust. "Here I was, thinking you still resented me."

"If you help my girls tomorrow, I'll reconsider."

From the gleam in those golden eyes, he very much doubted that, but a half smile tugged on his mouth. "Another massage today?"
\emph{Please}, he nearly added. His muscles already ached from his exercising, and moving so much between bed and sofa and chair and bath---

"No." Yrene gestured for him to lie facedown on the sofa. "I'm going to begin today."

"You found information on it?"

"No," she repeated, tugging off his pants with that cool, swift efficiency. "But after last night  I do not want to delay."

"I will---I can \ldots" He ground his teeth. "We'll find a way to protect you while you research." He hated the words, felt them curl like rancid milk on his tongue, along his throat.

"I think they know that," she said quietly, and dabbed spots of oil along his spine. "I'm not sure if it's the information, though. That they want to keep me from finding."

His gut tightened, even as she ran soothing hands down his back. They lingered near that splotch at its apex. "What do you think they want, then?"

He already suspected, but he wanted to hear her say it---wanted to know if she thought the same, understood the risks as much as he did.

"I wonder," she said at last, "if it was not just what I was researching, but also that I'm healing \emph{you}."

He craned his head to look at her as the words settled between them. She only stared at that mark on his spine, her tired face drawn. He doubted she'd slept. "If you're too tired---"

"I am not."

He clenched his jaw. "You can nap here. I'll look after you." Useless as it would be. "Then work on me later---"

"I will work on you now. I am not going to let them scare me away." Her voice did not tremble or waver.

She added, more quietly but no less fiercely, "I once lived in fear of other people. I let other people walk all over me just because I was too afraid of the consequences for refusing. I did not know \emph{how} to refuse." Her hand pushed down on his spine in a silent order to rest his head again. "The day I reached these shores, I cast aside that girl. And I will be damned if I let her reemerge. Or let someone tell
\emph{me} what to do with my life, my choices again."

The hair on his arms rose at the simmering wrath in her voice. A woman made of steel and crackling embers. Heat indeed flared beneath her palm as she slid it up the column of his spine, toward that splotch of white.

"Let's see if it enjoys being pushed around for a change," she breathed.

Yrene laid her hand directly atop the scar. Chaol opened his mouth to speak

---

But a scream came out instead.

