
\chapter{15}

Yrene felt the anger simmering off Chaol as if it were heat rippling from a kettle.

Not at the girls and women. They adored him. Grinned and laughed, even as they concentrated on his thorough, precise lesson, even as the events in the library hung over them, the Torre, like a gray shroud. There had been many tears last night at the vigil---and a few red eyes still in the halls this morning as she'd hurtled past.

Mercifully, there had been no sign of either when Lord Chaol called in three guards to volunteer their bodies for the girls to flip into the gravel. Over and over.

The men agreed, perhaps because they knew that any injuries would be fussed over and patched up by the greatest healers outside Doranelle.

Chaol even returned their smiles, ladies and, to her shock, guards alike.

But Yrene  she received none of them. Not one.

Chaol's face only went hard, eyes glinting with frost, whenever she stepped in to ask a question or watch him walk an acolyte through the motions. He was commanding, his unrelenting focus missing nothing. If they had so much as one foot in the wrong position, he caught it before they moved an inch.

The hour-long lesson ended with each one of them flipping a guard onto his back. The poor men limped off, smiling broadly. Mostly because Hafiza promised them a cask of ale each---and her strongest healing tonic. Which was better than any alcohol.

The women dispersed as the bells chimed ten, some to lessons, some to chores, some to patients. A few of the sillier girls lingered, batting their eyelashes toward Lord Westfall, one even looking inclined to perch in his lap before Hafiza drily reminded her of a pile of laundry with her name on it.

Before the Healer on High hobbled after the acolyte, Hafiza merely gave Yrene what she could have sworn was a warning, knowing look.

"Well," Yrene said to Chaol when they were again alone---despite the gaggle of girls peering out one of the Torre windows. They noticed Yrene's stare and snapped their heads back in, slamming the window with riotous giggles.

Silba save her from teenage girls.

She'd never been one---not like that. Not so carefree. She hadn't even kissed a man until last autumn. Certainly had never giggled over one. She wished she had; wished for a lot of things that had ended with that pyre and those torches.

"That went better than expected," Yrene said to Chaol, who was frowning up at the looming Torre. "I'm sure they'll be begging me next week for you to return. If you're interested, I suppose." He said nothing.

She swallowed. "I would like to try again today, if you're up for it. Would you prefer I find a room here, or shall we ride back to the palace?"

He met her stare then. His eyes were dark. "The palace."

Her stomach twisted at the icy tone. "All right," was all she managed to say, and walked off in search of the guards and their horses.

They rode back in silence. They'd been quiet during portions of the ride over, but this was  pointed. Heavy.

Yrene wracked her memory for what she might have said during the lesson--- what she might have forgotten. Perhaps seeing the guards so active had reminded him of what he did not currently have. Perhaps just seeing the guards themselves had set him down this path.

She mused over it as they returned to the palace, while he was aided by Shen and another guard into the awaiting chair. He offered only a tight smile in thanks.

Lord Chaol looked up at her over a shoulder, the morning heat rising enough to make the courtyard stifling. "Are you going to push it, or shall I?" Yrene blinked.

"You can move it yourself just fine," she said, her proverbial heels digging in at that tone.

"Perhaps you should ask one of your acolytes to do it. Or five of them. Or whatever number you deem fit to deal with an Adarlanian lord."

She blinked again. Slowly. And didn't give him any warning as she strode off at a clip. Not bothering to wait to see if he followed, or how fast he did.

The columns and halls and gardens of the palace passed in a blur. Yrene was so intent on reaching his rooms that she barely noticed someone had called her name.

It wasn't until it was repeated a second time that she recognized it---and cringed.

By the time she turned, Kashin---clad in armor and sweating enough to reveal he'd likely been exercising with the palace guards---had reached her side.

"I've been looking for you," he said, his brown eyes immediately going to her chest. No---to the stain still on her dress. Kashin's brows lifted. "If you want to send that to the laundry, I'm sure Hasar can lend you some clothes while it is cleaned."

She'd forgotten she was still in it---the stained, wrinkled dress. Hadn't really felt like she was quite as much of a mess until now. Hadn't felt like a barnyard animal.

"Thank you for the offer, but I'll manage."

She took a step away, but Kashin said, "I heard about the assailant in the library. I arranged for additional guards to arrive at the Torre after sundown every night and stay until dawn. No one will get in without our notice."

It was generous---kind. As he had always been with her. "Thank you."

His face remained grave as he swallowed. Yrene braced herself for the words he'd voice, but Kashin only said, "Please be careful. I know you made your thoughts clear, but---"

"Kashin."

"---it doesn't change the fact that we are, or were, friends, Yrene."

Yrene made herself meet his eyes. Made herself say, "Lord Westfall mentioned your  thoughts about Tumelun."

For a moment, Kashin glanced to the white banners streaming from the nearby window. She opened her mouth, perhaps to finally offer her condolences, to try to mend this thing that had fractured between them, but the prince said,

"Then you understand how dire this threat may be."

She nodded. "I do. And I will be careful."

"Good," he said simply. His face shifted into an easy smile, and for a heartbeat, Yrene wished she'd been able to feel anything beyond mere friendship. But it had never been that way with him, at least on her part. "How is the healing of Lord Westfall? Have you made progress?"

"Some," she hedged. Insulting a prince, even one who was a former friend, by striding off was not wise, but the longer this conversation went on  She took a breath. "I would like to stay and talk---"

"Then stay." That smile broadened. Handsome---Kashin was truly a handsome man. If he had been anyone else, bore any other title---

She shook her head, offering a tight smile. "Lord Westfall is expecting me."

"I heard you rode with him this morning to the Torre. Did he not come back with you?"

She tried to keep the pleading expression off her face as she bobbed a curtsy.

"I have to go. Thank you again for the concern---and the guards, Prince." The title hung between them, pealing like a struck bell.

But Yrene walked on, feeling Kashin's stare until she rounded a corner.

She leaned against the wall, closing her eyes and exhaling deeply. Fool. So many others would call her a fool and yet---

"I almost feel bad for the man."

She opened her eyes to find Chaol, breathless and eyes still smoldering, wheeling himself around the corner.

"Of course," he went on, "I was far back enough that I couldn't hear you, but I certainly saw \emph{his} face when he left."

"You don't know what you're talking about," Yrene said blandly, and resumed walking toward his suite. Slower.

"Don't check your pace on my account. You made impressive time."

She sliced him a glare. "Did I \emph{do} something to offend you today?"

His level stare revealed nothing, but his powerful arms kept working the wheels of his chair as he pushed himself along.

"Well?"

"Why do you shove away the prince? It seems like you two were once close."

It was not the time or the place for this conversation. "That is none of your business."

"Indulge me."

"No."

He easily kept pace with her as she increased her own. All the way to the doors to his suite.

Kadja was standing outside, and Yrene gave her an inane order---"I need dried thyme, lemon, and garlic"---that might have very well been one of her mother's old recipes for fresh trout.

The servant vanished with a bow, and Yrene flung open the suite doors, holding one wide for him to pass.

"Just so you know," Yrene hissed as she shut the doors loudly behind him, "your piss-poor attitude helps no one and nothing."

Chaol slammed his chair to a halt in the middle of the foyer, and she winced

at what it must have done to his hands. He opened his mouth, but shut it.

Right as the door to the other bedroom opened and Nesryn emerged, hair wet and gleaming.

"I was wondering where you went," she said to him, then gave Yrene a nod of greeting. "Early morning?"

It took Yrene a few heartbeats to reorder the room, the dynamic with Nesryn now in it. Yrene was not the primary  person. She was the help, the secondary  whatever.

Chaol shook out his hands---indeed red marks marred them---but said to

Nesryn, "I went to the Torre to help the girls with a defense lesson." Nesryn looked at the chair.

"On horseback," he said.

Nesryn's eyes now shot to Yrene, bright and wide. "You---how?"

"A brace," Yrene clarified. "We were just about to resume our second attempt at healing."

"And you could truly ride?"

Yrene felt Chaol's inward flinch---mostly because she flinched as well. At the disbelief.

"We didn't try out anything more than a fast walk, but yes," he said calmly. Evenly. Like he expected such questions from Nesryn. Had grown used to it. "Maybe tomorrow I'll try a trot."

Though without leverage from his legs, the bouncing  Yrene went through her mental archives on groin injuries. But she stayed quiet.

"I'll go with you," Nesryn said, dark eyes lighting. "I can show you the city ---perhaps my uncle's home."

Chaol only replied, "I would like that," before Nesryn pressed a kiss to his cheek.

"I'm seeing them now for an hour or two," said Nesryn. "Then meeting with

---you know. I'll be back this afternoon. And resume my  duties afterward." Careful words. Yrene didn't blame her. Not with the weapons stacked on the desk in Nesryn's bedroom---barely visible through the ajar door. Knives, swords, multiple bows and quivers  The captain had a small armory in her chamber.

Chaol just grunted his approval, smiling slightly as Nesryn strode for the suite doors. The captain paused in the threshold, her grin broader than any Yrene had seen before.

Hope. Full of hope.

Nesryn shut the door with a click.

Alone in the silence again, still feeling very much the intruder, Yrene crossed her arms. "Can I get you anything before we begin?" He just wheeled forward---into his bedroom.

"I'd prefer the sitting room," she said, snatching her supply bag from where Kadja had set it on the foyer table. And likely rifled through it.

"I'd prefer to be in bed while in agony." He added over his broad shoulder, "And hopefully you won't pass out on the floor this time."

He easily moved himself from the chair onto the bed, then began unbuckling his jacket.

"Tell me," Yrene said, lingering in the doorway. "Tell me what I did to upset you."

He peeled off his jacket. "You mean beyond displaying me like some broken doll in front of your acolytes and having them haul me off that horse like a limp fish?"

She stiffened, pulling out the bit before dumping the supply bag on the floor. "Plenty of people help you here in the palace."

"Not as many as you'd think."

"The Torre is a place of learning, and people with your injury do not come often---not when we usually have to go to them. I was showing the acolytes things that might help with untold numbers of patients in the future."

"Yes, your prized, shattered horse. Look how well broken I am to you. How docile."

"I did not mean that, and you know it."

He ripped off his shirt, nearly tearing it at the seams as he hauled it over his head. "Was it some sort of punishment? For serving the king? For being from Adarlan?"

"\emph{No.}" That he believed she could be that cruel, that unprofessional---"It was precisely what I just said: I wanted to
\emph{show} them." "\emph{I} didn't want you to show them!" Yrene straightened.

Chaol panted through his gritted teeth. "\emph{I} didn't want you to parade me around. To let them \emph{handle} me." His chest heaved, the lungs beneath those muscles working like bellows. "Do you have
\emph{any} idea what it is like? To go from \emph{that}"---he waved a hand toward her, her body, her legs, her spine---"to \emph{this}?"

Yrene had the sense of the ground sliding from beneath her. "I know it is hard

---"

"It is. But you made it \emph{harder} today. You make me sit here mostly naked in this room, and yet I have \emph{never} felt more bare than I did this morning." He blinked, as if surprised he'd vocalized it---surprised he'd admitted to it.

"I---I'm sorry." It was all she could think to say.

His throat bobbed. "Everything I thought, everything I had planned and wanted  It's gone. All I have left is my king, and this ridiculous, slim scrap of hope that we survive this war and I can find a way to \emph{make} something of it."

"Of what?"

"Of \emph{everything} that crumbled in my hands. \emph{Everything}." His voice broke on the word.

Her eyes stung. Shame or sorrow, Yrene didn't know.

And she didn't want to know---what it was, or what had happened to him. What made that pain gutter in his eyes. She knew, she knew he had to face it, had to talk about it, but 

"I'm sorry," she repeated. She added stiffly, "I should have considered your feelings on the matter."

He watched her for a long moment, then removed the belt from his waist.

Then took off his boots. Socks.

"You can leave the pants on, if---if you want." He removed them. Then waited.

Still brimming with anger. Still gazing at her with such resentment in his eyes.

Yrene swallowed once. Twice. Perhaps she should have scrounged up breakfast.

But walking away, even for that  Yrene had a feeling, one she couldn't quite place, that if she walked away from him, if he saw her back turn  Healers and their patients required trust. A bond.

If she turned her back on him and left, she didn't think that rift would be repaired.

So she motioned him to move to the center of the bed and turn onto his stomach while she took up a seat on the edge.

Yrene hovered a hand over his spine, the muscled groove cutting deep through it.

She hadn't considered---his feelings. That he might have them. The things haunting him 

His breathing was shallow, quick. Then he said, "Just to be clear: is your grudge against me, or Adarlan in general?"

He stared at the distant wall, the entrance to the bathing room blocked by that carved wood screen. Yrene held her hand steady, poised over his back, even as shame sluiced through her.

No, she had not been in her best form these past few days. Not even close.

That scar atop his spine was stark in the midmorning light, the shadow of her hand upon his skin like some sister-mark.

The thing that waited within that scar  Her magic again recoiled at its proximity. She'd been too tired last night and too busy this morning to even think about facing it again. To contemplate what she might see, might battle--- what he might endure, too.

But he'd been good to his word, had instructed the girls despite her foolish, callous missteps. She supposed that she could only return the favor by doing as she'd promised as well.

Yrene took a steadying breath. There was no preparing for it, she knew. There was no bracing breath steeling enough to make this any less harrowing. For either of them.

Yrene silently offered Chaol the leather bit.

He slid it through his teeth and clamped down lightly.

She stared at him, his body braced for pain, face unreadable as he angled it toward the door.

Yrene said quietly, "Soldiers from Adarlan burned my mother alive when I was eleven."

And before Chaol could answer, she laid her hand on the mark atop his spine.

