
\chapter{16}

There was only darkness, and pain.

He roared against it, distantly aware of the bit in his mouth, the rawness of his throat.

\emph{Burned alive burned alive burned alive}

The void showed him fire. A woman with golden-brown hair and matching skin screaming in agony toward the heavens.

It showed him a broken body on a bloody bed. A head rolling across a marble floor.

\emph{You did this you did this you did this}

It showed a woman with eyes of blue flame and hair of pure gold poised above him, dagger raised and angling to plunge into his heart.

He wished. He sometimes wished that she hadn't been stopped.

The scar on his face---from the nails she'd gouged into it when she first struck him  It was that hateful wish he thought of when he looked in the mirror. The body on the bed and that cold room and that scream. The collar on a tan throat and a smile that did not belong to a beloved face. The heart he'd offered and had been left to drop on the wooden planks of the river docks. An assassin who had sailed away and a queen who had returned. A row of fine men hanging from the castle gates.

All held within that slim scar. What he could not forgive or forget.

The void showed it to him, again and again.

It lashed his body with red-hot, pronged whips. And showed him those things, over and over.

It showed him his mother. And his brother. And his father.

Everything he had left. What he'd failed. What he'd hated and what he'd become.

The lines between the last two had blurred.

And he had tried. He had tried these weeks, these months.

The void did not want to hear of that.

Black fire raced down his blood, his veins, trying to drown out those thoughts.

The burning rose left on a nightstand. The final embrace of his king.

He had tried. Tried to \emph{hope}, and yet---

Women little more than children hauling him off a horse. Poking and prodding at him.

Pain struck, low and deep in his spine, and he couldn't breathe around it, couldn't out-scream it--- White light flared.

A flutter. Far in the distance.

Not the gold or red or blue of flame. But white like sunlight, clear and clean.

A flicker through the dark, arcing like lightning riding through the night  And then the pain converged again.

His father's eyes---his father's raging eyes when he announced he was leaving to join the guard. The fists. His mother's pleading. The anguish on her face the last time he'd seen her, as he'd ridden away from Anielle. The last time he'd seen his city, his home. His brother, small and cowering in their father's long shadow.

A brother he had traded for another. A brother he had left behind.

The darkness squeezed, crushing his bones to dust.

It would kill him.

It would kill him, this pain, this  this endless, churning pit of \emph{nothing}.

Perhaps it would be a mercy. He wasn't entirely certain his presence---his presence \emph{beyond} made any sort of difference. Not enough to warrant trying.

Coming back at all.

The darkness liked that. Seemed to thrive on that.

Even as it tightened the vise around his bones. Even as it boiled the blood in his veins and he bellowed and bellowed--- White light slammed into him. Blinding him.

Filling that void.

The darkness shrieked, surging back, then rising like a tidal wave around him

---

Only to bounce off a shell of that white light, wrapped around him, a rock against which the blackness broke.

A light in the abyss.

It was warm, and quiet, and kind. It did not balk at the dark.

As if it had dwelled in such darkness for a long, long time---and understood how it worked.

Chaol opened his eyes.

Yrene's hand had slipped from his spine.

She was already twisting away from him, lunging for his discarded shirt on the bedroom carpet.

He saw the blood before she could hide it.

Spitting out the bit, he gripped her wrist, his panting loud to his ears. "You're hurt."

Yrene wiped at her nose, her mouth, and her chin before she faced him.

It didn't hide the stains down her chest, soaking into the neckline of her dress.

Chaol surged upright. "Holy gods, Yrene---"

"I'm fine."

The words were stuffy, warped with the blood still sliding from her nose.

"Is---is that common?" He filled his lungs with air to call for someone to fetch \emph{another} healer---

"Yes."

"Liar." He heard the falsehood in her pause. Saw it in her refusal to meet his stare. Chaol opened his mouth, but she laid her hand on his arm, lowering the bloodied shirt.

"I'm fine. I just need---rest."

She appeared anything but, with blood staining and crusting her chin and mouth.

Yrene pressed his shirt again to her nose as a new trickle slid out. "At least," she said around the fabric and blood, "the stain from earlier now matches my dress."

A sorry attempt at humor, but he offered her a grim smile. "I thought it was part of the design."

She gave him an exhausted but bemused glance. "Give me five minutes and I can go back in and---"

"Lie down. Right now." He slid away a few feet on the mattress for emphasis.

Yrene surveyed the pillows, the bed large enough for four to sleep undisturbed beside one another. With a groan, she pressed the shirt to her face and slumped on the pillows, kicking off her slippers and curling her legs up. She tipped her head upward to stop the bleeding.

"What can I get you," he said, watching her stare blankly at the ceiling. She'd done this---done this while helping him, likely because of whatever shitty mood he'd been in before--- Yrene only shook her head.

In silence, he watched her press the shirt to her nose. Watched blood bloom across it again and again. Until it slowed at last. Until it stopped.

Her nose, mouth, and chin were ruddy with the remnants, her eyes fogged with either pain or exhaustion. Perhaps both.

So he found himself asking, "How?"

She knew what he meant. Yrene dabbed at the blood on her chest. "I went in there, to the site of the scar, and it was the same as before. A wall that no strike of my magic could crumble. I think it showed me \ldots" Her fingers tightened on the shirt as she pressed it against the blood soaking her front.

"What?"

"Morath," she breathed, and he could have sworn even the birds' singing faltered in the garden. "It showed some memory, left behind in
\emph{you}. It showed me a great black fortress full of horrors. An army waiting in the mountains around it."

His blood iced over as he realized whose memory it might belong to. "Real or ---was it some manipulation against you?" The way his own memories had been wielded.

"I don't know," Yrene admitted. "But then I heard your screaming. Not out here, but  in there." She wiped at her nose again. "And I realized that attacking that solid wall was  I think it was a distraction. A diversion. So I followed the sounds of your screaming. To you." To that place deep within him. "It was so focused upon ripping you apart that it did not see me coming." She shivered. "I don't know if it did anything, but  I couldn't stand it. To watch and listen. I startled it when I leaped in, but I don't know if it will be waiting the next time. If it will remember. There's a  sentience to it. Not a living thing, but as if a memory were set free in the world."

Chaol nodded, and silence fell between them. She wiped at her nose again, his shirt now coated in blood, then set the fabric on the table beside the bed.

For uncounted minutes, sunshine drifted across the floor, wind rustling the palms.

Then Chaol said, "I'm sorry---about your mother."

Thinking through the timeline  It had likely occurred within a few months of Aelin's own terror and loss.

So many of them---the children whom Adarlan had left such deep scars upon. If Adarlan had left them alive at all.

"She was everything good in the world," Yrene said, curling onto her side to gaze at the garden windows beyond the foot of the bed. "She
 I made it out because she \ldots" Yrene did not say the rest.

"She did what any mother would do," he finished for her.

A nod.

As healers, they had been some of the first victims. And continued to be executed long after magic had vanished. Adarlan had always ruthlessly hunted down the magically gifted healers. Their own townsfolk might have sold them out to Adarlan to make quick, cheap coin.

Chaol swallowed. After a heartbeat, he said, "I watched the King of Adarlan butcher the woman Dorian loved in front of me, and I could do nothing to stop it. To save her. And when the king went to kill me for planning to overthrow him  Dorian stepped in. He took on his father and bought me time to run. And I ran ---I ran because 
there was no one else to carry on the rebellion. To get word to the people who needed it. I let him take on his father and face the consequences, and I \emph{fled}."

She watched him in silence. "He is fine now, though."

"I don't know. He is free---he is alive. But is he fine? He suffered. Greatly. In ways I can't begin to \ldots" His throat tightened to the point of pain. "It should have been me. I had always planned for it to be me instead." A tear slid over the bridge of her nose.

Chaol scooped it up with his finger before it could slide to the other side.

Yrene held his stare for a long moment, her tears turning those eyes nearradiant in the sun. He didn't know how long had passed. How long it had taken for her to even attempt to cleave that darkness---just a little.

The door to the suite opened and closed, silently enough that he knew it was

Kadja. But it drew Yrene's stare away from him. Without it---there was a sense of cold. A quiet and a cold.

Chaol clenched his fist, that tear seeping into his skin, to keep from turning her face toward his again. To read her eyes.

But her head whipped upward so fast she nearly knocked his nose.

The gold in Yrene's eyes flared.

"Chaol," she breathed, and he thought it might have been the first time she'd called him such.

But she looked down, dragging his stare with her.

Down his bare torso, his bare legs.

To his toes.

To his toes, slowly curling and uncurling. As if trying to remember the movement.

