
\chapter{17}

Nesryn's cousins were off at school when she knocked on the outer door to her aunt and uncle's lovely home in the Runni Quarter. From the dusty street, all one could glimpse of the house beyond the high, thick walls was the carved oak gate, reinforced with scrolling iron.

But as it swung open under the hands of two guards who instantly beckoned her in, it revealed a shaded, broad courtyard of pale stone, flanked by pillars crawling with magenta bougainvillea, and a merry fountain inlaid with sea glass burbling in its center.

The house was typical of Antica---and of the Balruhni people from whom Nesryn and her family hailed. Long adjusted to desert climes, the entire building had been erected around sun and wind: outer windows never placed near the heat of the southern exposure, the breeze-catching narrow towers atop the building facing away from the sand-filled eastern wind to keep it from infiltrating the rooms it cooled. Her family was not fortunate enough to have a canal running beneath the house, as many of the wealthier in Antica did, but with the towering plants and carved wooden awnings, the shade kept the public lower levels around the courtyard cool enough during the day.

Indeed, Nesryn inhaled deeply as she strode through the pretty courtyard, her aunt greeting her halfway across with, "Have you eaten yet?"

She had, but Nesryn said, "I saved myself for your table, Aunt." It was a common Halha greeting amongst family---\emph{no one} visited a house, especially in the Faliq family, without eating. At least once.

Her aunt---still a full-figured beautiful woman whose four children had not slowed her down one bit---nodded in approval. "I told Brahim just this morning that our cook is better than the ones up at that palace."

A snort of amusement from a level up, from the wood-screened window overlooking the courtyard. Her uncle's study. One of the few common rooms on the usually private second level. "Careful, Zahida, or the khagan may hear you and haul dear old Cook to his palace."

Her aunt rolled her eyes at the figure just barely visible through the ornate wood screen and looped her arm through Nesryn's. "Snoop. Always eavesdropping on our conversations down here."

Her uncle chuckled but made no further comment.

Nesryn grinned, letting her aunt lead her toward the spacious interior of the home, past the curvy-bodied statue of Inna, Goddess of Peaceful Households and the Balruhni people, her arms upraised in welcome and defense. "Perhaps the palace's inferior cook is why the royals are so skinny."

Her aunt huffed, patting her belly. "And no doubt why I've added so much padding these years." She gave Nesryn a wink. "Perhaps I
\emph{should} get rid of old Cook, then."

Nesryn kissed her aunt's petal-soft cheek. "You are more beautiful now than you were when I was a child." She meant it.

Her aunt waved her off but still beamed as they entered the dim, cool interiors of the house proper. Pillars upheld the high ceilings of the long hallway, the wood beams and furniture carved and fashioned after the lush flora and fauna of their distant, long-ago homeland. Her aunt led her deeper into the house than most guests would ever see, right to the second, smaller courtyard at the back. The one just for family, most of it occupied by a long table and deep-seated chairs beneath the shade of an overhanging awning. At this hour, the sun was on the opposite side of the house---precisely why her aunt had chosen it.

Her aunt guided her into a seat adjacent to the head of the table, the place of honor, and hurried off to inform the cook to bring out refreshments.

In the silence, Nesryn listened to the wind sighing through the jasmine crawling up the wall to the balcony hanging above. As serene a home as she'd ever seen---especially compared to the chaos of her family's house in Rifthold.

An ache tightened her chest, and Nesryn rubbed at it. They were alive;
they had gotten out.

But it did not answer where they now were. Or what they might face on that continent full of so many terrors.

"Your father gets that same look when he's thinking too hard," her uncle said from behind her.

Nesryn twisted in her chair, smiling faintly as Brahim Faliq entered the courtyard. Her uncle was shorter than her father, but slimmer---mostly thanks to \emph{not} baking pastries for his livelihood. No, her uncle was still trim for a man of his age, his dark hair peppered with silver, both perhaps due to the merchant life that kept him so active.

But Brahim's face  it was Sayed Faliq's face. Her father's face. With less than two years separating them, some had thought them twins while growing up. And it was the sight of that kind, still-handsome face that made Nesryn's throat tighten. "One of the few traits I inherited from him, it seems."

Indeed, where Nesryn was quiet and prone to contemplation, her father's booming laugh had been as constant in their house as her sister's merry singing and giggling.

She felt her uncle studying her as he took the seat across from hers, leaving the head of the table for Zahida. Men and women governed the household together, their joint rule treated as law by their children. Nesryn had certainly fallen into line, though her sister  She could still hear the screeching fights between her sister and father as Delara had grown older and longed for independence.

"For the Captain of the Royal Guard," her uncle mused, "I am surprised you have the time to visit us so often."

Her aunt bustled in, bearing a tray of chilled mint tea and glasses. "Hush.

Don't complain, Brahim, or she'll stop coming."

Nesryn smiled, glancing between them as her aunt gave them each a glass of the tea, set the tray on the table between them, and claimed the seat at the head of the table. "I thought to come by now---while the children are at school."

Another of the khaganate's many wonderful decrees: every child, no matter how poor or rich, had the right to attend school. Free of charge. As a result, nearly everyone in the empire was literate---far more than Nesryn could claim of Adarlan.

"And here I was," her uncle said, smiling wryly, "hoping you'd be back to sing more for us. Since you left the other day, the children have been yowling your songs like alley cats. I haven't the heart to tell them that their voices are not quite up to the same standard as their esteemed cousin's."

Nesryn chuckled, even as her face heated. She sang for very few---only her family. She'd never sung for Chaol or the others, or even mentioned that her voice was  better than good. It wasn't something that could easily be brought up in conversation, and the gods knew that the last several months had not been conducive to singing. But she'd found herself singing to her cousins the other night---one of the songs her father had taught her. A lullaby of Antica. By the end of it, her aunt and uncle had been gathered round, her aunt dabbing at her eyes, and
 well, now there was no going back with it, was there?

She'd likely be teased about it until she never opened her mouth again.

But if only she had come here just for singing. She sighed a bit, steeling herself.

In the silence, her aunt and uncle exchanged looks. Her aunt asked quietly, "What is it?"

Nesryn sipped from her tea, considering her words. Her aunt and uncle, at least, gave her the gift of waiting for her to speak. Her sister would have been shaking her shoulders by now, demanding an answer. "There was an attack at the Torre the other night. A young healer was killed by an intruder. The murderer has not yet been found."

No matter how she and Sartaq had combed through the few sewers and canals beneath Antica last night, they had not found a single path toward the Torre; nor any sign of a Valg's nest. All they'd discovered were typical, awful city smells and rats scurrying underfoot.

Her uncle swore, earning a look from her aunt. But even her aunt rubbed at her chest before asking, "We'd heard the rumors, but  You have now come to warn us?"

Nesryn nodded. "The attack lines up with the techniques of enemies in Adarlan. If they are here, in this city, I fear it may be in connection to my arrival."

She had not dared tell her aunt and uncle too much. Not for lack of trust, but for fear of who might be listening. So they did not know of the Valg, or Erawan, or the keys.

They knew of her quest to raise an army, for that was no secret, but
 She did not risk telling them of Sartaq. That he and his rukhin might be the path toward winning support from the khagan, that his people might know something about the Valg that even they had not discovered in dealing with them. She did not even risk telling them she'd been on the prince's ruk. Not that they'd really believe it. Well-off as her family might be, there was wealth, and then there was royalty.

Her uncle said, "Will they target our family---to get to you?"

Nesryn swallowed. "I don't believe so, but I would put nothing past them. I--- it is still unknown if this attack \emph{was} in relation to my arrival, or if we are jumping to conclusions, but on the chance that it is true  I came to warn you to hire more guards if you can." She looked between them, laying her hands palmup on the table. "I am sorry to have brought this to your household."

Another glance between her aunt and uncle, then each took her by the hand.

"There is nothing to be sorry for," her aunt said. Just as her uncle added,

"Getting to see you so unexpectedly has been a blessing beyond measure."

Her throat closed up. This---this was what Erawan was poised to destroy.

She'd find a way to raise that army. Either to rescue her family from war, or keep it from reaching these shores.

Her aunt declared, "We will hire more guards, have an escort for the children to and from school." A nod to her husband. "And anywhere we go in this city."

Nesryn's uncle added, "And what of you? Traipsing about the city on your own." Nesryn waved a hand, though their concern warmed her. She refrained from telling them she'd hunted Valg in Rifthold's sewers for weeks, that she'd been stalking them through Antica's sewers last night. And most certainly refrained from telling them just how involved she'd been in the glass castle's demise. She had no wish to see her uncle keel over in his chair, or see her aunt's thick, beautiful hair go white. "I can handle myself."

Her aunt and uncle did not look so convinced, but they nodded all the same. Just as Cook emerged, smiling broadly at Nesryn, little dishes of chilled salads between her withered hands.

For long moments, Nesryn ate everything her aunt and uncle piled onto her plate, which was indeed as good as any food at the palace. By the time she was stuffed to the point of exploding, by the time she'd drained her tea to its dregs, her aunt said slyly to her, "I had hoped you'd be bringing a guest, you know."

Nesryn snorted, brushing the hair from her face. "Lord Westfall is quite busy, Aunt." But if Yrene had gotten him onto a horse this morning  perhaps she'd indeed get him here tomorrow. Introduce him to her family---to the four children who filled this house with chaos and joy.

Her aunt sipped daintily from her tea. "Oh, I didn't mean him." A wry grin between Zahida and Brahim. "I meant Prince Sartaq."

Nesryn was glad she'd finished her tea. "What of him?"

That sly smile didn't fade. "Rumor claims \emph{someone}"---a pointed look at Nesryn---"was spotted riding with the prince at dawn yesterday. Atop his ruk."

Nesryn reined in her wince. "I  was." She prayed no one had seen her with him last night---that word would not reach the Valg agent's ears they were being hunted.

Her uncle chuckled. "And you planned to tell us when? The children were beside themselves with excitement that their beloved cousin had ridden on

Kadara herself."

"I did not want to brag." A pathetic excuse.

"Hmmm," was all her uncle replied, mischief dancing in his gaze.

But Nesryn's aunt gave her a knowing look, steel in her brown eyes, as if she, too, did not forget for one moment the family who remained in Adarlan and perhaps now tried to flee to these shores. Her aunt simply said, "The ruks will not fear wyverns."

