
\chapter{21}

Nesryn blinked at Hasar.

The princess smiled, cold as a snake, and clarified, "It is not polite to only sit with your companion. We should have separated you two before now."

Nesryn glanced to him. Everyone watched. Chaol had no idea---absolutely none---what to say. Yrene seemed inclined to melt into the green marble floor.

Sartaq cleared his throat. "Join me here, Captain Faliq."

Nesryn stood quickly, and Hasar beamed up at her. The princess patted the back of the seat Nesryn had vacated and crooned to Yrene, lingering a few feet away, "You sit here. In case you are needed."

Yrene shot Chaol a look that might have been considered pleading, but he kept his face neutral and offered a close-lipped smile.

Nesryn found her seat beside Sartaq, who had asked a vizier to move down the table, and Hasar, satisfied that the adjustments had been done to her liking, deemed that her own usual seats were not to her taste and kicked out two viziers down by Arghun. The second seat was for Renia, who gave her lover a mildly disapproving glance, but smiled to herself---as if it were typical.

The meal resumed, and Chaol slid his attention to Yrene. The vizier on her other side paid her no heed. Platters were passed around by servants, food and drink piled and poured. Chaol muttered under his breath, "Do I want to know?"

Yrene cut into the simmered lamb and saffron rice heaped on her golden plate. "No."

He was willing to bet whatever shadows had been in her eyes earlier today, the thing she'd halted herself from saying to him  It went hand in hand with whatever was unfolding here.

He peered down the table, to where Nesryn watched them, half listening to Sartaq as the prince spoke about something Chaol could not hear over the clatter of silverware and discussion.

He shot her an apologetic look.

Nesryn threw him a warning one in answer---directed toward Hasar.
\emph{Be careful}.

"How are your toes?" Yrene said, taking tiny bites of her food. He'd seen her devour the box of carob sweets she'd gotten for them atop their horses. The dainty eating here---for show.

"Active," he said with a half smile. No matter that it had only been two hours since they'd last seen each other.

"Sensation?"

"A tingle."

"Good." Her throat bobbed, that scar shifting with it.

He knew they were being watched. Listened to. She did as well.

Yrene's knuckles were white as she clenched her utensils, her back ramrod straight. No smile. Little light in her kohl-lined eyes.

Had the princess maneuvered them to sit together to talk, or to manipulate Kashin into some sort of action? The prince was indeed watching, even while he engaged two gold-robed viziers in conversation.

Chaol murmured to Yrene, "The role of pawn doesn't suit you."

Those gold-brown eyes flickered. "I don't know what you're talking about." But she did. The words weren't meant for him.

He scrambled for topics to get them through the meal. "When do you meet with the ladies for their next lesson?"

Some of the tension drained from Yrene's shoulders as she said, "Two weeks.

It would normally be next week, but many of them have their examinations then, and will be focused on studying."

"Some exercise and fresh air might be helpful."

"I'd say so, but to them, these tests are life and death. They certainly were to me."

"Do you have any more remaining?"

She shook her head, her jeweled earrings catching the light. "I completed my final one two weeks ago. I am an official healer of the Torre." A bit of a selfeffacing humor danced in her eyes.

He lifted his goblet to her. "Congratulations."

A shrug, but she nodded in thanks. "Though Hafiza thinks to test me one last time."

Ah. "So I am indeed an experiment."

A piss-poor attempt at making light of their argument days ago, of that rawness that had ripped a hole through him.

"No," Yrene said quietly, quickly. "You have very little to do with it. This last, unofficial test  It is about me."

He wanted to ask, but there were too many eyes upon them. "Then I wish you luck," he said formally. So at odds with how they'd spoken while riding through the city.

The meal passed slowly and yet swiftly, their conversation stilted and infrequent.

It was only when the desserts and \emph{kahve} were served that Arghun clapped his hands and called for entertainment.

"With our father in his chambers," Chaol heard Sartaq confide to Nesryn,

"we tend to have more  informal celebrations."

Indeed, a troupe of musicians in finery, bearing instruments both familiar and foreign, emerged into the space between the pillars beyond the table. Rumbling drums and flutes and horns announced the arrival of the main event: dancers.

A circle of eight dancers, both male and female---a holy number, Sartaq explained to a tentatively smiling Nesryn---emerged from the curtains to the side of the pillars.

Chaol tried not to choke.

They had been painted in gold, bedecked with jewels and gauzy, belted robes of thinnest silk, but beneath that  nothing.

Their bodies were lithe and young, the peak of youth and virility. Hips rolled, backs arched, hands twined in the air above them as they began to weave around one another in circles and lines.

"I told you," was all Yrene muttered to him.

"I think Dorian would enjoy this," he muttered back, and was surprised to find the corners of his mouth tugging upward at the thought.

Yrene threw him a bemused look, some light back in her eyes. People had twisted in their seats to better watch the dancers, their sculpted bodies and nimble, bare feet.

Perfect, precise movements, their bodies merely instruments of the music. Beautiful---ethereal and yet  tangible. Aelin, he realized, would have enjoyed this, too. Greatly.

As the dancers performed, servants hauled over chairs and couches, arranging pillows and tables. Bowls of smoking herbs were laid atop them, the smell sweet and cloying.

"Don't get too close if you want your senses intact," Yrene warned as a male servant bore one of the smoking metal dishes toward a carved wood table. "It's a mild opiate."

"They really let their hair down when their parents are away."

Some of the viziers were leaving, but many left the table to take up cushioned seats, the entirety of the great hall remade in a matter of moments to accommodate lounging, and---

Servants emerged from the curtains, well groomed and dressed in gauzy, rich silk as well. Men and women, all beautiful, found their way to laps and armrests, some curling at the feet of viziers or nobility.

He'd seen fairly unleashed parties at the glass castle, but there had still been a stiffness. A formality and sense that such things were hidden behind closed doors. Dorian had certainly saved it for his own room. Or someone else's. Or he just dragged Chaol into Rifthold, or down to Bellhaven, where the nobility held parties far more uninhibited than those of Queen Georgina.

Sartaq remained at the table beside Nesryn, who watched the skilled dancers with wide-eyed admiration, but the other royal children 
Duva, a hand on her belly, bid her farewells, her husband at her side, silent as always. The smoke was not good for the babe in her womb, Duva claimed, and Yrene nodded in approval, though no one looked her way.

Arghun claimed a couch for himself around the dancing, reclining and breathing in the smoke rippling off the embers in those small metal bowls beside them. Courtiers and viziers vied for the seats nearest the eldest prince.

Hasar and her lover took a small couch for themselves, the princess's hands soon tangling in her lover's thick black hair. Her mouth found a spot on the woman's neck a moment later. Renia's answering smile was slow and broad--- her eyes fluttering closed as Hasar whispered something against her skin.

Kashin seemed to wait for minutes as Yrene and Chaol watched the unfolding decadence from the emptying banquet table.

Waiting for Yrene, no doubt, to rise.

Color had stained her cheeks as she kept her eyes firmly on her
\emph{kahve}, steam curling from the small cup.

"You've seen this before?" Chaol asked her.

"Give it an hour or two, and they'll all slip away to their rooms---not alone, of course."

Prince Kashin seemed to have dragged out his conversation with the vizier beside him for as long as he could stomach. He opened his mouth, looking right toward Yrene, and Chaol read the invitation in his eyes before the man could speak.

Chaol had perhaps a heartbeat to decide. To see that Sartaq had invited Nesryn to sit with him---not at the table, not on one of the couches, but at a pair of chairs to the far back of the room, where there was no smoke and the windows were open, and yet they could still watch. She gave Chaol a reassuring nod, her pace unhurried as she walked with the prince.

So as Kashin leaned forward to invite Yrene to join him at a couch, Chaol turned to the healer and said, "I would like to sit with you."

Her eyes were slightly wide. "Where."

Kashin shut his mouth, and Chaol had the sense that there was a target being drawn on his chest.

But he held Yrene's gaze and said, "Where it is quieter."

There were only a few couches left free---all close to the thickest smoke and dancing. But there was one half hidden in shadow near an alcove across the room, a small brazier of those herbs smoldering on the low-lying table before it. "If we are meant to be seen together tonight," he said so quietly only Yrene could hear, "then remaining here for a while would be better than leaving together." What a message
\emph{that} would send, given the shift in the party's atmosphere. "And I would not have you walk alone."

Yrene rose silently, smiling grimly. "Then let us relax, Lord Westfall." She gestured toward the shadowed couch beyond the edge of the light.

She let him wheel himself over. Kept her chin high, the skirts of her gown trailing behind her as she headed for that alcove. The back of the dress was mostly open---revealing smooth, unblemished skin and the fine groove of her spine. It dipped low enough for him to make out the twin indentations in her lower back, as if some god had pressed his thumbs there.

He felt too many eyes upon them as she settled herself on the couch, the skirts of her dress twisted along the floor past her ankles, her arms bare as she spread one along the back of the plush cushions.

Chaol held her low-lidded stare as he reached the couch, faster than the servants could approach, and eased himself from chair to cushions. A few movements had him angled toward her---and he nodded his thanks to the servant who moved his chair away. From this vantage, they had an unobstructed view of the dancers, the seating areas, the servants and nobility now starting to run hands and mouths over skin and fabric, even as they watched the unparalleled entertainment.

Something twisted---not unpleasantly---in his gut at the display.

"They do not force servants here," Yrene said quietly. "It was the first thing I asked during my initial time at these gatherings. The servants are eager to raise their positions, and the ones who are here know what privilege it might bring them if they leave here with someone tonight."

"But if they are paid," he countered, "if they worry for their positions should they decline, then how can this ever be true consent?"

"It isn't. Not when you put it that way. But the khaganate has made sure that other lines are maintained. Age restrictions. Vocal consent. Punishments for those---even royalty---who break those rules." She'd said as much days ago.

A young woman and man had positioned themselves on either side of Arghun, one nibbling at his neck while the other traced circles along the prince's thighs. All the while, the prince continued conversation with a vizier seated in a chair to his left, unfazed.

"I thought he had a wife," Chaol said.

Yrene followed his gaze. "He does. She stays at his country estate. And servants are not considered affairs. The needs they see to  It might as well be giving a bath." Her eyes danced as she said, "I'm sure you discovered that your first day."

His face heated. "I was  surprised at the attention to detail. And involvement."

"Kadja was likely selected to please you."

"I'm not inclined to stray. Even with a willing servant."

Yrene glanced toward Nesryn, deep in conversation with Sartaq. "She is lucky to have such a loyal companion, then."

He waited for a tug of jealousy at seeing Nesryn's smile to the prince, whose body was the pinnacle of relaxed, his arm draped along the back of the couch behind her, an ankle crossed over a knee.

Perhaps he just trusted Nesryn, but nothing stirred in him at the sight.

Chaol found Yrene watching him, her eyes like topaz in the shadows and smoke.

"I met with my friend the other evening," she said, her lashes fluttering. No more than a woman lulled by the smoldering opiates. Even his own head was starting to feel fuzzy. His body warm. Cozy. "And again this evening before dinner."

Hasar.

"And?" He found himself studying the slight curl to the ends of Yrene's long hair. Found his fingers shifting, as if imagining the feel of it between them.

Yrene waited until a servant bearing a tray of candied fruits walked past. "She told me \emph{your} friend is still unaccounted for. And a net has been stretched across the center of the table."

He blinked, sorting through the smoke and the words.

Armies. Perrington's armies had been stretched across the continent. No wonder she hadn't discussed it earlier in the streets; no wonder it had brought such shadows to her eyes. "Where?"

"Mountains to---your usual haunt."

He recalled a mental map of the land. From the Ferian Gap to Rifthold. Holy gods.

"You are sure of it?" A nod.

He felt eyes sliding toward them now and then.

Yrene did, too. He tried not to start at the hand she laid on his arm. As she looked up at him beneath lowered lashes, eyes sleepy---inviting. "I was asked the other day, and again today, in a manner I cannot refuse." She was threatened. He clenched his jaw.

"I need a place. A direction," she murmured. "For where your
\emph{other} friend might go."

Aelin. "She is  where is she?"

"They do not know."

Aelin was---missing. Unaccounted for by even the khaganate's spies.

"Not in her home?"

A shake of the head that made Chaol's heart begin to pound wildly. Aelin and Dorian---both unaccounted for. Missing. If Perrington were to strike
\ldots"I don't know where she would go. What she planned to do." He laid his hand over hers. Blocked out the softness of her skin. "Her plan was to return home. Rally a host."

"She has not. And I do not doubt the clarity of the \emph{eyes} here. And there." Hasar's spies. And others.

Aelin was not in Terrasen. Had never reached Orynth.

"Wipe that look off your face," Yrene purred, and though her hand brushed his arm, her eyes were hard.

He struggled to do so, but managed to give her a sleepy smile. "Does your friend think they have fallen into the hands of someone else?"

"She does not know." Yrene trailed fingers up his arm, light and unhurried. That simple ring still sat upon her hand. "She wants me to ask you. Pry it from you."

"Ah." Her slender, beautiful hand slid along his arm. "Hence the new seating arrangement." And why Yrene had so often seemed on the verge of speaking today and then opted for silence.

"She will make life very difficult if I do not appear to get you to warm to me."

He halted her hand at his bicep, finding her fingers shaking slightly. Perhaps it was the sweet, cloying smoke curling around them, perhaps it was the music and the dancers with their bare skin and jewels, but Chaol said, "I would think you'd already done that, Yrene Towers."

He watched the color bloom on her face. Watched how it made the gold in her eyes brighten.

Dangerous. Dangerous and stupid and---

He knew others were watching. Knew Nesryn sat with the prince.

She'd understand that it was for show. Nesryn's presence with Sartaq was merely another part of it. Another display.

He told himself that as he continued to hold Yrene's gaze, continued to press her hand against his upper arm. Continued to watch the color stain her cheeks.

The tip of her tongue darted out to moisten her lips.

He watched that, too.

A heavy, calming warmth settled deep into him.

"I need a place. Any place."

It took him a few heartbeats to figure out what she was asking. The threat the princess implied for not getting information from him.

"Why lie at all? I would have told you the truth." His mouth felt far away. "After the lesson with the girls," she murmured, "I owed you something."

And this reveal of Hasar's interests  "Will she be swayed to our cause?"

Yrene studied the room, and Chaol found his hand drifting from hers. Sliding up her bare shoulder, to rest along her neck.

Her skin was soft as sun-warmed velvet. His thumb stroked up the side of her throat, so near that slender scar, and she cut her eyes to him.

There was warning there---warning and yet  He knew the warning was not directed at him. But herself. Yrene breathed, "She \ldots" He couldn't resist a second stroke of his thumb down the side of her neck. Her throat brushed against his hand as she swallowed again. "She is concerned about the threat of fire."

And fear could be a motivation that either helped or destroyed any chance of alliance.

"She thinks  thinks you are potentially behind the library attack. As some manipulation."

He snorted, but his thumb stilled, right over her fluttering pulse. "She gives us more credit than we're due." But that was alarm now flaring to life in Yrene's eyes. "What do you believe, Yrene Towers?"

She laid her hand atop his own but made no move to remove his touch from her neck.

"I think your presence may have triggered other forces to act, but I do not believe you are the sort of man who plays games." Even if their current position said otherwise.

"You go after what you want," Yrene continued, "and you pursue it directly. Honestly."

"I used to be that sort of man," Chaol countered. He could not look away from her.

"And now?" Her words were breathless, her pulse hammering beneath his palm.

"And now," Chaol said, bringing his head closer to hers, near enough that her breath brushed his mouth, "I wonder if I should have listened to my father when he tried to teach me."

Yrene's eyes dropped to his mouth, and every instinct, every bit of focus, narrowed on that movement. Every part of him came to aching attention.

And the sensation of it, as he casually adjusted his jacket over his lap, was better than an ice bath.

The smoke---the opiates. It was some sort of aphrodisiac, some lulling of common sense.

Yrene was still watching his mouth as if it were a piece of fruit, her uneven breath lifting those lush, high breasts within the confines of her gown.

He forced himself to remove his hand from her neck. Forced himself to lean back.

Nesryn had to be watching. Had to be wondering what the hell he was doing.

He owed her better than this. He owed Yrene better than whatever he had just done, whatever madness---

"Skull's Bay," he threw out. "Tell her fire can be found at Skull's Bay."

It was perhaps the one place Aelin would never go---down to the domain of the Pirate Lord. He'd heard her story, once, of her "misadventure" with Rolfe. As if destroying his city and wrecking his prized ships were just another bit of fun. Heading there would indeed be the last thing Aelin would do, with the Pirate Lord's promise to slaughter her on sight.

Yrene blinked, as if remembering herself, the situation that had brought them here, to this couch, to be knee-to-knee and nearly nose-to-nose.

"Yes," she said, pulling away, blinking furiously again. She frowned at the smoldering embers within their metal cage on the table. "That will do."

She waved away an unfurling talon of smoke that tried to wend between them. "I should go."

A wild, keen-edged panic glinted in her eyes. As if she, too, had realized, had \emph{felt}---

She stood, straightening the skirts of her gown. Gone was the sultry, steady woman who had strutted over to this couch. Here---here was the girl of about two-and-twenty, alone in a foreign city, prey to the whims of its royal children. "I hope \ldots," she said, glancing toward Nesryn. Shame. It was---shame and guilt now weighing her shoulders. "I hope you never learn to play those sorts of games."

Nesryn remained deep in conversation with Sartaq, showing no sign of distress, of knowledge of  of whatever had happened here.

He was a bastard. A gods-damned bastard.

"I'll see you tomorrow," was all he could think to say to Yrene. But he blurted as she walked away, "Let me get you an escort."

Because Kashin was watching them from across the room, a servant girl in his lap, running a hand through his hair. And that was  oh, that was cold violence in Kashin's face as he noticed Chaol's attention.

The others might think what had just gone on between him and Yrene was an act, but Kashin  The man wasn't as stupidly loyal as the others thought. No, he was well aware of those around him. He could read men. Assess them.

And it had not been the arousal that had let the prince realize it was genuine. But the guilt Chaol realized too late he and Yrene had let show.

"I will ask Hasar," Yrene said, and headed toward where the princess and her lover sat on their couch, mouths roving over each other with an unhurried attention to detail.

He remained on the couch, monitoring as Yrene approached the women.

Hasar blinked up blearily at her.

But the lust fogging the princess's face cleared at the curt nod Yrene gave. Mission accomplished. Yrene leaned down and whispered into Hasar's ear as she kissed her cheeks in farewell. Chaol read the movement of her lips even from across the room. \emph{Skull's Bay}.

Hasar smiled slowly, then snapped her fingers to a waiting guard. The man immediately strode for them. He watched her order the man, watched her undoubtedly threaten him with death and worse if Yrene did not make it back to the Torre safely.

Yrene only gave the princess an exasperated smile before bidding her and Renia good night and following the guard out. She glanced back at the archway.

Even across the nearly hundred feet of polished marble and towering pillars, the space between them went taut.

As if that white light he'd glimpsed inside himself two days ago was a living rope. As if she'd somehow planted herself in him that afternoon.

Yrene did not so much as nod before she left, skirts swirling around her.

When Chaol looked to Nesryn again, he found her attention upon him.

Found her face blank---so carefully blank---as she gave him a little nod of what he assumed was understanding. The match was over for tonight. She was waiting to hear the final score.

The smoke was still clinging to Chaol's nostrils, his hair, his jacket as he and Nesryn entered their suite an hour later. He had joined her and Sartaq in their quiet little area, watching guests peel off to their own chambers---or someone else's. Yes, Dorian would certainly have loved this court.

Sartaq escorted them to their room and offered them a somewhat stiff good night. More restrained than his words and smiles of earlier. Chaol didn't blame him. There were likely eyes everywhere.

Even if the prince's own lingered mostly on Nesryn as she bid Sartaq farewell and she and Chaol slipped into their suite.

The suite was mostly dark, save for a colored glass lantern Kadja had left burning on the foyer table. Their bedroom doors loomed like cavern mouths.

The pause in the dim foyer went on for a heartbeat too long.

Nesryn silently stepped toward her room.

Chaol grabbed her hand before she could make it a foot.

Slowly, she looked back over her shoulder, her dark hair shifting like midnight silk.

Even in the dimness, he knew Nesryn read what lay in his eyes.

His skin tightened around his bones, his heart a thundering beat, but he waited.

She said at last, "I think I am needed elsewhere than this palace right now."

He maintained his grip on her hand. "We shouldn't discuss this in the hall."

Nesryn's throat bobbed, but she nodded once. She made to push his chair, but he moved before she could, steering himself into his bedroom. Letting her follow.

Letting her shut the door behind them.

Moonlight leaked in through the garden windows, spilling upon the bed.

Kadja had not lit the candles, either anticipating the use of this room after the party for purposes other than sleeping or that he might not return at all. But in the dark, in the humming from the cicadas in the garden trees  "I need you here," Chaol said.

"Do you?" A stark, honest question.

He gave Nesryn the respect of considering her question. "I  We were supposed to do this together. Everything."

She shook her head, short hair shifting. "Paths change. You know that as much as anyone."

He did. He really damn did. But it still  "Where do you mean to go?"

"Sartaq mentioned that he wishes to seek out answers amongst his people, about whether the Valg made it to this continent before. I
 I am tempted to go with him, if he will let me. To see if there are indeed answers to be found, and if I might convince him to perhaps go against his father's orders. Or at least speak on our behalf."

"To go with him to where, though? The ruk riders in the south?"

"Perhaps. He mentioned at the party that he'll leave in a few days. But you and I have a slim enough shot. Maybe I can better our odds with the prince, find information of value amongst the rukhin. If one of Erawan's agents is in Antica  I trust the khagan's guard to protect this palace and the Torre, but you and I, we must gather what forces we can before Erawan can send more against us." She paused. "And you 
you are making good progress. I would not interfere with that."

Unspoken words ran beneath her offer.

Chaol scrubbed at his face. For her to leave, to simply accept it, this fork in the path before them  He blew out a breath. "Let's wait until morning before we decide anything. No good comes from choices made late at night."

Nesryn fell silent, and he hoisted himself onto the mattress before removing his jacket and boots. "Will you sit with me? Tell me about your family---about the celebration today with them." He had only received the barest of details, and perhaps it was guilt that now fueled him, but 

Their eyes met in the dark, a nightingale's hymn flitting through the closed doors. He could have sworn he saw understanding shine in her face, then settle, a rock dropped into a pool.

Nesryn approached the bed on silent feet, unbuttoning her jacket and slinging it over a chair before toeing off her boots. She climbed onto the mattress, a pillow sighing as she leaned against it.

\emph{I saw}, he could have sworn he read flickering in her gaze. \emph{I know}.

But Nesryn spoke of the dockside ceremony, how her four little cousins had chucked flower wreaths into the sea and then run shrieking from the gulls that swarmed them to steal the little almond cakes out of their hands. She told him of her uncle, Brahim, and her aunt, Zahida, and their beautiful house, with its multiple courtyards and crawling flowers and lattice screens.

With every glance, those unspoken words still echoed. \emph{I know}. \emph{I know}.

Chaol let Nesryn talk, listened until her voice lulled him to sleep, because he knew, too.

