
\chapter{22}

Yrene debated not showing up the next day.

What had happened on the couch last night 

She'd returned to her room overheated and frantic, unable to settle. Peeling off Hasar's gown and jewels, she'd folded them neatly on her chair with shaking hands. Then she'd pushed her trunk in front of the door, just in case that murdering demon had spied her inhaling ungodly amounts of that smoke and thought to catch her out of her wits.

Because she had been. Utterly out of her mind. All she had known was the heat and smell and comforting size of him---the scrape of his calluses against her skin and how she wanted to feel them elsewhere. How she had kept looking at his mouth and it was all she could do to keep from tracing it with her fingers. Her lips.

She hated those parties. The smoke that made one abandon any sort of common sense. Inhibitions. Precisely why the nobility and wealthy loved to bring it out, but 

Yrene had paced her tower room, running her hands over her face until she smudged the cosmetics Hasar had personally applied.

She'd washed her face thrice. Slipped into her lightest nightgown and then tossed and turned in bed, the fabric clinging and chafing against her sweaty, burning skin.

Counting down the hours, the minutes, until that smoke's grip loosened.

Cleared away.

It didn't let go easily. And it was only during the quietest, blackest hours of the night that Yrene took matters into her own hands.

A stronger dose than usual had been put out tonight. It crawled all over her, running talons along her skin. And the face it summoned, the hands she imagined brushing over her skin--- Release left her hollow---unsatisfied.

Dawn broke, and Yrene scowled at her haggard reflection in the sliver of mirror above the washbasin.

The opiate's grip had vanished with the few hours of sleep she'd managed to steal, but  Something twisted low in her gut.

She washed and dressed and packed Hasar's finery and jewels in a spare satchel. It was best to get it over with. She'd return the princess's clothes and jewels after. Hasar had been smug as a Baast Cat at the information Yrene had given her, the lie Chaol had fed her to hand to the princess.

She had debated not telling him, but even before the smoke, before that madness  When he'd offered to sit with her to avoid refusing Kashin, after a day spent wandering the city in unhurried ease, she'd decided. To trust him. And then lost her mind entirely.

Yrene could barely look the guards, the servants, the viziers and nobility in the face as she entered the palace and made her way to Lord Westfall's rooms. There was no doubt some had spied her on the couch with him. Some hadn't--- though they might have heard.

She'd never shown such behavior at the palace. She should tell Hafiza. Let the Healer on High hear of her brazenness before it reached the Torre from other lips.

Not that Hafiza would scold her, but  Yrene could not escape the feeling that she needed to confess. To make it right.

She'd keep today's session brief. Or as brief as they could, when she lost all sense of time and place in that dark, raging hell of his wound.

Professional.

Yrene entered the suite, telling Kadja, "Ginger, turmeric, and lemon," before walking to Chaol's bedroom. Kadja seemed inclined to object, but Yrene ignored her and pushed open the bedroom door.

Yrene halted so fast she nearly stumbled.

It was the rumpled sheets and pillows she noticed first. Then his naked chest, his hips barely covered by a swath of white silk.

Then a dark head, facedown on the pillow beside his. Still sleeping.

Exhausted.

Chaol's eyes instantly flew open, and all Yrene managed was a silent, "Oh." Shock and---something else flared in his gaze, his mouth opening.

Nesryn stirred beside him, brows knotting, her shirt wrinkled.

Chaol grabbed fistfuls of the sheet, the muscles of his chest and abdomen shifting as he rose up on his elbows--- Yrene simply walked out.

She waited on the gold sofa in the sitting room, her knee bouncing as she watched the garden, the climbing flowers just beginning to open up along the pillars outside the glass doors.

Even with the burbling fountain, it didn't quite block out the sounds of Nesryn murmuring as she awoke---then the pad of soft feet from his bedroom to her own, followed by the shutting of her door.

A moment later, wheels groaned, and there he was. In his shirt and pants. Hair still disheveled. As if he'd run his hands through it. Or Nesryn had.

Repeatedly.

Yrene wrapped her arms around herself, the room somehow so very large. The space between them too open. She should have eaten breakfast. Should have done something to keep from this lightness. This hollow pit in her stomach.

"I didn't realize you'd be here so early," he said softly. She could have sworn guilt laced his tone.

"You said I could come at dawn," she replied with equal quiet, but hated the note of accusation in her voice and quickly added, "I should have sent word."

"No. I---"

"I can come back later," she said, shooting to her feet. "Let you two eat breakfast."

Together. Alone.

"No," he said sharply, pausing his approach near their usual couch. "Now is fine."

She couldn't look at him. Couldn't meet his eyes. Or explain why.

"Yrene."

She ignored the command in her name and went to the desk, seating herself behind it, grateful for the wall of carved wood between them. The stability of it beneath her palm as she opened up her satchel from where she'd left it along the edge and began unpacking her things with careful precision. Vials of oils she did not need. Journals.

Books---the ones she'd taken from the library, \emph{The Song of Beginning} with them. Along with those ancient, precious scrolls. She had not been able to think of a safer place for them beyond here. Beyond him.

Yrene said very quietly, "I can make up a tonic. For her. If such a thing is needed. Isn't wanted, I mean."

\emph{A child}, she couldn't bring herself to say. Like the fat babe she'd spied him smiling so broadly at yesterday. As if it was a blessing, a joy he one day might desire---

"And I can make up a daily one for you," she added, every word stumbling and tripping out of her mouth.

"She's already taking one," he said. "Since she was fourteen."

Likely since she first started bleeding. For a woman in a city like Rifthold, it was wise. Especially if she planned to enjoy herself as well.

"Good," was all Yrene could think to say, still stacking her books. "Smart." He approached the desk until his knees slid beneath the other end. "Yrene." She thumped book after book on top of each other.

"Please."

The word had her lifting her gaze. Meeting his stare---the sun-warmed soil of his eyes.

And it was the formation of those two words that she beheld brewing in his gaze---\emph{I'm sorry}---that had her shooting up from the desk again. Walking across the room. Flinging open the garden doors.

There was nothing to be sorry for. Nothing.

They were lovers, and she 

Yrene lingered at the garden doors until Nesryn's bedroom door opened and closed. Until she heard Nesryn poke her head into the sitting room, murmur a farewell to Chaol, and leave.

Yrene tried to bring herself to look over a shoulder at Captain Faliq, to offer a polite smile, but she pretended not to hear the brief encounter. Pretended to be too busy examining the pale purple flowers unfurling in the morning sunlight.

She shoved back against the hollowness. She had not felt so small, so
 insignificant for a long, long time.

\emph{You are the heir apparent to Hafiza, Healer on High}. \emph{You are nothing to this man and he is nothing to you. Stay the course. Remember Fenharrow---your home. Remember those who are there---who need your help.}

\emph{Remember all that you promised to do. To be.}

Her hand slid into her pocket, curling around the note there.

\emph{The world needs more healers.}

"It's not what you think," Chaol said behind her.

Yrene closed her eyes for a heartbeat.

\emph{Fight---fight for your miserable, useless, wasted life.}

She turned, forcing a polite smile to her face. "It is a natural thing. A healthy thing. I'm glad you're feeling  up to the task."

From the ire that rippled in his eyes, the tightness of his jaw, Chaol perhaps was not.

\emph{The world needs more healers. The world needs more healers. The world needs more healers.}

Finish with him, heal him, and she could leave Hafiza, leave the Torre, with her head held high. She could return home, to war and bloodshed, and make good on her promise. Make good on that stranger's gift of freedom that night in Innish.

"Shall we begin?"

It would be in here today. Because the prospect of sitting on that rumpled bed that likely still smelled of them---

There was a tightness to her throat, her voice, that she could not shake, no matter how many breaths she took.

Chaol studied her. Weighing her tone. Her words. Her expression.

He saw it---heard it. That tightness, that brittleness.

\emph{I expected nothing}, she wanted to say. \emph{I---I am}
nothing\emph{.}

\emph{Please don't ask. Please don't push. Please.}

Chaol seemed to read that, too. He said quietly, "I didn't take her to bed."

She refrained from mentioning that the evidence seemed stacked against him.

Chaol went on, "We spoke long into the night and fell asleep. Nothing happened."

Yrene ignored the way her chest both hollowed out and filled at the words. Didn't trust herself to speak as the information settled.

As if sensing her need for a breath, Chaol began to turn toward the couch, but his attention snagged on the books she'd stacked on the table. On the scrolls.

The color drained from his face.

"What is that," he growled.

Yrene strode to the desk, picking up the parchment and unrolling it carefully

to display the strange symbols. "Nousha, the Head Librarian, found it for me that night when I asked her for information on  the things that hurt you. In all the ---upheaval, I forgot it. It was shelved near the Eyllwe books, so she threw it in, just in case. I think it's old. Eight hundred years at least." She was babbling, but couldn't stop, grateful for any subject but the one he'd been so near to breaching. "I think they're runes, but I've seen none like it. Neither had Nousha."

"They are not runes," Chaol said hoarsely. "They're Wyrdmarks."

And from what he had told her, Yrene knew there was much more. So much more he had not divulged. She stroked a hand over the dark cover of
\emph{The Song of Beginning}. "This book  It mentioned a gate. And keys. And three kings to wield them."

She wasn't certain he was breathing. Then Chaol said, voice low, "You read that. In that book."

Yrene opened the pages, flipping to the illustration of the three figures before that otherworldly gate. Approaching, she held the book open for him to see. "I couldn't read much of it---it's in an ancient form of Eyllwe---but \ldots" She flipped to the other illustration, of the young man being infested by that dark power on the altar. "Is that
 is that what they truly do?"

His hands slackened at the sides of his chair as he stared and stared at the panel featuring the young man's cold, dark eyes. "Yes."

The word held more pain and fear than she'd expected.

She opened her mouth, but he sliced a warning glare at her, mastering himself. "Hide it, Yrene. Hide \emph{all} of it. Now."

Her heart thundered in her chest, her limbs, but she snatched up the books. The scrolls. He watched the doors, the windows, while she set about placing them under cushions and inside some of the larger vases. But the scroll  it was too precious. Too ancient to treat so callously. Even flattening it out might harm the integrity of the paper, the ink.

He noticed her looking around helplessly, the scroll in her hands. "My boots,

if you will, Yrene," he said casually. "I have a second pair that I'd rather wear today."

Right. Right.

Yrene hurried from the sitting room into his bedroom, wincing at the askew bed linens, at what she'd so stupidly assumed and seemed like such an enormous fool about---

She strode into the small dressing room, spotted his boots, and slid the parchment down the neck of one. Then took the pair and shoved it in a drawer, covering it with a stack of linen towels.

She reentered the sitting room a moment later. "I couldn't find them. Perhaps

Kadja sent them out for cleaning."

"Too bad," he said casually, his own boots now removed. Along with his shirt.

Her heart still raged as he eased onto the gold sofa but did not lie down.

"Do you know how to read?" she asked, kneeling before him and taking his bare foot in her hands. \emph{The Wyrdmarks?}

"No." His toes shifted as she began careful rotations of his ankle. "But I know someone who does it for me when it's important." Careful, veiled words for anyone listening.

Yrene went about exercising his legs, stretching and bending, the motions repeated over and over while he moved his toes as much as he could. "I should show you the library sometime," she offered. "You might find something that strikes your fancy---for your reader to narrate to you."

"Do you have many similarly interesting texts?"

She lowered his left leg and started on the other. "I could ask---Nousha knows everything."

"When we're done. After you rest. It's been a while since I had a book to  intrigue me."

"It'd be my honor to escort you, my lord." He grimaced at the formal title,

but Yrene worked his right leg, going through the same motions, before she bade him to lie down on the couch. They worked in silence while she rotated his hips, urging him to try to move them on his own, while bending and stretching as much of his leg as she could.

She said after a moment, her voice barely audible, "You only talk of

Erawan." His eyes flashed in warning at the name. "But what of Orcus and

Mantyx?"

"Who?"

Yrene began another set of the exercises on his legs and hips and lower back. "The other two kings. They are named in that book."

Chaol stopped wriggling his toes; she flicked them in reminder. The air whooshed from him as he resumed. "They were defeated in the first war. Sent back to their realm or slain, I can't recall."

Yrene considered as she lowered his leg to the couch, nudging him to flip onto his stomach. "I'm sure you and your companions are adept at this whole saving-the-world thing," she mused, earning a snort from him, "but I would make sure you know for certain. Which one it is."

She took up a perch on the thin lip of golden sofa cushion that his body did not cover.

Chaol twisted his head toward her, the muscles in his back bunching. "Why?"

"Because if they were merely banished to their realm, who is to say they aren't still waiting to be let back into our world?"

