
\chapter{24}

Nesryn knew.

She knew it hadn't been mere interest that had prompted Chaol to ask her to talk to him last night, but guilt.

She was fine with it, she told herself.
She had been a replacement for not one, but two of the women in his life.
A third one\ldots She was fine with it, she repeated as she returned from stalking through Antica's streets---not a whisper of Valg to be found---and entered the palace grounds.

Nesryn braced herself as she peered up at the palace, not quite ready to return to their suite to wait out the brutal late afternoon heat.

A massive figure atop a minaret caught her eye, and she smiled grimly.

She was out of breath when she reached the aerie, but mercifully, Kadara was the only one present to witness it.

The ruk clicked her beak at Nesryn in greeting and went back to ripping at what appeared to be an entire slab of beef.
Ribs and all.

"I heard you were headed here," Sartaq said from the stairs behind her.

Nesryn whirled.
"I---how?"

The prince gave her a knowing smile and stepped into the aerie.
Kadara puffed her feathers with excitement and dug back into her meal, as if eager to finish and be in the skies.
"This palace is crawling with spies.
Some of them mine.
Is there anything you wanted?"

He scanned her---seeing the face that yesterday her aunt and uncle had complained looked tired.
Worn out.
Unhappy.
They'd crammed her with food, then insisted she take their four children back down to the docks to select fish for their evening meal, then shoved more food down her throat before she'd returned to the palace for the feast.
\emph{Still peaky}, Zahida clucked.
\emph{Your eyes are heavy.}

"I \ldots" Nesryn surveyed the view beyond, the city simmering in the late afternoon heat.
"I just wanted some quiet."

"Then I'll let you have it," Sartaq said, and turned to the open archway into the stairwell.

"No," she blurted, reaching toward him.
She halted her hand, dropping it immediately as it came within skimming distance of his leather jacket.
No one grabbed a prince.
No one.
"I didn't mean you had to leave.
I\ldots I don't mind your company."
She added quickly, "Your Highness."

Sartaq's mouth quirked up.
"It's a bit late to be throwing in my fancy title, isn't it?"

She gave him a pleading look.
But she'd meant what she said.

Last night, talking with him at the party, even talking with him in the alley outside the Torre a few nights before that\ldots She had not felt quiet or aloof or strange.
She had not felt cold or distant.
He'd done her an honor in giving her such attention, and in escorting her and Chaol back to their rooms.
She did not mind company---quiet as she could be, she \emph{enjoyed} being around others.
But sometimes 

"I spent most of yesterday with my family.
They can be\ldots tiring.
Demanding."

"I know how you feel," the prince said drily.

A smile tugged at her lips.
"I suppose you do."

"You love them, though."

"And you do not?"
A bold, brash question.

Sartaq shrugged.
"Kadara is my family.
The rukhin, they are my family.
My bloodline, though\ldots It's hard to love one another, when we will one day contend with each other.
Love cannot exist without trust."
He smiled at his ruk.
"I trust Kadara with my life.
I would die for her, and she for me.
Can I say the same of my siblings?
My own parents?"

"It's a shame," Nesryn admitted.

"At least I have her," he said of the ruk.
"And my riders.
Pity my siblings, who have none of those blessings."

He was a good man.
The prince\ldots he was a good man.

She strode for the open archways overlooking the deadly drop to the city far, far below.

"I am going to leave soon---for the mountains of the rukhin," Sartaq said softly.
"To seek the answers you and I discussed the other night in the city."

Nesryn peered over her shoulder at him, trying to gather the right words, the nerve.

His face remained neutral, even as he added, "I'm sure your family will have my head for offering, but\ldots would you like to accompany me?"

\emph{Yes}, she wanted to breathe.
But she made herself ask, "For how long?"

For time was not on her side.
Their side.
And to hunt for answers while so many threats gathered close 

"A few weeks.
No more than three.
I like to keep the riders in line, and if I go absent for too long, they pull at the leash.
So the journey will serve two purposes, I suppose."

"I---I would need to discuss.
With Lord Westfall."
She'd promised him as much last night.
That they'd consider this precise path, weighing the pitfalls and benefits.
They were still a team in that regard, still served under the same banner.

Sartaq nodded solemnly, as if he could read everything on her face.
"Of course.
Though I leave soon."

She then heard it---the grunt of servants coming up the aerie stairs.
Bringing supplies.

"You leave \emph{now}," Nesryn clarified as she noted the spear leaning against the far wall near the supply racks.
His \emph{sulde}.
The russet horsehair tied beneath the blade drifted in the wind weaving through the aerie, the dark wood shaft polished and smooth.

Sartaq's onyx eyes seemed to darken further as he strode to his \emph{sulde}, weighing the spirit-banner in his hands before resting it beside him, the wood thunking on the stone floor.
"I \ldots" It was the first she'd seen him stumble for words.

"You weren't going to say good-bye?"

She had no right to make such demands, expect such things, tentative allies or no.

But Sartaq leaned his \emph{sulde} against the wall again and began braiding back his black hair.
"After last night's party, I had thought you would be\ldots preoccupied."

With Chaol.
Her brows rose.
"All day?"

The prince gave her a roguish smile, finishing off his long braid and picking up his spear once more.
"I certainly would take all day."

By some god's mercy, Nesryn was saved from replying by the servants who appeared, panting and red-faced with the packs between them.
Weapons glinted from some of them, along with food and blankets.

"How far is it?"

"A few hours before nightfall, then all day tomorrow, then another half day of travel to reach the first of the aeries in the Tavan Mountains," Sartaq said as he handed his \emph{sulde} to a passing servant, and Kadara patiently allowed them to load her with various packs.

"You don't fly at night?"

"I tire.
Kadara doesn't.
Foolish riders have made that mistake---and tumbled through the clouds in their dreams."

She bit her lip.
"How long until you go?"

"An hour."

An hour to think 

She had not told Chaol.
That she'd seen his toes move last night.
She'd seen them curl and flex in his sleep.

She had cried, silent tears of joy sliding onto the pillow.
She hadn't told him.

And when he'd awoken 

\emph{Let's have an adventure,} \emph{Nesryn} \emph{Faliq}, he'd promised her in Rifthold.
She had cried then, too.

But perhaps\ldots perhaps neither of them had seen.
The path ahead.
The forks in it.

She could see down one path clearly.

Honor and loyalty, still unbroken.
Even if it stifled him.
Stifled her.
And she\ldots she did not want to be a consolation prize.
Be pitied or a distraction.

But this other path, the fork that had appeared, branching away across grasslands and jungles and rivers and mountains\ldots This path toward answers that might help them, might mean nothing, might change the course of this war, all carried on a ruk's golden wings 

She would have an adventure.
For herself.
This one time.
She would see her homeland, and smell it and breathe it in.
See it from high above, see it racing as fast as the wind.

She owed herself that much.
And owed it to Chaol as well.

Perhaps she and this dark-eyed prince might find some scrap of salvation against Morath.
And perhaps she might bring an army back with her.

Sartaq was still watching, his face carefully neutral as the last of the servants bowed and vanished.
His \emph{sulde} had been strapped just below the saddle, within easy reach should the prince need it, its reddish horsehairs trailing in the wind.
Trailing southward.

Toward that distant, wild land of the Tavan Mountains.
Beckoning, as all spirit-banners did, toward an unknown horizon.
Beckoning to claim whatever waited there.

Nesryn said quietly, "Yes."
The prince blinked.

"I will go with you," she clarified.

A small smile tugged on his mouth.
"Good."
Sartaq jerked his chin to the archway through which the servants had vanished down the minaret.
"Pack lightly, though---Kadara is already near her limit."

Nesryn shook her head, noting the bow and quiver stocked with arrows already atop Kadara.
"I have nothing to bring with me."

Sartaq watched her for a long moment.
"Surely you would wish to say goodbye---"

"I have nothing," she repeated.
His eyes flickered at that, but she added, "I--- I'll leave a note."

The prince solemnly nodded.
"I can outfit you with clothes when we arrive.
There is paper and ink in the cabinet by the far wall.
Leave the letter in the box by the stairs, and one of the messengers will come to check at nightfall."

Her hands shook slightly as she obeyed.
Not with fear, but 
freedom.

She wrote two notes.
The first one, to her aunt and uncle, was full of love and warning and well-wishes.
Her second note\ldots it was quick, and to the point:

\emph{I have gone with Sartaq to see the rukhin.
I shall be gone three weeks.} \emph{I hold you to no promises.
And I will hold to none of my own.}

Nesryn shut both notes in the box, undoubtedly checked often for any messages from the skies, and changed into the leathers she'd left from the last time she'd flown.

She found Sartaq atop Kadara, waiting for her.

The prince extended a callused hand to help her up into the saddle.

She didn't hesitate as she took his hand, his strong fingers wrapping around hers, and let him pull her into the saddle before him.

He strapped and buckled them in, checked all of it thrice.
But he reined in Kadara when she would have soared out of the minaret.

Sartaq whispered in Nesryn's ear, "I was praying to the Eternal Sky and all thirty-six gods that you'd say yes."

She smiled, even if he couldn't see it.

"So was I," Nesryn breathed, and they leaped into the skies.

