
\chapter{27}

Yrene healed six people by the time the sun set, and only then did she leave the slums.

One woman had a dangerous growth on her lungs that would have killed her.
She'd been too busy with work to see a healer or physician.
Three children had been burning up with fever in a too-cramped house, their mother weeping with panic.
And then with gratitude as Yrene's magic soothed and settled and purified.
One man had broken his leg the week before and visited a piss-poor physician in the slums because he could not afford a carriage to carry him up to the Torre.
And the sixth one 
The girl was no more than sixteen.
Yrene had noticed her first because of the black eye.
Then the cut lip.

Her magic had been wobbling, her knees with it, but Yrene had led the girl into a doorway and healed her eye.
The lip.
The cracked ribs.
Healed the enormous handprint-shaped bruises on her forearm.

Yrene asked no questions.
She read every answer in the girl's fearful eyes anyway.
Saw the girl consider whether it would land her with worse injuries to return home healed.

So Yrene had left the coloring.
Left the appearance of bruises but healed all beneath.
Leaving only the upper layer of skin, perhaps a little tender, to conceal the repaired damage.

Yrene did not try to tell her to leave.
Whether it was her family or a lover or something else entirely, Yrene knew that no one but the girl would decide whether to walk out that door.
All she did was inform her that should she ever need it, the door to the Torre would always be open.
No questions asked.
No fee demanded.
And they would make sure that no one was allowed to take her out again unless she wished it.

The girl had kissed Yrene's knuckles in thanks and scurried home in the falling dark.

Yrene herself had hurried, following the glimmering pillar of the Torre, her beacon home.

Her stomach was grumbling, her head throbbing with fatigue and hunger.

Drained.
It felt good to be drained.
To help.

And yet\ldots That hounding, restless energy still thrummed.
Still pushed.
\emph{More more more.}

She knew why.
What was left unsettled.
Still raging.

So she changed course, spearing for the glowing mass of the palace.

She paused at a favorite food stall, indulging in a meal of slow-roasted lamb that she devoured in a few minutes.
It was rare that she got to eat beyond the confines of the palace or the Torre, thanks to her busy schedule, but when she did\ldots Yrene was rubbing her satisfied belly as she made her way up to the palace.
But then spotted an open \emph{kahve} shop and managed to find room in her stomach for a cup of it.
And a honey-dipped pastry.

Dawdling.
Restless and angry and stupid.

Disgusted with herself, Yrene stomped up to the palace at last.
With the summer sun setting so late, it was well past eleven by the time she headed through the dark halls.

Perhaps he'd be asleep.
Maybe it would be a blessing.
She didn't know why she'd bothered to come.
Biting off his head could have waited until tomorrow.

He was likely asleep.

Hopefully asleep.
It'd probably be better if his healer didn't barge into his room and shake him silly.
It definitely wasn't behavior approved by the Torre.
By Hafiza.

And yet she kept walking, her pace increasing, steps near-clomping on the marble floors.
If he wanted to take a step back on their progress, that was just fine.
But she certainly didn't have to let him do it---not without trying.

Yrene stormed down a long, dim corridor.
She wasn't a coward; she wouldn't back down from this fight.
She'd left that girl in that alley in Innish.
And if he was inclined to sulk about Nesryn, then he was entitled to do so.
But to call off their \emph{session} because of it--- Unacceptable.

She'd simply tell him that and leave.
Calmly.
Rationally.

Yrene scowled with each step, muttering the word under her breath.
\emph{Unacceptable.}

And she had \emph{let} him kick her out, no matter what she might have tried to tell herself.

That was even \emph{more} unacceptable.

\emph{Stupid fool}.
She muttered that, too.

Loud enough that she nearly missed the sound.

The footstep---the scrape of shoes on stone---just behind her.

This late, servants were likely heading back to their masters' rooms, but--- There it was.
That sense, pricking again.

Only shadows and shafts of moonlight filled the pillar-lined hallway.

Yrene hurried her pace.

She heard it again---the steps behind.
A casual, stalking gait.

Her mouth went dry, her heart thundering.
She had no satchel, not even her little knife.
Nothing in her pockets beyond that note.

\emph{Hurry}, a small, gentle voice murmured in her ear.
In her \emph{head}.

She had never heard that voice before, but she sometimes felt its warmth.
Coursing through her as her magic flowed out.
It was as familiar to her as her own voice, her own heartbeat.

\emph{Hurry, girl.}

Urgency laced each word.

Yrene increased her pace, nearing a run.

There was a corner ahead---she need only round it, make it thirty feet down that hall, and she'd be at his suite.

Was there a lock on the door?
Would it be locked against her---or be able to keep whoever it was out?

\emph{Run, Yrene!}

And that voice 

It was her mother's voice that bellowed in her head, her heart.

She didn't stop to think.
To wonder.

Yrene launched into a sprint.

Her shoes slipped along the marble, and the person, the \emph{thing}
behind her--- those footsteps broke into a run, too.

Yrene turned the corner and slid, skidding into the opposite wall so hard her shoulder barked in pain.
Feet scrambling, she fought to regain momentum, not daring to look back--- \emph{Faster!}

Yrene could see his door.
Could see the light leaking out from beneath it.

A sob broke from her throat.

Those rushing steps behind her closed in.
She didn't dare risk her balance by looking.

Twenty feet.
Ten.
Five.

Yrene hurled for the handle, gripping it with all her strength to keep from sliding past as she shoved against it.

The door opened, and she whirled in, legs slipping beneath her as she slammed her entire body into the door and fumbled for the lock.
There were two.

She finished the first when the person on the other side barreled into the door.

The entire thing shuddered.

Her fingers shook, her breath escaping in sharp sobs as she fought for the second, heavier lock.

She flipped it closed just as the door buckled again.

"What in \emph{hell}---"

"Get inside your room," she breathed to Chaol, not daring to take her eyes off the door as it shuddered.
As the handle rattled.
"Get in---\emph{now}."

Yrene looked then to find him in the threshold of his bedroom, sword in his hand.
Eyes on the door.

"Who the hell is that."

"Get inside," she said, her voice breaking.
"\emph{Please.}" He read the terror in her face.
Read and understood.

He shoved back into the room, holding the door for her and then sealing it behind her.

The front door cracked.
Chaol locked his bedroom door with a click.
Only one lock.

"The chest," he said, his voice unfaltering.
"Can you move it?"

Yrene whirled to the chest of drawers beside the door.
She didn't reply as she threw herself against it, shoes again slipping on the polished marble---

She kicked off her shoes, bare skin finding better grip on the stone as she heaved and grunted and shoved---

The chest slid in front of the bedroom door.

"The garden doors," Chaol ordered, finishing locking them.

They were solid glass.

Dread and panic curled in her gut, ripping the breath from her throat.

"Yrene," Chaol said evenly.
Calmly.
He held her gaze.
Steadying her.
"How far is the nearest entrance to the garden from the outer hall?"

"A two-minute walk," she replied automatically.
It was only accessible from the interior rooms, and as most of these were occupied 
They'd have to take the hall to the very end.
Or risk running through the bedrooms next door, which\ldots "Or one."

"Make it count."

She scanned the bedroom for anything.
There was an armoire beside the glass doors, towering high above.
Too high, too enormously heavy---

But the movable screen to the bathroom 

Yrene hurtled across the room, Chaol lunging for a set of daggers on his nightstand.

She grabbed the heavy wooden screen and hauled and shoved it, cursing as it snagged on the rug.
But it moved---it got there.
She flung open the armoire doors and wedged the screen between it and the wall, shaking it a few times for good measure.
It held.

She rushed to the desk, throwing books and vases off it.
They shattered across the floor.

\emph{Stay calm; stay focused.}

Yrene hauled the desk to the wood screen and flipped it onto its side with a clattering crash.
She shoved it against the barricade she'd made.

But the window---

There was one across the room.
High and small, but---

"Leave it," Chaol ordered, sliding into place in front of the glass doors.
Sword angled and dagger in his other hand.
"If they try that route, the small size will force them to be slow."

Long enough for him to kill it---whoever it was.

"Get over here," he said quietly.

She did so, eyes darting between the bedroom door and the garden doors.

"Deep breaths," he told her.
"Center yourself.
Fear will get you killed as easily as a weapon."
Yrene obeyed.

"Take the dagger on the bed."

Yrene balked at the weapon.

"Do it."

She grabbed the dagger, the metal cool and heavy in her hand.
Unwieldy.

His breathing was steady.
His focus unrelenting as he monitored both doors.

The window.

"The bathroom," she whispered.

"The windows are too high and narrow."

"What if it's not in a human body?"

The words ripped from her in a hoarse whisper.
The illustrations she'd seen in that book---

"Then I'll keep it occupied while you run."

With the furniture in front of the exits--- His words sank in.

"You will do no such---"

The bedroom door shuddered beneath a blow.
Then another.

The handle shook and shook.

Oh, gods.

They hadn't bothered with the garden.
They'd simply gotten in the front doors.

Another bang that had her flinching away.
Another.

"Steady," Chaol murmured.

Yrene's dagger trembled as he angled himself to the bedroom door, his blades unwavering.

Another bang, furious and raging.

Then---a voice.

Soft and hissing, neither male nor female.

"Yrene," it whispered through the crack in the door.
She could hear the smile in its voice.
"Yrene."

Her blood went cold.
It was not a human voice.

"What is it you want," Chaol said, his own voice like steel.

\emph{"Yrene."}

Her knees buckled so wildly she could barely stand.
Every moment of training she'd done slithered right out of her head.

"\emph{Get out}," Chaol snarled toward the door.
"Before you regret it."

"Yrene," it hissed, laughing a bit.
"\emph{Yrene.}"

Valg.
One had indeed been hunting her that night, and had come for her again tonight---

Clapping her free hand over her mouth, Yrene sank onto the edge of the bed.

"Don't you waste one heartbeat being afraid of a coward who hunts women in the darkness," Chaol snapped at her.

The thing on the other side of the door growled.
The doorknob rattled.

"Yrene," it repeated.

Chaol only held her stare.
"Your fear grants it power over you."

\emph{"Yrene."}

He approached her, lowering his dagger and sword into his lap.
Yrene flinched, about to warn him not to lower his weapons.
But Chaol stopped before her.
Took her face in his hands, his back wholly to the door now.
Even though she knew he monitored every sound and movement behind it.
"I am not afraid," he said softly, but not weakly.
"And neither should you be."

"\emph{Yrene}," the thing snapped on the other side of the door, slamming into it.
She cringed away, but Chaol held her face tightly.
Did not break her gaze.

"We will face this," he said.
"Together."
Together.
Live or die here---together.

Her breathing calmed, their faces so close his own breath brushed her mouth.

Together.

She hadn't thought to use such a word, to \emph{feel} what it meant  She hadn't felt it since--- Together.

Yrene nodded.
Once.
Twice.

Chaol searched her eyes, his breath fanning her mouth.

He lifted her hand, still clutched around the dagger, and adjusted her grip.

"Angle it up, not straight in.
You know where it is."
He put a hand on his chest.
Over his heart.
"The other places."

Brain.
Through the eye socket.
Throat, slashing to unleash the life's blood.

All the various arteries that could be struck to ensure a swift bleed-out.

Things she had learned to save.
Not---end.

But this thing 

"Beheading works best, but try to get it down first.
Long enough to sever the head."

He'd done this before, she realized.
He'd killed these things.
Triumphed against them.
Had taken them on with no magic but his own indomitable will and courage.

And she\ldots she had crossed mountains and seas.
She had done it on her own.

Her hand stopped shaking.
Her breathing evened out.

Chaol's fingers squeezed around her own, the hilt's fine metal pushing into the palm of her hand.
"Together," he said one last time, and released her to pluck up his own weapons again.

To face the door.

There was only silence.

He waited, calculating.
Sensing.
A predator poised to strike.

Yrene's dagger held steady as she rose to her feet behind him.

A crash sounded through the foyer---followed by shouting.

She started, but Chaol loosed a breath.
One of shuddering relief.

He recognized the sounds before she did.

The shouts of guards.

They spoke in Halha---cries through the bedroom door about their status.

Safe?
Hurt?

Yrene replied in her own shoddy use of the language that they were unharmed.
The guards said the servant girl had seen the broken suite door and come running to fetch them.

There was no one else in the suite.

