
\chapter{3}

Nesryn had gone into shock.

And Chaol could not go to her, could not scoop her into his arms and hold her close.

Not when she had walked, silent and drifting like a wraith, right into a bedroom of the lavish suite they'd been appointed on the first floor of the palace, and shut the door behind her.
As if she had forgotten anyone else in the world existed.

He didn't blame her.

Chaol let the servant, a fine-boned young woman with chestnut hair that fell in heavy curls to her narrow waist, wheel him into the second bedroom.
The suite overlooked a garden of fruit trees and burbling fountains, cascades of pink and purple blossoms hanging from potted plants anchored into the balcony above.
They provided living curtains before his towering bedroom windows--- doors, he realized.

The servant mumbled something about drawing a bath, her use of his language unwieldy compared to the skill of the khagan and his children.
Not that he was in any position to judge: he was barely fluent in any of the other languages within his own continent.

She slipped behind a carved wooden screen that no doubt led into his bathing chamber, and Chaol peered through his still-open bedroom door, across the pale marble foyer, to the shut doors of Nesryn's bedroom.

They should not have left.

He couldn't have done anything, but\ldots He knew what the not-knowing would do to Nesryn.
What it was already doing to him.

Dorian was not dead, he told himself.
He had gotten out.
Fled.
If he were in Perrington's grip---Erawan's grip---they would have known.
Prince Arghun would have known.

His city, sacked by the witches.
He wondered if Manon Blackbeak had led the attack.

Chaol tried and failed to recount where the debts were stacked between them.
Aelin had spared Manon's life at Temis's temple, but Manon had given them vital information about Dorian under the Valg thrall.
Did it make them even?
Or tentative allies?

It was a waste to hope that Manon would turn against Morath.
But he sent up a silent prayer to whatever god might be listening to protect Dorian, to guide his king to friendlier harbors.

Dorian would make it.
He was too clever, too gifted, not to.
There was no other alternative---none---that Chaol would accept.
Dorian was alive, and safe.
Or on his way to safety.
And when Chaol got a moment, he was going to squeeze the information out of the eldest prince.
Mourning or no.
Everything Arghun knew, \emph{he} would know.
And then he'd ask that servant girl to comb every merchant ship for information about the attack.

No word---there had been no word about Aelin.
Where she was now, what she'd been doing.
Aelin, who might very well be the thing that cost him this alliance.

He ground his teeth, and was still grinding them as the suite doors opened and a tall, broad-shouldered man strode in as if he owned the place.

Chaol supposed he did.
Prince Kashin was alone and unarmed, though he moved with the ease of a person confident in his body's unfailing strength.

How, Chaol supposed, he himself had once walked about the palace in Rifthold.

Chaol lowered his head in greeting as the prince shut the hall door and surveyed him.
It was a warrior's assessment, frank and thorough.
When his brown eyes at last met Chaol's, the prince said in Adarlan's tongue, "Injuries like yours are not uncommon here, and I have seen many of them---especially among the horse-tribes.
My family's people."

Chaol didn't particularly feel like discussing his injuries with the prince, with anyone, so he only nodded.
"I'm sure you have."

Kashin cocked his head, scanning Chaol again, his dark braid slipping over his muscled shoulder.
Reading, perhaps, Chaol's desire not to start down this particular road.
"My father indeed wishes you both to join us at dinner.
And more than that, to join us every night afterward while you are here.
And sit at the high table."

It wasn't a strange request of a visiting dignitary, and it was certainly an honor to sit at the khagan's own table, but to send his son to do it\ldots Chaol considered his next words carefully, then simply chose the most obvious one.
"Why?"

Surely the family wished to keep close to one another after losing their youngest member.
Inviting strangers to join them---

The prince's jaw tightened.
Not a man used to veiling his emotions, as his three elder siblings were.
"Arghun reports our palace is safe of spies from Duke Perrington's forces, that his agents have not yet come.
I am not of that belief.
And Sartaq---" The prince caught himself, as if not wanting to bring in his brother---or potential ally.
Kashin grimaced.
"There was a reason I chose to live amongst soldiers.
The double-talk of this court\ldots"

Chaol was tempted to say he understood.
Had felt that way for most of his life.
But he asked, "You think Perrington's forces have infiltrated this court?"

How much did Kashin, or Arghun, know of Perrington's forces---know the truth of the Valg king who wore Perrington's skin?
Or the armies he commanded, worse than any their imaginations might conjure?
But that information\ldots He'd keep that to himself.
See if it could somehow be used, if Arghun and the khagan did not know of it.

Kashin rubbed at his neck.
"I do not know if it is Perrington, or someone from Terrasen, or Melisande, or Wendlyn.
All I know is that my sister is now dead."

Chaol's heart stumbled a beat.
But he dared ask, "How did it come about?"

Grief flickered in Kashin's eyes.
"Tumelun was always a bit wild, reckless.
Prone to moods.
One day, happy and laughing; the next, withdrawn and hopeless.
They\ldots" His throat bobbed.
"They say she leaped from her balcony because of it.
Duva and her husband found her later that night."

Any death in a family was devastating, but a suicide\ldots "I'm sorry," Chaol offered quietly.

Kashin shook his head, sunlight from the garden dancing on his black hair.
"I do not believe it.
My Tumelun would not have jumped."

\emph{My Tumelun.} The words told enough about the prince's closeness to his younger sister.

"You suspect foul play?"

"All I know is that no matter Tumelun's moods\ldots I knew her.
As I know my own heart."
He put a hand over it.
"She would not have jumped."

Chaol considered his words carefully once again.
"As sorry as I am for your loss, do you have any reason to suspect why a foreign kingdom might have engineered it?"

Kashin paced a few steps.
"No one within \emph{our} lands would be stupid enough."

"Well, no one within Terrasen or Adarlan would ever do such a thing---even to manipulate you into this war."

Kashin studied him for a heartbeat.
"Even a queen who was once an assassin herself?"

Chaol didn't let one flicker of emotion show.
"Assassin she might have been, but Aelin had hard lines that she did not cross.
Killing or harming children was one of them."

Kashin paused before the dresser against the garden wall, adjusting a gilded box on its polished dark surface.
"I know.
I read that in my brother's reports, too.
Details of her kills."
Chaol could have sworn the prince shuddered before he added, "I believe you."

No doubt why the prince was even having this conversation with him.

Kashin went on, "Which leaves not many other foreign powers who might do it---and Perrington at the top of that short list."

"But why target your sister?"

"I do not know."
Kashin paced another few steps.
"She was young, guileless ---she rode with me amongst the Darghan, our mother-clans.
Had no \emph{sulde} of her own yet."

At Chaol's narrowed brows, the prince clarified, "It is a spear all Darghan warriors carry.
We bind strands of our favored horse's hair to the shaft, beneath the blade.
Our ancestors believed that where those hairs waved in the wind, there our destinies waited.
Some of us still believe in such things, but even those who think it mere tradition\ldots we bring them everywhere.
There is a courtyard in this palace where my \emph{sulde} and those of my siblings are planted to feel the wind while we remain at our father's palace, right beside his own.
But in death\ldots" Again, that shadow of grief.
"In death, they are the only object that we keep.
They bear the soul of a Darghan warrior for eternity, and are left planted atop a steppe in our sacred realm."
The prince closed his eyes.
"Now her soul will roam with the wind."

Nesryn had said as much earlier.
Chaol only repeated, "I'm sorry."

Kashin opened his eyes.
"Some of my siblings do not believe me about Tumelun.
Some do.
Our father\ldots he remains undecided.
Our mother will not even leave her room thanks to her grief, and mentioning my suspicions might---I cannot bring myself to mention them to her."
He rubbed his strong jaw.
"So I have convinced my father to have you join us at dinner every night, as a gesture of diplomacy.
But I should like you to watch with an outsider's eyes.
To report on anything amiss.
Perhaps you will see something we don't."

Help them\ldots and perhaps receive help in return.
Chaol said baldly, "If you trust me enough to have me do that, to tell me all this, then why not agree to join with us in this war?"

"It is not my place to say or guess."
A trained soldier.
Kashin examined the suite as if assessing any potential enemies lying in wait.
"I march only when my father gives the order."

If Perrington's forces were already here, if Morath was indeed behind the princess's murder\ldots It'd be too easy.
Too easy to sway the khagan into siding with Dorian and Aelin.
Perrington---Erawan was far smarter than that.

But if Chaol himself were to win over the commander of the khagan's terrestrial armies to their cause---

"I do not play those games, Lord Westfall," said Kashin, reading whatever sparked in Chaol's eyes.
"My other siblings are the ones you will wish to convince."

Chaol tapped a finger on the arm of his chair.
"Any advice on that front?"

Kashin snorted, smiling faintly.
"Others have come before you---from kingdoms far richer than your own.
Some succeeded, some didn't."
A glance at Chaol's legs, a flicker of pity entering the prince's eyes.
Chaol clenched the arms of the chair at that pity, from a man who recognized a fellow warrior.
"Wishes for good luck are all I can offer you."

Then the prince was striding for the doors, his long legs eating up the distance.

"If Perrington has an agent here," Chaol said as Kashin reached the suite doors, "then you've already seen that everyone in this palace is in grave danger.

You must take action."

Kashin paused with his hand on the carved doorknob, glancing over his shoulder.
"Why do you think I've asked a foreign lord for assistance?"

Then the prince was gone, his words hanging in the sweet-scented air.
The tone wasn't cruel, wasn't insulting, but the warrior's frankness of it 

Chaol struggled to master his breathing, even as the thoughts swirled.
He'd seen no black rings or collars, but then he hadn't been looking for them.
Had not even considered that the shadow of Morath might have already stretched this far.

Chaol rubbed at his chest.
Careful.
He'd have to be careful in this court.
With what he said publicly---with what he said in this room, too.

Chaol was still staring at the shut door, mulling over all Kashin had implied, when the servant emerged, her tunic and pants replaced by a tied robe of thinnest, sheerest silk.
It left nothing to the imagination.

He clamped down on the urge to shout for Nesryn to assist him instead.
"Only wash me," he said, as clearly and firmly as he could.

She showed no nerves, no tremor of hesitation.
And he knew she had done this before, countless times, as she only asked, "Am I not to your liking?"

It was a stark, honest question.
She was paid well for her services---all the servants were.
She chose to be here, and another could easily be found at no risk to her status.

"You are," Chaol said, only half lying, refusing to let his gaze drop below her eyes.
"Very pleasing," he clarified.
"But I only want a bath."
He added, just to be sure, "Nothing else from you."

He'd expected her gratitude, but the servant only nodded, unruffled.
Even with her, he'd have to be careful with what he said.
What he and Nesryn might discuss in these rooms.

There hadn't been a sound or flicker of movement behind Nesryn's closed bedroom doors.
And there certainly wasn't now.

So he motioned to let the servant push his chair into the bathing chamber, veils of steam rippling through the white-and-blue-tiled room.

The chair glided over carpet and tile, curving around the furniture with little effort.
Nesryn herself had found the chair in the now-vacant healers' catacombs of Rifthold's castle, right before they'd sailed here.
One of the few items the fleeing healers had left behind, it seemed.

Lighter and sleeker than what he'd expected, the large wheels flanking the seat rotated easily, even when he used the slender metal hand rim to guide them himself.
Unlike the stiff bulk of others he'd seen, this chair came equipped with two small front wheels, just on either side of the wooden footrests, each capable of swiveling in any direction he chose.
And now they smoothly turned into the wafting steam of the bathing chamber.

A large sunken pool filled most of it, oils gleaming on the surface, interrupted only by scattered, drifting petals.
A small window high in the far wall peeked into the greenery of the garden, and candles gilded the billowing steam.

Luxury.
Utter luxury while his city suffered.
While they pleaded for help that had not come.
Dorian would have wanted to stay.
Only absolute defeat, no chance of survival, would have prompted him to leave.
Chaol wondered if his magic had played any part.
Helped any of them.

Dorian would find his way to safety, to allies.
He knew it in his bones, though his stomach continued to roil.
There was nothing he could do to help his king from here---save for forging this alliance.
Even if every instinct screamed at him to return to Adarlan, to find Dorian, he'd stay the course.

Chaol barely noticed the servant removing his boots in efficient tugs.
And though he could have done it himself, he barely remarked on her removing his teal jacket, then the shirt beneath.
But he dragged himself from his thoughts at last when she began to remove his pants---when he leaned in to help, gritting his teeth as they worked together in stilted silence.
It was only when she reached to remove his undershorts that he gripped her wrist.

He and Nesryn still hadn't touched each other.
Beyond an ill-fated bout on the ship three days ago, he hadn't conveyed any sort of desire to take that step once again.
He'd wanted to, though.
Woke up most mornings aching to, especially when they'd shared that bed in their stateroom.
But the thought of being so prone, of not being able to take her the way he'd once done\ldots It had curdled any brimming lust.
Even while grateful that certain parts of him still undoubtedly worked.

"I can get in on my own," Chaol said, and before the servant could move, he gathered the strength in his arms, his back, and began easing himself from the chair.
It was an unceremonious process, one he'd figured out during the long days at sea.

First he flicked the locking mechanism on the wheels, the click echoing off the stone and water.
With a few motions, he maneuvered himself to the edge of the chair, then removed his feet from the wooden plates and onto the floor, angling his legs to his left as he did so.
With his right hand, he gripped the edge of the seat by his knees, while he curled the left into a fist as he bent over to brace it on the cool, steam-slick tiles.
Slippery---

The servant only padded over, laid a thick white cloth before him, and backed away.
He gave her a grateful, close-lipped smile as he braced his left fist again on the floor, atop the plush cloth, distributing his weight throughout the arm.
With an inhaled breath, his right hand still gripping the edge of his chair, he carefully lowered himself to the ground, swinging his rear away from the chair as his knees bent unbidden.

He landed with a thud, but he was on the floor, at least---hadn't toppled over, as he had the first half-dozen times he'd tried it on the ship.

Carefully, he scooted to the edge of the pool stairs, until he could set his feet into the warm water, right atop the second step.
The servant strode into the water a heartbeat later, graceful as an egret, her gossamer robe turning as insubstantial as dew while water crept up its length.
Her hands were gentle but steady while she gripped him under the arm and helped him hoist himself the last bit into the pool, setting himself down on the top step.
Then she guided him down another and another, until he was sitting up to his shoulders.
Eye-level with her full, peaked breasts.

She didn't seem to notice.
And he immediately averted his gaze toward the window as she reached for the small tray of supplies she'd left near the lip of the pool.
Oils and brushes and soft-looking cloths.
Chaol slid his undershorts off while she turned, setting them with a loud, wet smack upon the edge of the pool.

Nesryn still didn't emerge from her room.

So Chaol closed his eyes, submitting himself to the servant's ministrations, and wondered what the hell he was going to do.

