
\chapter{33}

The Watchtower of Eidolon jutted up from the mist-shrouded pines like the shard of a broken sword. It had been situated atop a low-lying peak that overlooked a solid wall of gargantuan mountains, and as Nesryn and Sartaq swept near the tower, sailing along the tree-crusted hills, she had the sense of racing toward a tidal wave of hard stone.

For a heartbeat, a wave of lethal glass swept for her instead. She blinked, and it was gone.

"There," Sartaq whispered, as if fearful that any might hear while he pointed toward the enormous mountains lurking beyond. "Over that lip, that is the start of \emph{kharankui} territory, the Dagul Fells. Those in the watchtower would have been able to see anyone coming down from those mountains, especially with their Fae sight."

Fae sight or not, Nesryn scanned the barren slopes of the Fells---a wall of boulders and shards of rock. No trees, no streams. As if life had fled. "Houlun flew over \emph{that}?"

"Believe me," Sartaq grumbled, "I am not pleased. Borte got an earful about it this morning."

"I'm surprised your kneecaps still function."

"Didn't you notice my limp earlier?"

Despite the nearing watchtower, despite the wall of mountain that rose up beyond it, Nesryn chuckled. She could have sworn Sartaq leaned closer, his broad chest pushing into the quiver and bow she had strapped across her back, along with the twin long knives courtesy of Borte.

They hadn't told anyone where they were going or what they sought, which had earned no shortage of glares from Borte over breakfast, and curious glances from Falkan across the round table. But they had agreed last night, when Sartaq left Nesryn at her bedroom door, that secrecy was vital---for now.

So they'd departed an hour after dawn, armed and bearing a few packs of supplies. Even though they planned to be headed home well before sunset, Nesryn had insisted on bringing their gear. Should the worst happen, should \emph{anything} happen, it was better to be prepared.

Borte, despite her ire at being left in the dark, had braided Nesryn's hair after breakfast---a tight, elegant plait starting at the crown of her head and landing just where her cape fell to cover her flying leathers. The braid was tight enough that Nesryn had avoided the urge to loosen it these hours that they'd flown, but now that the tower was in sight and her hair had barely shifted, Nesryn supposed the braid could stay.

Kadara circled the watchtower twice, dropping lower with each pass.

"No signs of webs," Nesryn observed. The upper levels of the watchtower had been destroyed by weather or some long-ago passing army, leaving only two floors above the ground. Both were exposed to the elements, the winding stairwell in the center coated in pine needles and dirt. Broken beams and blocks of stone also littered it, but no indications of life. Or any sort of miraculously preserved library.

With Kadara's size, the ruk had to find a clearing nearby to land, since Sartaq didn't trust the watchtower walls to hold her. The bird leaped into the air as soon as they'd begun the climb up the small incline to the watchtower proper. She'd circle overhead until Sartaq whistled for her, apparently.

Another trick of the rukhin and the Darghan on the steppes: the whistling, along with their whistling arrows. They had long allowed both peoples to communicate in a way that few noticed or bothered to comprehend, passing messages through enemy territory or down army lines. The riders had trained the ruks to understand the whistles, too---to know a call for help from a warning to flee.

Nesryn prayed with each grueling step through the thick pine trees and granite boulders that they would only need the whistle to summon the bird. She was no great tracker, but Sartaq, it seemed, was deftly reading the signs around them.

A shake of the prince's head told Nesryn enough: no hint of a presence, arachnid or otherwise. She tried not to look too relieved. Despite the tall trees, the Fells were a solid, looming presence to her right, drawing the eye even as it repelled every instinct.

Blocks of stone greeted them first. Great, rectangular chunks, half buried in the pine needles and soil. The full weight of summer lay upon the land, yet the air was cool, the shade beneath the trees outright chilly.

"I don't blame them for abandoning it if it's this cold in the summer," Nesryn muttered. "Imagine it in winter."

Sartaq smiled but pressed a finger to his lips as they cleared the last of the trees. Blushing that he'd needed to remind her, Nesryn unslung her bow and nocked an arrow, letting it hang limply while they tipped back their heads to take in the tower.

It must have been enormous, thousands of years ago, if the ruins were enough to make her feel small. Any barracks or living quarters had long since tumbled away or rotted, but the stone archway into the tower itself remained intact, flanked by twin statues of some sort of weather-worn bird.

Sartaq approached, his long knife gleaming like quicksilver in the watery light as he studied the statues. "Ruks?" The question was a mere breath.

Nesryn squinted. "No---look at the face. The beak. They're 
owls." Tall, slender owls, their wings tucked in tight. The symbol of Silba, of the Torre.

Sartaq's throat bobbed. "Let's be swift. I don't think it's wise to linger."

Nesryn nodded, one eye behind them as they slipped through the open archway. It was a familiar position, the rearguard---in Rifthold's sewers, she'd often let Chaol stalk ahead while she covered behind, arrow aimed into the darkness at their backs. So her body acted on pure muscle memory while Sartaq took the first steps through the archway and she twisted back, arrow aimed at the pine forest, scanning the trees.

Nothing. Not a bird or rustle of wind through the pines.

She turned a heartbeat later, assessing efficiently, as she had always done, even before her training: marking exits, pitfalls, possible sanctuaries. But there wasn't much to note in the ruin.

The tower floor was well lit thanks to the vanished ceiling above, the crumbling staircase leading into the gray sky. Slits in the stone revealed where archers might have once positioned themselves---or watched from within the warmth of a tower on a freezing day. "Nothing up," Nesryn observed perhaps a bit uselessly, facing Sartaq just as he took a step toward an open archway leading down into a dark stairwell. She grabbed his elbow. "Don't." He gave her an incredulous look over his shoulder.

Nesryn kept her own face like stone. "Your \emph{ej} said these towers were laid with traps. Just because we have yet to see one does not mean they are not still here." She pointed with her arrow toward the open archway to the levels belowground. "We keep quiet, tread carefully. I go first."

To hell with being the rearguard, if he was prone to plunging into danger.

The prince's eyes flared, but she didn't let him object. "I faced some of the horrors of Morath this spring and summer. I know how to mark them---and where to strike."

Sartaq looked her over again. "You really should have been promoted."

Nesryn smiled, releasing his muscled bicep. Wincing as she realized the liberties she'd taken by grabbing him, touching a prince without permission--- "Two captains, remember?" he said, noting the cringe she failed to hide.

Indeed. Nesryn inclined her head and stepped in front of him---and into the archway of the stairs leading below.

Her arm strained as she pulled the bowstring taut, scanning the darkness immediately beyond the stairwell entrance. When nothing leaped out, she slackened the bow, placed her arrow back in the quiver, and plucked up a handful of rocks from the ground, shards and chips from the felled blocks of stone around them.

A step behind, Sartaq did the same, filling his pockets with them.

Listening carefully, Nesryn rolled one of the rocks down the spiral stairs, letting it bounce and crack and---

A faint \emph{click}, and Nesryn hurled herself back, slamming into Sartaq and sending them both sprawling to the ground. A thud sounded within the stairwell below, then another.

In the quiet that followed, her heavy breathing the only sound, she listened again. "Hidden bolts," she observed, wincing as she found Sartaq's face mere inches away. His eyes were upon the stairwell, even as he kept a hand on her back, the other angling his long knife toward the archway.

"Seems I owe you my life, Captain," Sartaq said, and Nesryn quickly peeled back, offering a hand to help him rise. He clasped it, his hand warm around hers as she hauled him to his feet.

"Don't worry," Nesryn said drily. "I won't tell Borte." She plucked up another handful of rocks and sent them rolling and scattering down the gloom of the stairs. A few more clicks and thumps---then silence.

"We go slow," she said, all amusement fading, and didn't wait for his nod as she prodded the first step down with the tip of her bow.

She tapped and pushed along the stair, watching the walls, the ceiling. Nothing. She did it to the second, third, and fourth steps---as far as her bow could reach. And only when she was satisfied that no surprises waited did she allow them to step onto the stairs.

Nesryn repeated it with the next four steps, finding nothing. But when they reached the first turn of the spiral stairs \ldots"I \emph{really}
owe you my life," Sartaq breathed as they beheld what had been fired from a slit in the wall at the ninth step.

Barbed iron spikes. Designed to slam into flesh and stay there---unless the victim wanted to rip out more of their skin or organs on the curved, vicious hooks on the way out.

The spike had been fired so hard that it had sunk deep into the mortar between the stones. "Remember that these traps were not for human assailants," she breathed.

But for spiders as large as horses. Who could speak, and plan, and remember.

She tapped the steps ahead, the wood of her bow a hollow echo through the dark chamber, prodding the slit where the bolt had been fired. "The Fae must have memorized what stairs to avoid while living here," she observed as they cleared another few feet. "I don't think they were stupid enough to do an easy pattern, though."

Indeed, the next bolt had emerged three steps down. The one after that, five apart. But after that  Sartaq reached into his pocket and pulled out another handful of stones. They both squatted as he rolled a few down the stairs.

\emph{Click}.

Nesryn was so focused on the wall ahead that she didn't consider where the click had come from. Not in front, but below.

One heartbeat, she was crouched on a step.

The next, it had slid away beneath her feet, a black pit yawning open beneath

---

Strong hands wrapped around her shoulder, her collar, a blade clattering on stone---

Nesryn scrabbled for the lip of the nearest stair as Sartaq held her, grunting at

her weight, his long knife tumbling into the blackness beneath.

Metal hit metal. Bounced off it again and again, the clanking filling the stairwell.

Spikes. Likely a field of metal spikes---

Sartaq hauled her up, and her nails cracked on stone as she grappled for purchase on the smooth step. But then she was up, half sprawled on the stairs between Sartaq's legs, both of them panting as they peered to the gap beyond.

"I think we're even," Nesryn said, fighting and failing to master her shaking.

The prince clasped her shoulder, while his other hand brushed down the back of her head. A comforting, casual touch. "Whoever built this place had no mercy for the \emph{kharankui}."

It took her another minute to stop trembling. Sartaq patiently waited, stroking her hair, fingers rippling over the ridges of Borte's braid. She let him, leaned into the touch while she studied the gap they'd now have to jump, the stairs still beyond.

When she could at last stand without her knees clacking together, they carefully jumped the hole---and made it several more steps before another one appeared, this time accompanied by a bolt. But they kept going, the minutes dripping by, until they at last reached the level below.

Shafts of pale light shone from carefully hidden holes in the ground above, or perhaps through some mirror contraption in the passageways high above. She didn't care, so long as the light was bright enough to see by.

And see they did.

The bottom level was a dungeon.

Five cells lay open, the doors ripped off, prisoners and guards long gone. A rectangular stone table lay in the center.

"Anyone who thinks the Fae are prancing creatures given to poetry and singing needs a history lesson," Sartaq murmured as they lingered on the bottom step, not daring to touch the floor. "That stone table was not used for writing reports or dining."

Indeed, dark stains still marred the surface. But a worktable lay against the nearby wall, scattered with an assortment of weapons. Any papers had long ago melted away in the snow and rain, and any leather-bound books  also gone.

"Do we risk it, or leave?" Sartaq mused.

"We've come this far," Nesryn said. She squinted toward the far wall. "There ---there is some writing there." Near the floor, in dark lettering---a tangle of script.

The prince just reached into his pockets, casting more stones throughout the space. No clicks or groans answered. He chucked a few at the ceiling, at the walls. Nothing.

"Good enough for me," Nesryn said.

Sartaq nodded, though they both tested each block of stone with the tip of the bow or his fine, thin sword. They made it past the stone table, and Nesryn did not bother to examine the various instruments that had been discarded.

She'd seen Chaol's men hanging from the castle gates. Had seen the marks on their bodies.

Sartaq paused at the worktable, sorting through the weapons there. "Some of these are still sharp," he observed, and Nesryn approached as he pulled a long dagger from its sheath. The watery sunlight caught in the blade, dancing along the markings carved down the center.

Nesryn reached for a short-sword, the leather scabbard nearly crumbling beneath her hand. She brushed away the ancient dirt from the hilt, revealing shining dark metal inlaid with swirls of gold, the cross-guard curving slightly at its ends.

The scabbard was indeed so old that it fell apart as she lifted the sword, its weight light despite its size, the balance perfect. More markings had been engraved down the fuller of the blade. A name or a prayer, perhaps.

"Only Fae blades could remain this sharp after a thousand years," said Sartaq, setting down the knife he'd been inspecting. "Likely forged by the Fae smiths in Asterion, to the east of Doranelle---perhaps even before the first of the demon wars."

A prince who had studied not only his own empire's history, but that of many others.

History was certainly not her strongest subject, so she asked, "Asterion---like the horses?"

"One and the same. Great smiths and horse-breeders. Or so it once was--- before borders closed and the world darkened."

Nesryn studied the short-sword in her hand, the metal shining as if imbued with starlight, interrupted only by the carvings down the fuller. "I wonder what the markings say."

Sartaq examined another blade, shards of light bouncing over the planes of his handsome face. "Likely spells against enemies; perhaps even against the---" He halted at the word.

Nesryn nodded all the same. The Valg. "Half of me hopes we never have to find out." Leaving Sartaq to pick one for himself, she fastened the short-sword to her belt as she approached the far wall and the scribbled dark writing along the bottom.

She tested each block of stone on the floor, but found nothing.

At last, she peered at the script in flaking black letters. Not black, but--- "Blood," Sartaq said, coming up beside her, an Asterion knife now at his side.

No sign of a body, or any lingering effects of whoever had written it, perhaps while they lay dying.

"It's in the Fae tongue," Nesryn said. "I don't suppose your fancy tutors taught you the Old Language during your history lessons?" A shake of the head.

She sighed. "We should find a way to write it down. Unless your memory is the sort that---"

"It's not." He swore, turning toward the stairs. "I have some paper and ink in Kadara's saddlebags. I could---"

It wasn't his cut-off words that made her whirl. But the way he went utterly still.

Nesryn slid that Fae blade free from where she'd tied it.

"There is no need to translate it," said a light female voice in Halha. "It says, \emph{Look up}. Pity you didn't heed it."

Nesryn indeed looked up at what emerged from the stairwell, crawling along the ceiling toward them, and swallowed her scream.

