
\chapter{34}

It was worse than Nesryn had ever dreamed.

The \emph{kharankui} that slid from the ceiling and onto the floor was so much worse.

\emph{Bigger} than a horse.
Her skin was black and gray, mottled with splotches of white, her multiple eyes depthless pools of obsidian.
And despite her bulk, she was slender and sleek---more black widow than wolf spider.

"Those Fae morsels forgot to \emph{look up} when they built this place," the spider said, her voice so lovely despite her utter monstrosity.
Her long front legs clicked against the ancient stone.
"To remember who they laid these traps for."

Nesryn sized up the stairwell behind the spider, the light shafts, for any exits.
Found none.

And this watchtower had now become a veritable web.
Fool; utter fool for lingering---

The claws at the tops of the spider's legs scraped over the rock.

Nesryn sheathed her sword again.

"Good," the spider purred.
"Good that you know how useless that Fae rubbish will be."

Nesryn drew her bow, nocking an arrow.

The spider laughed.
"If Fae archers did not halt me long ago, human, you will not now."

Beside her, Sartaq's sword lifted a fraction.

Dying here, now, had not occurred to her at breakfast while Borte braided her hair.

But there was nothing to do as the spider advanced, fangs slipping from her jaws.

"When I am done with you, rider, I shall make your bird scream."
Drops of liquid plopped from those fangs.
Venom.

Then the spider lunged.

Nesryn fired an arrow, another aimed before her first found its mark.
But the spider moved so swiftly that the blow intended for an eye hit the hard shell of her abdomen, barely embedding.
The spider slammed into the stone torture table, as if she'd leap off to pounce on them---

Sartaq struck, a brutal slash toward the nearest clawed leg.

The spider shrieked, black blood spurting, and they hurtled for that distant doorway---

The \emph{kharankui} intercepted them first.
Slammed her legs between the wall and the stone table, blocking their path.
So close, the reek of death leaking from those fangs---

"Human filth," the spider spat, venom spraying onto the stones at their feet.

From the corner of her eye, Nesryn saw Sartaq fling an arm in her path, to shove her away, to leap in front of those deadly jaws--- She didn't know what happened at first.

What the blur of motion was, what made the \emph{kharankui} scream.

One heartbeat, she'd been ready to fight past Sartaq's self-sacrificing idiocy, the next\ldots the spider was crashing through the room, tumbling over and over.
Not Kadara, but something large, armed with claws and fangs--- A gray wolf.
As large as a pony, and utterly ferocious.

Sartaq wasted no time, and neither did Nesryn.
They sprinted for the archway and stairs beyond, not caring how many bolts or arrows shot from the walls as they outraced even the traps.
Tearing up the stairs, leaping the gaps between them, they did not stop at the crashing and screeching below--- A canine yelp sounded, then silence.

Nesryn and Sartaq hit the top of the stairs, running for the trees beyond the open doorway.
The prince had a hand on her back, shoving her along, both of them half turned toward the tower.

The spider exploded from the gloom, aiming not for the trees, but the upper stairs of the watchtower.
As if she'd climb up to ambush the wolf when it chased after her.

And exactly as she'd planned, the wolf flew from the stairwell, heading for the open archway to the woods, not even looking behind.

The spider leaped.
Gold flashed from the skies.

Kadara's war cry sent the pines trembling, her claws ripping right into the abdomen of the \emph{kharankui} and sending her toppling off the stairs.

The wolf darted away as Sartaq's roar of warning to his ruk was swallowed by the screaming of bird and spider.
The \emph{kharankui}
landed on her back, precisely where Kadara wanted her.

Leaving her underbelly exposed to the ruk's talons.
And her blade-sharp beak.

A few vicious slashes, black blood spraying and sleek limbs flailing, and--- silence.

Nesryn's bow dangled from her shaking hands as Kadara dismembered the twitching spider.
She whirled to Sartaq, but his eyes were turned away.
To the wolf.

She knew.
Right as the wolf limped toward them, a deep gash in its side, and she beheld its dark sapphire eyes.

Knew what it was, \emph{who} it was, as the edges of his gray coat shimmered, his entire body filling with light that shrank and flowed.

And when Falkan waved on his feet before them, a hand pressed to the bloody wound in his ribs, Nesryn breathed, "You're a shape-shifter."

