
\chapter{4}

Of all the rooms in the Torre Cesme, Yrene Towers loved this one best.

Perhaps it was because the room, located at the very pinnacle of the palestoned tower and its sprawling complex below, had unparalleled views of the sunset over Antica.

Perhaps it was because this was the place where she'd felt the first shred of safety in nearly ten years. The place she had first looked upon the ancient woman now sitting across the paper- and book-strewn desk, and heard the words that changed everything: \emph{You are welcome here, Yrene Towers}.

It had been over two years since then.

Two years of working here, living here, in this tower and in this city of so many peoples, so many foods and caches of knowledge.

It had been all she'd dreamed it would be---and she had seized every opportunity, every challenge, with both hands. Had studied and listened and practiced and saved lives, changed them, until she had climbed to the very top of her class. Until an unknown healer's daughter from Fenharrow was approached by healers old and young, who had trained their entire lives, for her advice and assistance.

The magic helped. Glorious, lovely magic that could make her breathless or so tired she couldn't get out of bed for days. Magic demanded a cost---to both healer and patient. But Yrene was willing to pay it. She had never minded the aftermath of a brutal healing.

If it meant saving a life\ldots Silba had granted her a gift---and a young stranger had given her another gift, that final night in Innish two years ago. Yrene had no plans to waste either.

She waited in silence as the slender woman across from her finished reading through some message on her chronically messy desk. Despite the servants' best efforts, the ancient rosewood desk was always chaotic, covered with formulas or spells or vials and jars brewing some tonic.

There were two such vials on the desk now, clear orbs atop silver feet fashioned after ibis legs. Being purified by the endless sunshine within the tower.

Hafiza, Healer on High of the Torre Cesme, plucked up one of the vials, swirled its pale blue contents, frowned, and set it down. "The damned thing always takes twice as long as I anticipate." She asked casually, using Yrene's own language, "Why do you think that is?"

Yrene leaned forward in the worn, tufted armchair on her side of the desk to study the tonic. Every meeting, every encounter with Hafiza, was a lesson---a chance to learn. To be challenged. Yrene lifted the vial from its stand, holding it to the golden light of sunset as she examined the thick azure liquid within. "Use?"

"Ten-year-old girl developed a dry cough six weeks ago. Saw the physicians, who advised honey tea, rest, and fresh air. Got better for a time, but returned a week ago with a vengeance."

The physicians of the Torre Cesme were the finest in the world, distinguished only from the Torre's healers by the fact that they did not possess magic. They were the first line of inspection for the healers in the tower, their quarters occupying the sprawling complex around its base.

Magic was precious, its demands costly enough that some Healer on High centuries ago had decreed that if they were to see a patient, a physician must first inspect the person. Perhaps it had been a political maneuver---a bone tossed to the physicians so often passed over by a people clamoring for the cure-all remedies of magic.

Yet magic could not cure all things. Could not halt death, or bring someone back from it. She'd learned it again and again these past two years, and earlier. And even with the protocols with the physicians, Yrene still---as she had always done---found herself walking toward the sound of coughing in the narrow, sloped streets of Antica.

Yrene tilted the vial this way and that. "The tonic might be reacting to the heat. It's been unseasonably warm, even for us."

With the end of summer finally near, even after two years, Yrene was still not entirely accustomed to the unrelenting, dry heat of the god-city. Mercifully, some long-ago mastermind had invented the \emph{bidgier}, wind-catching towers set atop buildings to draw in fresh air to the rooms below, some even working in tandem with the few underground canals winding beneath Antica to transform hot wind into cool breezes. The city was peppered with the small towers, like a thousand spears jutting toward the sky, ranging from the small houses made of earthen bricks to the great, domed residences full of shaded courtyards and clear pools.

Unfortunately, the Torre had predated that stroke of brilliance, and though the upper levels possessed some cunning ventilation that cooled the chambers far below, there were plenty of days when Yrene wished some clever architect would take it upon themselves to outfit the Torre with the latest advances. Indeed, with the rising heat and the various fires burning throughout the tower, Hafiza's room was near-sweltering. Which led Yrene to add, "You could put it in a lower chamber---where it's cooler."

"But the sunlight needed?"

Yrene considered. "Bring in mirrors. Catch the sunlight through the window, and focus it upon the vial. Adjust it a few times a day to match the path of the sun. The cooler temperature and more concentrated sunlight might have the tonic ready sooner."

A little, pleased nod. Yrene had come to cherish those nods, the light in those brown eyes. "Quick wits save lives more often than magic," was Hafiza's only reply.

She'd said it a thousand times before, usually where Yrene was involved---to her eternal pride---but Yrene bowed her head in thanks and set the vial back upon its stand.

"So," Hafiza said, folding her hands atop each other on the near-glowing rosewood desk, "Eretia informs me that she believes you are ready to leave us."

Yrene straightened in her seat, the very same chair she'd sat in that first day she'd climbed the thousand steps to the top of the tower and begged for admittance. The begging had been the least of her humiliations that meeting, the crowning moment being when she dumped the bag of gold on Hafiza's desk, blurting that she didn't care what the cost was and to take it all.

Not realizing that Hafiza did not take money from students. No, they paid for their education in other ways. Yrene had suffered through endless indignities and degradations during her year working at the backwater White Pig Inn, but she had never been more mortified than the moment Hafiza ordered her to put the money back in that brown pouch. Scraping the gold off the desk like some cardplayer scrambling to collect his winnings, Yrene had debated leaping right out the arc of windows towering behind Hafiza's desk.

Much had changed since then. Gone was the homespun dress, the too-slim body. Though Yrene supposed the endless stairs of the Torre had kept in check the weight she'd gained from steady, healthy eating, thanks to the Torre's enormous kitchens, the countless markets teeming with food stalls, and the dinein shops along every bustling street and winding alley.

Yrene swallowed once, trying and failing to glean the Healer on High's face. Hafiza had been the one person here whom Yrene could never read, never anticipate. She'd never once shown a display of temper---something that couldn't be said of many of the instructors here, Eretia especially---and had never raised her voice. Hafiza had only three expressions: pleased, neutral, and disappointed. Yrene lived in terror of the latter two.

Not for any punishment. There was no such thing here. No rations held, no pain threatened. Not like at the White Pig, where Nolan had docked her pay if she stepped out of line or was overgenerous with a customer, or if he caught her leaving out nightly scraps for the half-feral urchins who had prowled the filthy streets of Innish.

She'd arrived here thinking it would be the same: people who took her money, who made it harder and harder to leave. She'd spent a year working at the White Pig due to Nolan's increases in her rent, decreases in her pay, his cut of her meager tips, and knowledge that most women in Innish worked the streets, and his place, disgusting as it had been, was a far better alternative.

She'd told herself never again---until she'd arrived here. Until she'd dumped that gold on Hafiza's desk and had been ready to do it all over, indebt and sell herself, just for a chance to learn.

Hafiza did not even consider such things. Her work was in direct opposition to the people who did, the people like Nolan. Yrene still remembered the first time she'd heard Hafiza say in that thick, lovely accent of hers, nearly the same words that Yrene's mother had told her, over and over: they did not charge, students or patients, for what Silba, Goddess of Healing, gifted them for free.

In a land of so many gods that Yrene was still struggling to keep them all straight, at least Silba remained the same.

Yet another clever thing the khaganate had done upon patching together the kingdoms and territories during their years of conquest: keep and adapt the gods of \emph{everyone}. Including Silba, whose dominance over the healers had been established in these lands long ago. History was written by the victors, apparently. Or so Eretia, Yrene's direct tutor, had once told her. Even the gods seemed no more immune to it than mere mortals.

But it didn't stop Yrene from offering up a prayer to Silba and whatever gods might be listening as she said at last, "I am ready, yes."

"To leave us." Such simple words, offered with that neutral face---calm and patient. "Or have you considered the other option I presented to you?"

Yrene had. She'd thought about it endlessly in the two weeks since Hafiza had summoned her to this office and spoke the one word that had clenched a fist around her heart: \emph{Stay}.

Stay, and learn more---stay, and see what this fledgling life she'd built here might grow into.

Yrene rubbed at her chest as if she could still feel that viselike grip. "War is coming to my home again---the northern continent." So they called it here. Yrene swallowed. "I want to be there to help those fighting against the empire's control."

At last, after so many years, a force was rallying. Adarlan itself had been sundered, if rumors were to be believed, by Dorian Havilliard in the north, and the dead king's Second, Duke Perrington, in the south. Dorian was backed by Aelin Galathynius, the long-lost queen now ripe with power and ravenous for vengeance, judging by what she'd done to the glass castle and its king. And Perrington, rumor also claimed, was aided by horrors birthed from some dark nightmare.

But if this was the only chance at freedom for Fenharrow\ldots

Yrene would be there to help, in whatever way she could. She still smelled smoke, late at night or when she was drained after a hard healing. Smoke from that fire those Adarlanian soldiers had built---and burned her mother upon. She still heard her mother's screaming and felt the wood of that tree trunk dig beneath her nails as she'd hidden at the edge of Oakwald. As she watched them burn her mother alive. After her mother had killed that soldier to buy Yrene time to run.

It had been ten years since then. Nearly eleven. And though she had crossed mountains and oceans  there were some days when Yrene felt as if she were still standing in Fenharrow, smelling that fire, splinters slicing under her nails, watching as the soldiers took their torches and burned her cottage, too.

The cottage that had housed generations of Towers healers.

Yrene supposed it was fitting, somehow, she'd wound up \emph{in} a tower herself. With only the ring on her left hand as proof that once, for hundreds of years, there had existed a line of prodigally gifted female healers in the south of Fenharrow. A ring she now toyed with, that last shred of proof that her mother and mother's mother and all the mothers before them had once lived and healed in peace. It was the first of only two objects Yrene would not sell---even before selling herself.

Hafiza had not replied, and so Yrene went on, the sun sinking farther toward the jade waters of the harbor across the city, "Even with magic now returned to the northern continent, many of the healers might not have the training, if any survived at all. I could save many lives."

"War could also claim \emph{your} life."

She knew this. Yrene lifted her chin. "I am aware of the risks."

Hafiza's dark eyes softened. "Yes, yes, you are."

It had come out during that first, mortifying meeting with the Healer on High.

Yrene had not cried for years---since that day her mother had become ash on the wind---and yet the moment Hafiza had asked about Yrene's parents she had buried her face in her hands and wept. Hafiza had come from around that desk and held her, rubbing her back in soothing circles.

Hafiza often did that. Not just to Yrene, but to all her healers, when the hours were long and their backs had cramped and the magic had taken \emph{everything} and it was still not enough. A quiet, steady presence who steeled them, soothed them.

Hafiza was as close to a mother as Yrene had found since she was eleven. And now weeks away from twenty-two, she doubted she'd ever find another like her.

"I have taken the examinations," Yrene said, even though Hafiza knew that already. She'd given them to Yrene herself, overseeing the grueling week of tests on knowledge, skill, and actual human practice. Yrene had made sure she received the highest marks of her class. As near to a perfect score as anyone had ever been given here. "I'm ready."

"Indeed you are. And yet I still wonder how much you might learn in five years, ten years, if you have already learned so much in two."

Yrene had been too skilled to begin with the acolytes in the lower levels of the Torre.

She'd shadowed her mother since she was old enough to walk and talk, learning slowly, over the years, as all the healers in her family had done. At eleven, Yrene had learned more than most would in another decade. And even during the six years that had followed, where she'd pretended to be an ordinary girl while working on her mother's cousin's farm---the family unsure what to really do with her, unwilling to get to know her when war and Adarlan might destroy them all---she'd quietly practiced.

But not too much, not too noticeably. During those years, neighbor had sold out neighbor for even the whisper of magic. And even though magic had vanished, taking Silba's gift with it, Yrene had been careful never to appear more than a simple farmer's relative, whose grandmother had perhaps taught her a few natural remedies for fevers or birthing pain or sprained and broken limbs.

In Innish, she'd been able to do more, using her sparse pocket money to purchase herbs, salves. But she didn't often dare, not with Nolan and Jessa, his favored barmaid, watching her day and night. So these past two years, she'd \emph{wanted} to learn as much as she could. But it had also been an unleashing. Of years of stifling, of lying and hiding.

And that day she'd walked off the boat and \emph{felt} her magic stir, felt it reach for a man limping down the street\ldots She had fallen into a state of shock that had not ended until she wound up weeping in this very chair three hours later.

Yrene sighed through her nose. "I could return here one day to continue my studies. But---with all due respect, I \emph{am} a full healer now." And she could venture wherever her gift called her.

Hafiza's white brows rose, stark against her brown skin. "And what of Prince

Kashin?"

Yrene shifted in her seat. "What of him?"

"You were once good friends. He remains fond of you, and that is no small thing to ignore."

Yrene leveled a look few dared to direct toward the Healer on High. "Will he interfere with my plans to leave?"

"He is a prince, and has been denied nothing, save the crown he covets. He may find that your leaving is not something he will tolerate."

Dread sluiced through her, starting at her spine and ending curled deep in her gut. "I've given him no encouragement. I made my thoughts on that matter perfectly clear last year."

It had been a disaster. She'd gone over it again and again, the things she'd said, the moments between them---everything that had led up to that awful conversation in that large Darghan tent atop the windswept steppes.

It had started a few months after she'd arrived in Antica, when one of Kashin's favored servants had fallen ill. To her surprise, the prince himself had been at the man's bedside, and during the long hours Yrene worked, the conversation had flowed, and she'd found herself smiling. She'd cured the servant, and upon leaving that night, she'd been escorted by Kashin himself to the gates of the Torre. And in the months that followed, friendship had sprung up between them.

Perhaps freer, lighter than the friendship she also wound up forming with Hasar, who had taken a liking to Yrene after requiring some healing of her own. And while Yrene had struggled to find companions within the Torre thanks to her and her fellow students' conflicting hours, the prince and princess had become friends indeed. As had Hasar's lover, the sweet-faced Renia---who was as lovely inside as she was out.

A strange group they made, but\ldots Yrene had enjoyed their company, the dinners Kashin and Hasar invited her to, when Yrene knew she had no reason to really be there. Kashin often managed to find a way to sit next to her, or near enough to engage her in conversation. For months, things had been fine---better than fine. And then Hafiza had brought Yrene out to the steppes, the native home of the khagan's family, to oversee a grueling healing. With Kashin as their escort and guide.

The Healer on High now examined Yrene, frowning slightly. "Perhaps your lack of encouragement has made him more eager."

Yrene rubbed her eyebrows with her thumb and forefinger. "We've barely spoken since then." It was true. Though mostly due to Yrene avoiding him at the dinners to which Hasar and Renia still invited her.

"The prince does not seem like a man easily deterred---certainly not in matters of the heart."

She knew that. She'd liked that about Kashin. Until he'd wanted something she couldn't give him. Yrene groaned a bit. "Will I have to leave like a thief in the night, then?" Hasar would never forgive her, though she had no doubt Renia would try to soothe and rationalize it to the princess. If Hasar was pure flame, then Renia was flowing water.

"Should you decide to remain, you will not have to worry about such things at all."

Yrene straightened. "You would really use Kashin as a way to keep me here?"

Hafiza laughed, a crow of warmth. "No. But forgive an old woman for trying to use any avenue necessary to convince you."

Pride and guilt eddied in her chest. But Yrene said nothing---had no answer.

Returning to the northern continent  She knew there was no one and nothing left there for her. Nothing but unforgiving war, and those who would need her help.

She did not even know where to \emph{go}---where to sail, how to find those armies and their wounded. She'd traveled far and wide before, had evaded enemies bent on slaughtering her, and the thought of doing it all again  She knew some would think her mad. Ungrateful for the offer Hafiza had laid before her. She'd thought those things of herself for a long while now.

Yet not a single day passed without Yrene gazing toward the sea at the foot of the city---gazing northward.

Yrene's attention indeed slid from the Healer on High to the windows behind her, to the distant, darkening horizon, as if it were a lodestone.

Hafiza said, a shade more gently, "There is no rush to decide. Wars take a long time."

"But I will need---"

"There is a task I would first have you do, Yrene."

Yrene stilled at that tone, the hint of command in it.

She glanced to the letter Hafiza had been reading when she'd entered. "What is it?"

"There is a guest at the palace---a special guest of the khagan. I would ask you to treat him. Before you decide whether now is the right time to leave these shores, or if it is better to remain."

Yrene angled her head. Rare---very rare for Hafiza to pass off a task from the khagan to someone else. "What is his ailment?" Common, standard words for healers receiving cases.

"He is a young man, age twenty-three. Healthy in every regard, in fit condition. But he suffered a grave injury to his spine earlier this summer that left him paralyzed from the hips downward. He cannot feel or move his legs, and has been in a wheeled chair since. I am bypassing the initial physicians' examination to appeal directly to you."

Yrene's mind churned. A complex, long process to heal that manner of injury.

Spines were nearly as difficult as brains. Connected to them quite closely. With that sort of healing, it wasn't a matter of letting her magic wash over them---that wasn't how it worked.

It was finding the right places and channels, in finding the correct amount of magic to wield. It was getting the brain to again send signals to the spine, down those broken pathways; it was replacing the damaged, smallest kernels of life within the body with new, fresh ones. And on top of it\ldots learning to walk again. Weeks. \emph{Months}, perhaps.

"He is an active young man," Hafiza said. "The injury is akin to the warrior you aided last winter on the steppes."

She'd guessed as much already---it was likely why she'd been asked. Two months spent healing the horse-lord who'd taken a bad fall off his mount and injured his spine. It was not an uncommon injury among the Darghan, some of whom rode horses and some of whom soared on ruks, and they had long relied on the Torre's healers. Working on the warrior had been her first time putting her lessons on the subject into effect, precisely why Hafiza had accompanied her to the steppes. Yrene was fairly confident she could do another healing on her own this time, but it was the way Hafiza glanced down at the letter---just once---that made Yrene pause. Made her ask, "Who is he?"

"Lord Chaol Westfall." Not a name from the khaganate. Hafiza added, holding Yrene's gaze, "He was the former Captain of the Guard and is now Hand to the new King of Adarlan." 

Silence.

Yrene was silent, in her head, her heart. Only the crying of the gulls sailing above the Torre and the shouts of vendors going home for the night in the streets beyond the compound's high walls filled the tower room.

"No."

The word pushed out of Yrene on a breath.

Hafiza's slim mouth tightened.

"No," Yrene said again. "I will not heal him."

There was no softness, nothing motherly in Hafiza's face, as she said, "You took an oath upon entering these halls."

"No." It was all she could think to say.

"I am well aware how difficult it may be for you---"

Her hands started shaking. "No."

"Why?"

"You know why." The words were a strangled whisper. "Y-y-you know."

"If you see Adarlanian soldiers suffering on those battlefields, will you stomp right over them?"

It was the cruelest Hafiza had ever been to her.

Yrene rubbed the ring on her finger. "If he was Captain of the Guard for the last king, he---he worked for the man who---" The words spilled and stumbled out. "He took \emph{orders} from him."

"And now works for Dorian Havilliard."

"Who indulged in his father's riches---the riches of \emph{my} people. Even if Dorian Havilliard did not participate, the fact that he stood \emph{back} while it happened \ldots" The pale stone walls pressed in, even the solid tower beneath them feeling unwieldy. "Do you know what the king's men \emph{did} these years? What his armies, his soldiers, his guards \emph{did}? And you ask me to heal a man who commanded them?"

"It is a reality of who you are---who \emph{we} are. A choice all healers must make."

"And you have made it so often? In your peaceful kingdom?"

Hafiza's face darkened. Not with ire, but memory. "I was once asked to heal a man who was injured while evading capture. After he had committed a crime so unspeakable  The guards told me what he'd done before I walked into his cell. They wanted him patched up so he could live to be put on trial. He'd undoubtedly be executed---they had victims willing to testify and proof aplenty. Eretia herself saw the latest victim. His last one. Gathered all the evidence she needed and stood in that court and condemned him with what she had seen." Hafiza's throat bobbed. "They chained him down in that cell, and he was hurt enough that I knew I could use my magic to make the internal bleeding worse. They'd never know. He'd be dead by morning, and no one would dare question me." She studied the vial of blue tonic. "It was the closest I have ever come to killing. I \emph{wanted} to kill him for what he had done. The world would be better for it. I had my hands on his chest---I was ready to do it. But I remembered. I remembered that oath I had taken, and remembered that they had asked me to heal him so that he would live---so that justice might be found for his victims. And their families." She met Yrene's eyes. "It was not my death to dole out."

"What happened?" The words were a wobble.

"He tried to plead innocent. Even with what Eretia presented, with what that victim was willing to talk about. He was a monster through and through. They convicted him, and he was executed at sunrise the next day."

"Did you watch it?"

"I did not. I came back up here. But Eretia did. She stood at the front of the crowd and stayed until they hauled his corpse into a cart. She stayed for the victims who could not bear to watch. Then she returned here, and we both cried for a long, long while."

Yrene was quiet for a few breaths, enough that her hands steadied. "So I am to heal this man---so he may find justice elsewhere?"

"You do not know his story, Yrene. I suggest listening to it before contemplating such things."

Yrene shook her head. "There will be no justice for him---not if he served the old and new king. Not if he's cunning enough to remain in power. I know how Adarlan works."

Hafiza watched her for a long moment. "The day you walked into this room, so terribly thin and covered with the dust of a hundred roads I had never sensed such a gift. I looked into those beautiful eyes of yours, and I nearly gasped at the uncut power in you."

Disappointment. It was disappointment on the Healer on High's face, in her voice.

"I thought to myself," Hafiza went on, "\emph{Where has this young woman been hiding? What god reared you, guided you to my doorstep?} Your dress was in tatters around your ankles, and yet you walked in, straight-backed as any noble lady. As if you were the heir to Kamala herself."

Until Yrene had dumped the money on the desk and fallen apart moments later. She doubted the very first Healer on High had ever done such a thing.

"Even your family name: \emph{Towers}. A hint at your foremothers' long-ago association with the Torre, perhaps. I wondered in that moment if I had at last found \emph{my} heir---my replacement."

Yrene felt the words like a blow to the gut. Hafiza had never so much as hinted 

\emph{Stay}, the Healer on High had offered. To not only continue the training, but to also take up the mantle now laid before her.

But it had not been Yrene's own ambition, to one day claim this room as her own. Not when her sights had always been set across the Narrow Sea. And even now  it was an honor beyond words, yes. But one that rang hollow.

"I asked what you wanted to do with the knowledge I would give you," Hafiza went on. "Do you remember what you said to me?"

Yrene did. She had not forgotten it for a moment. "I said I wanted to use it to do some good for the world. To do something with my useless, wasted life."

The words had guided her these years---along with the note she carried every day, moving it from pocket to pocket, dress to dress. Words from a mysterious stranger, perhaps a god who had worn the skin of a battered young woman, whose gift of gold had gotten her here. Saved her.

"And so you shall, Yrene," Hafiza said. "You shall one day return home, and you shall do good, you shall do \emph{wonders}. But before you do, I would ask this of you. Help that young man. You have done the healing before---you can do it again now."

"Why can't you?"

She'd never sounded so sullen, so\ldots ungrateful.

Hafiza gave her a small, sad smile. "It is not my own healing that is needed."

Yrene knew the Healer on High did not mean the man's healing, either. She swallowed against the thickness in her throat.

"It is a soul-wound, Yrene. And letting it fester these years I cannot blame you. But I will hold you accountable if you let it turn into something worse. And I will mourn you for it."

Yrene's lips wobbled, but she pressed them together, blinking back the burning in her eyes.

"You passed the tests, better than anyone who has ever climbed into this tower," Hafiza said softly. "But let this be my personal test for you. The final one. So that when you decide to go, I may bid you farewell, send you off to war, and know \ldots" Hafiza put a hand on her chest. "Know that wherever the road takes you, however dark, you will be all right."

Yrene swallowed the small sound that tried to come out of her and instead looked toward the city, its pale stones resplendent in the last light of the setting sun. Through the open windows behind the Healer on High, a night breeze laced with lavender and cloves flitted in, cooling her face and ruffling Hafiza's cloud of white hair.

Yrene slid a hand into the pocket of her pale blue dress, her fingers wrapping around the familiar smoothness of the folded piece of parchment. She clutched it, as she had often done on the sailing over here, during those initial few weeks of uncertainty even after Hafiza had admitted her, during the long hours and hard days and moments that had nearly broken her while she trained.

A note, written by a stranger who had saved her life and granted her freedom in a matter of hours. Yrene had never learned her name, that young woman who had worn her scars like some ladies wore their finest jewelry. The young woman who was a trained killer, but had purchased a healer's education.

So many things, so many good things, had come from that night. Yrene sometimes wondered if it had actually happened---might have believed she'd dreamed it if not for the note in her pocket, and the second object Yrene had never sold, even when the gold had thinned.

The ornate gold-and-ruby brooch, worth more than entire blocks of Antica.

Adarlan's colors. Yrene had never learned where the young woman had come from, who had bestowed the beating that had left lingering bruises on her pretty face, but she had spoken of Adarlan as Yrene did. As all the children who had lost everything to Adarlan did---those children with their kingdoms left in ash and blood and ruin.

Yrene ran a thumb over the note, the words inked there:

\emph{For wherever you need to go---and then some. The world needs more healers.}

Yrene breathed in that first night breeze, the spices and brine it ushered into the Torre.

She looked back to Hafiza at last, the Healer on High's face calm. Patient.

Yrene would regret it, if she refused. Hafiza would yield, but Yrene knew that whether she left here, whether she somehow decided to remain, she would\ldots regret. Think back on this. Wonder if she had repaid the extraordinary kindness she'd been given rather poorly. Wonder what her mother would have thought of it.

And even if this man hailed from Adarlan, even if he'd done the bidding of that butcher 

"I will meet with him. Assess him," Yrene conceded. Her voice only wobbled slightly. She clutched that piece of paper in her pocket. "And then decide if I will heal him."

Hafiza considered. "Fair enough, girl," she said quietly. "Fair enough."

Yrene blew out a shaking breath. "When do I see him?"

"Tomorrow," Hafiza said, and Yrene winced. "The khagan has asked you to come to Lord Westfall's chambers tomorrow."

