
\chapter{40}

Standing and walking a few steps wasn't the same as being back to full capacity.

The next week proved it. Yrene still battled with whatever lurked in Chaol's spine, still clinging---down to the very base, she explained---and still keeping him from full motion. Running, most jumping, kicking: out of the question. But thanks to the sturdy wooden cane she procured for him, he could stand, and he could walk.

And it was a gods-damned miracle.

He brought the cane and the chair to his morning training with Hashim and the guards, for the moments when he pushed himself too hard and couldn't manage the return trip to his rooms. Yrene joined him during the early lessons, instructing Hashim on where to focus in his legs. To rebuild more muscle. To stabilize him further. She'd done the same for Shen, Hashim had confided one morning---had come to supervise most of his initial training sessions after his injury.

So Yrene had been there, watching from the sidelines, that first day Chaol had taken up a sword against Hashim and dueled. Or did it as best he could with the cane in one hand.

His balance was shit, his legs unreliable, but he managed to get in a few good hits against the man. And a cane  not a bad weapon, if the fight called for it.

Yrene's eyes had been wide as saucers when they stopped and Chaol approached her spot on the wall, leaning heavily on the cane as his body trembled.

The color on her face, he realized with no small amount of male satisfaction, was from far more than the heat. And when they'd eventually left, walking slowly into the cool shadows of the halls, Yrene had tugged him into a curtained-off alcove and kissed him.

Leaning against a supply shelf for support, his hands had roved all over her, the generous curves and small waist, tangling into her long, heavy hair. She'd kissed and kissed him, breathless and panting, and then licked---actually \emph{licked} the sweat from his neck.

Chaol had groaned so loudly that it was no surprise a servant appeared a heartbeat later, ripping the curtain away, as if to chide two workers for shirking their duties.

Yrene had blanched as she'd righted herself and asked the bowing and scraping male servant not to say anything. He assured her that he wouldn't, but Yrene had been shaken. She'd kept her distance for the rest of the walk back.

And maintained it every day since. It was driving him mad.

But he understood. With her position, both in the Torre and within the palace, they should be smarter. More careful.

And with Kadja always in his rooms 

Chaol kept his hands to himself. Even when Yrene laid her own hands upon his back and healed him, pushed and pushed herself, to break through that final wall of darkness.

He wanted to tell her, debated telling her, that it was already enough. He would gladly live with the cane for the rest of his life. She had given him more than he could ever hope for.

For he saw the guards every morning. The weapons and shields.

And he thought of that war, unleashing itself at last upon his friends. His homeland.

Even if he did not bring an army with him when he returned, he'd find some way to stand on those battlefields. Riding, at least, was now a viable option while fighting alongside them.

Fighting for---her.

He was thinking of it as they walked to dinner one night, over a week later. With the cane, it took him longer than usual, but he did not mind any extra moment spent in her company.

She was wearing her purple gown---his favorite---her hair half up and curling softly from the unusually humid day. But she was jumpy, unsettled.

"What is it?"

The royals hadn't cared the first night he'd walked on his own two legs to dinner. Another everyday miracle of the Torre, though the khagan himself had commended Yrene. She'd beamed at the praise. Even as the khagan had ignored Chaol---as he had done since that ill-fated meeting.

Yrene rubbed at the scar on her neck as if it ached. He hadn't asked about it ---didn't want to know. Only because if he did  Even with a war upon them, he might very well take the time to hunt down whoever had done it and bury them.

"I convinced Hasar to throw me a party," Yrene said quietly.

He waited until they'd passed a cluster of servants before asking, "For what reason?"

She blew out a breath. "It's my birthday. In three days."

"Your birthday?"

"You know, the celebration of the day of your birth---"

He nudged her with an elbow, though his spine slipped and shifted with the movement. The cane groaned as he pressed his weight upon it. "I had no idea that she-devils actually had them."

She stuck out her tongue. "Yes, even my kind has them."

Chaol grinned. "So you asked her to throw one for you?" Considering how the last \emph{party} had gone  He might very well wind up one of those people slipping away into a darkened bedroom. Especially if Yrene wore that dress again.

"Not exactly," Yrene said wryly. "I mentioned that my birthday was coming up, and how dull \emph{your} plans for it were \ldots"

He chuckled. "Presumptuous of you."

She batted her eyelashes. "And I \emph{might} have mentioned that in all my years here, I've never been to the desert and was debating a trip of my own, but that

I'd be sad to not celebrate with her \ldots"

"And I'm guessing that she suggested an oasis owned by her family instead?"

Yrene hummed. "A little overnight excursion to Aksara---half a day's ride to the east, to their permanent tented camp within the oasis."

So the healer could scheme after all. But---"It'll be boiling in this heat."

"The princess wants a party in the desert. So she shall have one." She chewed on her lip, those shadows dancing again. "I also managed to ask her about it--- Aksara. The history." Chaol braced himself. "Hasar grew bored before she told me much, but she said that she'd once heard that the oasis grew atop a city of the dead. That the ruins now there were merely the gateway inside. They don't like to risk disturbing the dead, so they never leave the spring itself---to venture into the jungle around it."

No wonder she'd seemed concerned. "Not only caves to be found, then."

"Perhaps Nousha means something different; perhaps there are also caves there with information." She blew out a breath. "I suppose we'll see. I made sure to yawn while Hasar told me, enough that I doubt she'll wonder why I asked at all."

Chaol kissed her temple, a swift brush of his mouth that no one might see.

"Clever, Yrene."

"I meant to tell you the other week, but then you stood, and I forgot. Some court schemer I am."

He caressed his free hand down the length of her spine. A bit lower. "We've been otherwise engaged." Her face flushed a beautiful shade of pink, but a thought settled into him. "What do \emph{you} really want for your birthday? And which one is it?"

"Twenty-two. And I don't know. If it wasn't for this, I wouldn't have brought it up at all."

"You weren't going to tell me?"

She gave him a guilty frown. "I figured that with everything pressing on you, birthdays were inconsequential." Her hand slid into her pocket---to hold that thing he'd never inquired about.

They neared the clamor of dinner in the great hall. He brushed his fingers against hers. She halted at the silent request, the hall spreading away before them, servants and viziers striding past.

Chaol leaned on his cane while they rested, letting it stabilize his weight. "Am I invited to this desert party, at least?"

"Oh, yes. You, and all my other favorite people: Arghun, Kashin, and a handful of delightful viziers."

"I'm glad I made the cut, considering that Hasar hates me."

"No." Yrene's eyes darkened. "If Hasar hated you, I don't think you'd be alive right now."

Gods above. This was the woman she'd befriended.

Yrene went on, "At least Renia will be there, but Duva shouldn't be in the heat in her condition and her husband won't leave her side. I'm sure that once we get there, information or no, I'll probably wish I could have made a similar excuse."

"We've got a few days. We could, technically, make the same one if we need to leave."

The words settled in. The invitation and implication. Yrene's face went delightfully red, and she smacked his arm. "Rogue."

Chaol chuckled, and eyed the hallway for a shadowed corner. But Yrene breathed, "We can't."

Not about his sorry joke, but about the want she no doubt saw building in his eyes. The want he beheld simmering in hers.

He adjusted his jacket. "Well, I'll attempt to find you a suitable present that can compare to an entire desert \emph{retreat}, but don't hold me to it."

Yrene looped her arm through Chaol's free one, no more than a healer escorting her patient to the table. "I have everything I need," was all she said.

