
\chapter{42}

The hatchling had been a trap.

It was the last thought Nesryn had as Kadara crashed into the web---the \emph{net} woven between the two peaks.
Built not to catch the wind, but \emph{ruks}.

She only had the sense of Sartaq throwing his body into hers, anchoring her into the saddle and holding tight as Kadara screamed.

Snapping and shimmering and rock; shale and gray sky and golden feathers.
Wind howling, the hatchling's piercing cry, and Sartaq's bellow.

Then twisting, slamming into stone so hard the impact sang through her teeth, her bones.
Then falling, tumbling, Kadara's restrained body curving, curving as Sartaq was curled over Nesryn, shielding that hatchling in her talons from the final impact.

Then the \emph{boom}.
And the bounce---the bounce that snapped the leather straps on the saddle.
Still tied to it, they were still tied together as they soared off Kadara's body, Nesryn's bow scattering from her hand, her fingers clasping on open air---

Sartaq pivoted them, his body a solid wall around hers as Nesryn realized where the sky was, where the pass floor was---

He roared as they struck the shale, as he kept her atop him, taking the full brunt of the impact.

For a heartbeat, there was only the skittering trickle of shifting shale and the thud of crumbling rock off the pass walls.
For a heartbeat, she could not remember where her body was, her breath was--- Then a scrape of wing on shale.

Nesryn's eyes snapped open, and she was moving before she had the words to name her motions.

A cut slashed down her wrist, caked with small rocks and dust.
She didn't feel it, barely noticed the blood as she blindly fumbled for the straps to the saddle, snapping them free, panting through her teeth as she managed to lift her head, to dare to look---

He was dazed.
Blinking up at the gray sky.
But alive, \emph{breathing}, blood sliding down his temple, his cheek, his mouth 

She sobbed through her teeth, her legs at last coming free, allowing her to roll over to get to his own, to the tangled bits of leather shredded between them.

Sartaq was half buried in shale.
His hands sliced up, but his legs---

"Not broken," he rasped.
"Not broken."
It was more to himself than her.
But Nesryn managed to keep her fingers steady as she freed the buckles.
The thick riding leathers had saved his life, saved his skin from being flayed off his bones.
He'd taken the impact for her, moved her so that he'd hit it first---

She clawed at the shale covering his shoulders and his upper arms, sharp rock cutting into her fingers.
The leather strap at the end of her braid had come free in the impact, and her hair now fell about her face, half blocking her view of the forest behind and rock around them.
"Get up," she panted.
"Get up."
He took a breath, blinking furiously.
"\emph{Get up}," she begged him.

Shale shifted ahead, and a low, pained cry echoed off the rock.

Sartaq snapped upright.
"\emph{Kadara---}"

Nesryn twisted on her knees, scanning for her bow even as she took in the ruk.

Lying thirty feet ahead, Kadara was coated in the near-invisible silk.
A phantom net, her wings pinned, her head tucked in---

Sartaq scrambled upright, swaying, slipping on the loose shale as he drew his Asterion knife.

Nesryn managed to rise, her legs shaking, head spinning as she scanned and scanned the pass for her bow---

There.
Near the pass wall.
Intact.

She hurtled for it while Sartaq ran to the ruk, reaching her weapon just as he sliced the first of the webbing free.

"You'll be fine," he was saying to Kadara, blood coating his hands, his neck.

"I'll get you out---"

Nesryn shouldered her bow, pressing a hand to her pocket.
Falkan--- A little leg pushed against her in answer.
\emph{Alive}.

She wasted no time rushing to the ruk, drawing her own Fae blade from the sheath Borte had found for her and slicing at the thick strands.
It clung to her fingers, ripping away skin, but she severed and sliced, working her way down the wing as Sartaq hacked his way down the other.

They reached Kadara's legs at the same time.

Saw that her talons were empty.

Nesryn's head snapped up, scanning the pass, the piles of disturbed shale---

The hatchling had been thrown during the collision.
As if even Kadara's talons couldn't keep shut against the pain of impact.
The baby ruk now lay on the ground near the lip of the pass, struggling to rise, low chirps of distress echoing off the rock.

"Up, Kadara," Sartaq commanded, his voice breaking.
"\emph{Get up.}"

Great wings shifted, shale clacking as the ruk tried to obey.
Nesryn staggered toward the hatchling, blood unmistakable on its fluffy gray head, its large dark eyes wide with terror and pleading---

It happened so fast Nesryn didn't have time to shout.

One heartbeat, the hatchling had opened its beak to cry for help.

The next it screamed, eyes flaring as a long ebony leg emerged from behind a pillar of rock and slammed through its spine.

Bone crunched and blood sprayed.
And Nesryn threw herself into a stop, swaying so hard she teetered backward onto her ass, a wordless cry on her lips as the hatchling was hauled around the rock, flailing and shrieking--- It went silent.

And she had seen horrific things, things that had made her sick and kept her from sleep, and yet that baby ruk, terrified and pleading, in pain and dragged away, going \emph{silent---}

Nesryn whirled, feet slipping on the shale as she scrambled toward Kadara, toward Sartaq, who beheld the hatchling being snatched behind that rock and screamed at Kadara to fly---

The mighty ruk tried and failed to rise.

"\emph{FLY}," Sartaq bellowed.

Slowly, so slowly the ruk lumbered to her legs, her scraped beak dragging through the loose rock.

She wasn't going to make it.
Wasn't going to get airborne in time.
For just beyond the web-shrouded tree line\ldots Shadows writhed.
Scuttled closer.

Nesryn sheathed her sword and drew her bow, arrow shaking as she aimed it toward the rock the hatchling had been hauled behind, then the trees a hundred yards off.

"\emph{Go, Kadara}," Sartaq begged.
"\emph{Get up!}"

The bird was barely in shape to fly, let alone carry riders---

Rock clacked and skittered behind her.
From the labyrinth of rock within the pass.

Trapped.
They were trapped---

Falkan shifted in her pocket, trying to wriggle free.
Nesryn covered him with her forearm, pressing hard.
"Not yet," she breathed.
"Not yet."

His powers were not Lysandra's.
He had tried and failed to shift into a ruk this week.
But the large wolf was as big as he could manage.
Anything larger was beyond his magic.

\emph{"Kadara---"}

The first of the spiders broke from the tree line.
As black and sleek as her fallen sister.

Nesryn let her arrow fly.

The spider fell back, screaming---an unholy sound that shook the rocks as that arrow sank into an eye.
Nesryn instantly had another arrow drawn, backing toward Kadara, who was just now beginning to flap her wings--- The ruk stumbled.

Sartaq screamed, "\emph{FLY!}"

Wind stirred Nesryn's hair, sending shards of shale skittering.
The ground rumbled behind, but Nesryn did not dare take her eyes off the second spider that emerged from the trees.
She fired again, the song of her arrow drowned out by the flap of Kadara's wings.
A heavy, pained beat, but it held steady---

Nesryn glanced behind for a breath.
Just one, just to see Kadara bobbing and waving, fighting for every wing beat upward through the narrow pass, blood and shale dripping from her.
Right as a \emph{kharankui} emerged from one of the shadows of the rocks high up the peak, legs bending as if it would leap upon the ruk's back---

Nesryn fired, a second arrow on its tail.
Sartaq's.

Both found their marks.
One through an eye, the other through the open mouth of the spider.

It shrieked, tumbling down from its perch.
Kadara swung wide to dodge it, narrowly avoiding the jagged face of the peak.
The spider's splat thudded through the maze of rock ahead.

But then Kadara was up, into the gray sky, flapping like hell.

Sartaq whirled toward Nesryn just as she looked back at the pine forest.

To where half a dozen \emph{kharankui} now emerged, hissing.

Blood coated the prince, his every breath ragged, but he managed to grab Nesryn's arm and breathe, "\emph{Run}."

So they did.

Not toward the pines behind.

But into the gloom of the winding pass ahead.

