
\chapter{43}

Without the brace, Chaol was given a black mare, Farasha, whose name was about as ill-fitting as they came. It meant \emph{butterfly}, Yrene told him as they gathered in the palace courtyard three days later.

Farasha was anything but.

Yanking at the bit, stomping her hooves and tossing her head, Farasha savored testing his limits long before the desert-bound company finished gathering. Servants had gone ahead the day before to prepare the camp.

He'd known the royals would give him their fiercest horse. Not a stallion, but one close enough to match it in fury. Farasha had been born furious, he was willing to bet.

And he'd be damned if he let those royals make him ask for another horse. One that would not strain his back and legs so much.

Yrene was frowning at Farasha, at him, as she stroked a hand down her chestnut mare's night-black mane.

Both beautiful horses, though neither compared to the stunning Asterion stallion Dorian had gifted Chaol for his birthday last winter.

Another birthday celebration. Another time---another life.

He wondered what had happened to that beautiful horse, whom he had never named. As if he'd known, deep down, how fleeting those few happy weeks were. He wondered if it was still in the royal stables. Or if the witches had pillaged him---or let their horrible mounts use him to fill their bellies.

Perhaps that was why Farasha resented his very presence. Perhaps she sensed that he had forgotten that noble-hearted stallion in the north. And wanted to make him pay for it.

The breed was an offshoot of the Asterions, Hasar had tittered as she'd trotted past on her white stallion, circling him twice. The refined, wedge-shaped head and high tails were twin markers of their Fae ancestry. But these horses, the Muniqi, had been bred for the desert climes of this land. For the sands they were to cross today, and the steppes that had once been the khagan's homeland. The princess had even pointed to a slight bulge between the horses' eyes---the \emph{jibbah}
---the marker of the larger sinus capacity that allowed the Muniqi to thrive in the dry, unyielding deserts of this continent.

And then there was the Muniqi's speed. Not as fast, Hasar admitted, as an Asterion. But close.

Yrene had watched the princess's little \emph{lesson}, face carefully neutral, using the time to adjust where she'd strapped Chaol's cane behind her saddle, then fiddle with the clothes she wore.

While Chaol was in his usual teal jacket and brown pants, Yrene had forgone a dress.

They'd swathed her in white and gold against the sun, her long tunic flowing to her knees to reveal loose, gauzy pants tucked into high brown boots. A belt cinched her slim waist, and a glinting bandolier of gold and silver beading sliced between her breasts. Her hair, she'd left in her usual half-up fashion, but someone had woven bits of gold thread through it.

Beautiful. As lovely as a sunrise.

There were perhaps thirty of them in total, none people Yrene really knew, as Hasar had not bothered to invite any of the healers from the Torre. Swift-legged hounds paced in the courtyard, weaving under the hooves of the dozen guards' horses. Definitely not Muniqi, those horses. Fine indeed for guards---his men had received beasts nowhere near their quality---but without that \emph{awareness} the Muniqi possessed, as if they listened to every word spoken.

Hasar signaled to Shen, standing proud at the gate, who blew a horn--- And then they were off.

For a woman who commanded ships, Hasar seemed far more interested in the equine heritage of her family's people. And seemed more than eager to unleash her skills as a Darghan rider. The princess cursed and scowled as the city streets slowed them. Even with word given well in advance to clear the path out of Antica, the narrow and steep streets checked their speed considerably.

And then there was the brutal heat. Already sweating, Chaol rode beside Yrene, keeping a tight leash on Farasha, who tried to take a bite out of not one but two vendors gawking from the sidewalks. \emph{Butterfly}
indeed.

He kept one eye upon the mare and the other upon the city passing by. And as they rode for the eastern gates into the arid, scrub-covered hills beyond, Yrene pointed out landmarks and tidbits of information.

Water ran through aqueducts wending between the buildings, feeding the houses and public fountains and countless gardens and parks scattered throughout. A conqueror might have taken this city three centuries ago, but that same conqueror had loved it well. Treated it well and nourished it.

They cleared the eastern gate, then passed down a long, dusty road that cut through the sprawl beyond the city proper. Hasar didn't bother to wait, and launched her stallion into a gallop that left them waving away her dust.

Kashin, claiming he didn't want to eat her dust the entire way to the oasis, followed suit after giving a small smile toward Yrene and a whistled command to his horse. Then most of the nobles and viziers, apparently having already taken bets, launched into various races at breakneck speed through towns cleared well in advance. As if this kingdom were their playground.

Birthday party indeed. The princess had likely been bored and didn't want to look too irresponsible to her father. Though he was surprised to find that Arghun had joined them. Surely with most of his siblings away, he would have seized the chance to hatch some plot. But there was Arghun, galloping close to Kashin as they blended into the horizon.

Some of the nobility remained back with Chaol and Yrene, letting the others put some miles between them. They cleared the last of the outlying towns, their horses sweat-soaked and panting as they ascended a large, rocky hill. The dunes began just on its other side, Yrene had told him. They would water the horses here---then make the last leg of the trek across the sands.

She was smiling faintly at him as they ascended the crag, taking a deer path through the scrub. Horses had trampled through here; bushes were broken and shattered under careless riders. A few bushes even bore speckles of blood, already dried in the brutal sun.

Someone should flay the rider who'd been so reckless with their mount.

Others had reached the top of the crag, watered their horses, and moved on. All he saw of them were bodies and horseflesh disappearing into the sky---as if they simply walked off the edge of the cliff and into thin air.

Farasha stomped and surged her way up the hill, and his back and thighs strained to keep seated without the brace to steady him. He didn't dare let her get a whiff of discomfort.

Yrene reached the summit first, her white clothes like a beacon in the cloudless blue day around them, her hair shining bright as dark gold. She waited for him, the chestnut mare beneath her panting heavily, its rich coat gleaming with hues of deepest ruby.

She dismounted as he urged Farasha up the last of the hill, and then--- It knocked the breath from him.

The desert.

It was a barren, hissing sea of golden sand. Hills and waves and ravines, rippling on forever, empty and yet humming. Not a tree or bush or gleam of water to be seen.

The unforgiving hand of a god had shaped this place. Still blew his breath across it, shifting the dunes grain by grain.

He had never seen such a sight. Such a wonder. It was a new world entirely.

Perhaps it was an unexpected boon that the information they sought dwelled out here.

Chaol dragged his attention to Yrene, who was reading his face. His reaction.

"Its beauty is not for everyone," she said. "But it sings to me, somehow."

This sea where no ships would ever sail, some men would look upon it and see only burning death. He saw only quiet---and clean. And slow, creeping life. Untamed, savage beauty.

"I know what you mean," he said, carefully dismounting from Farasha. Yrene monitored, yet did nothing but hold out the cane, letting him find the best way to swing his leg over, back groaning and wobbling, and then slide down to the sandy rock. The cane was instantly in his hand, though Yrene made no move to steady him while he finally released the saddle and reached for Farasha's reins.

The horse tensed, as if considering lunging for him, but he gave her a nononsense glare, the cane groaning as he dug it into the rock beneath him.

Farasha's dark eyes glowed as if she'd been forged in Hellas's burning realm, but Chaol stood tall---as tall as he could. Didn't break her stare.

Finally, the horse huffed, and deigned to let him haul her toward the sandcrusted trough that was half crumbling with age. The trough perhaps had been here for as long as the desert had existed, had watered the horses of a hundred conquerors.

Farasha seemed to grasp that they were to enter that ocean of sand and drank heartily. Yrene led her horse over, keeping the chestnut a healthy distance away from Farasha, and said, "How are you feeling?"

"Solid," he said, and meant it. "I'll be aching by the time we get there, but the strain isn't so bad." Without the cane, he didn't dare try to walk more than a few steps. Could barely manage it.

She still put a hand on his lower spine, then his thighs, letting her magic assess. Even with the clothes and the heat, the press of her hands left him aware of every inch of space between them.

But others gathered around the ancient, enormous trough, and so he pulled out of Yrene's assessing touch, leading Farasha a safe distance away. Mounting the mare again, though 

"Take your time," Yrene murmured, but remained a few steps away.

He'd had a block at the palace. Here, short of climbing onto the precarious lip of the trough  The distance between his foot and the stirrup had never seemed so long. Balancing on one foot while he lifted it, pushing down with the other to propel him up, swinging his leg around the saddle  Chaol went through the steps, feeling the motions he'd done a thousand times before. He'd learned to ride before he was six---had been on a horse nearly his entire life.

Of course he'd been given a devil of a horse to do this with.

But Farasha held still, staring toward the sifting sea of sand, to the path that had been trampled down the hill---their entry into the desert. Even with the shifting winds hauling the sands into new shapes and valleys, the tracks the others had left were clear enough. He could even spy some of them cresting hills and then flying down them, little more than specks of black and white.

And yet he remained here. Staring at the stirrups and saddle.

Yrene offered casually, "I can find a block or bucket---"

Chaol moved. Perhaps not as graceful as he'd like, perhaps more struggling than he'd intended, but he managed, the cane groaning as he used it to push upward, then clattering to the rock as he let go to grab the pommel of the saddle, right as his foot slid---barely---into the stirrup. Farasha shifted at his weight while he hauled himself higher into the saddle, his back and thighs barking as he swung his leg over, but he was up.

Yrene strode to the fallen cane and dusted it off. "Not bad, Lord Westfall."

She strapped the cane behind her saddle and mounted her mare. "Not bad at all."

He hid his smile, his face still over-warm, and nudged Farasha down the sandy hill at last.

They followed the tracks the others had left slowly, the heat rippling off the sands.

Up, and down, the only sounds the muffled thumping of their horses and the sighing sands. Their party meandered in a long, snaking line. Guards had been posted throughout, standing with towering poles topped with the khagan's flag and insignia of a dark running horse. Markers of the general direction toward the oasis. He pitied the poor men ordered to stand in the heat for a princess's whim, but said nothing.

The dunes evened out after a time, the horizon shifting to reveal a flat, sandy plain. And in the distance, waving and bobbing in the heat


"There we make our camp," Yrene said, pointing toward a dense cluster of green. No sign of the ancient, buried city of the dead that Hasar claimed the oasis had grown over. Not that they expected to see much of anything from their vantage point.

From the distance, it might very well be another thirty minutes. Certainly at their pace.

Despite the sweat soaking through her white clothes, Yrene was smiling. Perhaps she, too, had needed a day away. To breathe the open air.

She noticed his attention and turned. The sun had brought out her freckles, darkening her skin to a glowing brown, and tendrils of hair curled about her smiling face.

Farasha tugged on the reins, her body quivering with impatience.

"I own an Asterion horse," he said, and her mouth curved in an impressed frown. Chaol shrugged. "I'd like to see how a Muniqi measures up."

Her brows narrowed. "You mean \ldots" She noted the flat, smooth spread of land between them and the oasis. Perfect for running. "Oh, I can't---a gallop?" He waited for the words about his spine, his legs. None came.

"Are you afraid?" he asked, arching a brow.

"Of these things? \emph{Yes}." She cringed at her mount, restless beneath her.

"She's as sweet as a dairy cow," he said of Yrene's chestnut mare.

Chaol leaned down to pat "Butterfly's" neck.

She tried to bite him. He yanked on the reins enough to tell her he was fully aware of her bullshit.

"I'll race you," he said.

Yrene's eyes sparkled. And to his shock she breathed, "The prize?"

He could not remember the last time. The last time he had felt so aware of every bit of breath and blood, simmering and thrumming, in his body.

"A kiss. When and where of my choosing."

"What do you mean \emph{where}."

Chaol only grinned. And let Farasha run free.

Yrene cursed, more viciously than he'd ever heard her, but he didn't dare look back---not as Farasha became a black storm upon the sand.

He'd never gotten to test out the Asterion. But if it was faster than
\emph{this}---

Flying over the sand, Farasha was a bolt of dark lightning spearing across the golden desert. It was all he could do to keep up, to grit his teeth against his barking muscles.

He forgot about them anyway at the blur of reddish brown and black that emerged in the corner of his eye---and the white rider atop it.

Yrene's hair rose and fell behind her in a golden-brown tangle of curls, lifting with each thunderous pound of her mare's legs on the hard sand. White clothes streaming in the wind, the gold and silver sparkled like stars, and her face---

Chaol couldn't breathe as he beheld the wild joy on Yrene's face, the unchecked exhilaration.

Farasha marked the mare gaining on them, meeting them beat for beat, and made to charge ahead. To leave them in the dust.

He checked her with the reins and his feet, marveling that he could even do so. That the woman now closing in, now riding beside him, now beaming at him as if he were the only thing in this barren, burning sea 
She had done this. Given him this.

Yrene was smiling, and then she was laughing, as if she could not contain it inside her.

Chaol thought it was the most beautiful sound he'd ever heard.

And that this moment, flying together over the sands, devouring the desert wind, her hair a golden-brown banner behind her  Chaol felt, perhaps for the first time, as if he was awake.

And he was grateful, right down to his very bones, for it.

