
\chapter{46}

It broke her, and unmade her, and rebirthed her.

Sprawled over Chaol's chest hours later, listening to the thump of his heartbeat, Yrene still did not have words for what had passed between them.
Not the physical joining, not the repeated bouts of it, but simply the sense of \emph{him}.
Of belonging.

She'd never known it could \emph{be} like that.
Her quick, unimpressive, and only brush with sex had been just last autumn, and had left her in no hurry to seek it out again.
But this 

He'd made sure she found her pleasure.
Repeatedly.
Before he ever found his own.

And beyond that, the \emph{things} he made her feel--- Not just as a result of his body, but who he was 

Yrene pressed an idle kiss to the sculpted muscle of his chest, savoring the fingers he still trained down her spine, over and over.

It was safety, and joy, and comfort, and knowing that no matter what befell them\ldots He would not balk.
He would not break.
Yrene nuzzled her face against him.

It was dangerous, she knew, to feel such things.
She'd known what lay in her eyes when he'd looked at her.
The heart she'd offered up without saying as much.
But seeing that locket that he'd somehow found and had been so thoughtful about\ldots Her initials were beautifully done, but the mountains and waves\ldots It was stunning work, done by a master jeweler in Antica.

"I didn't do it on my own," Yrene murmured against his skin.

"Hmm?"

She ran her fingers over the grooves of Chaol's stomach before rising onto an elbow to study his face in the dimness.
The lanterns had long since burned out, and silence had settled over the camp, replaced by the buzz and hum of beetles in the palm trees.
"Getting here.
The mountains yes, but the seas\ldots Someone helped me."

Alertness filled those sated eyes.
"Oh?"

Yrene plucked up the locket.
Between bouts of lovemaking, when she'd gone to move his cane within easy reach of the bed, she'd slid the small note inside.
The fit had been perfect.

"I was stuck in Innish, with no way of leaving.
And one night, this stranger appeared at the inn.
She was\ldots everything I was not.
Everything I'd forgotten.
She was waiting for a boat, and during the three nights she was there, I think she \emph{wanted} the lowlifes to try to rob her---she was spoiling for a fight.
But she kept her distance.
I was left with cleaning up alone that night \ldots" Chaol's hand tensed on her back, but he said nothing.

"And mercenaries who had given me a hard time earlier that evening found me in the alley."

He went utterly still.

"I think---I \emph{know} they wanted to \ldots" She shook off the icy grip of horror, even all these years later.
"The woman, girl, whatever she was, she interrupted before they could so much as try.
She 
dealt with them.
And when she finished, she taught me how to defend myself."

His hand began stroking again.
"So that's how you learned."

She ran a hand over the scar on her neck.
"But other mercenaries, friends of the earlier ones, returned.
One held a knife to my throat to get her to drop her weapons.
She refused to do so.
So I used what she'd taught me to disarm and disable the man."

He blew out an impressed breath that ruffled her hair.

"To her, it was a test.
She'd been aware of the second group circling, and told me she wanted me to have some \emph{controlled} experience.
I'd never heard of anything more ridiculous."
The woman had been either brilliant or insane.
Likely both.
"But she told me\ldots told me it was better to be suffering in the streets of Antica than in Innish.
And that if I wanted to come here, I should go.
That if I wanted something, I should \emph{take} it.
She told me to fight for my miserable life."

Yrene brushed the sweat-damp hair from his eyes.
"I patched her up and she went on her way.
And when I got back to my room\ldots She had left me a bag of gold.
And a golden brooch with a ruby the size of a robin's egg.
To pay for my passage here, and any tuition at the Torre."

He blinked in surprise.
Yrene whispered, voice breaking, "I think she was a god.
I---I don't know who would \emph{do} that.
I have a little gold left, but the brooch  I never sold it.
I still have it."

He frowned at the necklace, as if he'd misjudged its size.

Yrene added, "That's not what I keep in my pocket."
His brows rose.
"I left Innish that morning.
I took the gold and the brooch and got on a ship here.
So I crossed mountains alone, yes---but the Narrow Sea \ldots" Yrene traced the waves on the locket.
"I crossed because of her.
I teach the women at the Torre because she told me to share the knowledge with any women who would listen.
I teach it because it makes me feel like I'm paying her back, in some small way."

Yrene ran her thumb over the initials on the front.
"I never learned her name.
She only left a note with two lines.
\emph{For wherever you need to} \emph{go---and then some.
The world needs more healers}.
That's what I keep in my pocket---that little scrap of paper.
What's now in here."
Yrene tapped the locket.
"I know it's silly, but it gave me courage.
When things were hard, it gave me courage.
It still does."

Chaol swept the hair from her brow and kissed it.
"There is nothing silly about it.
And whoever she is\ldots I will be forever grateful."

"Me too," Yrene whispered as he slid his mouth over her jaw and her toes curled.
"Me too."

