
\chapter{48}

Nesryn awoke to sharp biting.

She jerked upright, a scream on her lips---

It died when she felt the little teeth biting at her neck, her ear.
Nipping her awake.

Falkan.
She winced, her head throbbing.
Bile surged up her throat.

Not biting at her head.
But the silk that bound her body, the thick strands reeking.
And the cave she was in 

No, not cave.
But a covered section of the pass.
Dimly illuminated by the moon.

She scanned the dark to either side, the arch of stone above them no more than thirty feet wide, keeping her breathing steady---

There.
Sprawled on the ground nearby, covered foot to neck with silk.
His face crusted with blood, eyes closed--- Sartaq's chest rose and fell.

Nesryn shuddered with the force of keeping her sob contained as Falkan slithered down her body, chewing at the strands with his vicious teeth.

She didn't need to tell the shifter to hurry.
She scanned the empty passage, scanned the dim stars beyond.

Wherever they were\ldots It was different here.

The rock smooth.
Polished.
And carved.
Countless carvings had been etched in the space, ancient and primitive.

Falkan chewed and chewed, the silk snapping strand by strand.

"Sartaq," Nesryn dared to whisper.
"Sartaq."
The prince did not stir.

Clicking sounded from beyond the archway.
"Stop," she murmured to Falkan.
"\emph{Stop.}"

The shifter halted his path down her back.
Clung to her leathers as a shadow darker than the night emerged from around the corner behind them.
Or ahead--- she had no idea where true north lay.
If they were still within the pass itself, or atop another peak.

The spider was slightly larger than the others.
Her blackness deeper.
As if the starlight itself was loath to touch her.

The \emph{kharankui} halted as she noted Nesryn staring at her.

Nesryn controlled her breathing, rallying her mind to come up with \emph{something} to buy them time, buy Sartaq and Falkan time 

"You are the ones who have been poking about in forgotten places," the spider said in Halha, her voice beautiful, lyrical.

Nesryn swallowed once, twice, trying and failing to moisten her paper-dry tongue.
She managed to rasp, "Yes."

"What is it that you seek?"

Falkan pinched her back in warning---and order.
Keep her distracted.
While he chewed.

Nesryn blurted, "We were paid by a merchant, who traded with your sisters to the north, the stygian spiders---"

"Sisters!"
The spider hissed.
"Our blood kin they may be, but no true sisters of the soul.
Gentlehearted fools, trading with mortals---\emph{trading}, when we were born to \emph{devour} you."

Nesryn's hands shook behind her back.
"T-that is why he sent us.
He was unimpressed by them.
S-said they did not live up to the legend \ldots" She had no idea what was spewing from her mouth.
"So he wished to see you, see if you might t-t-trade."

Falkan brushed against her arm in quiet comfort.

"Trade?
We have nothing to trade, beyond the bones of your kin."

"There is no Spidersilk here?"

"No.
Though we delight in tasting your dreams, your years.
Before we finish with you."

Had they already done so for Sartaq?
Was that why he did not stir?
Nesryn forced herself to ask as the threads behind her snapped free so slowly, "Then--- then what is it you do here?"

The spider took a step forward, and Nesryn braced herself.
But the spider lifted a thin, clawed leg and pointed to one of the polished, carved walls.
"We wait."

And as her eyes at last adjusted to the dimness, Nesryn saw what the spider pointed to.

A carving of an archway---a gate.

And a cloaked figure standing within it.

She squinted, straining to make out who stood there.
"W-who do you wait for?"

Houlun had said the Valg had once passed through here---

The spider brushed aside the dirt crusted over the figure.
Revealing long, flowing hair etched there.
And what she'd thought to be a cloak  It was a dress.

"Our queen," the spider said.
"We wait for Her Dark Majesty to return at last."

"Not---not Erawan?"
Servants to a dark crown, Houlun had said 

The spider spat, the venom landing near Sartaq's covered feet.
"Not him.
Never \emph{him}."

"Then who---"

"We wait for the Queen of the Valg," the spider purred, rubbing against the carving.
"Who in this world calls herself Maeve."

