
\chapter{49}

Queen of the Valg.

"Maeve is Queen of the \emph{Fae}," Nesryn countered carefully.

The spider chuckled, low and wicked. "So she has made them believe."

\emph{Think, think, think}. "What---what a mighty and powerful queen she must be," Nesryn stammered. "To rule both." Falkan furiously chewed, each strand slowly, so slowly, yielding. "Will you---will you tell me the tale?"

The spider studied her, those depthless eyes like pits of hell. "It will not buy you your life, mortal."

"I---I know." She shook further, the words tumbling out. "But stories
 I have always loved stories---of these lands especially.
\emph{Wind-seeker}, my mother called me, because I was always drifting where the wind tugged me, always dreaming of those stories. And here
 here the wind has taken me. So I would hear one last tale, if you allow it. Before I meet my end."

The spider remained quiet for a heartbeat. Another. Then she settled herself beneath the carving of the archway---the Wyrdgate. "Consider it a gift---for your boldness in even asking."

Nesryn said nothing, heart thundering through every part of her body.

"Long ago," the spider said softly in that beautiful voice, "in another world, another lifetime, there existed a land of dark, and cold, and wind. Ruled by three kings, masters of shadow and pain. Brothers. The world had not always been that way, had not been born that way. But they waged a mighty war. A war to end all wars. And those three kings conquered it. Turned it into a wasteland, a paradise for those who had dwelled in darkness. For a thousand years, they ruled, equal in power, their sons and daughters spread throughout the land to ensure their continued dominion. Until a queen appeared---her power a new, dark song in the world. Such wondrous things she could do with her power, such horrible, wondrous things \ldots"

The spider sighed. "They each desired her, those kings. Pursued her, wooed her. But she only deigned to ally with one, the strongest of them." "Erawan," Nesryn murmured.

"No. Orcus, eldest of the Valg kings. They wed, but Maeve was not content. Restless, our queen spent long hours pondering the riddles of the world---of other worlds. And with her gifts, she found a way to look. To pierce the veil between worlds. To see realms of green, of light and song." The spider spat, as if such a thing were abhorrent. "And one day, when Orcus was gone to see his brothers, she took a path between realms. Stepped beyond her world, and into the next."

Nesryn's blood went cold. "H-how?"

"She had watched. Had learned of such rips between worlds. A door that could open and close at random, or if one knew the right words." The spider's dark eyes gleamed. "We came with her---her beloved handmaidens. We stepped with her into this  place. To this very spot."

Nesryn glanced at the polished stone. Even Falkan seemed to pause to do the same.

"She bade us stay---to guard the gate. Lest anyone should pursue her. For she had decided she did not wish to go back. To her husband, her world. So she went, and we only heard whisperings through our sisters and smaller kin, carried on the wind." The spider fell silent.

Nesryn pushed, "What did you hear?"

"That Orcus arrived, his brothers in tow. That Orcus had learned of his wife's leaving and discovered how she'd done it. Went beyond what she'd done, and found a way to \emph{control} the gate between worlds. Made keys to do so, shared with his brothers. Three keys, for the three kings.

"They went from world to world, opening gates as they willed it, sweeping in their armies and laying waste to those realms as they hunted for her. Until they reached this world."

Nesryn could barely draw breath to ask, "And they found her?"

"No," the spider said, something like a smile in its voice. "For Her Dark Majesty had left these mountains, had found another land, and prepared herself well. She knew that one day she would be found. And planned to hide within plain sight. So she did. She came across a lovely, long-lived people---nearimmortals themselves---ruled over by two sister-queens."

Mab and Mora. Holy gods---

"And using her powers, she ripped into their minds. Made them believe they had a sister, an eldest sister to rule with them. Three queens---for the three kings that might one day come. When they returned to their palace, she tore into the minds of all those who dwelled there, too. And any who came. Planting the thought that a third queen had always existed, always ruled. If they somehow resisted her power, she found ways to end them." A wicked chuckle.

Nesryn had heard the legends. Of Maeve's dark, unnamed power---a darkness that could devour the stars. That Maeve had never revealed a Fae form, only that deadly darkness. And she had lived far beyond the lifespan of any known Fae.

Lived so long that the only comparable lifespan  Erawan.

A Valg life span. For a Valg queen.

The spider again paused. Falkan had nearly reached her hands---but still not enough to free them.

Nesryn asked, "So the Valg kings arrived, but did not know who faced them in the war?"

"Precisely." A delighted purr. "Disguised in a Fae body, they did not recognize her, the fools. But she used it against them. Knew how to defeat them, how their armies worked. And when she realized what they had done to arrive here, the keys they possessed  she wanted them. To banish them, kill them, and to use the keys as she saw fit within this world. And others.

"So she took them. Snuck in and took them, surrounding herself with Fae warriors so others might not ask just \emph{how} she knew so many things. Oh, the clever queen claimed it was from communing with the spirit world, but  she knew. She had run those war camps. Knew how the kings worked. So she stole the keys. Managed to send two of those kings back, Orcus one of them. And before she could go after the final king, the youngest one who loved his brothers so very deeply, the keys were taken from her." A hiss.

"By Brannon," Nesryn breathed.

"Yes, the fire-king. He saw the darkness in her but did not recognize it. He wondered, suspected, but all he'd known of the Valg, our people, were their \emph{male} soldiers. Their grunts and princes and kings. He did not know that a female  How different, how extraordinary a female Valg is. Even \emph{he} was tricked by her; she found paths into his mind to keep him from truly realizing it." Another soft, lovely laugh. "Even now, when all should be clear to his meddlesome spirit
 Even now, he does not know. To his oncoming doom---yes, to his doom, and the other's."

Nausea roiled through her. \emph{Aelin}. Aelin's doom.

"But while he did not guess correctly about our queen's origins, he still knew that his fire  She greatly feared his fire. As all true Valg do." Nesryn tucked away that kernel. "He left, building his kingdom far away, and she built her defenses, too. So many clever defenses, should Erawan rise again and realize that the queen he'd sought for his brother, conquered worlds to find, was here all along. That she had built armies of Fae, and would let them battle each other." A spider in a web. That's what Maeve was.

Falkan reached Nesryn's hands, chewing through the silk there. Sartaq remained unconscious, so perilously close to the spider.

"So you have waited these thousands of years---for her to return to these mountains?"

"She ordered us to hold the pass, to guard the rip in the world. So we have.

And so we will, until she summons us to her side once more."

Nesryn's head spun. Maeve---she'd think on it later. If they lived through this.

She flicked her fingers at Falkan, signaling him.

Silently, keeping to the shadows, the shifter scuttled into the dark.

"And now you know---how the Black Watch came to dwell here." The spider rose with a mighty heave. "I hope it was a fitting final tale for you, Windseeker."

Nesryn opened her mouth as the spider advanced, rotating her wrists behind her back---

"Sister," a female voice hissed from the darkness beyond. "Sister, a word."

The spider halted, pivoting her bulbous body toward the archway entrance.

"\emph{What}."

A beat of fear. "There is a problem, sister. A threat."

The spider scuttled toward her kin, snapping, "Tell me."

"Ruks on the northern horizon. Twenty at least---"

The spider hissed. "Guard the mortals. I shall deal with the birds."

Clicking legs, shale shifting all around her. Nesryn's heart hammered as she flexed her aching fingers. "Sartaq," she breathed.

His eyes flicked open across the way. Alert. Calm.

The other spider crawled in, smaller than her leader. Sartaq tensed, shoulders straining as if he'd try to burst from the silk that held him.

But the spider only whispered, "\emph{Hurry}."

