
\chapter{5}

Chaol had barely slept. Partially due to the unrelenting heat, partially due to the fact that they were in a tentative ally's fraught household, full of potential spies and unknown dangers---perhaps even from Morath itself---and partially due to what had befallen Rifthold and all he held dear.

And partially due to the meeting that he was now minutes away from having.

Nesryn paced with uncharacteristic nerves through the sitting room that was to be his sickroom. Low-lying couches and clusters of cushions filled the space, the shining floors interrupted only by rugs of thickest and finest weaving---from the skilled hands of craftswomen in the west, Nesryn told him. Art and treasures from across the khagan's empire adorned the space, interspersed with potted palms sagging in the heat and sunlight trickling through the garden windows and doors.

Ten in the morning, the khagan's eldest daughter had declared to him at dinner last night. Princess Hasar---plain and yet fierce-eyed. A lovely young woman had sat at her side, the only person at whom Hasar smiled. Her lover or wife, judging by the frequent touching and long looks.

There had been enough of an edge to Hasar's wicked grin as she told Chaol when the healer would arrive that he'd been left to wonder who, precisely, they were sending.

He still did not know what to make of these people, this place. This city of high learning, this blend of so many cultures and history, peacefully dwelling together\ldots Not at all like the raging and broken spirits dwelling in Adarlan's shadow, living in terror, distrusting one another, enduring its worst crimes.

They'd asked him about the butchering of the slaves in Calaculla and Endovier at dinner.

Or the oily one, Arghun, did. Had the prince been among Chaol's new recruits to the royal guard, he would have easily gotten him to fall in line thanks to a few well-timed shows of skill and sheer dominance. But here, he had no authority to bring the conniving, haughty prince to heel.

Not even when Arghun wanted to know why the former King of Adarlan had deemed it necessary to enslave his people. And then put them down like animals. Why the man had not looked to the southern continent for education on the horrors and stain of slavery---and avoided instituting it.

Chaol had offered curt answers that verged on impolite. Sartaq, the only one of them beyond Kashin whom Chaol was inclined to like, had finally tired of his elder brother's questioning and steered the conversation away. To what, Chaol had no idea. He'd been too busy fighting against the roaring in his ears over Arghun's razor-sharp inquiries. And then too busy monitoring every face---royal, vizier, or servant---who made an appearance in the khagan's great hall. No signs of black rings or collars; no strange behavior to remark on.

He'd given Kashin a subtle shake of his head at one point to tell him as much. The prince had pretended not to see, but the warning flared in his eyes: \emph{Keep looking}.

So Chaol had, half paying attention to the meal unfolding before him, half monitoring every word and glance and breath of those around him.

Despite their youngest sister's death, the heirs made the meal lively, conversation flowing, mostly in languages Chaol did not know or recognize. Such a wealth of kingdoms in that hall, represented by viziers and servants and companions---the now-youngest princess, Duva, herself wedded to a darkhaired, sad-eyed prince from a faraway land who kept close to his pregnant wife and spoke little to anyone around him. But whenever Duva smiled softly at him\ldots Chaol did not think the light that filled the prince's face was feigned. And wondered if the man's silence was not from reticence but perhaps not yet knowing enough of his wife's language to keep up.

Nesryn, however, had no such excuse. She'd been silent and haunted at dinner. He'd only learned that she'd bathed before it thanks to the shout and slamming door in her chambers, followed by a huffy-looking male servant scrambling out of her rooms. The man did not come back again, nor did a replacement arrive.

Kadja, the servant assigned to Chaol, had helped him dress for dinner, then undress for bed, and had brought breakfast this morning immediately upon his awakening.

The khagan certainly knew how to eat well.

Exquisitely spiced and simmered meats, so tender they fell right off the bone; herbed rice of various colors; flatbreads coated in butter and garlic; rich wines and liquors from the vineyards and distilleries across his empire. Chaol had passed on the latter, accepting only the ceremonial glass offered before the khagan made a half-hearted toast to his new guests. For a grieving father, it was a warmer welcome than Chaol had expected.

Yet Nesryn had a sip of her drink, barely a bite of her meal, and waited a scant minute until the feast was cleared before asking to return to their suite. He'd agreed---of course he'd agreed, but when they'd closed the suite doors and he'd asked if she wanted to talk, she had said no. She wanted to sleep and would see him in the morning.

He'd had the nerve to ask Nesryn if she wanted to share his room or hers.

The shutting of her door was emphasis enough.

So Kadja had helped him into bed, and he had tossed and turned, sweating and wishing he could kick off the sheets instead of having to throw them back. Even the cool breeze that drifted in through the cleverly crafted ventilation system---the air hauled from wind-snaring towers amid the domes and spires to be cooled by canals beneath the palace, then scattered amongst the rooms and halls---had not offered any reprieve.

He and Nesryn had never been good at talking. They'd tried, usually with disastrous results.

They'd done everything out of order, and he'd cursed himself again and again for not making it right with her. Not trying to \emph{be} better.

She'd barely looked at him these past ten minutes they'd been waiting for the healer to arrive. Her face was haggard, her shoulder-length hair limp. She hadn't put on her captain's uniform, but rather returned to her usual midnight-blue tunic and black pants. As if she couldn't stand to be in Adarlan's colors.

Kadja had dressed him again in his teal jacket, even going so far as to polish the buckles down the front. There was a quiet pride to her work, not at all like the timidity and fear of so many of the castle servants in Rifthold.

"She's late," Nesryn murmured. Indeed, the ornate wooden clock in the corner announced the healer was ten minutes late. "Should we call for someone to find out if she's coming?"

"Give her time."

Nesryn paused before him, frowning deeply. "We need to begin immediately. There is no time to waste."

Chaol took a breath. "I understand that you want to return home to your family---"

"I will not rush you. But even a day makes a difference."

He noted the lines of strain bracketing her mouth. He had no doubt twin ones marked his own. Forcing himself to stop contemplating and dreading where Dorian might now be had been an effort of pure will this morning. "Once the healer arrives, why don't you go track down your kin in the city? Perhaps they've heard from your family in Rifthold."

A slicing wave of her slender hand. "I can wait until you're done."

Chaol lifted his brows. "And pace the entire time?"

Nesryn sank onto the nearest sofa, the gold silk sighing beneath her slight weight. "I came here to help you---with this, and with our cause. I won't run off for my own needs."

"What if I give you an order?"

She only shook her head, her dark curtain of hair swaying with the movement.

And before he could give that exact order, a brisk knock thudded on the heavy wood door.

Nesryn shouted a word that he assumed meant \emph{enter} in Halha, and he listened to the footsteps as they approached. One set---quiet and light.

The door to the sitting room drifted open beneath the press of a honeycolored hand.

It was her eyes that Chaol noticed first.

She likely stopped people dead in the street with those eyes, a vibrant golden brown that seemed lit from within. Her hair was a heavy fall of rich browns amid flashes of dark gold, curling slightly at the ends that brushed her narrow waist.

She moved with a nimble grace, her feet---clad in practical black slippers--- swift and unfaltering as she crossed the room, either not noticing or caring about the ornate furnishings.

Young, perhaps a year or two older than twenty.

But those eyes\ldots they were far older than that.

She paused at the carved wooden chair across from the golden couch, Nesryn shooting to her feet. The healer---for there was no one else she could be, with that calm grace, those clear eyes, and that simple, pale blue muslin dress--- glanced between them. She was a few inches shorter than Nesryn, built with similar delicacy, yet despite her slender frame He didn't look long at the other features the healer had been generously blessed with.

"Are you from the Torre Cesme?" Nesryn asked in Chaol's own tongue.

The healer only stared at him. Something like surprise and anger lighting those remarkable eyes.

She slid a hand into the pocket of her gown, and he waited for her to withdraw something, but it remained there. As if she was grasping an object within.

Not a doe ready to bolt, but a stag, weighing the options of fighting or fleeing, of standing its ground, lowering its head, and charging.

Chaol held her gaze, cool and steady. He'd taken on plenty of young bucks during the years of being captain---had gotten them all to heel.

Nesryn asked something in Halha, no doubt a repeat of her question.

A thin scar sliced across the healer's throat. Perhaps three inches long.

He knew what sort of weapon had given that scar. All the possibilities that burst into his head for why it might have happened were not pleasant ones.

Nesryn fell silent, watching them.

The healer only turned on her heel, walked to the desk near the windows, took a seat, and pulled a piece of parchment toward her from the neat stack in the corner.

Whoever these healers were, the khagan was right: they certainly did not answer to his throne. Or find it in themselves to be impressed with any manner of nobility and power.

She opened a drawer, found a glass pen, and held it poised over the paper. "Name."

She did not have an accent---or, rather, the accent of these lands.

"Chaol Westfall."

"Age."

The accent. It was from---

"Fenharrow."

Her pen stalled. "Age."

"You're from Fenharrow?"

\emph{What are you doing here, so far from home?}

She leveled a cool, unimpressed stare at him.

He swallowed and said, "Twenty-three."

She scribbled something down. "Describe where the injury begins." Each word was clipped, her voice low.

Had it been an insult to be assigned his case? Had she other things to do when she was summoned here? He thought again of Hasar's wicked smile the night before. Perhaps the princess knew that this woman was not praised for her bedside manner.

"What is your name?"

The question came from Nesryn, whose face was beginning to tighten.

The healer stilled as she took in Nesryn, blinking like she had not really noticed her. "You---are from here?"

"My father was," Nesryn said. "He moved to Adarlan, wed my mother, and I now have family there---and here." She impressively hid any trace of dread at the mention of them as she added coaxingly, "My name is Nesryn Faliq. I am the

Captain of the Royal Guard of Adarlan."

That surprise in the healer's eyes turned wary. But she again gazed at him.

She knew who he was. The look conveyed it---the analysis. She knew he'd once held that title, and now was something else. So the name, the age the questions were bullshit. Or some bureaucratic nonsense. He doubted it was the latter.

A woman from Fenharrow, meeting with two members from Adarlan's court\ldots

It didn't take much to read her. What she saw. Where that mark on her throat might have come from.

"If you don't want to be here," Chaol said roughly, "then send someone else." Nesryn whirled on him.

The healer only held his stare. "There is no one else to do this." The unspoken words said the rest: \emph{They sent their best.}

With that steady, self-assured posture, he didn't doubt it. She angled her pen again. "Describe where the injury begins."

A sharp knock on the sitting room door cut through the silence. He started, cursing himself for not having heard the approach.

But it was Princess Hasar, clad in green and gold and smirking like a cat. "Good morning, Lord Westfall. Captain Faliq." Her braided hair swaying with each swaggering step, Hasar strolled over to the healer, who looked up at her with an expression Chaol dared call exasperation, and leaned down to kiss her on either cheek. "You're not usually so grumpy, Yrene." There---a name.

"I forgot my \emph{kahve} this morning." The thick, spiced, bitter drink Chaol had choked down with his breakfast. An acquired taste, Nesryn had said when he'd asked about it later.

The princess took up a perch along the edge of the desk. "You didn't come to dinner last night. Kashin was sulking about it."

Yrene's shoulders tightened. "I had to prepare."

"Yrene Towers locking herself in the Torre to work? I might die of shock."

From the princess's tone, he filled in enough. The best healer in the Torre Cesme had become so thanks to that grueling work ethic.

Hasar looked him over. "Still in the chair?"

"Healing takes time," Yrene said mildly to the princess. Not an ounce of subservience or respect to the tone. "We were just beginning."

"So you agreed to do it, then?"

Yrene cut the princess a sharp glare. "We were assessing the lord's needs."

She jerked her chin toward the doors. "Shall I find you when I'm done?"

Nesryn gave Chaol an impressed, wary glance. A healer dismissing a princess of the most powerful empire in the world.

Hasar leaned forward to ruffle Yrene's gold-brown hair. "If you weren't gods-blessed, I'd carve out your tongue myself." The words were honeyed venom. Yrene only offered a faint, bemused smile before Hasar hopped off the desk and gave him a mocking incline of the head. "Don't worry, Lord Westfall. Yrene has healed injuries similar and far worse than your own. She'll have you back on your feet and able to do your master's bidding again in no time." With that lovely parting shot, which left Nesryn cold-eyed, the princess vanished.

They waited a good few moments to make sure they heard the outer door shut.

"Yrene Towers," was all Chaol said.

"What of it."

Gone was the faint amusement. Fine.

"The lack of feeling and movement begins at my hips."

Yrene's eyes shot right to them, dancing over him. "Are you capable of using your manhood?"

He tried not to flinch. Even Nesryn blinked at the frank question.

"Yes," he said tightly, fighting the heat rising in his cheeks.

She looked between them, assessing. "Have you used it to completion?"

He clenched his jaw. "How is that relevant?" And how had she gleaned what was between them?

Yrene only wrote something down.

"What are you writing?" he demanded, cursing the damned chair for keeping him from storming to rip the paper out of her hands.

"I'm writing a giant \emph{no}."

Which she then underlined.

He growled, "I suppose you'll ask about my bathroom habits now?"

"It was next on my list."

"They are unchanged," he bit out. "Unless you need Nesryn to confirm."

Yrene merely turned to Nesryn, unruffled. "Have you seen him struggle with it?"

"Do \emph{not} answer that," he snarled at Nesryn.

Nesryn had the good wits to sink into a chair and remain quiet.

Yrene rose, setting down the pen, and came around the desk. The morning sunlight caught in her hair, bouncing off her head in a corona.

She knelt at his feet. "Shall you remove your boots or shall I?"

"I'll do it."

She sat back on her heels and watched him move. Another test. To discern how mobile and agile he was. The weight of his legs, having to constantly adjust their position  Chaol gritted his teeth as he gripped his knee, lifting his foot off the wooden slat, and bent to remove his boot in a few sharp tugs. When he finished with the other one, he asked, "Pants, too?"

Chaol knew he should be kind, should beseech her to help him, and yet---

"After a drink or two, I think," Yrene only said. Then looked over her shoulder to a bemused Nesryn. "Sorry," she added---and sounded only slightly less sharp-tongued.

"Why are you apologizing to her?"

"I assume she has the misfortune of sharing your bed these days."

It took his self-restraint to keep from going for her shoulders and shaking her soundly. "Have I \emph{done} something to you?"

That seemed to give her pause. Yrene only yanked off his socks, throwing them atop where he'd discarded his boots. "No." A lie. He scented and tasted it.

But it focused her, and Chaol watched as Yrene picked up his foot in her slim hands. Watched, since he didn't feel it---beyond the shift in his abdominal muscles. He couldn't tell if she was squeezing or holding lightly, if her nails were digging in; not without looking. So he did.

A ring adorned her fourth finger---a wedding band. "Is your husband from here?" Or wife, he supposed.

"I'm not---" She blinked, frowning at the ring. She didn't finish the sentence.

Not married, then. The silver ring was simple, the garnet no more than a droplet. Likely worn to keep men from bothering her, as he'd seen many women do in the streets of Rifthold.

"Can you feel this?" Yrene asked. She was touching each toe.

"No."

She did it on the other foot. "And this?"

"No."

He'd been through such examinations before---at the castle, and with Rowan.

"His initial injury," Nesryn cut in, as if remembering the prince as well, "was to the entire spine. A friend had some knowledge of healing and patched him up as best he could. He regained movement in his upper body, but not below the hips."

"How was it attained---the injury?"

Her hands were moving over his foot and ankle, tapping and testing. As if she'd indeed done this before, as Princess Hasar had claimed.

Chaol didn't immediately reply, sorting through those moments of terror and pain and rage.

Nesryn opened her mouth, but he cut her off. "Fighting. I received a blow to my back while fighting. A magical one."

Yrene's fingers were inching up his legs, patting and squeezing. He felt none of it. Her brows bunched in concentration. "Your friend must have been a gifted healer if you regained so much motion."

"He did what he could. Then told me to come here."

Her hands pushed and pressed on his thighs, and he watched with no small amount of growing horror as she slid them higher and higher. He was about to demand if she planned to ascertain for herself about the life in his \emph{manhood}, but Yrene lifted her head and met his stare.

This close, her eyes were a golden flame. Not like the cold metal of Manon Blackbeak's, not laced with a century of violence and predator's instincts, but\ldots like a long-burning flame on a winter's night. "I need to see your back," was all Yrene said. Then she peeled away. "Lie down on the nearest bed."

Before Chaol could remind her that it wasn't quite so easy to do that, Nesryn was instantly in motion, wheeling him into his room. Kadja had already made his bed, and left a bouquet of orange lilies on the table beside it. Yrene sniffed at the scent---as if it was unpleasant. He refrained from asking.

He waved off Nesryn when she tried to help him onto the bed. It was low enough that he could manage.

Yrene lingered in the doorway, observing while he braced one hand on the mattress, one on the arm of the chair, and in a powerful push, heaved himself into a sitting position on the bed. He unbuckled each of those newly polished buttons on his jacket, then peeled it off. Along with the white shirt beneath.

"Facedown, I assume?"

Yrene gave him a curt nod.

Gripping his knees, abdomen clenching, he pulled his legs onto the mattress as he lay flat on his back.

For a few heartbeats, spasms shook his legs. Not real, controlled motion, he'd realized after the first time it had happened weeks ago. He could still feel that crushing weight in his chest after he'd understood it was some effect of the injury---that it usually happened if he moved himself about a great deal.

"Spasms in the legs are common with such an injury," Yrene supplied, observing them fade away into stillness once again. "These may calm with time." She waved a hand to him in silent reminder to turn over onto his belly.

Chaol said nothing as he sat up to fold one ankle over the other, lay down again on his back, and then twisted over, his legs following suit.

Whether she was impressed that he'd picked up on the maneuverings so quickly, she didn't let on. Didn't even lift a brow.

Folding his hands under his chin, he peered over his shoulder and watched her approach, watched her motion Nesryn to sit when the woman began pacing again.

He scanned Yrene for any sort of flickering magic. What it'd look like, he had not the faintest inkling. Dorian's had been ice and wind and flashing light; Aelin's had been raging, singing flame, but healing magic\ldots Was it something external, something tangible? Or something only his bones and blood might witness?

He'd once balked at those sorts of questions---might once have even balked at the idea of letting magic touch him. But the man who had done those things, feared those things\ldots He was glad to leave him in the shattered ruin of the glass castle.

Yrene stood over him for a moment, surveying his back.

Her hands were as warm as the morning sun when she laid them palm-down on the skin between his shoulder blades. "You were hit here," she observed quietly.

There was a mark. A faint, splattering paleness to his skin where the king's blow had hit. Dorian had shown him using a trick with two hand-mirrors before he'd left.

"Yes."

Her hands trailed along the groove of his spine. "It rippled down here, shredding and severing." The words were not for him---but as if she were speaking to herself, lost in some trance.

He fought against the memory of that pain, the numbness and oblivion it summoned.

"You can---tell that?" Nesryn asked.

"My gift tells me." Yrene's hand stalled along the middle of his back, pushing and prodding. "It was terrible power---what struck you." "Yes," was all he said.

Her hands went lower, lower, until they shoved down the waist of his pants a few inches. He hissed through his teeth and glared over his bare shoulder. "A little warning."

Yrene ignored him and touched the lowest part of his back. He did not feel it.

She spider-walked her fingers up his spine as if counting the vertebrae. "Here?"

"I can feel you."

She backtracked one step. "Here?"

"Nothing."

Her face bunched, as if making a mental note of the location. She began on the outer edges of his back, creeping up, asking where he stopped feeling it. She took his neck and head in her hands, turning it this way and that, testing and assessing.

Finally, she ordered him to move. Not to rise, but to turn over again.

Chaol stared up at the arched, painted ceiling as Yrene poked and prodded his pectorals, the muscles of his abdomen, those along his ribs. She reached the vee of muscles leading beneath his pants, kept moving lower, and he demanded, "Really?"

Yrene shot him an incredulous look. "Is there something you're particularly embarrassed for me to see?"

Oh, she certainly had some fight in her, this Yrene Towers from Fenharrow. Chaol held her stare, the challenge in it.

Yrene only snorted. "I had forgotten that men from the northern continent are so proper and guarded."

"And here they are not?"

"No. Bodies are celebrated, not shamed into hiding. Men and women both." That would explain the servant who had no qualms about such things.

"They seemed plenty dressed at dinner."

"Wait until the parties," Yrene countered coolly. But she lifted her hands from the already-low waist of his pants. "If you have not noticed any problems externally or internally with your manhood, then I don't need to look."

He shoved against the feeling that he was again thirteen years old and trying to talk to a pretty girl for the first time and ground out, "Fine."

Yrene withdrew a step and handed him his shirt. He sat up, arms and abdominal muscles straining, and slid it on.

"Well?" Nesryn asked, stalking close.

Yrene toyed with a heavy, loose curl. "I need to think. Talk to my superior." "I thought you were the best," Nesryn said carefully.

"I am one of many who are skilled," Yrene admitted. "But the Healer on High assigned me to this. I should like to speak to her first."

"Is it bad?" Nesryn demanded. He was grateful she did---he didn't have the nerve to.

Yrene only looked to him, her gaze frank and unafraid. "You know it is bad." "But can you help him?" Nesryn pushed, sharper this time.

"I have healed such injuries before. But this  it remains to be seen," Yrene said, meeting her gaze now.

"When---when will you know?"

"When I have had time to think."

To decide, Chaol realized. She wanted to \emph{decide} whether to help him.

He held Yrene's stare again, letting her see that he, at least, understood. He was glad Nesryn had not entertained the idea. He had a feeling Yrene would be face-first against the wall if she did.

But for Nesryn  the healers were beyond reproach. Holy as one of the gods here. Their ethic unquestionable.

"When will you return?" Nesryn asked.

\emph{Never}, he almost answered.

Yrene slid her hands into her pockets. "I'll send word," was all she said, and left.

Nesryn stared after her, then rubbed her face.

Chaol said nothing.

But Nesryn straightened, then dashed out---to the sitting room. Rustling paper, and then---

Nesryn halted in the doorway to his room, brows crossed, Yrene's paper in her hands.

She handed it to him. "What does this even mean?"

There were four names written on the paper, her handwriting messy.

\emph{Olgnia.}

\emph{Marte.}

\emph{Rosana.}

\emph{Josefin.}

It was the final name that had been written down several times.

The final name that had been underlined, over and over.

\emph{Josefin. Josefin. Josefin}.

"Perhaps they're other healers in the Torre who could help," he lied. "Perhaps she feared spies overhearing her suggest someone else."

Nesryn's mouth quirked to the side. "Let's see what she says---when she returns. At least we know Hasar can track her down if need be." Or Kashin, whose very name had set the healer on edge. Not that he'd force Yrene to work on him, but  it was useful information.

Chaol studied the paper again. The fervent underlining of that final name.

As if Yrene had needed to remind herself while here. In his presence. As if she needed whoever they were to know that she remembered them.

He had met another talented young healer from Fenharrow. His king had loved her enough to consider fleeing with her, to seek a better life for them. Chaol knew what had gone on in Fenharrow during their youth. Knew what Sorscha had endured there---and what she'd endured in Rifthold.

He'd ridden through Fenharrow's scarred grasslands over the years. Had seen the burned or abandoned stone cottages, their thatched roofs long since gone.

Owners either enslaved, dead, or fled elsewhere. Far, far away.

No, Chaol realized as he held that piece of paper, Yrene Towers would not be returning.

