
\chapter{50}

Sartaq sagged at Falkan's voice as it came from the \emph{kharankui}'s hideous mouth.

Nesryn hauled her hands free from the webbing, swallowing her grunt of pain as the fibers tore at her skin.
Falkan's mouth and tongue had to be aching---

She glanced at the spider hovering over Sartaq, slicing through the silk binding the prince with slashes of the claws.
Indeed, where those pincers waved, blood leaked out.

"Quickly," the shifter whispered.
"Your weapons are in the corner there."

She could just make out the faint gleam of starlight on the curve of her bow, along the naked silver of her Asterion short-sword.

Falkan cut through Sartaq's bindings, and the prince sprang free, shoving off the webbing.
He swayed as he stood, bracing a hand on the stone.
Blood, there was so much blood all over him---

But he rushed to her, ripping at the threads still covering her feet.
"Are you hurt?"

"Faster," Falkan said, glancing to the archway entrance behind.
"It won't take her long to realize no one's coming."

Nesryn's feet came free, and Sartaq hauled her up.
"Did you hear what she said about Maeve---"

"Oh, I heard," Sartaq breathed as they rushed to their weapons.
He handed her the bow and quiver, the Fae blade.
Grabbed his own Asterion daggers as he hissed to Falkan, "Which way?"

The shifter scuttled forward, past the carving of Maeve.
"Here---there is a slope upward.
We're just on the other side of the pass.
If we can get up high---"

"Have you seen Kadara?"

"No," the shifter said.
"But---"

They didn't wait to hear the rest as they crept on silent feet from the archway, entering the starlight-filled pass beyond.
Sure enough, a rough slope of loose stone rose from the ground, as if it were a path into the stars themselves.

They'd made it halfway up the treacherous slope, Falkan a dark shadow at their backs, when a shriek rose from the mountain beyond.
But the skies were empty, no sign of Kadara---

"Fire," Nesryn breathed as they hurtled toward the apex of the peak.
"She said all Valg hate fire.
\emph{They} hate fire."
For the spiders, devouring life, devouring souls\ldots They were as Valg as Erawan.
Hailed from the same dark hell.
"Get the flint from your pocket," she ordered the prince.

"And light \emph{what}?"
His eyes drifted to the arrows at her back as they halted atop the narrow apex of the peak---the curved horn.
"We're trapped up here."
He scanned the sky.
"It might not buy us anything."

Nesryn withdrew an arrow, shouldering her bow as she tugged a strip of her shirt from beneath the jacket of her flying leathers.
She ripped off the bottom, sliced the piece in two, and wrapped one around the shaft of the arrow.
"We need kindling," she said as Sartaq withdrew the flint stone from his breast pocket.

A knife flashed, and then a section of Sartaq's braid was in his outstretched hand.

She didn't hesitate.
Just wrapped the braid around the fabric, holding the arrow out for him as he struck the flint over and over.
Sparks flew, drifting---

One caught.
Fire flared.
Just as darkness spilled into the pass below.
Shoulder to shoulder, the spiders surged for them.
Two dozen at least.

Nesryn nocked the arrow, drawing back the string---and aimed up.

Not directly to them.
But a shot into the sky, high enough to pierce the frosty stars.

The spiders paused, watching the arrow reach its zenith and then plunge down, down---

"Another," Nesryn said, taking that second strip of fabric and wrapping it again around the head of her next arrow.
Only three remained in her quiver.
Sartaq sliced off a second piece of his braid, looping it over the tip.
Flint struck, sparks glowed, and as that first arrow plummeted toward the spiders scattering from its path, she loosed her second arrow.

The spiders were so distracted looking up they did not stare ahead.

The largest of them, the one who had spoken to her for so long, least of all.

And as Nesryn's burning arrow slammed into her abdomen, sticking deep, the spider's scream shook the very stones beneath them.

"Another," Nesryn breathed, fumbling for her next arrow as Sartaq ripped the fabric from his shirt.
"Hurry."

Nowhere to go, no way to keep them at bay.

"Shift," she told Falkan, who monitored the panicking spiders, who balked at their leader's screaming orders to put out the fire atop her abdomen.
"If you are going to shift into something, do it \emph{now}."

The shifter turned that hideous spider's face toward them.
Sartaq sliced off another piece of his braid and slid it over the head of her third arrow.
"I will hold them," Falkan said.

Sparks showered, flame kindled on that third flaming arrow.

"A favor, Captain," the shifter said to her.

Time.
They did not have \emph{time}---

"When I was seven, my older brother sired a bastard daughter off a poor woman in Rifthold.
Abandoned them both.
It has been twenty years since then, and from when I was old enough to go to the city, to begin my trade, I looked for her.
Found the mother after some years---on her deathbed.
She could barely talk long enough to say she'd kicked the girl out.
She did not know where my niece was.
Didn't care.
She died before she could give me a name."

Nesryn's hands shook as she aimed the arrow toward the spider trying to edge past her burning sister.
Sartaq warned, "Hurry."

Falkan said, "If she survived, if she is grown, she might have the shifter gift, too.
But it doesn't matter if she does or does not.
What matters\ldots She is my family.
All I have left.
And I have looked for her for a very long time."

Nesryn fired the third arrow.
A spider screamed as it found its mark.
The others fell back.

"Find her," Falkan said, taking a step toward the horrors churning below.
"My fortune---all of it is for her.
And I may have failed her in this life.
But not in my death."

Nesryn opened her mouth, not believing it, the words surging up---

But Falkan sprinted down the path.
Leaped right in front of that burning line of spiders.

Sartaq grabbed her elbow, pointing toward the steep slope downward from the tiny peak.
"This---"

One moment, she was standing upright.
The next, Sartaq had thrown her back, his sword whining.

She stumbled, arms flailing to keep her upright as she realized what had crept up the other side of the peak.
The spider now hissing at them, enormous fangs dripping venom to the stone.

It lunged for Sartaq with its front two legs.

He dodged one and swung down, striking true.

Black blood sprayed, the spider shrieking---but not before it slashed that claw deep into the prince's thigh.

Nesryn moved, her fourth arrow flying, right into one of those eyes.
The fifth and final arrow flew a moment later, shooting for the spider's open mouth as it screamed.

It bit down on the arrow, slicing it in half.

Nesryn dropped her bow and drew her Fae blade.

The spider hissed at it.

Nesryn stepped between Sartaq and the spider.
Down below, the \emph{kharankui} screamed and shrieked.
She did not dare to look to see what Falkan was doing.
If he still fought.

The blade was a sliver of moonlight between her and the spider.

The \emph{kharankui} advanced a step.
Nesryn yielded one, Sartaq struggling to rise beside her.

"\emph{I will make you beg for death}," the spider seethed, advancing again.

It recoiled, preparing to spring.
\emph{Make it count; make the swing count---} The spider leaped.

And went tumbling off the cliff as a dark ruk slammed into it, roaring her fury.

Not Kadara.
But Arcas.

Borte.

