
\chapter{51}

A whirlwind of fury, Arcas reared up, then dove again, Borte's battle cry ringing off the stones as she and her ruk aimed for the \emph{kharankui} in the pass below.
To the spider holding them off, blood---red blood---leaking from him.

Another cry split the night, one she'd learned as well as her own voice.

And there was Kadara, sailing hard for them, two other ruks in her wake.

Sartaq let out what might have been a sob as one of the other ruks broke away, diving to where Borte swept and lunged and shattered through the \emph{kharankui} ranks.

A ruk of darkest brown feathers\ldots and a young man atop it.

Yeran.

Nesryn did not recognize the other rider who sailed in behind Kadara.
Blood stained Kadara's golden feathers, but she flew steady, hovering overhead as the other ruk closed in.

"Hold still, and don't fear the drop," Sartaq breathed, brushing a hand over Nesryn's cheek.
In the moonlight, his face was caked in dirt and blood, his eyes full of pain, and yet---

Then there was a wall of wings, and mighty talons spread wide.

They wrapped around her waist and beneath her upper thighs, hauling her sitting upright into the air, Sartaq clutched in the other, and then the great bird shot into the night.

The wind roared, but the ruk lifted them higher.
Kadara fell into rank behind ---guarding their rear.
Through her whipping hair, Nesryn looked back toward the fire-limned pass.

To where Borte and Yeran now soared upward, a dark form clutched in the claws of Yeran's ruk.
Utterly limp.

Borte was not done.

A light sparked atop her ruk.
A flaming arrow.

Borte fired it high into the sky.

A signal, Nesryn realized as countless wings filled the air around them.
And as Borte's arrow landed atop a web, flame erupting, hundreds of lights kindled in the sky.

Ruk riders.
Each bearing a flaming arrow.
Each now pointing downward.

Like a rain of shooting stars, the arrows fell upon the darkness of Dagul.
Landed on web and tree.
And caught fire.
One after another after another.

Until the night was lit up, until smoke streamed, mingling with the rising screams from the peaks and wood.

The ruks veered northward, Nesryn shaking as she clung to the talons holding her.
Across the way, Sartaq met her gaze, his now-shoulder-length hair rippling in the wind.

With the flames below, it made the wounds to his face, his hands, his neck all the more gruesome.
His skin was wan, his lips pale, his eyes heavy with exhaustion and relief.
And yet 

Sartaq smiled, barely a curve of his mouth.
The words the prince had confessed drifted on the wind between them.

She could not take her eyes from him.
Could not look away.

So Nesryn smiled back.

And below and behind them, long into the night, the Dagul Fells burned.

