
\chapter{55}

The agony tore through him, unending and depthless.

He blacked out within a minute.
Leaving him to free-fall into this place.
This pit.

The bottom of the descent.

The hollow hell beneath the roots of a mountain.

Here, where all was locked and buried.
Here, where all had come to take root.

The empty foundation, mined and hacked apart, crumbled away into nothing but this pit.

Nothing.

Nothing.

Nothing.

Worthless and nothing.

He saw his father first.
His mother and brother and that cold mountain keep.
Saw the stairs crusted with the ice and snow, stained with blood.
Saw the man he'd gladly sold himself out to, thinking it would get Aelin to safety.
\emph{Celaena} to safety.

He'd sent the woman he'd loved to the safety of another assassination.
Had sent her to Wendlyn, thinking it better than Adarlan.
To \emph{kill}
its royal family.

His father emerged from the dark, the mirror of the man he might have become, might one day be.
Distaste and disappointment etched his father's features as he beheld him, the son that might have been.

His father's asking price\ldots he'd thought it a prison sentence.

But perhaps it had been a shot at freedom---at saving his useless, wayward son from the evil he likely suspected was about to be unleashed.

He had broken that promise to his father.

He hated him, and yet his father---that horrible, miserable bastard---had upheld his end of the bargain.

\emph{He}  he had not.

Oath-breaker.
Traitor.

\emph{Everything} he had done, Aelin had come to rip it apart.
Starting with his honor.

She, with her fluidity, that murky area in which she dwelled 
He'd broken his vows for her.
Broken everything he was for her.

He could see her, in the dark.

The gold hair, those turquoise eyes that had been the last clue, the final piece of the puzzle.

Liar.
Murderer.
Thief.

She basked in the sun atop a chaise longue on the balcony of that suite she'd occupied in the palace, a book in her lap.
Tilting her head to the side, she looked him over with that lazy half smile.
A cat being stirred from its repose.

He hated her.

He hated that face, the amusement and sharpness.
The temper and viciousness that could reduce someone to shreds without so much as a word--- only a look.
Only a beat of silence.

She \emph{enjoyed} such things.
Savored them.

And he had been so bewitched by it, this woman who had been a living flame.
He'd been willing to leave it all behind.
The honor.
The vows he'd made.

For this haughty, swaggering, self-righteous woman, he had shattered parts of himself.

And afterward, she had walked away, as if he were a broken toy.

Right into the arms of that Fae Prince, who emerged from the dark.
Who approached that lounge chair on the balcony and sat on its end.

Her half smile turned different.
Her eyes sparked.

The lethal, predatory interest honed in on the prince.
She seemed to glow brighter.
Become more aware.
More centered.
More\ldots alive.

Fire and ice.
An end and a beginning.

They did not touch each other.

They only sat on that chaise, some unspoken conversation passing between them.
As if they had finally found some reflection of themselves in the world.

He hated them.

He \emph{hated} them for that ease, that intensity, that sense of completion.

She had wrecked him, wrecked his life, and had then strolled right to this prince, as if she were going from one room to another.

And when it had all gone to hell, when he'd turned his back on everything he knew, when he had lied to the one who mattered most to keep her secrets, she had not been there to fight.
To help.

She had only returned, months later, and thrown it in his face.

His uselessness.
His nothingness.

\emph{You remind me of how the world ought to be.
What the world can be.}

Lies.
The words of a girl who had been grateful to him for offering her freedom, for pushing and pushing her until she was roaring at the world again.

A girl who had stopped existing the night they'd found that body on the bed.

When she had ripped his face open.

When she had tried to plunge that dagger into his heart.

The predator he'd seen in those eyes\ldots it had been unleashed.

There were no leashes that could ever keep her restrained.
And words like \emph{honor} and \emph{duty} and \emph{trust,} they were gone.

She had gutted that courtesan in the tunnels.
She'd let the man's body drop, closed her eyes, and had looked precisely as she had during those throes of passion.
And when she had opened her eyes again 
Killer.
Liar.
Thief.

She was still sitting on the chaise, the Fae Prince beside her, both of them watching that scene in the tunnel, as if they were spectators in a sport.

Watching Archer Finn slump to the stones, his blood leaking from him, face taut with shock and pain.
Watching Chaol stand there, unable to move or speak, as she breathed in the death before her, the vengeance.

As Celaena Sardothien ended, shattering completely.

He had still tried to protect her.
To get her out.
To atone.

\emph{You will always be my enemy}.

She had roared those words with ten years' worth of rage.

And she had meant it.
Meant it as any child who had lost and suffered at Adarlan's hand would mean it.

As Yrene meant it.

The garden appeared in another pocket of the darkness.
The garden and the cottage and the mother and laughing child.

Yrene.

The thing he had not seen coming.
The person he had not expected to find.

Here in the darkness\ldots here she was.

And yet he had still failed.
Hadn't done right by her, or by Nesryn.

He should have waited, should have respected them both enough to end one and begin with another, but he supposed he had failed in that, too.

Aelin and Rowan remained on that chaise in the sunshine.

He saw the Fae Prince gently, reverently, take Aelin's hand, turning it over.
Exposing her wrist to the sun.
Exposing the faint marks of shackles.

He saw Rowan rub a thumb over those scars.
Saw the fire in Aelin's eyes bank.

Over and over, Rowan brushed those scars with his thumb.
And Aelin's mask slid off.

There was fire in that face.
And rage.
And cunning.

But also sorrow.
Fear.
Despair.
Guilt.

Shame.

Pride and hope and love.
The weight of a burden she had run from, but now 

\emph{I love you.}

\emph{I'm sorry}.

She had tried to explain.
Had said it as clearly as she could.
Had given him the truth so he might piece it together when she had left and understand.
She meant those words.
\emph{I'm sorry}.

Sorry for the lies.
For what she had done to him, his life.
For swearing that she would pick him, choose him, no matter what.
\emph{Always}.

He wanted to hate her for that lie.
That false promise, which she had discarded in the misty forests of Wendlyn.

And yet.

There, with that prince, without the mask\ldots That was the bottom of her pit.

She had come to Rowan, soul limping.
She had come to him as she was, as she had never been with anyone.
And she had returned whole.

Still she had waited---waited to be with him.

Chaol had been lusting for Yrene, had taken her into his bed without so much as thinking of Nesryn, and yet Aelin 

She and Rowan looked to him now.
Still as an animal in the woods, both of them.
But their eyes full of understanding.
Knowing.

She had fallen in love with someone else, had wanted someone else---as badly as he wanted Yrene.

And yet it was Aelin, godless and irreverent, who had honored him.
More than he'd honored Nesryn.

Aelin's chin dipped as if to say \emph{yes}.

And Rowan\ldots The prince had let her return to Adarlan.
To make right by her kingdom, but to also decide for herself what she wanted.
Who she wanted.
And if Aelin had chosen Chaol instead\ldots He knew, deep down, Rowan would have backed off.
If it had made Aelin happy, Rowan would have walked away without ever telling her what he felt.

Shame pressed on him, sickening and oily.

He had called her a monster.
For her power, her actions, and yet  He did not blame her.

He understood.

That perhaps she had promised things, but\ldots she had changed.
The path had changed.

He understood.

He'd promised Nesryn---or had implied it.
And when he had changed, when the path had altered; when Yrene appeared down it\ldots He understood.

Aelin smiled softly at him as she and Rowan rippled into a sunbeam and vanished.

Leaving a red marble floor, blood pooling across it.

A head bumping vulgarly over smooth tile.

A prince screaming in agony, in rage and despair.

\emph{I love you}.

\emph{Go}.

That---if there had been a cleaving, it was that moment.

When he turned and ran.
And he left his friend, his brother, in that chamber.

When he ran from that fight, that death.

Dorian had forgiven him.
Did not hold it against him.

Yet he had still run.
Still left.

Everything he had planned, worked to save, all came crumbling down.

Dorian stood before him, hands in his pockets, a faint smile on his face.

He did not deserve to serve such a man.
Such a king.

The darkness pushed in further.
Revealing that bloody council room.
Revealing the prince and king he'd served.
Revealing what they had done.
To his men.

In that chamber beneath the castle.

How Dorian had smiled.
Smiled while Ress had screamed, while Brullo had spat in his face.

His fault---all of it.
Every moment of pain, those deaths 

It showed him Dorian's hands as they wielded those instruments beneath the castle.
As blood spurted and bone sundered.
Unfaltering, clean hands.
And that smile.

He knew.
He had known, had guessed.
Nothing would ever make it right.
For his men; for Dorian, left to live with it.

For Dorian, whom he'd abandoned in that castle.

That moment, over and over, the darkness showed him.

As Dorian held his ground.
As he revealed his magic, as good as a death sentence, and bought him time to run.

He had been so afraid---so afraid of magic, of loss, of \emph{everything}.
And that fear\ldots it had driven him to it anyway.
It had hurried him down this path.
He had clung so hard, had fought against it, and it had cost him everything.
Too late.
He'd been too late to see clearly.

And when the worst had happened; when he saw that collar; when he saw his men swinging from the gates, their broken bodies picked over by crows 

It had cracked him through to his foundation.
To this hollow pit beneath the mountain he'd been.

He had fallen apart.
Had let himself lose sight of it.

And he had found some glimmer of peace in Rifthold, even after the injury, and yet 

It was like applying a patch over a knife wound to the gut.

He had not healed.
Unmoored and raging, he had not \emph{wanted} to heal.

Not really.
His body, yes, but even that 

Some part of him had whispered it was deserved.

And the soul-wound\ldots He had been content to let it fester.

Failure and liar and oath-breaker.

The darkness swarmed, a wind stirring it.

He could stay here forever.
In the ageless dark.

\emph{Yes}, the darkness whispered.

He could remain, and rage and hate and curl into nothing but shadow.

But Dorian remained before him, still smiling faintly.
Waiting.

Waiting.

For---him.

He had made one promise.
He had not broken it yet.

To save them.

His friend, his kingdom.

He still had that.

Even here at the bottom of this dark hell, he still had that.

And the road that he had traveled so far\ldots No, he would not look back.

\emph{What if we go on, only to more pain and despair?}

Aelin had smiled at his question, posed on that rooftop in Rifthold.
As if she had understood, long before he did, that he would find this pit.
And learn the answer for himself.

\emph{Then it is not the end}.

This 

This was not the end.
This crack in him, this bottom, was not the end.

He had one promise left.

To that he would still hold.

\emph{It is not the end}.

He smiled at Dorian, whose sapphire eyes shone with joy---with love.

"I'm coming home," he whispered to his brother, his king.

Dorian only bowed his head and vanished into the darkness.

Leaving Yrene standing behind him.

She was glowing with white light, bright as a newborn star.

Yrene said quietly, "The darkness belongs to you.
To shape as you will.
To give it power or render it harmless."

"Was it ever the Valg's to begin with?"
His words echoed into nothing.

"Yes.
But it is yours to keep now.
This place, this final kernel of it."

It would remain in him, a scar and a reminder.
"Will it grow again?"

"Only if you let it.
Only if you do not fill it with better things.
Only if you do not forgive."
He knew she didn't just mean others.
"But if you are kind to yourself, if you---if you love yourself \ldots" Yrene's mouth trembled.
"If you love yourself as much as I love you \ldots"

Something began to pound in his chest.
A drumbeat that had gone silent down here.

Yrene held a hand toward him, her iridescence rippling into the darkness.

\emph{It is not the end}.

"Will it hurt?"
he asked hoarsely.
"The way back---the way out?"
The path back to life, to himself.

"Yes," Yrene whispered.
"But just this one last time.
The darkness does not want to lose you."

"I'm afraid I can't say the same."

Yrene's smile was brighter than the glow rippling off her body.
A star.
She was a fallen star.

She extended her hand again.
A silent promise---of what waited on the other side of the dark.

He still had much to do.
Oaths to keep.

And looking at her, at that smile 

Life.
He had \emph{life} to savor, to fight for.

And the breaking that had started and ended here\ldots Yes, it belonged to him.

He was \emph{allowed} to break, so that this forging might begin.

So that \emph{he} might begin again.

He owed it to his king, his country.

And he owed it to himself.

Yrene nodded as if to say yes.

So Chaol stood.

He surveyed the darkness, this piece of him.
He did not balk at it.

And smiling at Yrene, he took her hand.

