
\chapter{58}

Morning came and went, and Yrene was in no rush to rise from bed.
Neither was Chaol.
They ate a leisurely lunch in the sitting room, not bothering with proper clothes.

Hafiza would decide in her own time whether to give them those books.
So they'd just have to wait.
And then wait to encounter Aelin Galathynius again, or anyone else who might be able to decipher them.
Chaol said as much, after Yrene told him what Hafiza had confirmed.

"There must be considerable information inside those books," Chaol mused as he chewed on pomegranate seeds, the fruit like small rubies he popped into his mouth.

"If they date back as far as we think," Yrene said, "if many of those texts came from the necropolis or similar sites, it could be a trove.
About the Valg.

Our connection to them."

"Aelin lucked out in Rifthold, when she stumbled across those few books."

He'd told her last night---of the assassin named Celaena, who had turned out to be a queen named Aelin.
The entire history of it, laid bare.
A long one, and a sad one.
His voice had grown hoarse when he'd talked of Dorian.
Of the collar and the Valg prince.
Of those they had lost.
Of his own role, the sacrifices he'd made, the promises he'd broken.
All of it.

And if Yrene had not loved him already, she would have loved him then, learning that truth.
Seeing the man he was becoming, turning into, after all of it.
"The king somehow missed them during his initial research and purging."

"Or perhaps some god made sure he did," Yrene mused.
She lifted a brow.
"I don't suppose there are any Baast Cats at that library."

Chaol shook his head and set down the looted corpse of the pomegranate.
"Aelin has always had a god or two perched on her shoulder.
Nothing would surprise me at this point."

Yrene considered.
"Whatever did happen with the king?
If he had that Valg demon."

Chaol's face darkened as he leaned back on the not-nearly-as-comfortable replacement for the shredded gold sofa.
"Aelin healed him."

Yrene sat up straighter.
"How?"

"She burned it out of him.
Well, she and Dorian did."

"And the man---the true king---survived it?"

"No.
Initially, yes.
But neither Aelin nor Dorian wanted to talk much about what happened on that bridge.
He survived long enough to explain what had been done, but I think he was fading fast.
Then Aelin destroyed the castle.
And him with it."

"But fire rid the Valg demon within him?"

"Yes.
And I think it helped save Dorian, too.
Or at least bought him enough freedom to fight back on his own."
He angled his head.
"Why do you ask?"

"Because that theory I had \ldots" Yrene's knee bounced.
She scanned the room, the doors.
No one nearby.
"I think \ldots" She leaned closer, gripping his knee.
"I think the Valg are parasites.
Infections."

He opened his mouth, but Yrene plowed ahead.
"Hafiza and I pulled a tapeworm from Hasar when I first came here.
They feed off their host, much in the same way the Valg do.
Take over basic needs---like hunger.
And eventually kill their hosts, when all those resources have been used up."

Chaol went utterly still.
"But these are no mindless grubs."

"Yes, and that was what I wanted to see with you yesterday.
How much awareness that darkness had.
The extent of their power.
If it had left some sort of parasite in your bloodstream.
It didn't, but\ldots There was the other parasite--- feeding off you, giving it control."
He was silent.

Yrene cleared her throat, caressing her thumb over his wrist.
"I realized the night before.
That I had one of my own.
My hatred, my anger and fear and pain."
She brushed away a stray curl.
"They were all parasites, feeding on me these years.
Sustaining me, but also feeding on me."

And once she had understood that---that the place she most feared to tread was \emph{inside} herself, where she might have to acknowledge what, exactly, dwelled within \emph{her} 

"When I realized what \emph{I} was doing, I understood that's what the Valg truly is, deep down.
What your own shadows are.
\emph{Parasites.}
And enduring it these weeks was not the same as \emph{facing} it.
So I attacked it as I would any other parasite; swarmed around it.
Made it come to you---attack \emph{you} as hard as it could to get away from \emph{me}.
So that \emph{you} might face it, defeat it.
So you might go where you feared most to tread, and decide whether, at last, you were ready to fight back."

His eyes were clear, bright.
"That's a big realization."

"It certainly was."
She considered what he'd related---about Aelin and the demon inside the dead king.
"Fire is cleansing.
Purifying.
But amongst the healing arts, it's not often used.
Too unwieldy.
Water is better-tuned to the healing.
But then there are raw healing gifts.
Like mine."

"Light," Chaol said.
"It looked like swarming lights, against their darkness."

She nodded.
"Aelin managed to get Dorian and his father free.
Roughly, crudely, and one did not survive.
But what if a \emph{healer} with my sort of gifts was to treat someone possessed---\emph{infected} by the Valg?
The ring, the collar, they're implantation devices.
Like a bad bit of water, or tainted food.
Merely a carrier for something small, the kernel of those demons, who then grow within their hosts.
Removing it is the first step, but you said the demon can remain even afterward."

His chest began to heave in an uneven rhythm as he nodded.

Yrene whispered, "I think I can heal them.
I think the Valg\ldots I think they are parasites, and I can \emph{treat} the people they infect."

"Then everyone Erawan has captured, held with those rings and collars---"

"We could potentially free them."

He squeezed her hand.
"But you'd have to get close to them.
And their power, Yrene---"

"I would assume that is where Aelin and Dorian would come in.
To hold them down."

"There's no way to test this, though.
Without considerable risk."
His jaw tightened.
"It has to be why Erawan's agent is hunting you.
To erase the knowledge of that.
To keep you from realizing it by healing me.
And relaying it to other healers."

"If that is the case, though\ldots Why now?
Why wait this long?"

"Perhaps Erawan did not even consider it.
Until Aelin purged the Valg from Dorian and the king."
He rubbed at his chest.
"But there is a ring.
It belonged to Athril, friend to King Brannon and Maeve.
It granted Athril immunity from the Valg.
It was lost to history---the only one of its kind.
Aelin found it.
And Maeve wanted it badly enough that she traded Rowan for it.
Legend said Mala herself forged it for Athril, but\ldots Mala loved Brannon, not Athril."

Chaol shot up from the couch, and Yrene watched him pace.
"There was a tapestry.
In Aelin's old room.
A tapestry that showed a stag, and hid the entrance that led down to the tomb where the Wyrdkey had been hidden by Brannon.
It was Aelin's first clue that set her down this path."
"And?"
The word was a push of air.

"And there was an owl on it amongst the forest animals.
It was Athril's form.
Not Brannon's.
All of that was coded---the tapestry, the tomb.
Symbols upon symbols.
But the owl\ldots We never thought.
Never considered."

"Considered what?"

Chaol halted in the middle of the room.
"That the owl might not just be Athril's animal form, but his sigil because of his loyalty to someone else."

And despite the warm day, Yrene's blood chilled as she said, "Silba."

Chaol nodded slowly.
"Goddess of Healing."

Yrene whispered, "Mala did not make that ring of immunity."

"No.
She didn't."
Silba did.

"We need to go to Hafiza," Yrene said softly.
"Even if she won't let us take the books, we should ask her to look at them---see for ourselves what might have survived all this time.
What those Fae healers might have learned in that war."

He motioned her to rise.
"We'll go now."

But the suite doors opened, and Hasar breezed in, her gold-and-green dress flowing.

"Well," she said, smirking at their lack of clothes, their disheveled hair.
"At least you two are comfortable."

Yrene had the sense the world was about to be knocked from beneath her as the princess smiled at Chaol.
"We've had some news.
From your lands."
"What is it."
The words were ground out.

Hasar picked at her nails.
"Oh, just that Queen Maeve's armada managed to find the host Aelin Galathynius has been so sneakily patching together.
There was \emph{quite} the battle."

