
\chapter{59}

Chaol debated strangling the smirking princess.
But he managed to keep his hands at his sides, managed to keep his chin high despite the fact that he was only wearing his pants, and said, "What.
Happened."

A naval battle.
Aelin against \emph{Maeve}.
He waited for the dangling sword to drop.
If he had been too late---

Hasar looked up from her nails.
"It was a spectacle, apparently.
A Fae armada versus a cobbled-together human force---" "Hasar, please," Yrene murmured.

The princess sighed at the ceiling.
"Fine.
Maeve was trounced."
Chaol sank onto the sofa.

Aelin---thank the gods Aelin had managed to find a way---

"Though there were some interesting details."
Then the princess rattled off the facts.
The numbers.
A third of Maeve's armada, bearing Whitethorn flags, had turned on their own and joined Terrasen's fleet.
Dorian had fought---held the front lines with Rowan.
Then a pack of wyverns had soared in from nowhere--- to fight for Aelin.

Manon Blackbeak.
Chaol would be willing to bet his life that somehow, either through Aelin or Dorian, that witch had done them a favor, and possibly altered the course of this war.

"The magic, they say, was impressive," Hasar went on.
"Ice and wind and water."
Dorian and Rowan.
"Even rumor of a shape-shifter."
Lysandra.
"But no darkness.
Or whatever Maeve fights with.
And no flame."
Chaol braced his forearms on his knees.

"Though some reports claim they spotted flame and shadow on shore---far away.
Flickers of both.
There and gone.
And no one spotted Aelin or the Dark Queen in the fleet."

It would have been like Aelin, to shift the battle between her and Maeve to the shore.
To minimize casualties, so she could unleash her full power without hesitation.

"As I said," Hasar continued, fluffing the skirts of her dress, "They were victorious.
Aelin was spotted returning to her armada hours later.
They've set sail---north, apparently."

He muttered a prayer of thanks to Mala.
And a prayer of thanks to whatever god watched over Dorian, too.
"Any major casualties?"

"To their men, yes, but not to any of the interesting players," Hasar said, and Chaol hated her.
"But Maeve\ldots there and gone, not a whisper of her left."
She frowned at the windows.
"Maybe she'll sail here to lick her wounds."

Chaol prayed that wouldn't be the case.
Yet if Maeve's armada still sat in the Narrow Sea when they took the crossing\ldots "But the others sail north now---to where?"
\emph{Where can I find my king, my brother?}

"I'd assume Terrasen, now that Aelin has her armada.
Oh, and another one."
Hasar smiled at him.
Waiting for the question---the plea.

"What other armada," Chaol forced himself to ask.

Hasar shrugged, walking from the room.
"Turns out, Aelin called in a debt.

To the Silent Assassins of the Red Desert."
Chaol's eyes burned.

"And to Wendlyn."

His hands began shaking.

"How many ships," he breathed.

"All of them," Hasar said, hand on the door.
"All of Wendlyn's armada came, commanded by Crown Prince Galan himself."

Aelin\ldots Chaol's blood sparked, and he looked to Yrene.
Her eyes were wide, bright.
Bright with hope---burning, precious hope.

"Turns out," Hasar mused, as if it were a passing thought, "there are quite a few people who think highly of her.
And who believe in what she's selling."
"Which is what?"
Yrene whispered.

Hasar shrugged.
"I assume it's what she tried to sell to me, when she wrote me a message weeks ago, asking for my aid.
From one princess to another."

Chaol took a shuddering breath.
"What did Aelin promise you?"

Hasar smiled to herself.
"A better world."

