
\chapter{67}

Two weeks later, it was barely dawn when Yrene found herself on the deck of a fine, massive ship and watched the sun rise over Antica for the last time.

The ship was abuzz with activity, but she stood at the rail, and counted the minarets of the palace. Ran an eye over every shining quarter, the city stirring in the new light.

Autumn winds were already whipping the seas, the ship bobbing and lurching beneath her.

Home. They were to sail home today.

She hadn't made many good-byes, had not needed to. But Kashin had still found her, right as she'd ridden to the docks. Chaol had given the prince a nod before leading her mare onto the ship.

For a long moment, Kashin had stared at the ship---the others gathered in the harbor. Then he'd said quietly, "I wish I had never said a word to you on the steppes that night."

Yrene began to shake her head, unsure of what to even say.

"I have missed having you---as my friend," Kashin went on. "I do not have many of them."

"I know," she managed to get out. And then added, "I missed having you as my friend, too."

For she had. And what he was now willing to do for her, her people


She took Kashin's hand. Squeezed it. There was still pain in his eyes, limning

his handsome face, but  understanding. And a clear, undaunted gleam as he beheld the northern horizon.

The prince squeezed her hand in return. "Thank you again---for Duva." A small smile toward that northern sky. "We shall meet again, Yrene Towers. I am certain of it."

She smiled back at him, beyond words. But Kashin winked, pulling his hand from hers. "My \emph{sulde} still blows northward. Who knows what I may find on the road ahead? Especially now that Sartaq has the burden of being Heir, and I'm free to do as I please."

The city had been in an uproar about it. Celebrating, debating---it still raged on. What the other royal siblings thought, Yrene did not know, but  there was peace in Kashin's eyes. And in the eyes of the others, when Yrene had seen them. And part of her indeed wondered if Sartaq had struck some unspoken agreement that went beyond \emph{Never Duva}. To perhaps even \emph{Never Us}.

Yrene had smiled again at the prince---at her friend. "Thank you, for all your kindness."

Kashin had only bowed to her and strode off into the gray light.

And in the hour since then, Yrene had stood on the deck of this ship, silently watching the awakening city behind it, while the others readied things around and below.

For long minutes, she breathed in the sea and the spices and the sounds of Antica under the rising sun. Took them deep into her lungs, letting them settle. Let her eyes drink their fill of the cream-colored stones of the Torre Cesme rising above it all.

Even in the early morning, the tower was a beacon, a jutting lance of hope and calm.

She wondered if she would ever see it again. For what lay ahead of them


Yrene braced her hands on the rail as another gust of wind rocked the ship. A wind from inland, as if all thirty-six gods of Antica blew a collective breath to send them skittering home.

Across the Narrow Sea---and to war.

The ship began to move at last, the world a riot of action and color and sound, but Yrene remained at the rail. Watching the city grow smaller and smaller.

And even when the coast was little more than a shadow, Yrene could have sworn she still saw the Torre standing above it, glinting white in the sun, as if it were an arm upraised in farewell.

