
\chapter{68}

Chaol Westfall took none of his steps for granted. Even the ones that had sent him rushing to a bucket to hurl up the contents of his stomach for the first few days at sea.

But one of the advantages of traveling with a healer was that Yrene easily soothed his stomach. And after two weeks at sea, dodging fierce storms that the captain only called Ship-Wreckers  his stomach had finally forgiven him.

He found Yrene at the prow railing, gazing toward land. Or where the land would be, if they dared sail close enough. They were keeping far out as they skirted up the coast of their continent, and from his meeting with the captain moments before, they were somewhere near northern Eyllwe. Close to the Fenharrow border.

No sign of Aelin or her armada, but that was to be expected, considering how long they'd been delayed in Antica before leaving.

But Chaol pushed that from his mind as he slid his arms around Yrene's waist and pressed a kiss to the crook of her neck.

She didn't so much as freeze at the touch from behind. As if she'd learned the cadence of his steps. As if she took none of them for granted, either.

Yrene leaned back into him, her body loosening with a sigh as she laid her hands atop where his rested over her stomach.

It had taken a full day after Duva's healing before he'd been able to walk with the cane---albeit stiffly and unevenly. As it had been in those early days of recovery: his back strained to the point of aching, every step requiring his full attention. But he'd gritted his teeth, Yrene murmuring encouragement when he had to figure out various movements. A day after that, most of the limp had eased, though he'd kept the cane; and a day later, he'd walked with minimal discomfort.

But even now, after these two weeks at sea with little for Yrene to heal beyond queasy stomachs and sunburns, Chaol kept the cane in their stateroom, the chair stored belowdecks, for when they were next needed.

He peered over Yrene's shoulder, down to their interlaced fingers. To the twin rings now gracing both of their hands.

"Watching the horizon won't get us there any faster," he murmured onto her neck.

"Neither will teasing your wife about it."

Chaol smiled against her skin. "How else am I to amuse myself during the long hours than by teasing you, Lady Westfall?"

Yrene snorted, as she always did at the title. But Chaol had never heard anything finer---other than the vows they'd spoken in Silba's temple at the Torre two and a half weeks ago. The ceremony had been small, but Hasar had insisted on a feast afterward that put to shame all the others they'd had in the palace. The princess might have been many things, but she certainly knew how to throw a party.

And how to lead an armada.

Gods help him when Hasar and Aedion met.

"For someone who hates being called Lord Westfall," Yrene mused, "you certainly seem to enjoy using the title for me."

"You're suited to it," he said, kissing her neck again.

"Yes, so suited to it that Eretia won't stop mocking me with her curtsying and bowing."

"Eretia is someone whom I could have gladly left behind in Antica."

Yrene chuckled, but pinched his wrist, stepping out of his embrace. "You'll be glad for her when we get to land."

"I certainly hope so."

Yrene pinched him again, but Chaol caught her hand and pressed a kiss to her fingers.

Wife---his wife. He'd never seen the path ahead so clearly as he had that afternoon three weeks ago, when he'd spied her sitting in the garden and just  knew. He'd known what he wanted, and so he'd gone to her chair, knelt down before it, and simply asked.

\emph{Will you marry me, Yrene? Will you be my wife?}

She'd flung her arms around his neck, knocking them both right into the fountain. Where they had remained, to the annoyance of the fish, kissing until a servant had pointedly coughed on their way past.

And looking at her now, the sea air curling tendrils of her hair, bringing out those freckles on her nose and cheeks  Chaol smiled.

Yrene's answering smile was brighter than the sun on the sea around them.

He'd brought that damned gold couch with them, shredded cushions and all. It had earned him no shortage of comments from Hasar when it was hauled into the cargo hold, but he didn't care. If they survived this war, he'd build a house for Yrene around the damn thing. Along with a stable for Farasha, currently terrorizing the poor soldiers tasked with mucking out her stall aboard the ship.

A wedding gift from Hasar, along with Yrene's own Muniqi horse.

He'd almost told the princess that she could keep Hellas's Horse, but there was something to be said about the prospect of charging down Morath foot soldiers atop a horse named Butterfly.

Still leaning against him, Yrene wrapped a hand around the locket she never took off, save to bathe. He wondered if he could have it changed to reflect her new initials.

No longer Yrene Towers---but Yrene Westfall.

She smiled down at the locket, the silver near-blinding in the midday sun. "I suppose I don't need my little note any longer."

"Why?"

"Because I am not alone," she said, running her fingers over the metal. "And because I found my courage."

He kissed her cheek, but said nothing as she opened the locket and carefully removed the browned scrap. The wind tried to rip it from her fingers, but Yrene held tight, unfolding the slender fragment.

She scanned the text she'd read a thousand times. "I wonder if she'll return for this war. Whoever she was. She spoke of the empire like
\ldots" Yrene shook her head, more to herself, and folded it shut again. "Perhaps she will come home to fight, from wherever she sailed off to." She offered him the piece of paper and turned away to the sea ahead.

Chaol took the scrap from Yrene, the paper velvet-soft from its countless readings and foldings and how she'd held it in her pocket, clutched it, all these years.

He unfolded the note and read the words he already knew were within:

\emph{For wherever you need to go---and then some. The world needs more healers}.

The waves quieted. The ship itself seemed to pause.

Chaol glanced to Yrene, smiling serenely at the sea, then to the note.

To the handwriting he knew as well as his own.

Yrene went still at the tears he could not stop from sliding down his face.

"What's wrong?"

She would have been sixteen, nearly seventeen then. And if she had been in Innish 

It would have been on her way to the Red Desert, to train with the Silent Assassins. The bruises Yrene had described  The beating Arobynn Hamel had given her as punishment for freeing Rolfe's slaves and wrecking Skull's Bay.

"Chaol?"

\emph{For wherever you need to go---and then some. The world needs more healers}.

There, in her handwriting 

Chaol looked up at last, blinking away tears as he scanned his wife's face.

Every beautiful line, those golden eyes.

A gift.

A gift from a queen who had seen another woman in hell and thought to reach back a hand. With no thought of it ever being returned. A moment of kindness, a tug on a thread 

And even Aelin could not have known that in saving a barmaid from those mercenaries, in teaching her to defend herself, in giving her that gold and this note 

Even Aelin could not have known or dreamed or guessed how that moment of kindness would be answered.

Not just by a healer blessed by Silba herself, capable of wiping the Valg away.

But by the three hundred healers who had come with her.

The three hundred healers from the Torre, now spread across the one thousand ships of the khagan himself.

\emph{A favor}, Yrene had asked of the man in return for saving his most beloved daughter.

\emph{Anything}, the khagan had promised.

Yrene had knelt before the khagan. \emph{Save my people}.

That was all she asked. All she had begged.

\emph{Save my people.}

So the khagan had answered.

With one thousand ships from Hasar's armada, and his own. Filled with Kashin's foot soldiers and Darghan cavalry.

And above them, spanning the horizon far behind the flagship on which Chaol and Yrene now sailed  Above them flew one thousand rukhin led by Sartaq and Nesryn, from every aerie and hearth.

An army to challenge Morath, with more to come, still rallying in Antica under Kashin's command. Two weeks, Chaol had given the khagan and Kashin, but with the autumn storms, he had not wanted to risk waiting longer. So this initial host  Only half. Only half, and yet the scope of what sailed and flew behind him 

Chaol folded the note along its well-worn lines and carefully set it back within Yrene's locket.

"Keep it a while longer," he said softly. "I think there's someone who will want to see that."

Yrene's eyes filled with surprise and curiosity, but she asked nothing as Chaol again slid his arms around her and held her tightly.

Every step, all of it, had led here.

From that keep in the snow-blasted mountains where a man with a face as hard as the rock around them had thrown him into the cold; to that salt mine in Endovier, where an assassin with eyes like wildfire had smirked at him, unbroken despite a year in hell.

An assassin who had found his wife, or they had found each other, two godsblessed women wandering the shadowed ruins of the world. And who now held the fate of it between them.

Every step. Every curve into darkness. Every moment of despair and rage and pain.

It had led him to precisely where he needed to be.

Where he \emph{wanted} to be.

A moment of kindness. From a young woman who ended lives to a young woman who saved them.

That shriveled scrap of darkness within him shrank further. Shrank and fractured into nothing but dust that was swept away by the sea wind. Past the one thousand ships sailing proud and unyielding behind him. Past the healers scattered amongst the soldiers and horses, Hafiza leading them, who had all come when Yrene had also asked them to save her people. Past the ruks soaring through the clouds, scanning for any threats ahead.

Yrene was watching him warily. He kissed her once---twice.

He did not regret. He did not look back.

Not with Yrene in his arms, at his side. Not with the note she carried, that bit of proof  that bit of proof that he was exactly where he was meant to be. That he had always been headed there. \emph{Here.}

"Will I ever hear an explanation for this dramatic reaction," Yrene said at last, clicking her tongue, "or are you just going to kiss me for the rest of the day?"

Chaol rumbled a laugh. "It's a long story." He slung an arm around her waist and stared out toward the horizon with her. "And you might want to sit down first."

"Those are my favorite kinds," she said, winking.

Chaol laughed again, feeling the sound in every part of him, letting it ring clear and bright as a bell. A final, joyous pealing before the storm of war swept in.

"Come on," he said to Yrene, nodding to the soldiers working alongside Hasar's men to keep the ships sailing swiftly for the north---to battle and bloodshed. "I'll tell you over lunch."

Yrene rose onto her toes to kiss him before he led them toward their spacious stateroom. "This story of yours had better be worth it," she said with a wry grin.

Chaol smiled back at his wife, at the light he'd unknowingly walked toward his entire life, even when he had not been able to see it.

"It is," he said quietly to Yrene. "It is."

