
\chapter*{Fireheart}
\addcontentsline{toc}{chapter}{Fireheart}

They had entombed her in darkness and iron.

She slept, for they had forced her to---had wafted curling, sweet smoke through the cleverly hidden airholes in the slab of iron above.
Around.
Beneath.

A coffin built by an ancient queen to trap the sun inside.

Draped with iron, encased in it, she slept.
Dreamed.

Drifted through seas, through darkness, through fire.
A princess of nothing.

Nameless.

The princess sang to the darkness, to the flame.
And they sang back.

There was no beginning or end or middle.
Only the song, and the sea, and the iron sarcophagus that had become her bower.

Until they were gone.

Until blinding light flooded the slumbering, warm dark.
Until the wind swept in, crisp and scented with rain.

She could not feel it on her face.
Not with the death-mask still chained to it.

Her eyes cracked open.
The light burned away all shape and color after so long in the dim depths.

But a face appeared before her---above her.
Peering over the lid that had been hauled aside.

Dark, flowing hair.
Moon-pale skin.
Lips as red as blood.

The ancient queen's mouth parted in a smile.

Teeth as white as bone.

"You're awake.
Good."

Lovely and cold, it was a voice that could devour the stars.

From somewhere, from the blinding light, rough and scar-flecked hands reached into the coffin.
Grasped the chains binding her.
The queen's huntsman; the queen's blade.

He hauled the princess upright, her body a distant, aching thing.
She did not want to slide back into this body.
Struggled against it, clawing for the flame and the darkness that now ebbed away from her like a morning tide.

But the huntsman yanked her closer to that cruel, beautiful face watching with a spider's smile.

And he held her still as that ancient queen purred, "Let's begin."

