
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

Yet again, I'm faced with the daunting prospect of conveying my gratitude for the many wonderful people in my life who made this book a reality. But my endless love and thanks go out to:

My husband, Josh: You are my light, my rock, my best friend, my safe harbor ---basically, my \emph{everything}. Thank you for taking such good care of me, for loving me, for joining me on this incredible journey. Your laugh is my favorite sound in the entire world.

To Annie: You sat with me for the months it took to write and edit this book, so part of me feels like your name should be on the cover, too, but until they start giving canine companions writing credits, this will have to suffice. I love you, baby pup. Your curly tail, your bat-like ears, your general sass, and the unfailing pep in your step  All of it. Here's to writing many more books together---and many more cuddles.

To my agent, Tamar: Ten books in, and I'm still unable to convey how grateful I am for all that you do. Thank you, thank you, thank you for being in my corner, for working so damn hard, and for being an all-around badass.

To Laura Bernier: Your guidance, wisdom, and excitement for this book made working on it such a delight. Thank you \emph{so much} for all of your hard work and edits---and for helping me to transform this book.

To the global team at Bloomsbury, for being the best goddamn publishing team on the planet: Bethany Buck, Cindy Loh, Cristina Gilbert, Kathleen Farrar, Nigel Newton, Rebecca McNally, Sonia Palmisano, Emma Hopkin, Ian Lamb, Emma Bradshaw, Lizzy Mason, Courtney Griffin, Erica Barmash, Emily Ritter,

Grace Whooley, Eshani Agrawal, Alice Grigg, Elise Burns, Jenny Collins, Beth Eller, Kerry Johnson, Kelly de Groot, Ashley Poston, Lucy Mackay-Sim, Hali

Baumstein, Melissa Kavonic, Oona Patrick, Diane Aronson, Donna Mark, John Candell, Nicholas Church, Anna Bernard, Charlotte Davis, and the entire foreign rights team. Thank you, as always, for all that you do for me and my books. I'm honored to work with every single one of you.

To Jon Cassir, Kira Snyder, Anna Foerster, and the team at Mark Gordon:
You guys are the best. I'm so ecstatic these books are in your hands.

To Cassie Homer: Thank you x infinity for everything you do. You are absolutely fantastic. To David Arntzen: You've had our back since the very beginning. Thank you for all of your hard work and kindness. And a massive thank-you to the incomparable Maura Wogan and Victoria Cook, aka the best legal team around.

To Lynette Noni: I am so, so happy that we've gotten to know each other since that Supanova a few years ago! Thank you to the moon and back for all of your help with this book, for being a genius brainstorming partner, and for just being \emph{you}.

To Roshani Chokshi: To begin with: You're right up my wall. Thank you for the laughter, the solid advice, and for being an actual ray of sunshine. I'm honored to call you my friend.

To Steph Brown: You are my partner in fangirling. Thank you for all of your support---and for your friendship. It means more to me than I can possibly say. Can't wait for our next LotR marathon
(\#FellowshipoftheDrink).

To Jennifer Armentrout for being one of the most welcoming, warm, and generous people I've ever met, to Renée Ahdieh for the dinners that never fail to make me smile and laugh, to Alice Fanchiang for being a fellow fangirl and an all-around joy to know, and to Christina Hobbs and Lauren Billings for being two of my favorite people.

To Charlie Bowater: Where do I even start? Thank you for the spectacular map(s), thank you for the art that continues to blow my mind and inspire me, thank you for \emph{everything}. I can't even tell you what an honor it is to work with you, and how much your art means to me.

To Kati Gardner and Avery Olmstead: Thank you from the bottom of my heart for your thoughtful feedback and insight---I can't begin to tell you how invaluable it was, and how much it shaped this book. And beyond that, it was such a delight to get to know you both.

To Jack Weatherford, whose \emph{Genghis Khan and the Making of the Modern World} forever changed my view of history and provided such inspiration for the realm of the khaganate. And thank you to Paul Kahn, for his brilliant adaptation of the \emph{Secret History of the Mongols}, and to Caroline Humphrey, for her article, "Rituals of Death in Mongolia."

To my parents and my family: thank you for all the joy, love, and support you bring into my world. To the newest addition to my family, my niece: You have already made my life brighter by being in it. May you grow up to be one fierce lady.

A massive thank-you to my amazing friends: Jennifer Kelly, Alexa Santiago, Kelly Grabowski, Vilma Gonzalez, Rachel Domingo, Jessica Reigle, Laura Ashforth, Sasha Alsberg, and Diyana Wan. To Louisse Ang:
At this point, I feel like a broken record when it comes to thanking you for all that you do, but \emph{thank you so much} for being so supportive and marvelous.

And to \emph{you}, dear reader: thank you for making every bit of hard work worth it, and for being the loveliest group of people I've ever met. I adore you all.
