
\newpage
\vspace*{\fill}
\begin{Center} % Tower of Dawn blurb

    \hfill \break
    \textbf{A glorious empire. A desperate quest. An ancient secret.}

    \hfill \break
    The search for allies extends to a new land in the sixth book of the \#1 bestselling Throne of Glass series by Sarah J. Maas.          
    
    \hfill \break     
    Chaol Westfall and Nesryn Faliq have arrived in the shining city of Antica to forge an alliance with the Khagan of the Southern Continent, whose vast armies are Erilea's last hope. But they have also come to Antica for another purpose: to seek healing at the famed Torre Cesme for the wounds Chaol received in Rifthold.          
    
    \hfill \break     
    After enduring unspeakable horrors as a child at the hands of Adarlanian soldiers, Yrene Towers has no desire to help the young lord from Adarlan, let alone heal him. Yet she has sworn an oath to assist those in need, and she will honor it. But Lord Westfall carries his own dark past, and Yrene soon realizes that those shadows could engulf them both.          
    
    \hfill \break     
    Chaol, Nesryn, and Yrene will have to draw on every scrap of their resilience to overcome the danger that surrounds them. But while they become entangled in the political webs of the khaganate, long-awaited answers slumber deep in the mountains, where warriors soar on legendary ruks. Answers that might offer their world a chance at survival . . . or doom them all.          
    
    \hfill \break     
    The final battle looms in this sixth book in the \#1 bestselling Throne of Glass series.
\end{Center}
\vspace*{\fill}
